### 2017-11-28 manuscriptAnalysis/MS_Analysis.Rmd
add MS_Analysis.Rmd

---
title: "Growth model analysis"
output: html_notebook
---

Plots for the manuscript

```{r}
library(tidyverse)
d <- dddG[[1]]
#load(file = './data/out/ddD.RData')

```

```{r overview graphs - Fig 1}
d$riverOrderedGG <- factor(d$river,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
d$seasonGG <- factor(d$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
d$speciesGG <- factor(d$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Samlon"), ordered = T)

ggplot(d, aes(year,countPAllSpp)) +
  geom_point() +
  geom_line() +
  labs( x = "Year", y = "Estimated count") +
  theme_bw() +
  facet_grid(seasonGG ~ riverOrderedGG)

ggsave('figures/count.png')
```

```{r overview graphs - Fig 2}

pd <- position_dodge(0.75) 
d %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>% 
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T)) %>%
ggplot( aes(year,meanGR, color=speciesGG, shape=speciesGG) ) +
  geom_point( position=pd ) +
  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
  labs( x = "Year", y = "Estimated growth rate (mm/d)" ) +
  theme_bw() +
  facet_grid(seasonGG ~ riverOrderedGG)

ggsave('figures/gr.png')

```

```{r figs 3,4}
d %>% group_by(riverOrderedGG,seasonGG,year) %>% 
  summarize(meanF = mean(meanFlow, na.rm=T),
            sdF = sd(meanFlow, na.rm=T)) %>%
  ggplot( aes(year,meanF) ) +
  geom_point(  ) +
  geom_line() +
  geom_errorbar( aes(ymin = meanF - sdF, ymax = meanF + sdF, width = 0.33 ) ) +
  labs( x = "Year", y = "Stream flow (x/x)" ) +
  theme_bw() +
  facet_grid(seasonGG ~ riverOrderedGG)

ggsave('figures/flow.png')

d %>% group_by(riverOrderedGG,seasonGG,year) %>% 
  summarize(meanT = mean(meanTemperature, na.rm=T),
            sdT = sd(meanTemperature, na.rm=T)) %>%
  ggplot( aes(year,meanT) ) +
  geom_point(  ) +
  geom_line() +
  geom_errorbar( aes(ymin = meanT - sdT, ymax = meanT + sdT, width = 0.33 ) ) +
  labs( x = "Year", y = "Stream temperature (C)" ) +
  theme_bw() +
  facet_grid(seasonGG ~ riverOrderedGG)

ggsave('figures/temp.png')
```

### 2017-11-28 R_analysis/mainAnalysis.R

@@ -33,10 +33,10 @@ library(tidyverse)
 # selection criteria
 
 drainage <- "west" # ==
-species <- "bkt" #c("bkt", "bnt") #
+species <- c("bkt", "bnt") #
 minCohort <- 2002 # >=
 maxSampleInterval <- 200 # <
-runDetectionModelTF <- F
+runDetectionModelTF <- T
 
 reconnect()
 
@@ -89,7 +89,7 @@ ddddD <- cd %>%
 dddD <- ddddD %>% prepareDataForJags('detection')
 
 if (runDetectionModelTF) {
-  ddD <- dddD %>% runDetectionModel(parallel = TRUE)
+  ddD <- dddD[[1]] %>% runDetectionModel(parallel = TRUE)
   save(ddD,dddD,ddddD, file = paste0('./data/out/ddD_', dModelName,'.RData'))
 }
 done <- Sys.time()
@@ -211,12 +211,13 @@ jagsUI::traceplot(dG[[1]], parameters = "grInt[2,1,1,3]")
 jagsUI::traceplot(dG[[1]], parameters = "grIntSigma")
 
 whiskerplot(dG[[1]], parameters = "sigmaInt")
-whiskerplot(dG[[1]], parameters = "sigmaIntMu")
+whiskerplot(dG[[1]], parameters = "sigmaBetaMu")
+whiskerplot(dG[[1]], parameters = "sigmaBetaSigma")
 whiskerplot(dG[[1]], parameters = "sigmaBeta[4,,,,]")
 traceplot(dG[[1]], parameters = "sigmaIntSigma")
 
 whiskerplot(dG[[1]], parameters = "grBeta")
-whiskerplot(dG[[1]], parameters = "grBeta[15,,,,]")
+whiskerplot(dG[[1]], parameters = "grBeta[2,,,,]")
 whiskerplot(dG[[1]], parameters = "grBetaMu")
 whiskerplot(dG[[1]], parameters = "grBetaSigma")
 jagsUI::traceplot(dG[[1]], parameters = "grBeta")
@@ -302,7 +303,7 @@ p <- getPrediction( dG[[1]], limits, nPoints, itersForPred, c("len", "temp", "fl
 plotPred(p, "len", 1, "bkt")
 plotPred(p, "temp", 1, "bkt")
 plotPred(p, "flow", 1, "bkt")
-plotPred(p, "count", 1, "bkt")
[…]

### 2017-11-29 manuscriptAnalysis/MS_Analysis.Rmd
before leaving felek

@@
 
+```{r custom theme}
+theme_publication <- function(base_size=14, base_family="helvetica") {
+  library(grid)
+  library(ggthemes)
+  (theme_foundation(base_size=base_size, base_family=base_family)
+    + theme(plot.title = element_text(face = "bold",
+                                      size = rel(1.2), hjust = 0.5),
+            text = element_text(),
+            panel.background = element_rect(colour = NA),
+            plot.background = element_rect(colour = NA),
+            axis.title = element_text(face = "bold",size = rel(1)),
+            axis.title.y = element_text(angle=90,vjust =2),
+            axis.title.x = element_text(vjust = -0.2),
+            axis.text = element_text(),
+            axis.line = element_line(colour="black"),
+            axis.ticks = element_line(),
+            panel.grid.major = element_line(colour="#f0f0f0"),
+            panel.grid.minor = element_blank(),
+            legend.key = element_rect(colour = NA),
+            legend.position = "bottom",
+            legend.direction = "horizontal",
+            legend.key.size= unit(0.2, "cm"),
+            legend.margin = unit(0, "cm"),
+            legend.title = element_text(face="italic"),
+            plot.margin=unit(c(10,5,5,5),"mm"),
+            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
+            strip.text = element_text(face="bold"),
+            panel.border = element_rect(colour = "black")
+    ))
+
+}
+
+scale_fill_Publication <- function(...){
+  library(scales)
+  discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+
+}
+
+scale_colour_Publication <- function(...){
+  library(scales)
+  discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+
+}
+
+```
+
 ```{r overview graphs - Fig 1}
@@
 d$seasonGG <- factor(d$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
-d$speciesGG <- factor(d$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Samlon"), ordered = T)
+d$speciesGG <- factor(d$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
 
@@
   labs( x = "Year", y = "Estimated count") +
-  theme_bw() +
+  theme_publication() +
   facet_grid(seasonGG ~ riverOrderedGG)
@@
 
-```{r overview graphs - Fig 2}
+```{r figs 3,4}
+d %>% group_by(riverOrderedGG,seasonGG,year) %>%
+  filter( riverOrderedGG == "West Brook" ) %>%
+  summarize(meanF = mean(meanFlow, na.rm=T),
+            sdF = sd(meanFlow, na.rm=T)) %>%
+  ggplot( aes(year,meanF) ) +
+  geom_point( size = 3 ) +
+  geom_line() +
+ # geom_smooth(method = 'lm', se=F) +
+  geom_errorbar( aes(ymin = meanF - sdF, ymax = meanF + sdF, width = 0.33 ) ) +
+  labs( x = "Year", y = "Stream flow (x/x)" ) +
+  theme_publication() +
+  facet_wrap(~seasonGG)
 
-pd <- position_dodge(0.75) 
+ggsave('figures/flow.png')
+
+lmFunction <- function(df){ lm( meanT ~ year, data=df ) }
+
+tempMods <- d %>%
+  group_by(riverOrderedGG,seasonGG,year) %>%
+  summarize(meanT = mean(meanTemperature, na.rm=T),
+            sdT = sd(meanTemperature, na.rm=T)) %>%
+  group_by( riverOrderedGG, seasonGG ) %>%
+  nest() %>%
+  mutate( model = map(data,lmFunction) )
+
+tempModsTidy <- tempMods %>%
+  mutate(tidy = map(model,broom::tidy)) %>%
+  select(-data,-model) %>%
+  unnest() %>%
+  filter( term == 'year') %>%
+  mutate( sig = ifelse(p.value < 0.05,"*",""))
+
+d %>% group_by(riverOrderedGG,seasonGG,year) %>%
+  summarize(meanT = mean(meanTemperature, na.rm=T),
+            sdT = sd(meanTemperature, na.rm=T)) %>%
+  ggplot( aes(year,meanT) ) +
+  geom_smooth(method = 'lm', se=F, color = 'darkgrey') +
+  geom_point(  ) +
+  geom_line() +
+  geom_errorbar( aes(ymin = meanT - sdT, ymax = meanT + sdT, width = 0.33 ) ) +
+  labs( x = "Year", y = "Stream temperature (C)" ) +
+  geom_text(data=tempModsTidy,aes(x=1999,y=18, label=paste(round(estimate,2),sig))) +
+  theme_publication() +
+  facet_grid(seasonGG ~ riverOrderedGG)
+
+ggsave('figures/temp.png')
+```
+
+```{r questions}
+
+```
+
+```{r overview graphs - Fig Appendix}
+
+pd <- position_dodge(0.65)
+
+# isYOY1
 d %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>%
+  filter(isYOYDATA == 1) %>%
   summarize(meanGR = mean(grLength, na.rm=T),
@@
   geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
-  labs( x = "Year", y = "Estimated growth rate (mm/d)" ) +
-  theme_bw() +
+  ggtitle( "isYOY = 1" ) +
+  labs( x = "Year", y = "Growth rate (mm/d)" ) +
+  scale_x_continuous( breaks = 1997:2015 ) +
+  theme_publication() +
+  theme( panel.grid.minor = element_blank(),
+         axis.text.x  = element_text(angle=90, vjust=0.5, size=8) ) +
   facet_grid(seasonGG ~ riverOrderedGG)
 
-ggsave('figures/gr.png')
+ggsave('figures/grByYearYOY1.png')
+
+# isYOY2
+d %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>%
+  filter(isYOYDATA == 2) %>%
+  summarize(meanGR = mean(grLength, na.rm=T),
+            sdGR = sd(grLength, na.rm=T)) %>%
+  ggplot( aes(year,meanGR, color=speciesGG, shape=speciesGG) ) +
+  geom_point( position=pd ) +
+  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
+  ggtitle( "isYOY = 2" ) +
+  labs( x = "Year", y = "Growth rate (mm/d)" ) +
+  scale_x_continuous( breaks = 1997:2015 ) +
+  theme_publication() +
+  theme( panel.grid.minor = element_blank(),
+         axis.text.x  = element_text(angle=90, vjust=0.5, size=8) ) +
+  facet_grid(seasonGG ~ riverOrderedGG)
+
+ggsave('figures/grByYearYOY2.png')
 
 ```
-
-```{r figs 3,4}
-d %>% group_by(riverOrderedGG,seasonGG,year) %>% 
-  summarize(meanF = mean(meanFlow, na.rm=T),
-            sdF = sd(meanFlow, na.rm=T)) %>%
-  ggplot( aes(year,meanF) ) +
-  geom_point(  ) +
-  geom_line() +
-  geom_errorbar( aes(ymin = meanF - sdF, ymax = meanF + sdF, width = 0.33 ) ) +
-  labs( x = "Year", y = "Stream flow (x/x)" ) +
-  theme_bw() +
-  facet_grid(seasonGG ~ riverOrderedGG)
-
-ggsave('figures/flow.png')
-
-d %>% group_by(riverOrderedGG,seasonGG,year) %>% 
-  summarize(meanT = mean(meanTemperature, na.rm=T),
-            sdT = sd(meanTemperature, na.rm=T)) %>%
-  ggplot( aes(year,meanT) ) +
-  geom_point(  ) +
-  geom_line() +
-  geom_errorbar( aes(ymin = meanT - sdT, ymax = meanT + sdT, width = 0.33 ) ) +
-  labs( x = "Year", y = "Stream temperature (C)" ) +
-  theme_bw() +
-  facet_grid(seasonGG ~ riverOrderedGG)
-
-ggsave('figures/temp.png')
-```

### 2017-11-29 R/analyzeOutputFunctions.R

@@ -226,7 +226,7 @@ plotPred <- function(p, varsToPlot, isYOYGG, speciesGG) {
 
 #'Plot observed/predicted and return RMSE
 #'
-#'@param none
+#'@param empty Nothing passed to function
 #'@return Nothing, print text and plot graph
 #'@export
 #'

### 2017-11-29 R/getAndPrepareDataWB.R

@@ -420,34 +420,34 @@ getYOYCutoffs <- function(d,dr = 'west'){
 #'@return a data frame including meanBiomassAllSppStdDelta (changes in biomass with bioomass by sample standardized by all species) and meanBiomassStdDelta (changes in biomass with bioomass by sample standardized by each species)
 #'@export
 
-addBiomassDeltas <- function(d){
-
-  # first get biomass means and deltas by cohort and ageInSamples
-  meanBiomassCohort <- d %>%
-    group_by(species, cohort, ageInSamples,year,season) %>%
-    summarize( meanBiomassAllSppStd = mean(biomassAllSppStd, na.rm=T ),
-               sdBiomassAllSppStd = sd(biomassAllSppStd, na.rm=T ),
-               meanBiomassStd = mean(biomassStd, na.rm=T ),
-               sdBiomassStd = sd(biomassStd, na.rm=T ), n=n()) %>%
-    group_by(species,cohort) %>%
-    mutate( meanBiomassAllSppStdLag = lead(meanBiomassAllSppStd),
-            meanBiomassAllSppStdDelta = meanBiomassAllSppStd - meanBiomassAllSppStdLag,
-            meanBiomassStdLag = lead(meanBiomassStd),
-            meanBiomassStdDelta = meanBiomassStd - meanBiomassStdLag )
-
-  #ggplot( filter(meanBiomassCohort, species == "bkt", n>25), aes(ageInSamples,meanBiomassStdDelta, color = factor(cohort))) + geom_point() + geom_line()# + facet_wrap(~year)
-  #ggplot( filter(meanBiomassCohort, species == "bkt", n>20), aes(season,meanBiomassAllSppStdDelta, color = factor(cohort))) + geom_point() + geom_line() + facet_wrap(~year)
-
-  # get means across cohorts
-  biomassDeltaMeans <- meanBiomassCohort %>%
-    group_by(species, year,season) %>%
-    summarize( meanBiomassAllSppStdDelta = mean(meanBiomassAllSppStdDelta, na.rm=T),
-               meanBiomassStdDelta = mean(meanBiomassStdDelta, na.rm=T))
-
-  #ggplot( filter(biomassDeltaMeans), aes(season,meanBiomassAllSppStdDelta, color=species)) + geom_point() + geom_line() + facet_wrap(~year)
[…]

### 2017-11-29 R/growthModelFunctions.R

@@ -31,16 +31,16 @@ runGrowthModel <- function(d, parallel = FALSE){
   #    #          , 'grIndRE','grIndREMean','grIndRETau'
   #             )
 
-  params <- c('grInt', 'grBeta', 'grSigma','sigmaBeta', 'lengthExp', 'grIntMu', 'grIntSigma', 'grIndRE', 'grBetaMu', 'grBetaSigma', 'sigmaBetaMu', 'sigmaBetaSigma' )
+  params <- c('grInt', 'grBeta', 'grSigma','sigmaBeta', 'lengthExp', 'grIntMu', 'grIntSigma', 'grIndRE', 'sigmaInd', 'grBetaMu', 'grBetaSigma', 'sigmaBetaMu', 'sigmaBetaSigma' )
 
   outGR <- jags(data = d,
                 inits = inits,
                 parameters.to.save = params,
                 model.file = "./jags/grModel6.jags",
                 n.chains = 3,
-                n.adapt = 1000, #1000
-                n.iter = 1000,
-                n.burnin = 400,
+                n.adapt = 500, #1000
+                n.iter = 500,
+                n.burnin = 200,
                 n.thin = 5,
                 parallel = parallel
   )

### 2017-11-29 R/prepareDataForJags.R

@@ -7,7 +7,6 @@
 
 prepareDataForJags <- function(d,modelType){
 
-  nInd <- n_distinct(d$tagIndex, na.rm = T)
   nOcc <- n_distinct(d$sampleIndex, na.rm = T)
   minOcc <- min(d$sampleIndex)
   nRivers <- n_distinct(d$riverOrdered, na.rm = T)
@@ -108,10 +107,13 @@ prepareDataForJags <- function(d,modelType){
           )
 
   d$tagIndexJags <- as.numeric(as.factor(d$tagIndex)) #make sure have right tagIndices for subset of fish for Jags
+  nInd <- n_distinct(d$tagIndexJags, na.rm = T)
 
   d$rowNumber <- 1:nrow(d)
 
   d$isYOYDATA <- ifelse( d$ageInSamples <= 3, 1, 2 )
+
+  speciesByInd <- d %>% distinct(tagIndexJags,speciesN) %>% arrange(tagIndexJags)
 
   if ( modelType == "detection" ){
   data <- list( encDATA = d$enc,
@@ -193,7 +195,8 @@ prepareDataForJags <- function(d,modelType){
     #              biomassDelta = d$meanBiomassStdDelta,
            #       logitPhiStd = d$logitPhiStd,
   #                lForInit = d$lInterp,
-                  isYOYDATA = d$isYOYDATA
+                  isYOYDATA = d$isYOYDATA,
+                  speciesByInd = speciesByInd$speciesN
     )
   }
 

### 2017-11-29 R_analysis/mainAnalysis.R

@@ -17,9 +17,9 @@
 
 
 #install.packages("devtools")
+# library(devtools)
 #devtools::install_github('bletcher/linkedModels')
-#install.packages("devtools")
-#devtools::install_github('Conte-Ecology/getWBData')
+#devtools::install_github(repo = "Conte-Ecology/westBrookData", subdir = "getWBData")
 library(arm)
 library(zoo)
 library(arrayhelpers)
@@ -33,10 +33,12 @@ library(tidyverse)
 # selection criteria
 
 drainage <- "west" # ==
-species <- c("bkt", "bnt") #
-minCohort <- 2002 # >=
+species <- c("bkt", "bnt","ats") #
+minCohort <- 1995 # >=
 maxSampleInterval <- 200 # <
 runDetectionModelTF <- T
+runCrossValidationTF <- F
+percentLeftOut <- 10
 
 reconnect()
 
@@ -57,7 +59,7 @@ riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),l
 # Only need to run this when data or functions have changed
 # or you want to change drainages
 
-cdFile <- paste0('./data/cd_',drainage,'.RData')
+cdFile <- paste0('./data/cd_',drainage,"_",paste0(species,collapse =''),'.RData')
 
 if ( file.exists(cdFile) ) {
   load(cdFile)
@@ -77,7 +79,7 @@ if ( file.exists(cdFile) ) {
 ##################
 #
 #
-dModelName <- "nPasses"
+dModelName <- paste0(species,collapse = '')
 
 (start <- Sys.time())
 ddddD <- cd %>%
@@ -112,8 +114,6 @@ done <- Sys.time()
 #
 #
 
-# need to check grBeta estimates
-
 ddddG <- cd %>%
   filter(  species %in% speciesIn,
            cohort >= minCohort,
@@ -132,12 +132,9 @@ load(file = paste0('./data/out/ddD_', dModelName,'.RData'))
 ######################################
 ######################################
 
-meanOrIter = "mean"
+meanOrIter <- "mean"
 ####### or ########
 #meanOrIter = "iter"
-
-runCrossValidationTF <- F
-percentLeftOut <- 10
 
 chainToUse <- 1
 numItersToUse <- 2
@@ -169,7 +166,7 @@ for (iter in itersToUse) {
[…]

### 2017-12-01 manuscriptAnalysis/MS_Analysis.Rmd
started adding counts of untagged fish

@@
   labs( x = "Year", y = "Estimated count") +
+#  ylim(0,2500) +
   theme_publication() +
-  facet_grid(seasonGG ~ riverOrderedGG)
+  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
 

### 2017-12-01 R/growthModelFunctions.R

@@ -98,6 +98,13 @@ addDensityData <- function( ddddGIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
   # counts are missing for samples with propSampled == 0. For now, fill in mean (0). Need this for when enc==0 and propSampled==0 in the gr model
   ddddGIn$countPStd <- ifelse( is.na(ddddGIn$countPStd), 0, ddddGIn$countPStd )
 
+  #####
+  # counts by species in separate columns
+  countPStdBySpp <- denForMerge2 %>%
+    select(species, season, riverOrdered, year, countPStd) %>%
+    spread(species, countPStd, fill=0) %>%
+    rename(countPStdBKT = bkt,countPStdBNT = bnt, countPStdATS = ats)
+  ddddGIn <- left_join( ddddGIn,countPStdBySpp )
 
   # get mean masses by species
   massForMergeSummary <- ddddGIn %>%

### 2017-12-01 R/prepareDataForJags.R

@@ -189,6 +189,10 @@ prepareDataForJags <- function(d,modelType){
                   zForInit = d$zForInit, # z for firstObs gets set to zero in jags. Can't set values in inits for values assigned in jags
                   propSampledDATA = propSampled$propSampledDATA,
                   countPStd = d$countPStd,
+                  countPStdBKT = d$countPStdBKT,
+                  countPStdBNT = d$countPStdBNT,
+                  countPStdBKT = d$countPStdATS,
+                  countPAllSppStd = d$countPAllSppStd,
                   tempStd = d$tempStd,
                   flowStd = d$flowStd,
    #               biomassDeltaAllSpp = d$meanBiomassAllSppStdDelta,

### 2017-12-04 manuscriptAnalysis/MS_Analysis.Rmd
added propSampled back into det model

@@
 
+```{r p(detection)}
+  ggPInt <- array2df(ddD$sims.list$pBetaInt, label.x = "est")
+
+  ggPInt$chain <- rep(1:ddD$mcmc.info$n.chains, each = ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
+  ggPInt$iter <- 1:as.numeric(ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
+
+  ggplot(filter(ggPInt), aes(iter,est)) + 
+    geom_point( aes(color=factor(chain)), size = 0.1 ) + 
+    ylim(-1.5,1.5) + 
+    facet_grid(d2+d4~d5+d3)
+
+  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
+    rename(est=est,species=d1,season=d2,river=d3,year=d4)
+  ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
+
+```
+
 ```{r overview graphs - Fig 1}
@@
 ggsave('figures/count.png')
+
+ggplot(d, aes(year,countP.y,color=species)) +
+  geom_point() +
+  geom_line() +
+  labs( x = "Year", y = "Estimated count") +
+#  ylim(0,2500) +
+  theme_publication() +
+  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
 ```

### 2017-12-04 R/getAndPrepareDataWB.R

@@ -10,7 +10,7 @@ getCoreData <- function(drainage = "west"){
                          whichDrainage = drainage,
                          columnsToAdd=c("sampleNumber","river","riverMeter","survey",'observedLength','observedWeight')) %>%
     addTagProperties( columnsToAdd = c("cohort","species","dateEmigrated","sex","species")) %>%
-    dplyr::filter( !is.na(tag), area %in% c("trib","inside","below","above") ) %>%
+    dplyr::filter( !is.na(tag), area %in% c("trib","inside","below","above"), !is.na(sampleNumber) ) %>%
     createCmrData( maxAgeInSamples = 20, inside = F, censorDead = F, censorEmigrated = T) %>%
     addSampleProperties() %>%
     addEnvironmental() %>%
@@ -32,7 +32,7 @@ getCoreDataAllFish <- function(drainage = "west"){
                             columnsToAdd=c("sampleNumber","river","riverMeter","survey",'observedLength','observedWeight'),
                             includeUntagged = T) %>%
     addTagProperties( columnsToAdd = c("cohort","species","dateEmigrated","sex","species")) %>%
-    dplyr::filter( area %in% c("trib","inside","below","above") ) %>%
+    dplyr::filter( area %in% c("trib","inside","below","above"), !is.na(sampleNumber) ) %>%
     #  createCmrData( maxAgeInSamples = 20, inside = F, censorDead = F, censorEmigrated = T) %>%
     addSampleProperties() %>%
     addEnvironmental() %>%
@@ -234,11 +234,17 @@ getPropSampled <- function(nSeasons,nRivers,nYears,minYear){
 
   #check data
 
-  #  tmp <- dddD %>%
-  #           group_by(riverOrdered,year,season,section) %>%
-  #           summarize( s = sum(enc) ) %>%
-  #           filter( s == 0 )
-  #  table(tmp$riverOrdered,tmp$year,tmp$season)
+   # tmp <- dddD[[2]] %>%
+   #          group_by(riverOrdered,year,season,section) %>%
+   #          summarize( s = sum(enc) ) %>%
+   #          filter( s == 0 )
+   # table(tmp$riverOrdered,tmp$year,tmp$season)
+   #
+   #              1998 2000 2001 2002 2003 2004 2005 2006 2007 2008 2009 2010 2011 2012 2013 2014 2015
+   # west brook     0    1    0   50   22   49   52    0   53    1    0    0   12   53    6   33    0
[…]

### 2017-12-04 R/growthModelFunctions.R

@@ -11,15 +11,18 @@ runGrowthModel <- function(d, parallel = FALSE){
   #grBetaOutside = array( runif( 11 *2*d$nSpecies*d$nSeasons*d$nRivers,-2,2),c( 11 ,2,d$nSpecies,d$nSeasons,d$nRivers))
   #grBetaOutside[ ,1,,2, ] <- 0
 
+  nBetas <- 18
+  nBetasSigma <- 4
+
   inits <- function(){
     list(
       grInt = array(rnorm(2*d$nSpecies*d$nSeasons*d$nRivers,0.5,0.25),c(2,d$nSpecies,d$nSeasons,d$nRivers)),
       #grBeta[x,1:2,1,1:4,1:4]
-      grBeta = array(rnorm(2*2*d$nSpecies*d$nSeasons*d$nRivers,0,0.1),c(2,2,d$nSpecies,d$nSeasons,d$nRivers)),
+      grBeta = array(rnorm(nBetas*2*d$nSpecies*d$nSeasons*d$nRivers,0,0.1),c(nBetas,2,d$nSpecies,d$nSeasons,d$nRivers)),
       #grSigma[ yoy,spp,s,r ]
       grSigma = array(runif(2*d$nSpecies*d$nSeasons*d$nRivers,0,0.05),c(2,d$nSpecies,d$nSeasons,d$nRivers)),
       # sigmaBeta[ b,yoy,spp,s,r ]
-      sigmaBeta = array(rnorm(2*2*d$nSpecies*d$nSeasons*d$nRivers,0,0.05),c(2,2,d$nSpecies,d$nSeasons,d$nRivers)),
+      sigmaBeta = array(rnorm(nBetasSigma*2*d$nSpecies*d$nSeasons*d$nRivers,0,0.05),c(nBetasSigma,2,d$nSpecies,d$nSeasons,d$nRivers)),
       grIndRE = rnorm(d$nInd,0,0.1)
     )
   }

### 2017-12-04 R_analysis/mainAnalysis.R

@@ -90,7 +90,7 @@ if ( file.exists(cdFile) ) {
 ##################
 #
 #
-dModelName <- paste0(paste0(species,collapse = ''),minCohort)
+dModelName <- paste0(paste0(species,collapse = ''),minCohort,"_wPropSampled")
 
 (start <- Sys.time())
 

### 2017-12-06 manuscriptAnalysis/MS_Analysis.Rmd
start doing detMod runs by species

@@
 #load(file = './data/out/ddD.RData')
-
+load(file = './data/out/countsAndMasses.RData')
 ```
@@
 ```{r custom theme}
-theme_publication <- function(base_size=14, base_family="helvetica") {
+theme_publication <- function(base_size=14, base_family="") {
   library(grid)
@@
 
+```{r raw counts}
+allFishBySpecies$riverOrderedGG <- factor(allFishBySpecies$river,
+                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
+                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
+allFishBySpecies$seasonGG <- factor(allFishBySpecies$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+allFishBySpecies$speciesGG <- factor(allFishBySpecies$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+
+allFish$riverOrderedGG <- factor(allFish$river,
+                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
+                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
+allFish$seasonGG <- factor(allFish$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+
+ggplot(allFishBySpecies, aes(year,nAllFishBySpecies)) +
+  geom_point(aes(color = speciesGG)) +
+  geom_line(aes(color = speciesGG)) +
+  geom_line( data = allFish, aes(year,nAllFish) ) +
+  theme_publication() +
+  labs( x = "Year", y = "Count" ) +
+  facet_grid( seasonGG ~ riverOrderedGG)#, scales = "free_y" )
+
+ggsave('figures/rawCount.png')
+```
+
 ```{r p(detection)}
@@
   ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
+
+  phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
+    rename(est=est,species=d1,season=d2,river=d3,year=d4)
+  ggplot(phi, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
+
+  tmp <- dddD[[2]] %>%
+           group_by(riverOrdered,year,season,section) %>%
+           summarize( s = sum(enc) ) %>%
+           filter( s == 0 )
+  table(tmp$riverOrdered,tmp$year,tmp$season)
 

### 2017-12-06 R/detectionModelFunctions.R

@@ -20,9 +20,9 @@ runDetectionModel <- function(d, parallel = FALSE){   #iterToUse, firstNonBurnIt
                  parameters.to.save = params,
                  model.file = "./jags/detModel.jags",
                  n.chains = 3,
-                 n.adapt = 1000, #1000
-                 n.iter = 1000,
-                 n.burnin = 100,
+                 n.adapt = 150, #1000
+                 n.iter = 200,
+                 n.burnin = 50,
                  n.thin = 4,
                  parallel = parallel
   )

### 2017-12-06 R/getAndPrepareDataWB.R

@@ -44,7 +44,7 @@ getCountsAllFish <- function(drainage = "west", filteredAreas = c("inside","trib
 
     counts <- cdWBAll %>%
       filter( area %in% filteredAreas ) %>%
-      group_by( species,riverN,season,year ) %>%
+      group_by( species,river,season,year ) %>%
       summarize( nAllFishBySpecies = n(),
                  massAllFishBySpecies = sum(observedWeight,na.rm=T))
 
@@ -69,7 +69,7 @@ addCounts <- function(cd,drainage){
   cd <- cd %>% left_join(allFishBySpecies)
 
   allFish <- allFishBySpecies %>%
-    group_by(riverN,season,year) %>%
+    group_by(river,season,year) %>%
     summarize( nAllFish = sum(nAllFishBySpecies, na.rm=T),
                massAllFish = sum(massAllFishBySpecies, na.rm=T))
   cd <- cd %>% left_join(allFish)

### 2017-12-06 R/prepareDataForJags.R

@@ -117,6 +117,8 @@ prepareDataForJags <- function(d,modelType){
 
   speciesByInd <- d %>% distinct(tagIndexJags,speciesN) %>% arrange(tagIndexJags)
 
+  print(paste0("Number of input rows = ",nrow(d),", Number of encounters = ",sum(d$enc,na.rm=T)))
+
   if ( modelType == "detection" ){
     data <- list( encDATA = d$enc,
                   lengthDATA = d$lengthDATAStd,

### 2017-12-06 R_analysis/mainAnalysis.R

@@ -34,7 +34,7 @@ library(tidyverse)
 
 drainage <- "west" # ==
 
-species <- c("bkt", "bnt","ats") #
+species <- "bkt" #c("bkt", "bnt","ats") #
 speciesIn <- factor(species, levels = c('bkt','bnt','ats'), ordered = T)
 riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
 
@@ -61,7 +61,7 @@ reconnect()
 # Only need to run this when data or functions have changed
 # or you want to change drainages
 
-cdFile <- paste0('./data/cd_',drainage,"_",paste0(paste0(species,collapse = ''),minCohort),'.RData')
+cdFile <- paste0('./data/cd_',drainage,"_",paste0(paste0(species,collapse = ''),"_",minCohort),'.RData')
 
 if ( file.exists(cdFile) ) {
   load(cdFile)

### 2017-12-07 R/getAndPrepareDataWB.R
added removeUnsampledRows()

@@ -252,7 +252,7 @@ getPropSampled <- function(nSeasons,nRivers,nYears,minYear){
    #          summarize( s = sum(enc) ) %>%
    #          filter( s == 0 )
    # table(tmp$riverOrdered,tmp$year,tmp$season)
-   #
+   # Season 4
    #              1998 2000 2001 2002 2003 2004 2005 2006 2007 2008 2009 2010 2011 2012 2013 2014 2015
    # west brook     0    1    0   50   22   49   52    0   53    1    0    0   12   53    6   33    0
    # wb jimmy       0    0    0   14    0    0    0    0    0    0    2    0    0    0    0    0    0
@@ -276,15 +276,83 @@ getPropSampled <- function(nSeasons,nRivers,nYears,minYear){
   propSampledDATA[ c(3,4),c(1,4),2015 - minYear + 1 ] <- 0 #all fall and winter samples in 2015
 
   # zeroSectionsDATA - completely unsampled winter samples. not including samples before season 4,year 1 because we didn't want to rewrite the meanPhiS34 indexing [mostly noise ni these estimates anyway]
+
+  # tmp2 <- dddD[[2]] %>%
+  #          group_by(riverOrdered,year,season) %>%
+  #          summarize( s = sum(enc) ) %>%
+  #          filter( s == 0 )
+  # # show unsampled river/year/season combos
+  # table(tmp2$riverOrdered,tmp2$year,tmp2$season)
+  #
   zeroSectionsDATA <- array( 0, c(nSeasons,nRivers,nYears) ) #season, river year
 
-  zeroSectionsDATA[ 3:4,1:4,1 ] <- 1          #all winter samples in 2002
-  zeroSectionsDATA[ 3:4,1,4 ] <- 1            #WB winter sample in 2005
-  zeroSectionsDATA[ 3:4,1,6 ] <- 1            #WB winter sample in 2007
+  zeroSectionsDATA[ 4,2:4,2002 - minYear + 1 ] <- 1          #trib winter samples in 2002
+  zeroSectionsDATA[ 4,1,2005 - minYear + 1 ] <- 1            #WB winter sample in 2005
+  zeroSectionsDATA[ 4,1,2007 - minYear + 1 ] <- 1            #WB winter sample in 2007
+  zeroSectionsDATA[ 4,1,2012 - minYear + 1 ] <- 1            #WB winter sample in 2007
[…]

### 2017-12-07 R/prepareDataForJags.R

@@ -114,6 +114,7 @@ prepareDataForJags <- function(d,modelType){
   d$rowNumber <- 1:nrow(d)
 
   d$isYOYDATA <- ifelse( d$ageInSamples <= 3, 1, 2 )
+  d$proportionSampled <- ifelse( is.na(d$proportionSampled), 1, d$proportionSampled )
 
   speciesByInd <- d %>% distinct(tagIndexJags,speciesN) %>% arrange(tagIndexJags)
 

### 2017-12-07 R_analysis/mainAnalysis.R

@@ -34,7 +34,7 @@ library(tidyverse)
 
 drainage <- "west" # ==
 
-species <- "bkt" #c("bkt", "bnt","ats") #
+species <- c("bkt", "bnt","ats") #
 speciesIn <- factor(species, levels = c('bkt','bnt','ats'), ordered = T)
 riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
 
@@ -61,7 +61,7 @@ reconnect()
 # Only need to run this when data or functions have changed
 # or you want to change drainages
 
-cdFile <- paste0('./data/cd_',drainage,"_",paste0(paste0(species,collapse = ''),"_",minCohort),'.RData')
+cdFile <- paste0('./data/cd_',drainage,"_",minCohort,'.RData')
 
 if ( file.exists(cdFile) ) {
   load(cdFile)
@@ -78,14 +78,12 @@ if ( file.exists(cdFile) ) {
   save(cd, file = cdFile)
 }
 
-
-
 #################################
 # Detection model
 ##################
 #
 #
-dModelName <- paste0(paste0(species,collapse = ''),minCohort)
+dModelName <- paste0(paste0(species,collapse = ''),"_",minCohort)
 
 (start <- Sys.time())
 
@@ -95,7 +93,9 @@ ddddD <- cd %>%
            sampleInterval < maxSampleInterval  # this removes the later yearly samples. Want to stick with seasonal samples
   )
 
-dddD <- ddddD %>% prepareDataForJags('detection')
+dddD <- ddddD %>%
+  removeUnsampledRows(drainage,removeIncomplete = T) %>% # removes enc=0 rows for samples with no or very few() sections sampled
+  prepareDataForJags('detection')
 
 if (runDetectionModelTF) {
   ddD <- dddD[[1]] %>% runDetectionModel(parallel = TRUE)

### 2017-12-11 manuscriptAnalysis/MS_Analysis.Rmd
added removeUnsampledRows()
fixed summing over nAllFishBySpeciesP

@@
 d <- dddG[[1]]
-#load(file = './data/out/ddD.RData')
-load(file = './data/out/countsAndMasses.RData')
+load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
+load("D:/projects/linkedModels/data/out/countsAndMasses.RData")
 ```
@@
   ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
+  ggsave('figures/p.png')
 
@@
 
-  tmp <- dddD[[2]] %>%
-           group_by(riverOrdered,year,season,section) %>%
-           summarize( s = sum(enc) ) %>%
-           filter( s == 0 )
-  table(tmp$riverOrdered,tmp$year,tmp$season)
+  # tmp <- dddD[[2]] %>%
+  #          group_by(riverOrdered,year,season,section) %>%
+  #          summarize( s = sum(enc) ) %>%
+  #          filter( s == 0 )
+  # table(tmp$riverOrdered,tmp$year,tmp$season)
 
@@
 
-ggplot(d, aes(year,countPAllSpp)) +
+ggplot(d, aes(year,nAllFishP)) +
   geom_point() +
@@
 
-ggplot(d, aes(year,countP.y,color=species)) +
-  geom_point() +
-  geom_line() +
+ggplot(d, aes(year,nAllFishBySpeciesP)) +
+  geom_point(aes(color=species)) +
+  geom_line(aes(color=species)) +
+   geom_line(  aes(year,nAllFishP) ) +
   labs( x = "Year", y = "Estimated count") +

### 2017-12-11 R/detectionModelFunctions.R

@@ -20,9 +20,9 @@ runDetectionModel <- function(d, parallel = FALSE){   #iterToUse, firstNonBurnIt
                  parameters.to.save = params,
                  model.file = "./jags/detModel.jags",
                  n.chains = 3,
-                 n.adapt = 150, #1000
-                 n.iter = 200,
-                 n.burnin = 50,
+                 n.adapt = 500, #1000
+                 n.iter = 700,
+                 n.burnin = 200,
                  n.thin = 4,
                  parallel = parallel
   )
@@ -42,30 +42,34 @@ runDetectionModel <- function(d, parallel = FALSE){   #iterToUse, firstNonBurnIt
 #'@return a data frame
 #'@export
 
-getDensities <- function(dddd,dd, meanOrIter = "mean", sampleToUse = sampleToUse){
+getDensities <- function(ddddDIn,ddDIn, meanOrIter = "mean", sampleToUse = sampleToUse){
 
-  try( if (sampleToUse > dd$mcmc.info$n.samples) stop("requested iteration beyond max # of iterations") )
+  try( if (sampleToUse > ddDIn$mcmc.info$n.samples) stop("requested iteration beyond max # of iterations") )
 
-  counts <- dddd %>%
-    #   filter( enc == 1 ) %>%
-    filter( area %in% c("inside","trib") ) %>%
-    group_by( species,season,riverOrdered,year ) %>%
-    dplyr::summarise( count = n() ) %>%
-    mutate( speciesN = as.numeric(as.factor(species)),
-            seasonN = season,
-            riverN = as.numeric(riverOrdered),
-            yearN = year - min(year) + 1
-    ) %>%
-    ungroup()
+  # counts <- ddddDIn %>%
+  #   filter( enc == 1 ) %>%
+  #   filter( area %in% c("inside","trib") ) %>%
+  #   group_by( species,season,riverOrdered,year ) %>%
+  #   dplyr::summarise( count = n() ) %>%
+  #   mutate( speciesN = as.numeric(as.factor(species)),
+  #           seasonN = season,
+  #           riverN = as.numeric(riverOrdered),
+  #           yearN = year - min(year) + 1
+  #   ) %>%
+  #   ungroup()
 
-  if ( meanOrIter == 'mean') ddIn <- dd$q50$pBetaInt
[…]

### 2017-12-11 R/getAndPrepareDataWB.R

@@ -37,7 +37,7 @@ getCountsAllFish <- function(drainage = "west", filteredAreas = c("inside","trib
     # addEnvironmental() %>%
     # addKnownZ() %>%
     # fillSizeLocation(size = F) #assumes fish stay in same location until observed elsewhere
-    filter( species %in% c('bkt','bnt','ats'))
+    filter( species %in% c('bkt','bnt','ats'), observedLength > 60)
 
     cdWBAll$riverOrdered <- factor(cdWBAll$river,levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered=T)
     cdWBAll$riverN <- as.numeric(cdWBAll$riverOrdered)
@@ -58,21 +58,39 @@ getCountsAllFish <- function(drainage = "west", filteredAreas = c("inside","trib
     return(counts)
 }
 
-#'Add counts for all fish to cd
+#'Add variables with trialing N
 #'
 #'@param drainage Which drainage, "west" or "stanley"
+#'@return a data frame with added variables
+#'@export
+#'
+addxxxxN <- function(d){
+
+  d$seasonN <- d$season
+  d$yearN <- d$year - min(d$year) + 1
+  d$riverN <- as.numeric(d$riverOrdered)
+  d$speciesN <- as.numeric(factor(d$species, levels = c('bkt','bnt','ats'), ordered = T)) #as.numeric(as.factor(d$species))
+
+  return(d)
+}
+
+
+#'Add counts for all fish to cd
+#'
+#'@param drainage Which drainage, "west" or "stanley", filtered areas (default = c('inside','trib'))
 #'@return a data frame with vars nAllFishBySpecies, massAllFishBySpecies and nAllFish, massAllFish
 #'@export
 #'
-addCounts <- function(cd,drainage){
-  allFishBySpecies <- getCountsAllFish(drainage)
-  cd <- cd %>% left_join(allFishBySpecies)
+addRawCounts <- function(cd,drainage,filteredAreas){
+
+  allFishBySpecies <- getCountsAllFish(drainage,filteredAreas)
+  cd <- left_join(cd,allFishBySpecies)
 
   allFish <- allFishBySpecies %>%
     group_by(river,season,year) %>%
     summarize( nAllFish = sum(nAllFishBySpecies, na.rm=T),
[…]

### 2017-12-11 R/growthModelFunctions.R

@@ -59,7 +59,7 @@ runGrowthModel <- function(d, parallel = FALSE){
 #'@param ddddGIn detection data
 #'@param meanOrIterIn whether the growth model gets mean P from the detection model, or results from an iteration
 #'@param sampleToUse if detection results are from an iteration, which iteration
-#'@return a data frame with standardized counts, countPStd is standardized by species counts, countPAllSppStd is standardized by the sum of counts of all species in the analysis
+#'@return a data frame with standardized counts, nAllFishBySpeciesPStd is standardized by species counts, nAllFishBySpeciesPAllSppStd is standardized by the sum of counts of all species in the analysis
 #'@export
 #'
 
@@ -67,8 +67,8 @@ adjustCounts <- function( ddddGIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
 
   if ( meanOrIterIn == "mean") {
     den <- getDensities(ddddDIn, ddDIn, meanOrIterIn, sampleToUse )
-    #ggplot(filter(den,!is.na(countP)),aes(year,countP, color = species)) + geom_point() + geom_line() + facet_grid(riverOrdered~season)
-    #ggplot(filter(den,!is.na(countP)),aes(count,countP, color = species)) + geom_point()
+    #ggplot(filter(den,!is.na(nAllFishBySpeciesP)),aes(yearN,nAllFishBySpeciesP, color = factor(speciesN))) + geom_point() + geom_line() + facet_grid(riverN~seasonN)
+    #ggplot(filter(den,!is.na(nAllFishBySpeciesP)),aes(count,nAllFishBySpeciesP, color = species)) + geom_point()
     den$meanOrIter <- meanOrIterIn
     den$iterIn <- meanOrIterIn
     print("in mean")
@@ -84,190 +84,53 @@ adjustCounts <- function( ddddGIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
   }
 
   denForMerge <- den %>%
-    dplyr::select(species, season, riverOrdered, year, countP, meanOrIter, iterIn) %>%
-    filter( !is.na(countP) )
+    dplyr::select(species, season, riverOrdered, year, nAllFishBySpeciesP, nAllFishP, massAllFishBySpecies, massAllFish, meanOrIter, iterIn) %>%
+    filter( !is.na(nAllFishBySpeciesP) )
 
   # counts by species
[…]

### 2017-12-11 R_analysis/mainAnalysis.R

@@ -73,7 +73,7 @@ if ( file.exists(cdFile) ) {
     mergeSites(drainage) %>%
     mutate(drainage = drainage,
            countP = NA) %>% # placeholder so prepareDataForJags() works for detection model
-    addCounts(drainage) # counts and summed masses of all fish, tagged and untagged. Not adjusted for P (happens in addDensities())
+    addRawCounts(drainage, filteredAreas = c("inside","trib")) # counts and summed masses of all fish, tagged and untagged. Not adjusted for P (happens in addDensities())
 
   save(cd, file = cdFile)
 }
@@ -94,7 +94,7 @@ ddddD <- cd %>%
   )
 
 dddD <- ddddD %>%
-  removeUnsampledRows(drainage,removeIncomplete = T) %>% # removes enc=0 rows for samples with no or very few() sections sampled
+  removeUnsampledRows(drainage, removeIncomplete = T) %>% # removes enc=0 rows for samples with no or very few() sections sampled (p=0 otherwise for those samples)
   prepareDataForJags('detection')
 
 if (runDetectionModelTF) {
@@ -172,7 +172,7 @@ for (iter in itersToUse) {
 
   # saving into a list for now, could also map()
 
-  dddG[[ii]] <- addDensityData( ddddG,ddD,ddddD,meanOrIter,iter )
+  dddG[[ii]] <- adjustCounts( ddddG,ddD,ddddD,meanOrIter,iter )
   # dddG[[ii]] <- addBiomassDeltas( dddG[[ii]] )
   dddG[[ii]] <- addSurvivals( dddG[[ii]],ddD,meanOrIter,iter )
   #dddG[[ii]] <- crossValidate( dddG[[ii]],runCrossValidationTF ) # Moved inside prepareDataforJags()

### 2017-12-13 manuscriptAnalysis/MS_Analysis.Rmd
Trying to fix lack of convergence in gr model

@@
 ```{r p(detection)}
-  ggPInt <- array2df(ddD$sims.list$pBetaInt, label.x = "est")
-
-  ggPInt$chain <- rep(1:ddD$mcmc.info$n.chains, each = ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
-  ggPInt$iter <- 1:as.numeric(ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
-
-  ggplot(filter(ggPInt), aes(iter,est)) + 
-    geom_point( aes(color=factor(chain)), size = 0.1 ) + 
-    ylim(-1.5,1.5) + 
-    facet_grid(d2+d4~d5+d3)
+  # ggPInt <- array2df(ddD$sims.list$pBetaInt, label.x = "est")
+  # 
+  # ggPInt$chain <- rep(1:ddD$mcmc.info$n.chains, each = ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
+  # ggPInt$iter <- 1:as.numeric(ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
+  # 
+  # ggplot(filter(ggPInt), aes(iter,est)) + 
+  #   geom_point( aes(color=factor(chain)), size = 0.1 ) + 
+  #   ylim(-1.5,1.5) + 
+  #   facet_grid(d2+d4~d5+d3)
 
@@
   ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
+
    ggsave('figures/p.png')
@@
 
-  # tmp <- dddD[[2]] %>%
-  #          group_by(riverOrdered,year,season,section) %>%
-  #          summarize( s = sum(enc) ) %>%
-  #          filter( s == 0 )
-  # table(tmp$riverOrdered,tmp$year,tmp$season)
+# # of skunked sections    
+  tmp <- dddD[[2]] %>%
+           group_by(riverOrdered,year,season,section) %>%
+           summarize( s = sum(enc) ) %>%
+           filter( s == 0 )
+  table(tmp$riverOrdered,tmp$year,tmp$season)
 
@@
 
-ggplot(d, aes(year,nAllFishP)) +
-  geom_point() +
-  geom_line() +
+ggplot(d, aes(year,nAllFishBySpeciesP)) +
+  geom_point(aes(color=speciesGG)) +
+  geom_line(aes(color=speciesGG)) +
   labs( x = "Year", y = "Estimated count") +

### 2017-12-13 R/detectionModelFunctions.R

@@ -20,9 +20,9 @@ runDetectionModel <- function(d, parallel = FALSE){   #iterToUse, firstNonBurnIt
                  parameters.to.save = params,
                  model.file = "./jags/detModel.jags",
                  n.chains = 3,
-                 n.adapt = 500, #1000
-                 n.iter = 700,
-                 n.burnin = 200,
+                 n.adapt = 200, #1000
+                 n.iter = 200,
+                 n.burnin = 100,
                  n.thin = 4,
                  parallel = parallel
   )
@@ -86,9 +86,10 @@ getDensities <- function(ddddDIn,ddDIn, meanOrIter = "mean", sampleToUse = sampl
   p <- left_join( p, counts, by = c('speciesN','seasonN','riverN','yearN') ) %>%
          mutate( nAllFishBySpeciesP = nAllFishBySpecies/p )
 
-  # get counts of all speices by summing nAllFishBySpeciesP across species
+  # get counts of all species by summing nAllFishBySpeciesP across species
   p2 <- p %>%
-    group_by(speciesN,seasonN,riverN,yearN) %>%
+ #   group_by(speciesN,seasonN,riverN,yearN) %>%
+    group_by(seasonN,riverN,yearN) %>%
     summarize( nAllFishP = sum(nAllFishBySpeciesP, na.rm=T))
 
   p <- left_join(p,p2)

### 2017-12-13 R/getAndPrepareDataWB.R

@@ -325,15 +325,6 @@ getPropSampled <- function(nSeasons,nRivers,nYears,minYear){
 #'@return a data frame
 #'@export
 
-# zeroSectionsDATA - completely unsampled winter samples. not including samples before season 4,year 1 because we didn't want to rewrite the meanPhiS34 indexing [mostly noise ni these estimates anyway]
-
-# tmp2 <- dddD[[2]] %>%
-#          group_by(riverOrdered,year,season) %>%
-#          summarize( s = sum(enc) ) %>%
-#          filter( s == 0 )
-# # show unsampled river/year/season combos
-# table(tmp2$riverOrdered,tmp2$year,tmp2$season)
-#
 removeUnsampledRows <- function(d,drainage,removeIncomplete = F){
 
   nSeasons <- n_distinct(d$season, na.rm = T)
@@ -373,6 +364,15 @@ removeUnsampledRows <- function(d,drainage,removeIncomplete = F){
     filter( unsampled01 == 0 )
 
   return(d)
+  # zeroSectionsDATA - completely unsampled winter samples. not including samples before season 4,year 1 because we didn't want to rewrite the meanPhiS34 indexing [mostly noise ni these estimates anyway]
+
+  # tmp2 <- dddD[[2]] %>%
+  #          group_by(riverOrdered,year,season) %>%
+  #          summarize( s = sum(enc) ) %>%
+  #          filter( s == 0 )
+  # # show unsampled river/year/season combos
+  # table(tmp2$riverOrdered,tmp2$year,tmp2$season)
+  #
 }
 
 #'Get cutoFFYoy data

### 2017-12-13 R/growthModelFunctions.R

@@ -41,8 +41,8 @@ runGrowthModel <- function(d, parallel = FALSE){
                 parameters.to.save = params,
                 model.file = "./jags/grModel6.jags",
                 n.chains = 3,
-                n.adapt = 250, #1000
-                n.iter = 250,
+                n.adapt = 100, #1000
+                n.iter = 200,
                 n.burnin = 100,
                 n.thin = 5,
                 parallel = parallel
@@ -91,30 +91,31 @@ adjustCounts <- function( ddddGIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
   denForMergeSummaryBySpecies <- denForMerge %>%
     group_by( species,season,riverOrdered ) %>%
     summarize( nAllFishBySpeciesPMean = mean( nAllFishBySpeciesP, na.rm = T ),
-               nAllFishBySpeciesPSD = sd( nAllFishBySpeciesP, na.rm = T),
+               nAllFishBySpeciesPSD =     sd( nAllFishBySpeciesP, na.rm = T),
                massAllFishBySpeciesMean = mean( massAllFishBySpecies, na.rm = T ),
-               massAllFishBySpeciesSD = sd( massAllFishBySpecies, na.rm = T))
+               massAllFishBySpeciesSD =     sd( massAllFishBySpecies, na.rm = T))
 
   # counts for all species
   denForMergeSummary <- denForMerge %>%
     group_by( season,riverOrdered ) %>%
     summarize( nAllFishPMean = mean( nAllFishP, na.rm = T ),
-               nAllFishPSD = sd( nAllFishP, na.rm = T),
+               nAllFishPSD =     sd( nAllFishP, na.rm = T),
                massAllFishMean = mean( massAllFish, na.rm = T ),
-               massAllFishSD = sd( massAllFish, na.rm = T) )
+               massAllFishSD =     sd( massAllFish, na.rm = T) )
 
 
   denForMerge2 <- left_join( denForMerge, denForMergeSummaryBySpecies ) %>%
                   left_join( denForMergeSummary ) %>%
                   mutate( nAllFishBySpeciesPStd = ( nAllFishBySpeciesP - nAllFishBySpeciesPMean )/nAllFishBySpeciesPSD,
-                          nAllFishPStd = ( nAllFishP - nAllFishPMean )/nAllFishPSD,
[…]

### 2017-12-13 R/prepareDataForJags.R

@@ -193,11 +193,11 @@ prepareDataForJags <- function(d,modelType){
                   sampleInterval = d$sampleInterval,
                   zForInit = d$zForInit, # z for firstObs gets set to zero in jags. Can't set values in inits for values assigned in jags
                   propSampledDATA = d$proportionSampled, # propSampled$propSampledDATA,
-                  countPStd = d$countPStd,
-                  countPStdBKT = d$countPStdBKT,
-                  countPStdBNT = d$countPStdBNT,
-                  countPStdATS = d$countPStdATS,
-                  countPAllSppStd = d$countPAllSppStd,
+                  countPBySpeciesStd = d$nAllFishBySpeciesPStd,
+                  countPStdBKT = d$nAllFishBySpeciesPStdBKT,
+                  countPStdBNT = d$nAllFishBySpeciesPStdBNT,
+                  countPStdATS = d$nAllFishBySpeciesPStdATS,
+                  countPAllSppStd = d$nAllFishPStd,
                   tempStd = d$tempStd,
                   flowStd = d$flowStd,
                   #               biomassDeltaAllSpp = d$meanBiomassAllSppStdDelta,

### 2017-12-13 R_analysis/mainAnalysis.R

@@ -177,6 +177,8 @@ for (iter in itersToUse) {
   dddG[[ii]] <- addSurvivals( dddG[[ii]],ddD,meanOrIter,iter )
   #dddG[[ii]] <- crossValidate( dddG[[ii]],runCrossValidationTF ) # Moved inside prepareDataforJags()
 
+  dddG[[ii]] <- dddG[[ii]] %>% filter(tag != '1c2d6c51d3') # salmon with many missing obs before last one - trouble estimating
+
   ddG[[ii]] <- dddG[[ii]] %>% prepareDataForJags("growth") # returns a list, list for running model in [[1]], input df in [[2]]
 
   #####
@@ -202,6 +204,8 @@ for (iter in itersToUse) {
 
   save(dG,ddG,dddG, file = paste0('./data/out/dG_', as.integer(Sys.time()),'_', modelName, '.RData'))
 }
+
+ggplot(ddG[[1]][[2]], aes(nAllFishBySpeciesPStd,grLength)) + geom_point() + facet_grid(species+river~season)
 
 whiskerplot(dG[[1]], parameters = "lengthExp[1:20]")
 traceplot(dG[[1]], parameters = "lengthExp[7:8]")
@@ -239,11 +243,14 @@ jagsUI::traceplot(dG[[1]], parameters = "grBetaMu")
 # isYOY[ evalRows[i] ],species[ evalRows[i]],season[ evalRows[i] ],riverDATA[ evalRows[i] ]
 # [1:675, 1, 1:2, 1:2, 1:4, 1:4]
 plotInt <- function(){
-  ggGrInt <- array2df(dG[[1]]$sims.list$grInt, label.x = "est")
+  ggGrInt <- array2df(dG[[1]]$sims.list$grInt, label.x = "est") %>%
+    rename(yoy=d2,species=d3,season=d4,river=d5)
 
   ggGrInt$chain <- rep(1:dG[[1]]$mcmc.info$n.chains, each = dG[[1]]$mcmc.info$n.samples/dG[[1]]$mcmc.info$n.chains)
   ggGrInt$iter <- 1:as.numeric(dG[[1]]$mcmc.info$n.samples/dG[[1]]$mcmc.info$n.chains)
[…]

### 2017-12-15 manuscriptAnalysis/MS_Analysis.Rmd
spp-specific model runs working

@@
 ggsave('figures/rawCount.png')
+
+tmp <- d %>% distinct(season,year,sampleNumber)
+allFishBySpecies <- left_join(allFishBySpecies,tmp)
+allFish <- left_join(allFish,tmp)
+
+ggplot(allFishBySpecies, aes(sampleNumber,nAllFishBySpecies)) +
+  geom_point(aes(color = speciesGG)) +
+  geom_line(aes(color = speciesGG)) +
+  geom_line( data = allFish, aes(sampleNumber,nAllFish) ) +
+  theme_publication() +
+  labs( x = "SampleNumber", y = "Count" ) +
+  facet_wrap(  ~riverOrderedGG )#, scales = "free_y" )
+
 ```

### 2017-12-15 R/analyzeOutputFunctions.R

@@ -12,10 +12,13 @@
 getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, varsToEstimate){
 
   # get grInt in df format
-  grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="int")
+  #grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="int")
+  grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:nSeasons,river=riverOrderedIn), label.x="int")
 
   # get grBeta in df format and merge in grInt
-  grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="est")
+ # grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="est")
+  grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),season=1:nSeasons,river=riverOrderedIn), label.x="est")
+
   grBeta <- spread( grBeta1, key = beta, value = est, sep = "" ) %>%
     left_join( .,grInt )
 
@@ -184,8 +187,10 @@ plotPred <- function(p, varsToPlot, isYOYGG, speciesGG) {
     notPlot[2] <- all[!(all %in% varsToPlot)][2]
     notPlot[3] <- all[!(all %in% varsToPlot)][3]
 
-    pGG <- p %>% filter(isYOY == isYOYGG, species == speciesGG, eval(as.name(notPlot[1])) == 0, eval(as.name(notPlot[2])) == 0, eval(as.name(notPlot[3])) == 0 ) %>%
-                 distinct(eval(as.name(varsToPlot[1])), iter, isYOY, river, species, season, .keep_all = TRUE)
[…]

### 2017-12-15 R/getAndPrepareDataWB.R

@@ -125,6 +125,17 @@ addNPasses <- function(cd,dr){
   return(cd)
 }
 
+#'Remove low abundance rivers
+#'
+#'@param drainage Which drainage, "west" or "stanley"
+#'@return a data frame
+#'@export
+
+removeLowAbundanceRivers <- function(cd,drainage){
+  # Ats,Jimmy
+  cd <- cd %>% filter( !(species == 'ats' & river == "wb jimmy"))
+}
+
 
 #'Get data from sites table
 #'

### 2017-12-15 R/growthModelFunctions.R

@@ -8,7 +8,7 @@
 
 runGrowthModel <- function(d, parallel = FALSE){
 
-  #grBetaOutside = array( runif( 11 *2*d$nSpecies*d$nSeasons*d$nRivers,-2,2),c( 11 ,2,d$nSpecies,d$nSeasons,d$nRivers))
+  #grBetaOutside = array( runif( 11 *2*d$nSeasons*d$nRivers,-2,2),c( 11 ,2,d$nSeasons,d$nRivers))
   #grBetaOutside[ ,1,,2, ] <- 0
 
   nBetas <- 18
@@ -16,13 +16,13 @@ runGrowthModel <- function(d, parallel = FALSE){
 
   inits <- function(){
     list(
-      grInt = array(rnorm(2*d$nSpecies*d$nSeasons*d$nRivers,0.5,0.25),c(2,d$nSpecies,d$nSeasons,d$nRivers)),
+      grInt = array(rnorm(2*d$nSeasons*d$nRivers,0.5,0.25),c(2,d$nSeasons,d$nRivers)),
       #grBeta[x,1:2,1,1:4,1:4]
-      grBeta = array(rnorm(nBetas*2*d$nSpecies*d$nSeasons*d$nRivers,0,0.1),c(nBetas,2,d$nSpecies,d$nSeasons,d$nRivers)),
+      grBeta = array(rnorm(nBetas*2*d$nSeasons*d$nRivers,0,0.1),c(nBetas,2,d$nSeasons,d$nRivers)),
       #grSigma[ yoy,spp,s,r ]
-      grSigma = array(runif(2*d$nSpecies*d$nSeasons*d$nRivers,0,0.05),c(2,d$nSpecies,d$nSeasons,d$nRivers)),
+      grSigma = array(runif(2*d$nSeasons*d$nRivers,0,0.05),c(2,d$nSeasons,d$nRivers)),
       # sigmaBeta[ b,yoy,spp,s,r ]
-      sigmaBeta = array(rnorm(nBetasSigma*2*d$nSpecies*d$nSeasons*d$nRivers,0,0.05),c(nBetasSigma,2,d$nSpecies,d$nSeasons,d$nRivers)),
+      sigmaBeta = array(rnorm(nBetasSigma*2*d$nSeasons*d$nRivers,0,0.05),c(nBetasSigma,2,d$nSeasons,d$nRivers)),
       grIndRE = rnorm(d$nInd,0,0.1)
     )
   }
[…]

### 2017-12-15 R/plotFunctions.R

@@ -1,12 +1,13 @@
 plotInt <- function(){
   ggGrInt <- array2df(dG[[1]]$sims.list$grInt, label.x = "est") %>%
-    rename(yoy=d2,species=d3,season=d4,river=d5)
+  #  rename(yoy=d2,species=d3,season=d4,river=d5)
+    rename(yoy=d2,season=d3,river=d4)
 
   ggGrInt$chain <- rep(1:dG[[1]]$mcmc.info$n.chains, each = dG[[1]]$mcmc.info$n.samples/dG[[1]]$mcmc.info$n.chains)
   ggGrInt$iter <- 1:as.numeric(dG[[1]]$mcmc.info$n.samples/dG[[1]]$mcmc.info$n.chains)
   gg <- ggplot(filter(ggGrInt), aes(iter,est)) + geom_point( aes(color=factor(chain)), size = 0.1 ) + ylim(-1.5,1.5) +
     #   facet_grid(d2+d4~d5+d3)
-    facet_grid(yoy + river ~ season + species)
+    facet_grid(yoy + river ~ season )
   print(gg)
 }
 
@@ -21,7 +22,12 @@ plotBetas <- function(b){
   gg <- list()
   numBetas <- 18
   for (i in 1:numBetas){
-    gg[[i]] <- ggplot(filter(ggGrBeta,d2 == i), aes(iter,est)) + geom_hline(yintercept = 0) + geom_point( aes(color = factor(chain)), size = 0.1 ) + ylim(-1,1) + facet_grid(d3+d5~d6+d4) + ggtitle(paste("beta =", i))
+    gg[[i]] <- ggplot(filter(ggGrBeta,d2 == i), aes(iter,est)) +
+      geom_hline(yintercept = 0) +
+      geom_point( aes(color = factor(chain)), size = 0.1 ) +
+      ylim(-1,1) +
+      facet_grid(d3+d5 ~ d4) +
+      ggtitle(paste("beta =", i))
     if(i %in% b) print(gg[[i]])
   }
 }
@@ -33,7 +39,7 @@ plotSigma <- function(){
 
   ggSigmaInt$chain <- rep(1:dG[[1]]$mcmc.info$n.chains, each = dG[[1]]$mcmc.info$n.samples/dG[[1]]$mcmc.info$n.chains)
   ggSigmaInt$iter <- 1:as.numeric(dG[[1]]$mcmc.info$n.samples/dG[[1]]$mcmc.info$n.chains)
[…]

### 2017-12-15 R_analysis/mainAnalysis.R

@@ -37,16 +37,17 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "ats" #c("bkt", "bnt","ats") #
-speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
-
 riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
 
 minCohort <- 1997#1995 # >=
 maxSampleInterval <- 200 # <
-runDetectionModelTF <- T
+runDetectionModelTF <- F
 runCrossValidationTF <- F
 percentLeftOut <- 10
+
+meanOrIter <- "mean"; iter <- 1
+####### or ########
+#meanOrIter = "iter"
 
 reconnect()
 
@@ -78,14 +79,16 @@ if ( file.exists(cdFile) ) {
     mutate(drainage = drainage,
            countP = NA) %>% # placeholder so prepareDataForJags() works for detection model
     addRawCounts(drainage, filteredAreas = c("inside","trib")) %>% # counts and summed masses of all fish, tagged and untagged. Not adjusted for P (happens in addDensities())
-    removeUnsampledRows(drainage, removeIncomplete = T) # removes enc=0 rows for samples with no or very few() sections sampled (p=0 otherwise for those samples)
+    removeUnsampledRows(drainage, removeIncomplete = T) %>% # removes enc=0 rows for samples with no or very few() sections sampled (p=0 otherwise for those samples)
+    removeLowAbundanceRivers(drainage) # removes ats,jimmy fish from drainage=='west' - too few fish for estimates
 
   save(cd, file = cdFile)
 }
 
 #################################
 # Detection model
-##################
+# all species at once
+#################################
 #
 #
[…]

### 2018-01-30 manuscriptAnalysis/MS_Analysis.Rmd
all 3 species models running

@@
 ```{r}
+library(arrayhelpers)
 library(tidyverse)
-d <- dddG[[1]]
+
 load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
 load("D:/projects/linkedModels/data/out/countsAndMasses.RData")
+
+mcmc <- list()
+load("D:/projects/linkedModels/data/out/dG_1517338587_bkt1997_Nimble.RData")
+mcmc[['bkt']] <- mcmcProcessed
+d <- dddG[[1]]
+
+load("D:/projects/linkedModels/data/out/dG_1517344974_bnt1997_Nimble.RData")
+mcmc[['bnt']]  <- mcmcProcessed
+
+load("D:/projects/linkedModels/data/out/dG_1517347750_ats1997_Nimble.RData")
+mcmc[['ats']]  <- mcmcProcessed
+
+rm(dddG,ddG,dG,mcmcProcessed)
 ```
@@
 
+```{r mcmc output analysis}
+
+riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
+
+grInt <- list()
+grInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int")
+grInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int")
+grInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int")
+
+ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
+  geom_freqpoly(binwidth=0.05) +
+  geom_freqpoly(aes(int),color = 'brown', data = grInt[['bnt']]) +
+  geom_freqpoly(aes(int),color = 'lightblue', data = grInt[['ats']]) +
+  xlim(-0.5,1.5) +
+  theme_publication() +
+  facet_grid(season ~ river + isYOY)
+
+sigmaInt <- list()
+sigmaInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int")
+sigmaInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int")
+sigmaInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int")
+
+ggplot( sigmaInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
+  geom_freqpoly() +
+  geom_freqpoly(aes(int),color = 'brown', data = sigmaInt[['bnt']]) +
+  geom_freqpoly(aes(int),color = 'lightblue', data = sigmaInt[['ats']]) +
+  xlim(-4.5,-1) +
+  theme_publication() +
+  facet_grid(season ~ river + isYOY)
+
+```
+```{r ind RE among spp}
+
+grIndRE <- list()
+grIndRE[['bkt']] <- as.data.frame(mcmc[['bkt']]$q50$grIndRE); names(grIndRE[['bkt']]) <- 'value'
+grIndRE[['bnt']] <- as.data.frame(mcmc[['bnt']]$q50$grIndRE); names(grIndRE[['bnt']]) <- 'value'
+grIndRE[['ats']] <- as.data.frame(mcmc[['ats']]$q50$grIndRE); names(grIndRE[['ats']]) <- 'value'
+
+ggplot( grIndRE[[1]], aes(value) ) +
+  geom_freqpoly(binwidth = 0.0025) +
+  geom_freqpoly(aes(value), color = "brown", binwidth = 0.0025, data = grIndRE[[2]]) +
+  geom_freqpoly(aes(value), color = "lightblue", binwidth = 0.0025, data = grIndRE[[3]])
+
+```
+
 ```{r overview graphs - Fig Appendix}

### 2018-01-30 R/analyzeOutputFunctions.R

@@ -13,11 +13,11 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, v
 
   # get grInt in df format
   #grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="int")
-  grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn), label.x="int")
+  grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="int")
 
   # get grBeta in df format and merge in grInt
  # grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="est")
-  grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn), label.x="est")
+  grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="est")
 
   grBeta <- spread( grBeta1, key = beta, value = est, sep = "" ) %>%
     left_join( .,grInt )
@@ -389,7 +389,10 @@ getRMSE <- function(residLimit = 0.6){
 #'
 #'
 getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
-  estLen <- array2df(d$q50$lengthExp, label.x = "estLen") %>% rename(rowNumber = d1) #%>% mutate( estLen = na_if(estLen, 0) )
+  estLen <- array2df(d$q50$lengthExp, label.x = "estLen") %>%
+    rename(rowNumber = d1) %>%
+  #  filter( estLen != 0 ) #
+    mutate( estLen = na_if(estLen, 0) )
 
   ddGIn <- ddG[[ii]][[2]]
   ddGIn$isEvalRow <- ifelse( ddGIn$lOcc == 0,TRUE, FALSE )
[…]

### 2018-01-30 R/growthModelFunctions.R

@@ -108,6 +108,9 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
   ##"countPStdBKT"       "countPStdBNT"       "countPStdATS"
   ##"speciesByInd"       "grNotUse"
 
+  # Need to trim off fish at the end of the data that aer only observed once and aren't in evalRows
+
+
   constants <- list(riverDATA = d$riverDATA,
                     nRivers = d$nRivers,
                     nSpecies = d$nSpecies,
@@ -122,9 +125,8 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
                     tempStd = d$tempStd,
                     flowStd = d$flowStd)
   ##
-  #data <- list(lengthDATA = d$lengthDATA)
-  #data <- list(lengthDATA = d$lengthDATA[1:33518])
-  data <- list(lengthDATA = d$lengthDATA[1:34701])
+  data <- list(lengthDATA = d$lengthDATA[1:(max(constants$evalRows)+1)]) # so don't have trailing single obs fish at end of df
+  print(paste("Trimmed", length(d$lengthDATA) - length(data$lengthDATA), "fish that had single observation(s) at end of df"))
   ##
   nBetas <- 11
   nBetasSigma <- 6
@@ -384,7 +386,7 @@ crossValidate <- function(d, runCrossValidationTF){
 
 removeFishWithManyIntermediateNAs <- function(d){
 
-  tagsToRemove <- c('00088cc02a','1c2d6c51d3','00088cc364')
+  tagsToRemove <- c('00088cc02a','1c2d6c51d3','00088cc364','1c2c582218')
   d <- d %>% filter( !(tag %in% tagsToRemove) )
 
   return(d)

### 2018-01-30 R/plotFunctions.R

@@ -59,7 +59,7 @@ plotSigmaBetas_Nimble <- function(d,b){
   gg <- list()
   numBetas <- 6
   for (i in 1:numBetas){
-    gg[[i]] <- ggplot(filter(ggGrBeta,d2 == i), aes(iter,est)) + geom_hline(yintercept = 0) + geom_point( aes(color = factor(chain)), size = 0.1 ) +
+    gg[[i]] <- ggplot(filter(ggSigmaBeta,d2 == i), aes(iter,est)) + geom_hline(yintercept = 0) + geom_point( aes(color = factor(chain)), size = 0.1 ) +
       ylim(-1,1) + facet_grid(d3+d5~d4) + ggtitle(paste("beta =", i))
     if(i %in% b) print(gg[[i]])
   }

### 2018-01-30 nimble/mainAnalysis_Nimble.R

@@ -42,7 +42,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "bkt"
+speciesGr <- "ats"
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
 riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
@@ -104,9 +104,8 @@ dModelName <- paste0(paste0(speciesDet,collapse = ''),"_",minCohort)
 ddddD <- cdBeforeDetMod %>%
   filter(  species %in% speciesInDet,
            cohort >= minCohort,
-           sampleInterval < maxSampleInterval %>%  # this removes the later yearly samples. Want to stick with seasonal samples
-           removeUnsampledRows(drainage, removeIncomplete = T) # removes enc=0 rows for samples with no or very few() sections sampled (p=0 otherwise for those samples)
-  )
+           sampleInterval < maxSampleInterval) %>%  # this removes the later yearly samples. Want to stick with seasonal samples
+           removeUnsampledRows(drainage, removeIncomplete = TRUE) # removes enc=0 rows for samples with no or very few() sections sampled (p=0 otherwise for those samples)
 
 dddD <- ddddD %>%
   prepareDataForJags_Nimble('detection')
@@ -141,16 +140,13 @@ if (runDetectionModelTF) {
 # until they are seen somewhere else.
 # Accomplished with %>% fillSizeLocation(size = F) in getCoreData()
 
-##########################################################################################################################################
+##############################################################################################################################
 # Growth model
 # One species at a time
 ###############
-#
-#
-#speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
[…]

### 2018-02-02 manuscriptAnalysis/MS_Analysis.Rmd
added sampleInterval to gr in model

@@
 rm(dddG,ddG,dG,mcmcProcessed)
+
+load("D:/projects/linkedModels/data/cd_west_1997.RData")
 ```
@@
 ```
+```{r raw growth rates}
+
+cdMeans <- cd %>%
+  mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
+  group_by(species,riverOrdered,season) %>%
+  summarize( meanGr = mean( gr, na.rm = TRUE ),
+             sdGr = sd( gr, na.rm = TRUE )) %>%
+  mutate( meanGrUp = meanGr + sdGr,
+          meanGrDn = meanGr - sdGr
+          )
+
+pd <- position_dodge(0.05) # move them .05 to the left and right
+
+# all three species
+ggplot( cdMeans %>% filter(riverOrdered == 'west brook'), aes(season, meanGr, color = species) ) +
+  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
+  geom_point( size = 2 ) +
+  geom_line()
+
+cd$isYOY <- ifelse( cd$ageInSamples <= 3, 1, 2 )
+cdMeansByisYOY <- cd %>%
+  mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
+  group_by(species,riverOrdered,season,isYOY) %>%
+  summarize( meanGr = mean( gr, na.rm = TRUE ),
+             sdGr = sd( gr, na.rm = TRUE )) %>%
+  mutate( meanGrUp = meanGr + sdGr,
+          meanGrDn = meanGr - sdGr
+          )
+
+# all three species
+ggplot( cdMeansByisYOY %>% filter(riverOrdered == 'west brook'), aes(season, meanGr, color = species) ) +
+  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
+  geom_point( size = 2 ) +
+  geom_line()+
+  facet_wrap(~isYOY)
+
+# bkt only
+pdBKT <- position_dodge(0.05) # move them .05 to the left and right
+ggplot( cdMeans %>% filter(species=='bkt'), aes(season, meanGr, color = riverOrdered) ) +
+  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pdBKT) +
+  geom_point( size = 3 ) +
+  geom_line( size = 1 ) +
+  facet_wrap(~isYOY)
+
+```
 
@@
 
-ggplot( grIndRE[[1]], aes(value) ) +
+ggplot( grIndRE[[1]], aes(value,..density..) ) +
   geom_freqpoly(binwidth = 0.0025) +

### 2018-02-02 R/growthModelFunctions.R

@@ -11,7 +11,8 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
     ##
     for( i in 1:nEvalRows ) {
       ##
-      lengthDATA[ evalRows[i] + 1 ] ~ dnorm( lengthDATA[ evalRows[i] ] + gr[ evalRows[i] ], sd = expectedGRSigma[ evalRows[i] ] )
+      lengthDATA[ evalRows[i] + 1 ] ~ dnorm( lengthDATA[ evalRows[i] ] + gr[ evalRows[i] ] / sampleInterval[ evalRows[i] ],
+                                             sd = expectedGRSigma[ evalRows[i] ] )
       ##
       gr[ evalRows[i] ] <-
         grInt[         isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
@@ -123,7 +124,8 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
                     countPAllSppStd = d$countPAllSppStd,
                     isYOYDATA = d$isYOYDATA,
                     tempStd = d$tempStd,
-                    flowStd = d$flowStd)
+                    flowStd = d$flowStd,
+                    sampleInterval = d$sampleInterval)
   ##
   data <- list(lengthDATA = d$lengthDATA[1:(max(constants$evalRows)+1)]) # so don't have trailing single obs fish at end of df
   print(paste("Trimmed", length(d$lengthDATA) - length(data$lengthDATA), "fish that had single observation(s) at end of df"))

### 2018-02-02 nimble/mainAnalysis_Nimble.R

@@ -42,7 +42,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "ats"
+speciesGr <- "bkt"
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
 riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)

### 2018-02-08 manuscriptAnalysis/MS_Analysis.Rmd
changed lengthDATA to observedLength to get units correct for predictions

@@
 
-Plots for the manuscript
-
-```{r}
-library(arrayhelpers)
-library(tidyverse)
-
-load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
-load("D:/projects/linkedModels/data/out/countsAndMasses.RData")
-
-mcmc <- list()
-load("D:/projects/linkedModels/data/out/dG_1517338587_bkt1997_Nimble.RData")
-mcmc[['bkt']] <- mcmcProcessed
-d <- dddG[[1]]
-
-load("D:/projects/linkedModels/data/out/dG_1517344974_bnt1997_Nimble.RData")
-mcmc[['bnt']]  <- mcmcProcessed
-
-load("D:/projects/linkedModels/data/out/dG_1517347750_ats1997_Nimble.RData")
-mcmc[['ats']]  <- mcmcProcessed
-
-rm(dddG,ddG,dG,mcmcProcessed)
-
-load("D:/projects/linkedModels/data/cd_west_1997.RData")
-```
-
-```{r custom theme}
+```{r functions}
 theme_publication <- function(base_size=14, base_family="") {
@@
 
+```
+
+Plots for the manuscript
+
+```{r message=FALSE}
+library(arrayhelpers)
+library(tidyverse)
+
+load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
+load("D:/projects/linkedModels/data/out/countsAndMasses.RData")
+
+mcmc <- list()
+load("D:/projects/linkedModels/data/out/dG_1517846073_bkt1997_Nimble.RData")
+
+# input data
+d1 <- ddG[[1]][[1]]
+d2 <- ddG[[1]][[2]]
+meanSampleIntervalMean <- data.frame( meanSampleInterval = colMeans(d1$sampleIntervalMean), season = 1:d1$nSeasons )
+
+#RECALCULATE gr for dataset. Filtering by maxSampleInterval in the creat ddddG step leaves in trailing lengths from the long samp intervals
+d2 <- d2 %>%
+  group_by(tag) %>%
+  # arrange(tag,sampleNumber) %>%
+  mutate( lagObservedWeight = lead(observedWeight),
+          lagObservedLength = lead(observedLength),
+          grWeight = exp(lagObservedWeight - observedWeight)/as.numeric((lagDetectionDate - detectionDate)),
+          grLength = (lagObservedLength - observedLength)/as.numeric((lagDetectionDate - detectionDate))
+  )  
+#d2 %>% filter(tag=='00088cc059') %>% select(tag,riverOrdered,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength)
+
+# output data
+mcmc[['bkt']] <- mcmcProcessed
+
+load("D:/projects/linkedModels/data/out/dG_1517850064_bnt1997_Nimble.RData")
+mcmc[['bnt']]  <- mcmcProcessed
+
+load("D:/projects/linkedModels/data/out/dG_1517853143_ats1997_Nimble.RData")
+mcmc[['ats']]  <- mcmcProcessed
+
+rm(ddG,dG,mcmcProcessed)
+
+load("D:/projects/linkedModels/data/cd_west_1997.RData")
 ```
@@
 # all three species
-ggplot( cdMeansByisYOY %>% filter(riverOrdered == 'west brook'), aes(season, meanGr, color = species) ) +
+ggplot( cdMeansByisYOY %>% filter(riverOrdered == 'west brook', !(season == 2 & isYOY == 1)), aes(season, meanGr, color = species) ) +
   geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
@@
   facet_wrap(~isYOY)
+
+# all three species by river
+ggplot( cdMeansByisYOY %>% filter(!(season == 2 & isYOY == 1)) , aes(season, meanGr, color = riverOrdered) ) +
+  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
+  geom_point( size = 2 ) +
+  geom_line()+
+  facet_grid(species~isYOY)
 
@@
 
+```
+```{r growth by movement}
+d2$isYOY <- ifelse( d2$ageInSamples <= 3, 1, 2 )
+d2 <-  d2 %>%
+  group_by(tag) %>%
+  mutate( lagRiverN = lead(riverN), 
+          riverNMove = paste(riverN,lagRiverN, sep="_")
+          #gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate)
+          )
+
+#d2 %>% filter(tag=='00088cbf44') %>% select(tag,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength)
+table(d2$riverNMove)
+
+cdMeansByisYOYriverNMove <- d2 %>%
+  #mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
+  group_by(species,riverN,lagRiverN,season,isYOY) %>%
+  summarize( meanGr = mean( grLength, na.rm = TRUE ),
+             sdGr = sd( grLength, na.rm = TRUE ),
+             n = n()) %>%
+  mutate( meanGrUp = meanGr + sdGr,
+          meanGrDn = meanGr - sdGr
+          )
+
+# 
+ggplot( cdMeansByisYOYriverNMove %>% filter(!(season == 2 & isYOY == 1), species == "bkt", isYOY == 2) , aes(season, meanGr, color = factor(lagRiverN)) ) +
+  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
+  geom_point( size = 2 ) +
+  geom_line()+
+  facet_wrap(~riverN)
+
+d2 %>% filter(riverN == 1 & lagRiverN == 4) %>% select(tag,river,sampleNumber)
+d2 %>% filter(riverN == 2, is.na(lagRiverN), !is.na(grLength)) %>% select(tag,riverN,sampleNumber,lagRiverN,observedLength,lagObservedLength,gr,grLength)
+d2 %>% filter(tag=='00088cc059') %>% select(tag,riverOrdered,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength,gr,grLength)
 ```
@@
 
+# as range plot
+probs <- c(0.05,0.1,0.5,0.9,0.95)
+q <- grInt[['bkt']] %>%
+  group_by(isYOY,season,river) %>%
+  summarize(
+    p = list(probs),
+    q = list(quantile(int,probs))
+  ) %>%
+  unnest() %>%
+  spread(key = p, value = q)
+
+p <- array2df(mcmc[['bkt']]$mean$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>%
+  mutate( season = as.numeric(season) ) %>%
+  left_join(.,meanSampleIntervalMean, by = 'season')
+p$intByDay <- p$int/p$meanSampleInterval
+p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
+p$parameter <- paste(p$river,p$season,sep="_")
+
+pUp <- array2df(mcmc[['bkt']]$q97.5$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="intUp") %>%
+  mutate( season = as.numeric(season) ) 
+pDown <- array2df(mcmc[['bkt']]$q2.5$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="intDown") %>%
+  mutate( season = as.numeric(season) )
+p$intByDayUp <- p$intUp/p$meanSampleInterval; p$intByDayDown <- p$intDown/p$meanSampleInterval
+p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
+p <- left_join(p,pUp) %>% left_join(.,pDown)
+
+   ggplot(p, aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(season), shape = factor(season))) + 
+      geom_point(size = 3) +
+      facet_grid(~isYOY)
+
+      geom_segment(aes(x = Low, 
+      xend = High, yend = reorder(Parameter, median)), 
+      size = 1.5) + geom_segment(aes(x = low, xend = high, 
+      yend = reorder(Parameter, median)), size = 0.5) + 
+      xlab("HPD") + ylab("Parameter")
+
+```
+
+```{r}
+
 sigmaInt <- list()
@@
 ```
+
 ```{r ind RE among spp}
@@
   geom_freqpoly(aes(value), color = "lightblue", binwidth = 0.0025, data = grIndRE[[3]])
+
+```
+
+```{r tables}
+
+round(mcmc$summary$all.chains[startsWith(attributes(mcmc$summary$all.chains)$dimnames[[1]], "grBeta["),],2)
 

### 2018-02-08 R/analyzeOutputFunctions.R

@@ -9,7 +9,7 @@
 #'@return a data frame
 #'@export
 
-getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, varsToEstimate){
+getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, sampleIntervalMeanIn, varsToEstimate){
 
   # get grInt in df format
   #grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="int")
@@ -22,6 +22,8 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, v
   grBeta <- spread( grBeta1, key = beta, value = est, sep = "" ) %>%
     left_join( .,grInt )
 
+  sampleIntervalMean <- array2df(sampleIntervalMeanIn, levels = list( river=riverOrderedIn[1:constants$nRivers],season=1:constants$nSeasons,species=1:constants$nSpecies), label.x = "interval")
+  grBeta <- left_join(grBeta,sampleIntervalMean)
   # prediction template
   x <- seq( -limits,limits,length.out = nPoints )
 
@@ -71,7 +73,7 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, v
 
     # repeat predTemplate nrow( grBetaIter ) times
     predTemplateLong <- do.call("rbind", replicate( nrow( grBetaIter ), predTemplate, simplify = FALSE) )
-    # repeat each row of grbetaIter nrow(predTemplate) times
+    # repeat each row of grBetaIter nrow(predTemplate) times
     grBetaLong <- grBetaIter[rep(seq_len(nrow(grBetaIter)), each = nrow(predTemplate)),]
     # Put them together
     preds <- cbind( predTemplateLong,grBetaLong )
@@ -79,7 +81,7 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, v
   # This model structure needs to match that in grModelx.jags
   preds <- preds %>%
     mutate( predGr =
-              int +
+            ( int +
               beta1 * len +
               beta2 * count +
               beta3 * temp +
@@ -94,38 +96,9 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, v
               beta9 * temp * count +
               beta10 * count * flow +
 
[…]

### 2018-02-08 R/getAndPrepareDataWB.R

@@ -225,8 +225,8 @@ cleanData <- function(d,drainageIn){
             distMoved = section - lagSection,
             lagObservedWeight = lead(observedWeight),
             lagObservedLength = lead(observedLength),
-            grWeight = exp(lagObservedWeight - observedWeight)/as.numeric((lagDetectionDate - detectionDate)),
-            grLength = (lagObservedLength - observedLength)/as.numeric((lagDetectionDate - detectionDate)),
+        #    grWeight = exp(lagObservedWeight - observedWeight)/as.numeric((lagDetectionDate - detectionDate)),
+        #    grLength = (lagObservedLength - observedLength)/as.numeric((lagDetectionDate - detectionDate)),
             minSample = min(sampleNumber),
             maxSample = max(sampleNumber),
             minYear = minYear) %>%

### 2018-02-08 R/growthModelFunctions.R

@@ -11,12 +11,13 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
     ##
     for( i in 1:nEvalRows ) {
       ##
-      lengthDATA[ evalRows[i] + 1 ] ~ dnorm( lengthDATA[ evalRows[i] ] + gr[ evalRows[i] ] / sampleInterval[ evalRows[i] ],
+      mu[ evalRows[i] ] <- lengthDATA[ evalRows[i] ] + ( gr[ evalRows[i] ] * sampleInterval[ evalRows[i] ] )
+      lengthDATA[ evalRows[i] + 1 ] ~ dnorm( mu[ evalRows[i] ],
                                              sd = expectedGRSigma[ evalRows[i] ] )
       ##
       gr[ evalRows[i] ] <-
-        grInt[         isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
-        grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthDATA[evalRows[i]] +
+        grInt[     isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
+        grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]] +
         grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * countPAllSppStd[evalRows[i]] +
         grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] +
         grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]] +
@@ -37,7 +38,7 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
         grIndRE[ ind[evalRows[i]] ]
       ##
       log( expectedGRSigma[ evalRows[i] ] ) <- #grSigma
-        sigmaInt[ isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
+        sigmaInt[     isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
[…]

### 2018-02-08 R/plotFunctions.R

@@ -9,7 +9,7 @@ plotInt_Nimble <- function(d){
   ggGrInt$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples/mcmcInfo$nChains)
   ggGrInt$iter <- 1:as.numeric(mcmcInfo$nSamples/mcmcInfo$nChains)
 
-  gg <- ggplot(filter(ggGrInt), aes(iter,est)) + geom_point( aes(color=factor(chain)), size = 0.1 ) + ylim(-1.5,1.5) +
+  gg <- ggplot(filter(ggGrInt), aes(iter,est)) + geom_point( aes(color=factor(chain)), size = 0.1 ) + #ylim(-1.5,1.5) +
     #   facet_grid(d2+d4~d5+d3)
     facet_grid(yoy + river ~ season )
   print(gg)
@@ -29,7 +29,7 @@ plotBetas_Nimble <- function(d,b){
     gg[[i]] <- ggplot(filter(ggGrBeta,d2 == i), aes(iter,est)) +
       geom_hline(yintercept = 0) +
       geom_point( aes(color = factor(chain)), size = 0.1 ) +
-      ylim(-1,1) +
+   #   ylim(-1,1) +
       facet_grid(d3+d5 ~ d4) +
       ggtitle(paste("beta =", i))
     if(i %in% b) print(gg[[i]])

### 2018-02-08 R/prepareDataForJags_Nimble.R

@@ -168,7 +168,8 @@ prepareDataForJags_Nimble <- function(d,modelType){
 
   if ( modelType == "growth" ){
     data <- list( encDATA = d$enc,
-                  lengthDATA = d$lengthDATALnStd, #d$lengthDATAStd,
+                  lengthDATA = d$observedLength, #d$lengthDATAStd, #d$lengthDATALnStd,
+                  lengthDATAStd = d$lengthDATALnStd,
                   riverDATA = d$riverN,
                   ind = d$tagIndexJags,
                   nRivers = nRivers,
@@ -186,8 +187,8 @@ prepareDataForJags_Nimble <- function(d,modelType){
                   nLastObsRows = nLastObsRows, lastObsRows = lastObsRows,
                   nAllRows = nAllRows,
                   nSeasons = nSeasons,
-                  lengthMean = array(means$meanLen, dim = c(nRivers,nSeasons,nSpecies)),
-                  lengthSD = array(means$sdLen, dim = c(nRivers,nSeasons,nSpecies)),
+                  lengthMean = mean(d$observedLength, na.rm = TRUE), #array(means$meanLen, dim = c(nRivers,nSeasons,nSpecies)),
+                  lengthSD = sd(d$observedLength, na.rm = TRUE), #array(means$sdLen, dim = c(nRivers,nSeasons,nSpecies)),
                   sampleIntervalMean = array(means$sampleIntervalMean, dim = c(nRivers,nSeasons,nSpecies)),
                   #   cutoffYOYDATA = cutoffYOYDATA,
                   sampleInterval = d$sampleInterval,

### 2018-02-08 nimble/mainAnalysis_Nimble.R

@@ -42,7 +42,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "bkt"
+speciesGr <- "ats"
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
 riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
@@ -240,7 +240,7 @@ iter=1
   source("./R/jagsUIFunctions.R")
   mcmcProcessed <- process.output(mcmc$samples, DIC=FALSE, params.omit=FALSE)#,params.omit=("lengthExp")) #jagsUI function, DIC = FALSE because it requires 'deviance'
 
-  obsPred <- getRMSE_Nimble(mcmcProcessed,0.6)
+  obsPred <- getRMSE_Nimble(mcmcProcessed,20)
   obsPred$rmse
   obsPred$outliers%>% as.data.frame()
 
@@ -275,30 +275,30 @@ iter=1
   itersForPred <- sample( 1:mcmcInfo$nSamples, nItersForPred )
 
   # predictions across the grid
-  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, c("len", "temp", "flow","count") )#######################
-  # save(p,file = "./data/out/P_ForMikeBNT.RData")
+  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","count") )#######################
+    save(p,file = paste0("./data/out/P_ForMike_",speciesGr,".RData"))
   # graph function, in analyzeOutputFunctions.R
 
-  plotPred(p, "len", 1, "bkt") #spp is just a pass-through for title until I combine the species results into one df
-  plotPred(p, "temp", 1, "bkt")
-  plotPred(p, "flow", 1, "bkt")
-  plotPred(p, "count", 1, "bkt")
-  plotPred(p, c("flow", "temp"), 1, "bkt")
[…]

### 2018-03-29 manuscriptAnalysis/MS_Analysis.Rmd
switch to spp-specific abundances

@@
 mcmc <- list()
-load("D:/projects/linkedModels/data/out/dG_1517846073_bkt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1518555667_bkt1997_Nimble.RData")
 
@@
 
-load("D:/projects/linkedModels/data/out/dG_1517850064_bnt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1518559325_bnt1997_Nimble.RData")
 mcmc[['bnt']]  <- mcmcProcessed
 
-load("D:/projects/linkedModels/data/out/dG_1517853143_ats1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1518559991_ats1997_Nimble.RData")
 mcmc[['ats']]  <- mcmcProcessed
@@
 
-ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
-  geom_freqpoly(binwidth=0.05) +
-  geom_freqpoly(aes(int),color = 'brown', data = grInt[['bnt']]) +
-  geom_freqpoly(aes(int),color = 'lightblue', data = grInt[['ats']]) +
-  xlim(-0.5,1.5) +
+ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(exp(int))) +
+  geom_freqpoly() +
+  geom_freqpoly(aes(exp(int)),color = 'brown', data = grInt[['bnt']]) +
+  geom_freqpoly(aes(exp(int)),color = 'lightblue', data = grInt[['ats']]) +
+ # xlim(-0.5,1.5) +
   theme_publication() +
@@
 
+bw <- 0.05
 ggplot( sigmaInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
-  geom_freqpoly() +
-  geom_freqpoly(aes(int),color = 'brown', data = sigmaInt[['bnt']]) +
-  geom_freqpoly(aes(int),color = 'lightblue', data = sigmaInt[['ats']]) +
-  xlim(-4.5,-1) +
+  geom_freqpoly(binwidth = bw) +
+  geom_freqpoly(aes(int),binwidth = bw,color = 'brown', data = sigmaInt[['bnt']]) +
+  geom_freqpoly(aes(int),binwidth = bw,color = 'lightblue', data = sigmaInt[['ats']]) +
+  #xlim(-4.5,-1) +
+  xlim(-5,2.5) +
   theme_publication() +

### 2018-03-29 R/analyzeOutputFunctions.R

@@ -9,7 +9,7 @@
 #'@return a data frame
 #'@export
 
-getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, sampleIntervalMeanIn, varsToEstimate){
+getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, sampleIntervalMeanIn, varsToEstimate, ii=1){
 
   # get grInt in df format
   #grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="int")
@@ -97,7 +97,7 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
               beta10 * count * flow +
 
               beta11 * count * temp * flow
-            ) #/ interval
+            ) #* interval
 
 
     )
@@ -116,19 +116,21 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
 #'@return a data frame
 #'@export
 
-getPredictionSigma <- function(d, limits = 2, nPoints = 5, itersForPred, varsToEstimate){
+getPredictionSigma <- function(d, limits = 2, nPoints = 5, itersForPred, constants, sampleIntervalMeanIn, varsToEstimate, ii=1){
 
   # get grInt in df format
   #grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="int")
-  grInt <- array2df(d$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:nSeasons,river=riverOrderedIn), label.x="int")
+  grInt <- array2df(d$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="int")
 
   # get grBeta in df format and merge in grInt
   # grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="est")
-  grBeta1 <- array2df(d$sims.list$sigmaBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),season=1:nSeasons,river=riverOrderedIn), label.x="est")
[…]

### 2018-03-29 R/growthModelFunctions.R

@@ -13,54 +13,106 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
       ##
       mu[ evalRows[i] ] <- lengthDATA[ evalRows[i] ] + ( gr[ evalRows[i] ] * sampleInterval[ evalRows[i] ] )
       lengthDATA[ evalRows[i] + 1 ] ~ dnorm( mu[ evalRows[i] ],
-                                             sd = expectedGRSigma[ evalRows[i] ] )
+                                             sd = expectedGRSigma[ evalRows[i] ] * sampleInterval[ evalRows[i] ] )
       ##
+
       gr[ evalRows[i] ] <-
-        grInt[     isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
-        grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]] +
-        grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * countPAllSppStd[evalRows[i]] +
-        grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] +
-        grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]] +
-        ## grBeta[ 5, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthDATA[evalRows[i]]^2 +
-        grBeta[ 5, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * countPAllSppStd[evalRows[i]]^2 +
-        grBeta[ 6, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]]^2 +
-        grBeta[ 7, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]]^2 +
[…]

### 2018-03-29 nimble/mainAnalysis_Nimble.R

@@ -246,7 +246,7 @@ iter=1
 
   #########################################
   # save data to file
-  save(mcmcProcessed,dG,ddG, file = paste0('./data/out/dG_', as.integer(Sys.time()),'_', modelName, '_Nimble.RData'))
+  save(mcmcInfo,mcmcProcessed,dG,ddG, file = paste0('./data/out/dG_', as.integer(Sys.time()),'_', modelName, '_Nimble.RData'))
 
   done <- Sys.time()
   elapsed[[ii]] <- done - start
@@ -276,33 +276,46 @@ iter=1
 
   # predictions across the grid
   p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","count") )#######################
-    save(p,file = paste0("./data/out/P_ForMike_",speciesGr,".RData"))
+  p$variable <- "mean"
+  # predictions of sigma across the grid
+  pSigma <- getPredictionSigma( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","count") )
+  pSigma$variable <- "sd"
+  # combine predicted growth rates and sigma in predicted growth rates to get cv in predicted growth rates
+  pBoth <- left_join( p,pSigma, by = c('len','count','flow','temp','iter','isYOY','season','river')) %>%
+    mutate(predCV = predGrSigma/predGr)
+  pBoth$variable <- "cv"
+  pBoth$predCV <- ifelse(pBoth$predCV > 10, NA, pBoth$predCV) # to avoid very large CVs when gr is very small
+  pBoth$predCV <- ifelse(pBoth$predCV < 0, NA, pBoth$predCV) # to avoid negative CVs when gr is very small and negative
+
+  save(pBoth,file = paste0("./data/out/P_ForMike_",speciesGr,".RData"))
+
+     #
   # graph function, in analyzeOutputFunctions.R
 
-  plotPred(p, "len", 1, speciesGr) #spp is just a pass-through for title until I combine the species results into one df
+  plotPred(p, "predGr", "len", 1, speciesGr)
[…]

### 2018-04-04 manuscriptAnalysis/MS_Analysis.Rmd
update model selection

@@
 
+```
+
+```{r}
+# Correlation between age classes
+# justification for not using separate age class abundances
+# interesting that it is less for ATS
+# From the bottom of adjustCounts()
+# 
+#                               nAllFishBySpeciesPStdBKT_yoy1 nAllFishBySpeciesPStdBKT_yoy2 nAllFishBySpeciesPStdBNT_yoy1 nAllFishBySpeciesPStdBNT_yoy2
+# nAllFishBySpeciesPStdBKT_yoy1                          1.00                          0.96                         -0.46                         -0.43
+# nAllFishBySpeciesPStdBKT_yoy2                        **0.96**                        1.00                         -0.44                         -0.38
+# nAllFishBySpeciesPStdBNT_yoy1                         -0.46                         -0.44                          1.00                          0.94
+# nAllFishBySpeciesPStdBNT_yoy2                         -0.43                         -0.38                       * *0.94**                       1.00
+# nAllFishBySpeciesPStdATS_yoy1                         -0.13                         -0.17                         -0.21                          0.00
+# nAllFishBySpeciesPStdATS_yoy2                          0.06                         -0.03                         -0.05                          0.15
+#                               nAllFishBySpeciesPStdATS_yoy1 nAllFishBySpeciesPStdATS_yoy2
+# nAllFishBySpeciesPStdBKT_yoy1                         -0.13                          0.06
+# nAllFishBySpeciesPStdBKT_yoy2                         -0.17                         -0.03
+# nAllFishBySpeciesPStdBNT_yoy1                         -0.21                         -0.05
+# nAllFishBySpeciesPStdBNT_yoy2                          0.00                          0.15
+# nAllFishBySpeciesPStdATS_yoy1                          1.00                          0.47
+# nAllFishBySpeciesPStdATS_yoy2                         *0.47*                         1.00
 ```

### 2018-04-04 manuscriptAnalysis/linearGR_Models.Rmd
update model selection

---
title: "linearGR_Models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)

library(lme4)
library(tidyverse)
```

```{r load data}

load(file = paste0('D:/projects/linkedModels/data/out/dG_bktbntats1997_forLmer.RData')) # made by running mainAnalysis.R with speciesGr = c("bkt", "bnt","ats") through ddG[[ii]] <- dddG[[ii]] %>% prepareDataForJags("growth")

d2 <- data.frame(
  #sampleNumber=ddG[[1]][[2]]$sampleNumber,
  ind=ddG[[1]][[1]]$ind,
  river=ddG[[1]][[1]]$riverDATA,
  season=ddG[[1]][[1]]$season,
  species=ddG[[1]][[1]]$species,
  isYOY=ddG[[1]][[1]]$isYOYDATA,
  length=ddG[[1]][[1]]$lengthDATAStd,
  lengthByYear=ddG[[1]][[1]]$lengthDATAStd_ByYOY_Year,
  grLength=ddG[[1]][[1]]$grNotUse,
  tempStd=ddG[[1]][[1]]$tempStd,
  flowStd=ddG[[1]][[1]]$flowStd,
  countPStd=ddG[[1]][[1]]$countPAllSppStd,

  countPStdBKT=ddG[[1]][[1]]$countPStdBKT,
  countPStdBNT=ddG[[1]][[1]]$countPStdBNT,
  countPStdATS=ddG[[1]][[1]]$countPStdATS
  )

d <- d2 %>% filter(
  #  species == as.numeric(speciesInGr),
    !is.na(grLength)
  )
d <- d %>% mutate( tempStd2 = tempStd^2, flowStd2 = flowStd^2, countPStd2 = countPStd^2, length2 = length^2,
                   countPStdBKT2 = countPStdBKT^2,
                   countPStdBNT2 = countPStdBNT^2,
                   countPStdATS2 = countPStdATS^2,
                   isYOY = as.factor(isYOY), season = as.factor(season), river = as.factor(river), species = as.factor(species)
                 )
d$grLength <- ifelse(d$species == 2 & d$river == 3,NA,d$grLength)

```

Try new, more flexible model structure

2a is best for BKT
2 is best for BNT
```{r}

#BKT
sppMod <- 1
dIn <- d %>% filter(species == sppMod)

mod1 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2a <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2b <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 ) +
                         isYOY * river * season * ( countPStdBKT2 ) +
                         isYOY * river * season * ( countPStdBNT2 ) +
                         isYOY * river * season * ( countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2c <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 ) +
                         isYOY * river * season * ( countPStdBNT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod3 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod4 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod4a <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod5 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5) %>% rownames_to_column() %>% arrange(AIC)
```
For salmon  - need to get rid of 'river'
mod5 is best
```{r}

#ATS
sppMod <- 3
dIn <- d %>% filter(species == sppMod)

mod1 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         isYOY * season * ( length2 * countPStdBKT2 ) +
                         isYOY * season * ( length2 * countPStdBNT2 ) +
                         isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2a <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2b <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 ) +
                         isYOY * season * ( countPStdBKT2 ) +
                         isYOY * season * ( countPStdBNT2 ) +
                         isYOY * season * ( countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod2c <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 ) +
                         isYOY * season * ( countPStdBNT2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod3 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         # isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod4 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod4a <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2  ) +
                         isYOY * season * ( tempStd2 * flowStd2  ) +
                         isYOY * season * ( tempStd2 * flowStd2  ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

mod5 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn )

AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5) %>% rownames_to_column() %>% arrange(AIC)
```

### 2018-04-04 R/growthModelFunctions.R

@@ -451,14 +451,13 @@ adjustCounts <- function( cdIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
             riverOrdered = factor(riverOrdered,levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
           )
   # use this as merge template, then interpolate std values
-  # could break up by isYOY...
 
   denForMerge_possibleOccasions <- left_join( possibleOccasions,denForMerge2 ) %>%
     mutate( nAllFishBySpeciesPStd = zoo::na.approx(nAllFishBySpeciesPStd),
             nAllFishPStd = zoo::na.approx(nAllFishPStd),
             massAllFishBySpeciesStd = zoo::na.approx(massAllFishBySpeciesStd),
             massAllFishStd = zoo::na.approx(massAllFishStd)) %>%
-    select(-c(Freq,FreqUp,FreqDown))
+    dplyr::select(-c(Freq,FreqUp,FreqDown))
 
   cdIn <- left_join( cdIn,denForMerge_possibleOccasions, by = c("species", "year", "season", "riverOrdered") )
 
@@ -475,21 +474,26 @@ adjustCounts <- function( cdIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
 
   cdIn <- left_join( cdIn,nAllFishBySpeciesPStdBySpp )
 
-  #####
-  # counts by species in separate columns
-  nAllFishBySpeciesPStdBySppYOY <- denForMerge_possibleOccasions %>%
-    dplyr::select(isYOYN,species, season, riverOrdered, year, nAllFishBySpeciesPStd) %>%
-    unite(yoySpp, species, isYOYN, sep = "_") %>%
-    spread(key=yoySpp, value=nAllFishBySpeciesPStd, fill = -2.5) %>%
-    rename(nAllFishBySpeciesPStdBKT_yoy1 = bkt_1,
-           nAllFishBySpeciesPStdBKT_yoy2 = bkt_2,
-           nAllFishBySpeciesPStdBNT_yoy1 = bnt_1,
[…]

### 2018-04-04 manuscriptAnalysis/old/linearGR_Models.R

@@ -1,7 +1,7 @@
 library(lme4)
 library(tidyverse)
 
-# lm to compare against the jags model
+# lm for model selection, also to compare against the jags model
 # patterns generally match up well
 
 load(file = paste0('./data/out/dG_bktbntats1997_forLmer.RData')) # made by running mainAnalysis.R with speciesGr = c("bkt", "bnt","ats") through ddG[[ii]] <- dddG[[ii]] %>% prepareDataForJags("growth")
@@ -19,10 +19,21 @@ d2 <- data.frame(
   tempStd=ddG[[1]][[1]]$tempStd,
   flowStd=ddG[[1]][[1]]$flowStd,
   countPStd=ddG[[1]][[1]]$countPAllSppStd,
+
   countPStdBKT=ddG[[1]][[1]]$countPStdBKT,
   countPStdBNT=ddG[[1]][[1]]$countPStdBNT,
-  countPStdATS=ddG[[1]][[1]]$countPStdATS
-)
+  countPStdATS=ddG[[1]][[1]]$countPStdATS,
+
+  countPStdBKT_yoy1=ddG[[1]][[1]]$countPStdBKT_yoy1,
+  countPStdBKT_yoy2=ddG[[1]][[1]]$countPStdBKT_yoy2,
+
+  countPStdBNT_yoy1=ddG[[1]][[1]]$countPStdBKT_yoy1,
+  countPStdBNT_yoy2=ddG[[1]][[1]]$countPStdBKT_yoy2,
+
+  countPStdATS_yoy1=ddG[[1]][[1]]$countPStdATS_yoy1,
+  countPStdATS_yoy2=ddG[[1]][[1]]$countPStdATS_yoy2
+
+  )
 
 d <- d2 %>% filter(
   #  species == as.numeric(speciesInGr),
@@ -43,10 +54,14 @@ modl1 <- lmer( grLength ~ isYOY * species * river * season * lengthByYear + (1|i
 ggplot(d,aes(length,lengthByYear,color=isYOY)) + geom_point()
 AIC(modl0,modl1)
 
+
 # model with spp-specific abundances is a lot better. Stick with that to start
 moda0 <- lmer( grLength ~ isYOY * species * river * season * countPStd + (1|ind), data = d )
 moda1 <- lmer( grLength ~ isYOY * species * river * season * countPStdBKT * countPStdBNT * countPStdATS + (1|ind), data = d )
-AIC(moda0,moda1)
[…]

### 2018-04-06 manuscriptAnalysis/linearGR_Models.Rmd
sort out isYOY in det model and downstream

@@
 
+mod <- list(list())
+dIn <- list()
+
+bySpecies <- d %>% group_by(species) %>% nest()
 ```
@@
 2 is best for BNT
-```{r}
+```{r bkt}
 
@@
 sppMod <- 1
-dIn <- d %>% filter(species == sppMod)
+dIn[[sppMod]] <- d %>% filter(species == sppMod)
 
-mod1 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[1]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod2 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[2]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod2a <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[3]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod2b <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[4]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod2c <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[5]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod3 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[6]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod4 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[7]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod4a <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[8]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-mod5 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[sppMod]][[9]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[sppMod]] )
 
-AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5) %>% rownames_to_column() %>% arrange(AIC)
+mod[[sppMod]][[10]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
+                         isYOY * season * ( tempStd * flowStd * length ) +
+                         # isYOY * season * ( length * countPStdBKT ) +
+                         # isYOY * season * ( length * countPStdBNT ) +
+                         # isYOY * season * ( length * countPStdATS ) +
+
+                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
+                      #   isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
+                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
+                         # isYOY * season * ( length2 * countPStdBKT2 ) +
+                         # isYOY * season * ( length2 * countPStdBNT2 ) +
+                         # isYOY * season * ( length2 * countPStdATS2 ) +
+
+                         (1|ind), data = dIn[[sppMod]] )
+
+mod[[sppMod]][[11]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
+                         isYOY * season * ( tempStd * flowStd * length ) +
+                         # isYOY * season * ( length * countPStdBKT ) +
+                         # isYOY * season * ( length * countPStdBNT ) +
+                         # isYOY * season * ( length * countPStdATS ) +
+
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
+                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
+                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
+                         # isYOY * season * ( length2 * countPStdBKT2 ) +
+                         # isYOY * season * ( length2 * countPStdBNT2 ) +
+                         # isYOY * season * ( length2 * countPStdATS2 ) +
+
+                         (1|ind), data = dIn[[sppMod]] )
+
+mod[[sppMod]][[12]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
+                         isYOY * season * ( tempStd * flowStd * length ) +
+                         # isYOY * season * ( length * countPStdBKT ) +
+                         # isYOY * season * ( length * countPStdBNT ) +
+                         # isYOY * season * ( length * countPStdATS ) +
+
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
+                         isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
+                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
+                         # isYOY * season * ( length2 * countPStdBKT2 ) +
+                         # isYOY * season * ( length2 * countPStdBNT2 ) +
+                         # isYOY * season * ( length2 * countPStdATS2 ) +
+
+                         (1|ind), data = dIn[[sppMod]] )
+
+(aic[[sppMod]] <- AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5,mod5a,mod5b,mod5c) %>% rownames_to_column() %>% arrange(AIC))
 ```
+
 For salmon  - need to get rid of 'river'
@@
 sppMod <- 3
-dIn <- d %>% filter(species == sppMod)
+dIn[[3]] <- d %>% filter(species == sppMod)
 
-mod1 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[1]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod2 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[2]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod2a <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[3]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod2b <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[4]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod2c <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[5]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod3 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[6]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod4 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[7]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod4a <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[8]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-mod5 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+mod[[3]][[9]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                          isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
@@
 
-                         (1|ind), data = dIn )
+                         (1|ind), data = dIn[[3]] )
 
-AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5) %>% rownames_to_column() %>% arrange(AIC)
+mod[[3]][[10]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
+                         isYOY * season * ( tempStd * flowStd * length ) +
+                         # isYOY * season * ( length * countPStdBKT ) +
+                         # isYOY * season * ( length * countPStdBNT ) +
+                         # isYOY * season * ( length * countPStdATS ) +
+
+                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
+                      #   isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
+                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
+                         # isYOY * season * ( length2 * countPStdBKT2 ) +
+                         # isYOY * season * ( length2 * countPStdBNT2 ) +
+                         # isYOY * season * ( length2 * countPStdATS2 ) +
+
+                         (1|ind), data = dIn[[3]] )
+
+mod[[3]][[11]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
+                         isYOY * season * ( tempStd * flowStd * length ) +
+                         # isYOY * season * ( length * countPStdBKT ) +
+                         # isYOY * season * ( length * countPStdBNT ) +
+                         # isYOY * season * ( length * countPStdATS ) +
+
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
+                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
+                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
+                         # isYOY * season * ( length2 * countPStdBKT2 ) +
+                         # isYOY * season * ( length2 * countPStdBNT2 ) +
+                         # isYOY * season * ( length2 * countPStdATS2 ) +
+
+                         (1|ind), data = dIn[[3]] )
+
+mod[[3]][[12]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
+                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
+                         isYOY * season * ( tempStd * flowStd * length ) +
+                         # isYOY * season * ( length * countPStdBKT ) +
+                         # isYOY * season * ( length * countPStdBNT ) +
+                         # isYOY * season * ( length * countPStdATS ) +
+
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
+                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
+                         isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
+                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
+                         # isYOY * season * ( length2 * countPStdBKT2 ) +
+                         # isYOY * season * ( length2 * countPStdBNT2 ) +
+                         # isYOY * season * ( length2 * countPStdATS2 ) +
+
+                         (1|ind), data = dIn[[3]] )
+
+(aic[[sppMod]] <- AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5,mod5a,mod5b,mod5c) %>% rownames_to_column() %>% arrange(AIC))
 ```

### 2018-04-06 manuscriptAnalysis/linearGR_ModelsMap.Rmd
sort out isYOY in det model and downstream

---
title: "linearGR_Models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)

library(lme4)
library(tidyverse)
```

```{r load data}

load(file = paste0('D:/projects/linkedModels/data/out/dG_bktbntats1997_forLmer.RData')) # made by running mainAnalysis.R with speciesGr = c("bkt", "bnt","ats") through ddG[[ii]] <- dddG[[ii]] %>% prepareDataForJags("growth")

d2 <- data.frame(
  #sampleNumber=ddG[[1]][[2]]$sampleNumber,

  ind=ddG[[1]][[1]]$ind,
  river=ddG[[1]][[1]]$riverDATA,
  season=ddG[[1]][[1]]$season,
  year=ddG[[1]][[1]]$year,
  species=ddG[[1]][[1]]$species,
  sampleNumber=ddG[[1]][[1]]$sampleNumber,
  isYOY=ddG[[1]][[1]]$isYOYDATA,
  length=ddG[[1]][[1]]$lengthDATAStd,
  lengthByYear=ddG[[1]][[1]]$lengthDATAStd_ByYOY_Year,
  grLength=ddG[[1]][[1]]$grNotUse,
  tempStd=ddG[[1]][[1]]$tempStd,
  flowStd=ddG[[1]][[1]]$flowStd,
  countPStd=ddG[[1]][[1]]$countPAllSppStd,

  countPStdBKT=ddG[[1]][[1]]$countPStdBKT,
  countPStdBNT=ddG[[1]][[1]]$countPStdBNT,
  countPStdATS=ddG[[1]][[1]]$countPStdATS
  )

d <- d2 %>% filter(
  #  species == as.numeric(speciesInGr),
    !is.na(grLength)
  )
d <- d %>% mutate( tempStd2 = tempStd^2, flowStd2 = flowStd^2, countPStd2 = countPStd^2, length2 = length^2,
                   countPStdBKT2 = countPStdBKT^2,
                   countPStdBNT2 = countPStdBNT^2,
                   countPStdATS2 = countPStdATS^2,
                   isYOY = as.factor(isYOY), season = as.factor(season), river = as.factor(river), species = as.factor(species)
                 )
d$grLength <- ifelse(d$species == 2 & d$river == 3,NA,d$grLength)

mod <- list()

bySpecies <- d %>% 
  filter( species %in% c(1,2,3) ) %>%
  group_by(species) %>% 
  nest()

# turn factor off for ATS so the models run for all three spp
bySpecies$data[[3]]$river <- as.numeric(bySpecies$data[[3]]$river)
```

```{r}

ggplot(d, aes(sampleNumber,countPStdBKT)) + geom_point() + geom_line() + facet_grid(isYOY~river)
ggplot(d, aes(sampleNumber,countPStdBNT)) + geom_point() + geom_line() + facet_grid(isYOY~river)
ggplot(d, aes(year,countPStdBNT, color=isYOY)) + geom_point() + geom_line() + facet_grid(season~river)
ggplot(d, aes(sampleNumber,countPStdATS)) + geom_point() + geom_line() + facet_wrap(~river)

```

Try new, more flexible model structure

```{r}

mod[[1]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                  isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                  isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                  isYOY * river * season * ( tempStd * flowStd * length ) +
                  isYOY * river * season * ( length * countPStdBKT ) +
                  isYOY * river * season * ( length * countPStdBNT ) +
                  isYOY * river * season * ( length * countPStdATS ) +

                  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                  # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                  isYOY * river * season * ( length2 * countPStdBKT2 ) +
                  isYOY * river * season * ( length2 * countPStdBNT2 ) +
                  isYOY * river * season * ( length2 * countPStdATS2 ) +

   (1|ind), data = df ) }

mod[[2]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                  isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                  isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                  # isYOY * river * season * ( tempStd * flowStd * length ) +
                  # isYOY * river * season * ( length * countPStdBKT ) +
                  # isYOY * river * season * ( length * countPStdBNT ) +
                  # isYOY * river * season * ( length * countPStdATS ) +                
                  # 
                  # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                  # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                  # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                  # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                  # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                  # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                  # isYOY * river * season * ( length2 * countPStdATS2 ) +

   (1|ind), data = df ) }

mod[[3]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                   isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                   isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                   isYOY * river * season * ( tempStd * flowStd * length ) +
                   # isYOY * river * season * ( length * countPStdBKT ) +
                   # isYOY * river * season * ( length * countPStdBNT ) +
                   # isYOY * river * season * ( length * countPStdATS ) +

                   isYOY * river * season * ( tempStd2 * flowStd2 ) +
                   # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                   # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                   # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                   # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                   # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                   # isYOY * river * season * ( length2 * countPStdATS2 ) +

  (1|ind), data = df ) }

mod[[4]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 ) +
                         isYOY * river * season * ( countPStdBKT2 ) +
                         isYOY * river * season * ( countPStdBNT2 ) +
                         isYOY * river * season * ( countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[5]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 ) +
                         isYOY * river * season * ( countPStdBNT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[6]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[7]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[8]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[9]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[10]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[11]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                       #  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                       #   isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[12]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                       #  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[13]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[14]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

mod[[15]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * river * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = df ) }

```

```{r}

bySpecies <- bySpecies %>%
   mutate(  #model1 =  map(data, mod[[1]]),
  #          model2 =  map(data, mod[[2]]),
  #          model3 =  map(data, mod[[3]]),
  #          model4 =  map(data, mod[[4]]),
  #          model5 =  map(data, mod[[5]]),
  #          model6 =  map(data, mod[[6]]),
  #          model7 =  map(data, mod[[7]]),
  #          model8 =  map(data, mod[[8]]),
          # model9 =  map(data, mod[[9]]),
          # model10 = map(data, mod[[10]]),
          # model11 = map(data, mod[[11]]),
         #  model12 = map(data, mod[[12]]),
         # model13 = map(data, mod[[13]]),
         # model14 = map(data, mod[[14]]),
          model15 = map(data, mod[[15]])
        )

o <- bySpecies
b <- AIC(o$model1[[1]],o$model2[[1]],o$model3[[1]],o$model4[[1]],o$model5[[1]],o$model6[[1]],o$model7[[1]],o$model8[[1]],o$model9[[1]],o$model10[[1]],o$model12[[1]],o$model13[[1]],o$model14[[1]]) %>% rownames_to_column() %>% arrange(AIC) #bkt
n <- AIC(o$model1[[2]],o$model2[[2]],o$model3[[2]],o$model4[[2]],o$model5[[2]],o$model6[[2]],o$model7[[2]],o$model8[[2]],o$model9[[2]],o$model10[[2]],o$model12[[2]],o$model13[[2]],o$model14[[2]]) %>% rownames_to_column() %>% arrange(AIC)#bnt
a <- AIC(o$model1[[3]],o$model2[[3]],o$model3[[3]],o$model4[[3]],o$model5[[3]],o$model6[[3]],o$model7[[3]],o$model8[[3]],o$model9[[3]],o$model10[[3]],o$model12[[3]],o$model13[[3]],o$model14[[3]]) %>% rownames_to_column() %>% arrange(AIC)#ats

(all <- data.frame(b,n,a))

```

### 2018-04-06 R/detectionModelFunctions.R

@@ -63,7 +63,7 @@ getDensities <- function(ddddDIn,ddDIn, meanOrIter = "mean", sampleToUse = sampl
 
   counts <- ddddDIn %>%
     addxxxxN() %>%
-    distinct(species,season,riverOrdered,year,isYOYN,speciesN,seasonN,riverN,yearN,
+    distinct(isYOYN,species,season,riverOrdered,year,speciesN,seasonN,riverN,yearN,
              nAllFishBySpecies,nAllFish,massAllFishBySpecies,massAllFish)
 
   if ( meanOrIter == 'mean') dd <- ddDIn$q50$pBetaInt
@@ -92,10 +92,11 @@ getDensities <- function(ddddDIn,ddDIn, meanOrIter = "mean", sampleToUse = sampl
   p <- left_join( p, counts, by = c('isYOYN','speciesN','seasonN','riverN','yearN') ) %>%
          mutate( nAllFishBySpeciesP = nAllFishBySpecies/p )
 
-  # get counts of all species by summing nAllFishBySpeciesP across species
+  # get counts of each species by summing nAllFishBySpeciesP for each species
+  # summing over isYOY
   p2 <- p %>%
- #   group_by(speciesN,seasonN,riverN,yearN) %>%
-    group_by(isYOYN,seasonN,riverN,yearN) %>%
+    group_by(speciesN,seasonN,riverN,yearN) %>%
+ #   group_by(seasonN,riverN,yearN) %>%
     summarize( nAllFishP = sum(nAllFishBySpeciesP, na.rm=T))
 
   p <- left_join(p,p2)

### 2018-04-06 R/growthModelFunctions.R

@@ -413,21 +413,21 @@ adjustCounts <- function( cdIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
   }
 
   denForMerge <- den %>%
-    dplyr::select(isYOYN,species, season, riverOrdered, year, nAllFishBySpeciesP, nAllFishP, massAllFishBySpecies, massAllFish, meanOrIter, iterIn) %>%
+    dplyr::select(species, season, riverOrdered, year, nAllFishBySpeciesP, nAllFishP, massAllFishBySpecies, massAllFish, meanOrIter, iterIn) %>%
   #  filter( !is.na(nAllFishBySpeciesP) ) %>%
     arrange(species,riverOrdered,year,season)
 
-  # counts by species
+  # stats for counts by species
   denForMergeSummaryBySpecies <- denForMerge %>%
-    group_by( isYOYN,species,season,riverOrdered ) %>%
+    group_by( species,season,riverOrdered ) %>%
     summarize( nAllFishBySpeciesPMean = mean( nAllFishBySpeciesP, na.rm = T ),
                nAllFishBySpeciesPSD =     sd( nAllFishBySpeciesP, na.rm = T),
                massAllFishBySpeciesMean = mean( massAllFishBySpecies, na.rm = T ),
                massAllFishBySpeciesSD =     sd( massAllFishBySpecies, na.rm = T))
 
-  # counts for all species
+  # stats for counts for all species
   denForMergeSummary <- denForMerge %>%
-    group_by( isYOYN,season,riverOrdered ) %>%
+    group_by( season,riverOrdered ) %>%
     summarize( nAllFishPMean = mean( nAllFishP, na.rm = T ),
                nAllFishPSD =     sd( nAllFishP, na.rm = T),
                massAllFishMean = mean( massAllFish, na.rm = T ),
@@ -465,7 +465,7 @@ adjustCounts <- function( cdIn,ddDIn,ddddDIn,meanOrIterIn,sampleToUse ){
   #####
   # counts by species in separate columns
   nAllFishBySpeciesPStdBySpp <- denForMerge_possibleOccasions %>%
-    dplyr::select(isYOYN,species, season, riverOrdered, year, nAllFishBySpeciesPStd) %>%
+    dplyr::select(species, season, riverOrdered, year, nAllFishBySpeciesPStd) %>%
     spread(key=species, value=nAllFishBySpeciesPStd, fill = -2.5) %>%
[…]

### 2018-04-06 R/prepareDataForJags_Nimble.R

@@ -201,6 +201,7 @@ prepareDataForJags_Nimble <- function(d,modelType){
                   lengthDATAStd_ByYOY_Year = d$lengthDATALnStd_ByYOY_Year,
                   riverDATA = d$riverN,
                   ind = d$tagIndexJags,
+                  sampleNumber = d$sampleIndex,
                   nRivers = nRivers,
                   nSpecies = nSpecies,
                   nInd = nInd,

### 2018-04-06 nimble/mainAnalysis_Nimble.R

@@ -50,7 +50,7 @@ riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),l
 
 minCohort <- 1997#1995 # >=
 maxSampleInterval <- 200 # <
-runDetectionModelTF <- FALSE
+runDetectionModelTF <- TRUE
 runCrossValidationTF <- FALSE
 percentLeftOut <- 10
 

### 2018-05-16 manuscriptAnalysis/linearGR_ModelsMap_BKT.Rmd
updated prediction functions to include spp-specific variables

---
title: "linearGR_Models"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)

library(lme4)
library(caret)
library(tidyverse)
```

```{r load data}

load(file = paste0('D:/projects/linkedModels/data/out/dG_bktbntats1997_forLmer.RData')) # made by running mainAnalysis_Nimble.R with speciesGr = c("bkt", "bnt","ats") through ddG[[ii]] <- dddG[[ii]] %>% prepareDataForJags("growth")

d2 <- data.frame(
  #sampleNumber=ddG[[1]][[2]]$sampleNumber,

  ind=ddG[[1]][[1]]$ind,
  river=ddG[[1]][[1]]$riverDATA,
  season=ddG[[1]][[1]]$season,
  year=ddG[[1]][[1]]$year,
  species=ddG[[1]][[1]]$species,
  sampleNumber=ddG[[1]][[1]]$sampleNumber,
  isYOY=ddG[[1]][[1]]$isYOYDATA,
  length=ddG[[1]][[1]]$lengthDATAStd,
  lengthByYear=ddG[[1]][[1]]$lengthDATAStd_ByYOY_Year,
  grLength=ddG[[1]][[1]]$grNotUse,
  tempStd=ddG[[1]][[1]]$tempStd,
  flowStd=ddG[[1]][[1]]$flowStd,
  countPStd=ddG[[1]][[1]]$countPAllSppStd,

  countPStdBKT=ddG[[1]][[1]]$countPStdBKT,
  countPStdBNT=ddG[[1]][[1]]$countPStdBNT,
  countPStdATS=ddG[[1]][[1]]$countPStdATS,

  countPBKT=ddG[[1]][[1]]$cBKTStd,
  countPBNT=ddG[[1]][[1]]$cBNTStd,
  countPATS=ddG[[1]][[1]]$cATSStd,

  ATS01DATA=ddG[[1]][[1]]$ATS01DATA
  )

d <- d2 %>% filter(
  #  species == as.numeric(speciesInGr),
    !is.na(grLength),
    !is.na(countPStd) #removes 5 obs
  )

d <- d %>% mutate( tempStd2 = tempStd^2, 
                   flowStd2 = flowStd^2, 
                   countPStd2 = countPStd^2, 
                   length2 = length^2, lengthByYear2 = lengthByYear^2,
                   countPStdBKT2 = countPStdBKT^2,
                   countPStdBNT2 = countPStdBNT^2,
                   countPStdATS2 = countPStdATS^2,
                   isYOY = as.factor(isYOY), season = as.factor(season), 
                   river = as.factor(river), species = as.factor(species)

                 )
d$grLength <- ifelse(d$species == 2 & d$river == 3, NA, d$grLength)
d$grLength <- ifelse(d$species %in% c('2','3') & d$isYOY == 1 & d$season == "2", NA, d$grLength)
d$grLength <- ifelse(d$grLength < -0.025, NA, d$grLength)

d <- d %>%
  mutate(
    cBKTStd = as.numeric(scale(countPBKT)),
    cBNTStd = as.numeric(scale(countPBNT)),
    cATSStd = as.numeric(scale(countPATS)),
    cBKTStd2 = cBKTStd^2,
    cBNTStd2 = cBNTStd^2,
    cATSStd2 = cATSStd^2
  )

#turn off very low densities of ATS in jimmy 
#d$cATSStd <- ifelse(d$river %in% c('2') , NA, d$cATSStd)
#d$cATSStd2 <- ifelse(d$river %in% c('2') , NA, d$cATSStd2)

mod <- list()

bySpecies <- d %>% 
  filter( species %in% c(1,2,3) ) %>%
  group_by(species) %>% 
  nest()

# turn factor off for ATS so the models run for all three spp
bySpecies$data[[3]]$river <- as.numeric(bySpecies$data[[3]]$river)

```

```{r}
# -2.5 values are mostly from season==2 and isYOY==1
ggplot(d, aes(sampleNumber,cBKTStd)) + geom_point() + geom_line() + facet_grid(season~river)
ggplot(d, aes(sampleNumber,cBNTStd)) + geom_point() + geom_line() + facet_grid(season~river)
ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_grid(season~river)

ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_wrap(~river)

```

```{r}

ggplot(d, aes(sampleNumber,grLength)) + geom_point()  + facet_grid(species~river+season)

ggplot(d, aes(cBKTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
ggplot(d, aes(cBNTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
ggplot(d, aes(cATSStd,grLength)) + geom_point()  + facet_grid(species~river+season)

```

```{r}
pairs(d[,c('countPStd','countPStdBKT_01','countPStdBNT_01','countPStdATS_01')])
pairs(d[,c('countPBKT','countPBNT','countPATS')])
pairs(d[,c('cBKTStd','cBNTStd','cATSStd','tempStd','flowStd')])
pairs(d[,c('tempStd2','flowStd2','tempStd','flowStd')])
d20 <- d
d20[d20 == -2.5] <- NA
pairs(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')])
round(cor(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')], use="complete.obs"),2)
```

Try new, more flexible model structure

```{r}

mod[[1]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   (1|ind), data = df ) }

mod[[2]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd + 
                   lengthByYear  +
                   (1|ind), data = df ) }

mod[[3]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   (1|ind), data = df ) } 
# 3 is better for bkt

# need squared term for flow or temp?
mod[[4]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * tempStd2 + 
                   isYOY * river * season * flowStd2  +
                   (1|ind), data = df ) }

mod[[5]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * tempStd2 * flowStd2  +
                   (1|ind), data = df ) }

mod[[6]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * tempStd2 + 
                   (1|ind), data = df ) }

mod[[7]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * flowStd2  +
                   (1|ind), data = df ) } 
# 3 is best for bkt, bnt
# 5 is best for ATS
```
        rowname  df       AIC     rowname.1 df.1     AIC.1     rowname.2 df.2     AIC.2
1 o$model3[[1]] 132 -24138.75 o$model3[[2]]   60 -11185.96 o$model5[[3]]   53 -27273.26
2 o$model1[[1]] 130 -24066.23 o$model7[[2]]   74 -11185.65 o$model4[[3]]   46 -27271.94
3 o$model2[[1]] 131 -24051.02 o$model6[[2]]   74 -11140.56 o$model7[[3]]   39 -26891.76
4 o$model6[[1]] 164 -24031.80 o$model4[[2]]   88 -11113.99 o$model6[[3]]   39 -26866.52
5 o$model5[[1]] 226 -23972.19 o$model1[[2]]   58 -11093.02 o$model3[[3]]   32 -26711.17
6 o$model7[[1]] 164 -23945.62 o$model2[[2]]   59 -11076.95 o$model1[[3]]   30 -26675.04
7 o$model4[[1]] 196 -23919.37 o$model5[[2]]  102 -11021.51 o$model2[[3]]   31 -26664.86

```{r}

mod[[8]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   isYOY * season * cBKTStd +
                   (1|ind), data = df ) }

mod[[9]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   isYOY * season * cBNTStd +
                   (1|ind), data = df ) }

mod[[10]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   isYOY *         season * cATSStd +
                   (1|ind), data = df ) }

mod[[11]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                  isYOY * lengthByYear  +
                  isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd +
                  isYOY *         season * cATSStd +
                  (1|ind), data = df ) }

mod[[12]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * season * cBKTStd * cBNTStd * cATSStd +
                   (1|ind), data = df ) }

mod[[13]] <- function(df) {
  print(c('mod = 13' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear +
                   isYOY * season * cBKTStd * cBNTStd +
                   (1|ind), data = df ) } 
```

1  o$model11[[1]] 196 -24757.35 o$model13[[2]]   81 -11300.64 o$model12[[3]]   81 -29435.49
2   o$model8[[1]] 140 -24427.44  o$model9[[2]]   67 -11258.70 o$model11[[3]]   53 -28160.01
3  o$model13[[1]] 156 -24407.24  o$model8[[2]]   67 -11227.08 o$model13[[3]]   53 -27792.61
4  o$model12[[1]] 188 -24354.95 o$model11[[2]]   95 -11217.75  o$model8[[3]]   39 -27393.12
5   o$model3[[1]] 132 -24138.75 o$model10[[2]]   67 -11204.81  o$model5[[3]]   53 -27273.26
6   o$model9[[1]] 140 -24119.50  o$model3[[2]]   60 -11185.96  o$model4[[3]]   46 -27271.94
7  o$model10[[1]] 140 -24084.14  o$model7[[2]]   74 -11185.65  o$model9[[3]]   39 -26895.35
8   o$model1[[1]] 130 -24066.23 o$model12[[2]]  109 -11148.99  o$model7[[3]]   39 -26891.76
9   o$model2[[1]] 131 -24051.02  o$model6[[2]]   74 -11140.56  o$model6[[3]]   39 -26866.52
10  o$model6[[1]] 164 -24031.80  o$model4[[2]]   88 -11113.99 o$model10[[3]]   39 -26735.14
11  o$model5[[1]] 226 -23972.19  o$model1[[2]]   58 -11093.02  o$model3[[3]]   32 -26711.17
12  o$model7[[1]] 164 -23945.62  o$model2[[2]]   59 -11076.95  o$model1[[3]]   30 -26675.04
13  o$model4[[1]] 196 -23919.37  o$model5[[2]]  102 -11021.51  o$model2[[3]]   31 -26664.86 
```{r}
mod[[14]] <- function(df) {
    print(c('mod = 14' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd * tempStd * flowStd +
                   isYOY * river * season * cBNTStd * tempStd * flowStd +
                   isYOY *         season * cATSStd * tempStd * flowStd +

                   (1|ind), data = df ) }

mod[[15]] <- function(df) {
    print(c('mod = 15' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd * tempStd +
                   isYOY * river * season * cBNTStd * tempStd +
                   isYOY *         season * cATSStd * tempStd +
                   isYOY * river * season * cBKTStd * flowStd +
                   isYOY * river * season * cBNTStd * flowStd +
                   isYOY *         season * cATSStd * flowStd +

                   (1|ind), data = df ) }

mod[[16]] <- function(df) {
    print(c('mod = 16' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd * tempStd +
                   isYOY * river * season * cBNTStd * tempStd +
                   isYOY *         season * cATSStd * tempStd +
                   (1|ind), data = df ) }

mod[[17]] <- function(df) {
    print(c('mod = 17' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd * flowStd +
                   isYOY * river * season * cBNTStd * flowStd +
                   isYOY *         season * cATSStd * flowStd +
                   (1|ind), data = df ) }

mod[[18]] <- function(df) {
    print(c('mod = 18' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd * ATS01DATA +
                   (1|ind), data = df ) }
```

1  o$model11[[1]] 196 -24757.35 o$model13[[2]]   81 -11300.64 o$model12[[3]]   81 -29435.49
2  o$model16[[1]] 258 -24687.75  o$model9[[2]]   67 -11258.70 o$model14[[3]]  116 -29023.66
3  o$model14[[1]] 378 -24667.16  o$model8[[2]]   67 -11227.08 o$model15[[3]]   95 -28852.96
4  o$model17[[1]] 258 -24658.77 o$model11[[2]]   95 -11217.75 o$model16[[3]]   74 -28765.54
5  o$model15[[1]] 319 -24637.70 o$model10[[2]]   67 -11204.81 o$model17[[3]]   74 -28385.96
6   o$model8[[1]] 140 -24427.44  o$model3[[2]]   60 -11185.96 o$model11[[3]]   53 -28160.01
7  o$model13[[1]] 156 -24407.24  o$model7[[2]]   74 -11185.65 o$model13[[3]]   53 -27792.61
8  o$model18[[1]] 164 -24402.75 o$model17[[2]]  130 -11178.95 o$model18[[3]]   53 -27529.84
9  o$model12[[1]] 188 -24354.95 o$model18[[2]]   88 -11160.65  o$model8[[3]]   39 -27393.12
10  o$model3[[1]] 132 -24138.75 o$model12[[2]]  109 -11148.99  o$model5[[3]]   53 -27273.26
11  o$model9[[1]] 140 -24119.50  o$model6[[2]]   74 -11140.56  o$model4[[3]]   46 -27271.94
12 o$model10[[1]] 140 -24084.14  o$model4[[2]]   88 -11113.99  o$model9[[3]]   39 -26895.35
13  o$model1[[1]] 130 -24066.23  o$model1[[2]]   58 -11093.02  o$model7[[3]]   39 -26891.76
14  o$model2[[1]] 131 -24051.02 o$model16[[2]]  130 -11088.10  o$model6[[3]]   39 -26866.52
15  o$model6[[1]] 164 -24031.80  o$model2[[2]]   59 -11076.95 o$model10[[3]]   39 -26735.14
16  o$model5[[1]] 226 -23972.19 o$model15[[2]]  164 -11076.43  o$model3[[3]]   32 -26711.17
17  o$model7[[1]] 164 -23945.62  o$model5[[2]]  102 -11021.51  o$model1[[3]]   30 -26675.04
18  o$model4[[1]] 196 -23919.37 o$model14[[2]]  196 -11020.01  o$model2[[3]]   31 -26664.86

```{r}

mod[[19]] <- function(df) {
    print(c('mod = 19' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd * lengthByYear +
                   isYOY * river * season * cBNTStd * lengthByYear +
                   isYOY *         season * cATSStd * lengthByYear  +

                   (1|ind), data = df ) }

mod[[20]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                  isYOY * lengthByYear  +
                  isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd +
                  isYOY *         season * cATSStd +
                  isYOY * river * season * tempStd^2  +
                  isYOY * river * season * flowStd^2  +
                  (1|ind), data = df ) }

```

```{r}

bySpecies <- bySpecies %>%
      mutate( model1 =  map(data, mod[[1]]) ) %>%
      mutate( model2 =  map(data, mod[[2]]) ) %>%
      mutate( model3 =  map(data, mod[[3]]) ) %>%
      mutate( model4 =  map(data, mod[[4]]) ) %>%
      mutate( model5 =  map(data, mod[[5]]) ) %>%
      mutate( model6 =  map(data, mod[[6]]) ) %>%
      mutate( model7 =  map(data, mod[[7]]) ) %>%
     mutate( model8 =  map(data, mod[[8]]) ) %>%
     mutate( model9 =  map(data, mod[[9]]) ) %>%
     mutate( model10 = map(data, mod[[10]]) ) %>%
     mutate( model11 = map(data, mod[[11]]) ) %>%
     mutate( model12 = map(data, mod[[12]]) ) %>%
     mutate( model13 = map(data, mod[[13]]) ) %>%
      mutate( model14 = map(data, mod[[14]]) ) %>%
      mutate( model15 = map(data, mod[[15]]) ) %>%
      mutate( model16 = map(data, mod[[16]]) ) %>%
      mutate( model17 = map(data, mod[[17]]) ) %>%
      mutate( model18 = map(data, mod[[18]]) ) %>%
     mutate( model19 = map(data, mod[[19]]) ) %>%
      mutate( model20 = map(data, mod[[20]])) #%>%
     # mutate( model21 = map(data, mod[[21]])) %>%
    #  mutate( model22 = map(data, mod[[22]])) %>%
    #  mutate( model23 = map(data, mod[[23]]))

#2 or 5 fish have lengthByYear = NA whcih gives warining of diff # of observations when include mod with lengthByYear

o <- bySpecies
b <- AIC(o$model1[[1]],
         o$model2[[1]],
         o$model3[[1]],
         o$model4[[1]],
         o$model5[[1]],
         o$model6[[1]],
         o$model7[[1]],
         o$model8[[1]],
         o$model9[[1]],
         o$model10[[1]],
         o$model11[[1]],
         o$model12[[1]],
         o$model13[[1]],
           o$model14[[1]],
           o$model15[[1]],
           o$model16[[1]],
           o$model17[[1]],
           o$model18[[1]],
          o$model19[[1]],
          o$model20[[1]]
         # o$model21[[1]],
         # o$model22[[1]],
         # o$model23[[1]]
         ) %>% rownames_to_column() %>% arrange(AIC) #bkt
n <- AIC(o$model1[[2]],
         o$model2[[2]],
         o$model3[[2]],
         o$model4[[2]],
         o$model5[[2]],
         o$model6[[2]],
         o$model7[[2]],
         o$model8[[2]],
         o$model9[[2]],
         o$model10[[2]],
         o$model11[[2]],
         o$model12[[2]],
         o$model13[[2]],
           o$model14[[2]],
           o$model15[[2]],
           o$model16[[2]],
           o$model17[[2]],
           o$model18[[2]],
          o$model19[[2]],
          o$model20[[2]]
         # o$model21[[2]],
         # o$model22[[2]],
         # o$model23[[2]]
         ) %>% rownames_to_column() %>% arrange(AIC)#bnt
a <- AIC(o$model1[[3]],
         o$model2[[3]],
         o$model3[[3]],
         o$model4[[3]],
         o$model5[[3]],
         o$model6[[3]],
         o$model7[[3]],
         o$model8[[3]],
         o$model9[[3]],
         o$model10[[3]],
         o$model11[[3]],
         o$model12[[3]],
         o$model13[[3]],
           o$model14[[3]],
           o$model15[[3]],
           o$model16[[3]],
           o$model17[[3]],
           o$model18[[3]],
           o$model19[[3]],
          o$model20[[3]]
         # o$model21[[3]],
         # o$model22[[3]],
         # o$model23[[3]]
          ) %>% rownames_to_column() %>% arrange(AIC)#ats

(all <- data.frame(b,n,a))

```

```{r}

#d[d==-2.5] <- 0

#ftable(d$isYOY,d$species,d$river,d$season,d$year)
tmp1 <- 
 lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                  isYOY * season * cBKTStd * cBNTStd * cATSStd +

   (1|ind) + (1|river), data = bySpecies$data[[1]] )

tmp2 <- 
 lmer( grLength ~ isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd  +
                  isYOY * season * cATSStd  +

       #  
      #            isYOY * river * season * cBNTStd * tempStd * flowStd+
               #   isYOY *         season * cATSStd * tempStd * flowStd +

   (1|ind) , data = bySpecies$data[[1]]) #bySpecies$data[[1]] )

tmp3 <- 
 lmer( grLength ~ isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd +
                  isYOY * river * season * cATSStd  +
                  isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
         cBKTStd * cBNTStd * cATSStd * tempStd * flowStd +
                   # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                   # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                   # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                  # isYOY * river * season * ( tempStd2 * flowStd2 ) + 
                  # 
                 #  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                 #  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                #   isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                  # # isYOY * river * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                  # isYOY * river * season * ( length2 * countPStdBKT2 ) +
                  # isYOY * river * season * ( length2 * countPStdBNT2 ) +
                  # isYOY * river * season * ( length2 * countPStdATS2 ) +

   (1|ind), data = bySpecies$data[[1]] )#bySpecies$data[[2]] )

tmp4 <- 
 lmer( grLength ~  isYOY * river * season * tempStd * flowStd  +
                   #isYOY * river * season * tempStd2 * flowStd2  +
                   isYOY * season * cBKTStd * cBNTStd * cATSStd +
                   isYOY * season * cBKTStd2 * cBNTStd2 * cATSStd2 +

   (1|ind) , data = bySpecies$data[[2]] )#bySpecies$data[[2]] )

x <- model.matrix(~ isYOY * river * season * tempStd * flowStd  +
                   #isYOY * river * season * tempStd2 * flowStd2  +
                   isYOY * season * cBKTStd * cBNTStd * cATSStd +
                   isYOY * season * cBKTStd2 * cBNTStd2 * cATSStd2 +
   (1|ind) , data = bySpecies$data[[2]])

xx <- findLinearCombos((x))
getBadCols <- function(col){
  cols <- xx$linearCombos[[col]]
  badCols1 <- x[,cols]
  badCols <- dimnames(badCols1)[[2]]
  return(badCols)
}

getBadCols(41)

# removed dimnames
dimnames(x)[[2]][xx$remove]

d %>% filter(species==1, river==4) %>% select(cATSStd) %>% distinct()

AIC(tmp1,tmp2,tmp3) %>% rownames_to_column() %>% arrange(AIC)

ggplot(d%>%filter(species==2), aes(lengthByYear,grLength, color=isYOY)) + geom_point() + geom_smooth(method='lm') + facet_grid(isYOY+river~season)
ggplot(d%>%filter(species==2), aes(flowStd,grLength, color=isYOY)) + geom_point() + geom_smooth(method='lm') + facet_grid(isYOY~season)

ggplot(d%>%filter(species==2), aes(lengthByYear,countPStdATS, color=isYOY)) + geom_point() + geom_smooth(method='lm') + facet_grid(isYOY~season)

d%>%filter(species==2 & season==2 &isYOY==1)

d$countPStdATS <- ifelse(d$species %in% c('2') & d$isYOY == 1 & d$season == "2", NA, d$countPStdATS)
d$countPStdATS <- ifelse( d$river %in% c("3","4"), NA, d$countPStdATS)

d$cBNTStd <- ifelse(d$river %in% c('4') , NA, d$cBNTStd)
d$countPStdATS <- ifelse( d$river %in% c("3","4"), NA, d$countPStdATS)
```

```{r}

mod[[1]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * season * cBKTStd * cBNTStd * cATSStd +

                   (1|ind), data = df ) }

mod[[2]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                  isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd +
                  isYOY * river * season * cBNTStd +

                  (1|ind), data = df ) }

mod[[3]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * season * cBKTStd * cBNTStd +

                   (1|ind), data = df ) }

#mod[[4]] <- function(df) {
#  lmer( grLength ~ isYOY * river * season * cBKTStd * cBKTStd * cBKTStd +

#                   (1|ind), data = df ) }

mod[[5]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 ) +
                         isYOY * river * season * ( countPStdBNT2_01 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[6]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[7]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[8]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         isYOY * river * season * ( tempStd2 * flowStd2  ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[9]] <- function(df) { lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[10]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[11]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                       #  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                       #   isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[12]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                       #  isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[13]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[14]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

mod[[15]] <- function(df) {  lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS_01 ) +
                         isYOY * river * season * ( tempStd * flowStd * lengthByYear ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBKT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdBNT_01 ) +
                         # isYOY * river * season * ( lengthByYear * countPStdATS_01 ) +

                        # isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBKT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdBNT2_01 ) +
                         isYOY * river * season * ( tempStd2 * flowStd2 * countPStdATS2_01 ) +
                         # # isYOY * river * season * ( tempStd2 * flowStd2 * lengthByYear2 ) + # model error with this line in
                         # isYOY * river * season * ( lengthByYear2 * countPStdBKT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdBNT2_01 ) +
                         # isYOY * river * season * ( lengthByYear2 * countPStdATS2_01 ) +

                         (1|ind), data = df ) }

```

### 2018-05-16 R/analyzeOutputFunctions.R

@@ -16,14 +16,27 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
   grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="int")
 
   # get grBeta in df format and merge in grInt
- # grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),species=species,season=1:nSeasons,river=riverOrderedIn), label.x="est")
-  grBeta1 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="est")
+  grBeta3 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="est")
 
-  grBeta <- spread( grBeta1, key = beta, value = est, sep = "" ) %>%
+  grBeta2 <- spread( grBeta3, key = beta, value = est, sep = "" ) %>%
     left_join( .,grInt )
+
+  # grBetaBNT, 2 rivers only
+  grBetaBNT <- array2df(d$sims.list$grBetaBNT, levels = list(iter=NA,betaBNT=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:(4-(4-constants$nRivers))]), label.x="est")
+
+  grBeta1 <- spread( grBetaBNT, key = betaBNT, value = est, sep = "" ) %>%
+    left_join( .,grBeta2 )
+
+  # grBetaATS, no river
+  grBetaATS <- array2df(d$sims.list$grBetaATS, levels = list(iter=NA,betaATS=NA,isYOY=c(0,1),season=1:constants$nSeasons), label.x="est")
+
+  grBeta <- spread( grBetaATS, key = betaATS, value = est, sep = "" ) %>%
+    left_join( .,grBeta1 )
+
 
   sampleIntervalMean <- array2df(sampleIntervalMeanIn, levels = list( river=riverOrderedIn[1:constants$nRivers],season=1:constants$nSeasons,species=1:constants$nSpecies), label.x = "interval")
[…]

### 2018-05-16 R/growthModelFunctions.R

@@ -11,7 +11,7 @@ runGrowthModel_Nimble <- function(d,mcmcInfo){
   nBetas <- 7
   nBetasSigma <- 4
   nBetasATS <- 1
-  nBetasBNT <- 2
+  nBetasBNT <- 1
 
   source("./R/growthModelFunctions_Code.R")
   code <- codeSpp[[as.numeric(speciesInGr)]]

### 2018-05-16 R/growthModelFunctions_Code.R

@@ -1,4 +1,4 @@
-
+library(nimble)
 
 codeSpp <- list()
 
@@ -17,13 +17,15 @@ codeSpp[[1]] <- nimbleCode({
 
       grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthDATA[evalRows[i]] +
 
-      grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]+# * BKT01DATA[evalRows[i]] +
+      grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] +
       grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] +
       grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]] +
       grBeta[ 5, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] * flowStd[evalRows[i]] +
 
       grBeta[ 6, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd2[evalRows[i]] +
       grBeta[ 7, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd2[evalRows[i]] +
+
+      grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
 
       #    grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] * cBNTStd[evalRows[i]] +
 

### 2018-05-16 nimble/mainAnalysis_Nimble.R

@@ -297,21 +297,21 @@ iter=1
   itersForPred <- sample( 1:mcmcInfo$nSamples, nItersForPred )
 
   # predictions across the grid
-  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","count") )#######################
-  p$variable <- "mean"
+  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","cBKT", "cBNT", "cATS") )#######################
+  #p$variable <- "mean"
   # predictions of sigma across the grid
-  pSigma <- getPredictionSigma( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","count") )
-  pSigma$variable <- "sd"
+  pSigma <- getPredictionSigma( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","cBKT", "cBNT", "cATS") )
+  #pSigma$variable <- "sd"
   # combine predicted growth rates and sigma in predicted growth rates to get cv in predicted growth rates
-  pBoth <- left_join( p,pSigma, by = c('len','count','flow','temp','iter','isYOY','season','river')) %>%
+  pBoth <- left_join( p,pSigma, by = c('len',"cBKT", "cBNT", "cATS",'flow','temp','iter','isYOY','season','river')) %>%
     mutate(predCV = predGrSigma/predGr)
-  pBoth$variable <- "cv"
+  #pBoth$variable <- "cv"
   pBoth$predCV <- ifelse(pBoth$predCV > 10, NA, pBoth$predCV) # to avoid very large CVs when gr is very small
   pBoth$predCV <- ifelse(pBoth$predCV < 0, NA, pBoth$predCV) # to avoid negative CVs when gr is very small and negative
 
   save(pBoth,file = paste0("./data/out/P_ForMike_",speciesGr,".RData"))
 
-     #
+  #
   # graph function, in analyzeOutputFunctions.R
 
   plotPred(p, "predGr", "len", 1, speciesGr)

### 2018-06-01 manuscriptAnalysis/linearGR_ModelsMap_BKT.Rmd
after model selection

@@
 
-d <- d2 %>% filter(
-  #  species == as.numeric(speciesInGr),
-    !is.na(grLength),
+d <- d2 %>% filter( !is.na(grLength) )
+
+d <- d %>% filter(
  !is.na(countPStd) #removes 5 obs
@@
 # -2.5 values are mostly from season==2 and isYOY==1
-ggplot(d, aes(sampleNumber,cBKTStd)) + geom_point() + geom_line() + facet_grid(season~river)
-ggplot(d, aes(sampleNumber,cBNTStd)) + geom_point() + geom_line() + facet_grid(season~river)
-ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_grid(season~river)
-
-ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_wrap(~river)
+# ggplot(d, aes(sampleNumber,cBKTStd)) + geom_point() + geom_line() + facet_grid(season~river)
+# ggplot(d, aes(sampleNumber,cBNTStd)) + geom_point() + geom_line() + facet_grid(season~river)
+# ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_grid(season~river)
+# 
+# ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_wrap(~river)
 
@@
 
-ggplot(d, aes(sampleNumber,grLength)) + geom_point()  + facet_grid(species~river+season)
-
-ggplot(d, aes(cBKTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
-ggplot(d, aes(cBNTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
-ggplot(d, aes(cATSStd,grLength)) + geom_point()  + facet_grid(species~river+season)
+# ggplot(d, aes(sampleNumber,grLength)) + geom_point()  + facet_grid(species~river+season)
+# 
+# ggplot(d, aes(cBKTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
+# ggplot(d, aes(cBNTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
+# ggplot(d, aes(cATSStd,grLength)) + geom_point()  + facet_grid(species~river+season)
 
@@
 ```{r}
-pairs(d[,c('countPStd','countPStdBKT_01','countPStdBNT_01','countPStdATS_01')])
-pairs(d[,c('countPBKT','countPBNT','countPATS')])
-pairs(d[,c('cBKTStd','cBNTStd','cATSStd','tempStd','flowStd')])
-pairs(d[,c('tempStd2','flowStd2','tempStd','flowStd')])
-d20 <- d
-d20[d20 == -2.5] <- NA
-pairs(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')])
-round(cor(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')], use="complete.obs"),2)
+# pairs(d[,c('countPStd','countPStdBKT_01','countPStdBNT_01','countPStdATS_01')])
+# pairs(d[,c('countPBKT','countPBNT','countPATS')])
+# pairs(d[,c('cBKTStd','cBNTStd','cATSStd','tempStd','flowStd')])
+# pairs(d[,c('tempStd2','flowStd2','tempStd','flowStd')])
+# d20 <- d
+# d20[d20 == -2.5] <- NA
+# pairs(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')])
+# round(cor(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')], use="complete.obs"),2)
 ```
@@
 
+# need length? NO
 mod[[1]] <- function(df) {
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   (1|ind), data = df ) }
+                   (1|ind) + (1|season), data = df ) }
 
@@
                    lengthByYear  +
-                   (1|ind), data = df ) }
+                   (1|ind) + (1|season), data = df ) } 
+```
 
+        rowname  df       AIC     rowname.1 df.1     AIC.1     rowname.2 df.2     AIC.2
+1 o$model1[[1]] 131 -24064.23 o$model1[[2]]   59 -11091.02 o$model1[[3]]   31 -26673.04
+2 o$model2[[1]] 132 -24049.02 o$model2[[2]]   60 -11074.95 o$model2[[3]]   32 -26662.86
+```{r}
+
+# need squared term for flow or temp?
 mod[[3]] <- function(df) {
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
-                   (1|ind), data = df ) } 
-# 3 is better for bkt
+                   isYOY * river * season * tempStd2 + 
+                   isYOY * river * season * flowStd2  +
+                   (1|ind) + (1|season), data = df ) }
 
-# need squared term for flow or temp?
 mod[[4]] <- function(df) {
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
-                   isYOY * river * season * tempStd2 + 
-                   isYOY * river * season * flowStd2  +
-                   (1|ind), data = df ) }
+                   isYOY * river * season * tempStd2 * flowStd2  +
+                   (1|ind) + (1|season), data = df ) }
 
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
-                   isYOY * river * season * tempStd2 * flowStd2  +
-                   (1|ind), data = df ) }
+                   isYOY * river * season * tempStd2 + 
+                   (1|ind) + (1|season), data = df ) }
 
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
-                   isYOY * river * season * tempStd2 + 
-                   (1|ind), data = df ) }
+                   isYOY * river * season * flowStd2  +
+                   (1|ind) + (1|season), data = df ) } 
+# keep out squared terms for now
+```
+
+        rowname  df       AIC     rowname.1 df.1     AIC.1     rowname.2 df.2     AIC.2
+1 o$model1[[1]] 131 -24064.23 o$model1[[2]]   59 -11091.02 o$model3[[3]]   45 -27221.73
+2 o$model2[[1]] 132 -24049.02 o$model6[[2]]   73 -11085.12 o$model4[[3]]   52 -27214.79
+3 o$model5[[1]] 163 -23950.60 o$model2[[2]]   60 -11074.95 o$model6[[3]]   38 -26849.65
+4 o$model6[[1]] 163 -23862.94 o$model5[[2]]   73 -11045.37 o$model5[[3]]   38 -26825.20
+5 o$model4[[1]] 226 -23856.48 o$model3[[2]]   87 -11011.79 o$model1[[3]]   31 -26673.04
+6 o$model3[[1]] 195 -23825.07 o$model4[[2]]  101 -10916.61 o$model2[[3]]   32 -26662.86
+```{r}
+# add species densities?
 
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
-                   isYOY * lengthByYear  +
-                   isYOY * river * season * flowStd2  +
-                   (1|ind), data = df ) } 
-# 3 is best for bkt, bnt
-# 5 is best for ATS
+                   isYOY * season * cBKTStd +
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[8]] <- function(df) {
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
+                   isYOY * season * cBNTStd +
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[9]] <- function(df) {
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
+                   isYOY *         season * cATSStd +
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[10]] <- function(df) {
+ lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                  isYOY * river * season * cBKTStd +
+                  isYOY * river * season * cBNTStd +
+                  isYOY *         season * cATSStd +
+                  (1|ind) + (1|season), data = df ) }
+
+mod[[11]] <- function(df) {
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * season * cBKTStd * cBNTStd * cATSStd +
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[12]] <- function(df) {
+  print(c('mod = 12' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * season * cBKTStd * cBNTStd +
+                   (1|ind) + (1|season), data = df ) }
+
+# stick with 10 - good for bkt and easiest to code in jags
 ```
+
           rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
-1 o$model3[[1]] 132 -24138.75 o$model3[[2]]   60 -11185.96 o$model5[[3]]   53 -27273.26
-2 o$model1[[1]] 130 -24066.23 o$model7[[2]]   74 -11185.65 o$model4[[3]]   46 -27271.94
-3 o$model2[[1]] 131 -24051.02 o$model6[[2]]   74 -11140.56 o$model7[[3]]   39 -26891.76
-4 o$model6[[1]] 164 -24031.80 o$model4[[2]]   88 -11113.99 o$model6[[3]]   39 -26866.52
-5 o$model5[[1]] 226 -23972.19 o$model1[[2]]   58 -11093.02 o$model3[[3]]   32 -26711.17
-6 o$model7[[1]] 164 -23945.62 o$model2[[2]]   59 -11076.95 o$model1[[3]]   30 -26675.04
-7 o$model4[[1]] 196 -23919.37 o$model5[[2]]  102 -11021.51 o$model2[[3]]   31 -26664.86
+1  o$model10[[1]] 195 -24650.05 o$model12[[2]]   80 -11203.21 o$model11[[3]]   80 -29379.29
+2   o$model7[[1]] 139 -24336.63  o$model8[[2]]   66 -11166.73 o$model10[[3]]   52 -28077.66
+3  o$model12[[1]] 155 -24316.48  o$model7[[2]]   66 -11129.29 o$model12[[3]]   52 -27717.41
+4  o$model11[[1]] 187 -24259.03 o$model10[[2]]   94 -11119.43  o$model7[[3]]   38 -27339.65
+5   o$model1[[1]] 131 -24064.23  o$model9[[2]]   66 -11108.18  o$model3[[3]]   45 -27221.73
+6   o$model2[[1]] 132 -24049.02  o$model1[[2]]   59 -11091.02  o$model4[[3]]   52 -27214.79
+7   o$model8[[1]] 139 -24045.93  o$model6[[2]]   73 -11085.12  o$model6[[3]]   38 -26849.65
+8   o$model9[[1]] 139 -24007.57  o$model2[[2]]   60 -11074.95  o$model8[[3]]   38 -26845.97
+9   o$model5[[1]] 163 -23950.60 o$model11[[2]]  108 -11049.99  o$model5[[3]]   38 -26825.20
+10  o$model6[[1]] 163 -23862.94  o$model5[[2]]   73 -11045.37  o$model9[[3]]   38 -26695.14
+11  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
+12  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86
 
@@
 
-mod[[8]] <- function(df) {
-  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
-                   isYOY * lengthByYear  +
-                   isYOY * season * cBKTStd +
-                   (1|ind), data = df ) }
-
-mod[[9]] <- function(df) {
-  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
-                   isYOY * lengthByYear  +
-                   isYOY * season * cBNTStd +
-                   (1|ind), data = df ) }
-
-mod[[10]] <- function(df) {
-  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
-                   isYOY * lengthByYear  +
-                   isYOY *         season * cATSStd +
-                   (1|ind), data = df ) }
-
-mod[[11]] <- function(df) {
- lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                  isYOY * lengthByYear  +
-                  isYOY * river * season * cBKTStd +
-                  isYOY * river * season * cBNTStd +
-                  isYOY *         season * cATSStd +
-                  (1|ind), data = df ) }
-
-mod[[12]] <- function(df) {
-  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
-                   isYOY * season * cBKTStd * cBNTStd * cATSStd +
-                   (1|ind), data = df ) }
+# squared density terms?
 
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear +
-                   isYOY * season * cBKTStd * cBNTStd +
-                   (1|ind), data = df ) } 
-```
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                   isYOY * river * season * cBKTStd2 +
 
-1  o$model11[[1]] 196 -24757.35 o$model13[[2]]   81 -11300.64 o$model12[[3]]   81 -29435.49
-2   o$model8[[1]] 140 -24427.44  o$model9[[2]]   67 -11258.70 o$model11[[3]]   53 -28160.01
-3  o$model13[[1]] 156 -24407.24  o$model8[[2]]   67 -11227.08 o$model13[[3]]   53 -27792.61
-4  o$model12[[1]] 188 -24354.95 o$model11[[2]]   95 -11217.75  o$model8[[3]]   39 -27393.12
-5   o$model3[[1]] 132 -24138.75 o$model10[[2]]   67 -11204.81  o$model5[[3]]   53 -27273.26
-6   o$model9[[1]] 140 -24119.50  o$model3[[2]]   60 -11185.96  o$model4[[3]]   46 -27271.94
-7  o$model10[[1]] 140 -24084.14  o$model7[[2]]   74 -11185.65  o$model9[[3]]   39 -26895.35
-8   o$model1[[1]] 130 -24066.23 o$model12[[2]]  109 -11148.99  o$model7[[3]]   39 -26891.76
-9   o$model2[[1]] 131 -24051.02  o$model6[[2]]   74 -11140.56  o$model6[[3]]   39 -26866.52
-10  o$model6[[1]] 164 -24031.80  o$model4[[2]]   88 -11113.99 o$model10[[3]]   39 -26735.14
-11  o$model5[[1]] 226 -23972.19  o$model1[[2]]   58 -11093.02  o$model3[[3]]   32 -26711.17
-12  o$model7[[1]] 164 -23945.62  o$model2[[2]]   59 -11076.95  o$model1[[3]]   30 -26675.04
-13  o$model4[[1]] 196 -23919.37  o$model5[[2]]  102 -11021.51  o$model2[[3]]   31 -26664.86 
-```{r}
+                   (1|ind) + (1|season), data = df ) }
+
 mod[[14]] <- function(df) {
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
-                   isYOY * river * season * cBKTStd * tempStd * flowStd +
-                   isYOY * river * season * cBNTStd * tempStd * flowStd +
-                   isYOY *         season * cATSStd * tempStd * flowStd +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                   isYOY * river * season * cBNTStd2 +
 
-                   (1|ind), data = df ) }
+                   (1|ind) + (1|season), data = df ) }
 
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
                    isYOY * river * season * cBKTStd +
@@
                    isYOY *         season * cATSStd +
-                   isYOY * river * season * cBKTStd * tempStd +
-                   isYOY * river * season * cBNTStd * tempStd +
-                   isYOY *         season * cATSStd * tempStd +
-                   isYOY * river * season * cBKTStd * flowStd +
-                   isYOY * river * season * cBNTStd * flowStd +
-                   isYOY *         season * cATSStd * flowStd +
-
-                   (1|ind), data = df ) }
+                   isYOY * river * season * cATSStd2 +
+                   (1|ind) + (1|season), data = df ) }
 
@@
                    isYOY *         season * cATSStd +
-                   isYOY * river * season * cBKTStd * tempStd +
-                   isYOY * river * season * cBNTStd * tempStd +
-                   isYOY *         season * cATSStd * tempStd +
-                   (1|ind), data = df ) }
+                   isYOY * river * season * cBKTStd2 +
+                   isYOY * river * season * cBNTStd2 +
+                   (1|ind) + (1|season), data = df ) }
+```
+Keep model16
+          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
+1  o$model16[[1]] 249 -24778.30 o$model16[[2]]  122 -11211.56 o$model11[[3]]   80 -29379.29
+2  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model15[[3]]   59 -28755.46
+3  o$model13[[1]] 226 -24689.16 o$model13[[2]]  108 -11167.05 o$model16[[3]]   66 -28318.31
+4  o$model10[[1]] 195 -24650.05  o$model8[[2]]   66 -11166.73 o$model14[[3]]   59 -28310.73
+5  o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model13[[3]]   59 -28306.10
+6   o$model7[[1]] 139 -24336.63  o$model7[[2]]   66 -11129.29 o$model10[[3]]   52 -28077.66
+7  o$model12[[1]] 155 -24316.48 o$model10[[2]]   94 -11119.43 o$model12[[3]]   52 -27717.41
+8  o$model11[[1]] 187 -24259.03  o$model9[[2]]   66 -11108.18  o$model7[[3]]   38 -27339.65
+9   o$model1[[1]] 131 -24064.23  o$model1[[2]]   59 -11091.02  o$model3[[3]]   45 -27221.73
+10  o$model2[[1]] 132 -24049.02  o$model6[[2]]   73 -11085.12  o$model4[[3]]   52 -27214.79
+11  o$model8[[1]] 139 -24045.93  o$model2[[2]]   60 -11074.95  o$model6[[3]]   38 -26849.65
+12  o$model9[[1]] 139 -24007.57 o$model11[[2]]  108 -11049.99  o$model8[[3]]   38 -26845.97
+13  o$model5[[1]] 163 -23950.60  o$model5[[2]]   73 -11045.37  o$model5[[3]]   38 -26825.20
+14  o$model6[[1]] 163 -23862.94 o$model15[[2]]  108 -11030.68  o$model9[[3]]   38 -26695.14
+15  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
+16  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86
 
+```{r}
+
+#add interaction btw bkt and bnt?
 mod[[17]] <- function(df) {
@@
                    isYOY *         season * cATSStd +
-                   isYOY * river * season * cBKTStd * flowStd +
-                   isYOY * river * season * cBNTStd * flowStd +
-                   isYOY *         season * cATSStd * flowStd +
-                   (1|ind), data = df ) }
+                   isYOY * river * season * cBKTStd2 +
+                   isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   (1|ind) + (1|season), data = df ) }
+```
+Keep 17
+          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
+1  o$model17[[1]] 272 -24796.58 o$model16[[2]]  122 -11211.56 o$model11[[3]]   80 -29379.29
+2  o$model16[[1]] 249 -24778.30 o$model17[[2]]  136 -11207.54 o$model15[[3]]   59 -28755.46
+3  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model16[[3]]   66 -28318.31
+4  o$model13[[1]] 226 -24689.16 o$model13[[2]]  108 -11167.05 o$model17[[3]]   73 -28313.67
+5  o$model10[[1]] 195 -24650.05  o$model8[[2]]   66 -11166.73 o$model14[[3]]   59 -28310.73
+6  o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model13[[3]]   59 -28306.10
+7   o$model7[[1]] 139 -24336.63  o$model7[[2]]   66 -11129.29 o$model10[[3]]   52 -28077.66
+8  o$model12[[1]] 155 -24316.48 o$model10[[2]]   94 -11119.43 o$model12[[3]]   52 -27717.41
+9  o$model11[[1]] 187 -24259.03  o$model9[[2]]   66 -11108.18  o$model7[[3]]   38 -27339.65
+10  o$model1[[1]] 131 -24064.23  o$model1[[2]]   59 -11091.02  o$model3[[3]]   45 -27221.73
+11  o$model2[[1]] 132 -24049.02  o$model6[[2]]   73 -11085.12  o$model4[[3]]   52 -27214.79
+12  o$model8[[1]] 139 -24045.93  o$model2[[2]]   60 -11074.95  o$model6[[3]]   38 -26849.65
+13  o$model9[[1]] 139 -24007.57 o$model11[[2]]  108 -11049.99  o$model8[[3]]   38 -26845.97
+14  o$model5[[1]] 163 -23950.60  o$model5[[2]]   73 -11045.37  o$model5[[3]]   38 -26825.20
+15  o$model6[[1]] 163 -23862.94 o$model15[[2]]  108 -11030.68  o$model9[[3]]   38 -26695.14
+16  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
+17  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86
+
+```{r}
+# add squared flow and temp back in? 
+# models with temp or flow squared don't work if have either bnt2 or bkt2 also in model
+# test which one to take out with interaction btw cBNT and cBKT in
 
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
                    isYOY * river * season * cBKTStd +
                    isYOY * river * season * cBNTStd +
-                   isYOY *         season * cATSStd * ATS01DATA +
-                   (1|ind), data = df ) }
-```
-
-1  o$model11[[1]] 196 -24757.35 o$model13[[2]]   81 -11300.64 o$model12[[3]]   81 -29435.49
-2  o$model16[[1]] 258 -24687.75  o$model9[[2]]   67 -11258.70 o$model14[[3]]  116 -29023.66
-3  o$model14[[1]] 378 -24667.16  o$model8[[2]]   67 -11227.08 o$model15[[3]]   95 -28852.96
-4  o$model17[[1]] 258 -24658.77 o$model11[[2]]   95 -11217.75 o$model16[[3]]   74 -28765.54
-5  o$model15[[1]] 319 -24637.70 o$model10[[2]]   67 -11204.81 o$model17[[3]]   74 -28385.96
-6   o$model8[[1]] 140 -24427.44  o$model3[[2]]   60 -11185.96 o$model11[[3]]   53 -28160.01
-7  o$model13[[1]] 156 -24407.24  o$model7[[2]]   74 -11185.65 o$model13[[3]]   53 -27792.61
-8  o$model18[[1]] 164 -24402.75 o$model17[[2]]  130 -11178.95 o$model18[[3]]   53 -27529.84
-9  o$model12[[1]] 188 -24354.95 o$model18[[2]]   88 -11160.65  o$model8[[3]]   39 -27393.12
-10  o$model3[[1]] 132 -24138.75 o$model12[[2]]  109 -11148.99  o$model5[[3]]   53 -27273.26
-11  o$model9[[1]] 140 -24119.50  o$model6[[2]]   74 -11140.56  o$model4[[3]]   46 -27271.94
-12 o$model10[[1]] 140 -24084.14  o$model4[[2]]   88 -11113.99  o$model9[[3]]   39 -26895.35
-13  o$model1[[1]] 130 -24066.23  o$model1[[2]]   58 -11093.02  o$model7[[3]]   39 -26891.76
-14  o$model2[[1]] 131 -24051.02 o$model16[[2]]  130 -11088.10  o$model6[[3]]   39 -26866.52
-15  o$model6[[1]] 164 -24031.80  o$model2[[2]]   59 -11076.95 o$model10[[3]]   39 -26735.14
-16  o$model5[[1]] 226 -23972.19 o$model15[[2]]  164 -11076.43  o$model3[[3]]   32 -26711.17
-17  o$model7[[1]] 164 -23945.62  o$model5[[2]]  102 -11021.51  o$model1[[3]]   30 -26675.04
-18  o$model4[[1]] 196 -23919.37 o$model14[[2]]  196 -11020.01  o$model2[[3]]   31 -26664.86
-
-```{r}
+                   isYOY *         season * cATSStd +
+                 #  isYOY * river * season * cBKTStd2 +
+                   isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   (1|ind) + (1|season), data = df ) }
 
@@
   lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                   isYOY * lengthByYear  +
-                   isYOY * river * season * cBKTStd * lengthByYear +
-                   isYOY * river * season * cBNTStd * lengthByYear +
-                   isYOY *         season * cATSStd * lengthByYear  +
-
-                   (1|ind), data = df ) }
-
-mod[[20]] <- function(df) {
- lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
-                  isYOY * lengthByYear  +
                    isYOY * river * season * cBKTStd +
@@
                    isYOY *         season * cATSStd +
-                  isYOY * river * season * tempStd^2  +
-                  isYOY * river * season * flowStd^2  +
-                  (1|ind), data = df ) }
+                   isYOY * river * season * cBKTStd2 +
+                 #  isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[20]] <- function(df) {
+    print(c('mod = 20' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                 #  isYOY * river * season * cBKTStd2 +
+                  # isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   (1|ind) + (1|season), data = df ) }
+```
+Take out bkt2, for models >20
+          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
+1  o$model17[[1]] 272 -24796.58 o$model18[[2]]  122 -11217.98 o$model11[[3]]   80 -29379.29
+2  o$model18[[1]] 241 -24795.12 o$model16[[2]]  122 -11211.56 o$model15[[3]]   59 -28755.46
+3  o$model16[[1]] 249 -24778.30 o$model17[[2]]  136 -11207.54 o$model16[[3]]   66 -28318.31
+4  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model17[[3]]   73 -28313.67
+5  o$model19[[1]] 249 -24730.67 o$model20[[2]]  108 -11169.43 o$model14[[3]]   59 -28310.73
+6  o$model20[[1]] 218 -24727.16 o$model13[[2]]  108 -11167.05 o$model13[[3]]   59 -28306.10
+7  o$model13[[1]] 226 -24689.16  o$model8[[2]]   66 -11166.73 o$model19[[3]]   66 -28282.69
+8  o$model10[[1]] 195 -24650.05 o$model19[[2]]  122 -11146.57 o$model18[[3]]   66 -28267.13
+9  o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model10[[3]]   52 -28077.66
+10  o$model7[[1]] 139 -24336.63  o$model7[[2]]   66 -11129.29 o$model20[[3]]   59 -28017.53
+11 o$model12[[1]] 155 -24316.48 o$model10[[2]]   94 -11119.43 o$model12[[3]]   52 -27717.41
+12 o$model11[[1]] 187 -24259.03  o$model9[[2]]   66 -11108.18  o$model7[[3]]   38 -27339.65
+13  o$model1[[1]] 131 -24064.23  o$model1[[2]]   59 -11091.02  o$model3[[3]]   45 -27221.73
+14  o$model2[[1]] 132 -24049.02  o$model6[[2]]   73 -11085.12  o$model4[[3]]   52 -27214.79
+15  o$model8[[1]] 139 -24045.93  o$model2[[2]]   60 -11074.95  o$model6[[3]]   38 -26849.65
+16  o$model9[[1]] 139 -24007.57 o$model11[[2]]  108 -11049.99  o$model8[[3]]   38 -26845.97
+17  o$model5[[1]] 163 -23950.60  o$model5[[2]]   73 -11045.37  o$model5[[3]]   38 -26825.20
+18  o$model6[[1]] 163 -23862.94 o$model15[[2]]  108 -11030.68  o$model9[[3]]   38 -26695.14
+19  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
+20  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86
+
+```{r}
+mod[[21]] <- function(df) {
+    print(c('mod = 21' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                 #  isYOY * river * season * cBKTStd2 +
+                   isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   isYOY * river * season * tempStd2 +
+
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[22]] <- function(df) {
+    print(c('mod = 22' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                #   isYOY * river * season * cBKTStd2 +
+                   isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   isYOY * river * season * flowStd2 +
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[23]] <- function(df) {
+    print(c('mod = 23' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                #   isYOY * river * season * cBKTStd2 +
+                   isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   isYOY * river * season * tempStd2 +
+                   isYOY * river * season * flowStd2 +
+                   (1|ind) + (1|season), data = df ) }
 
 ```
+
+          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
+1  o$model17[[1]] 272 -24796.58 o$model18[[2]]  122 -11217.98 o$model11[[3]]   80 -29379.29
+2  o$model18[[1]] 241 -24795.12 o$model16[[2]]  122 -11211.56 o$model15[[3]]   59 -28755.46
+3  o$model16[[1]] 249 -24778.30 o$model17[[2]]  136 -11207.54 o$model22[[3]]   73 -28459.70
+4  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model23[[3]]   80 -28405.91
+5  o$model19[[1]] 249 -24730.67 o$model22[[2]]  136 -11193.90 o$model16[[3]]   66 -28318.31
+6  o$model20[[1]] 218 -24727.16 o$model20[[2]]  108 -11169.43 o$model17[[3]]   73 -28313.67
+7  o$model21[[1]] 272 -24699.83 o$model13[[2]]  108 -11167.05 o$model14[[3]]   59 -28310.73
+8  o$model13[[1]] 226 -24689.16  o$model8[[2]]   66 -11166.73 o$model13[[3]]   59 -28306.10
+9  o$model10[[1]] 195 -24650.05 o$model21[[2]]  136 -11152.36 o$model19[[3]]   66 -28282.69
+10 o$model22[[1]] 272 -24608.90 o$model19[[2]]  122 -11146.57 o$model18[[3]]   66 -28267.13
+11 o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model21[[3]]   73 -28244.31
+12 o$model23[[1]] 303 -24567.09 o$model23[[2]]  149 -11139.31 o$model10[[3]]   52 -28077.66
+13  o$model7[[1]] 139 -24336.63  o$model7[[2]]   66 -11129.29 o$model20[[3]]   59 -28017.53
+14 o$model12[[1]] 155 -24316.48 o$model10[[2]]   94 -11119.43 o$model12[[3]]   52 -27717.41
+15 o$model11[[1]] 187 -24259.03  o$model9[[2]]   66 -11108.18  o$model7[[3]]   38 -27339.65
+16  o$model1[[1]] 131 -24064.23  o$model1[[2]]   59 -11091.02  o$model3[[3]]   45 -27221.73
+17  o$model2[[1]] 132 -24049.02  o$model6[[2]]   73 -11085.12  o$model4[[3]]   52 -27214.79
+18  o$model8[[1]] 139 -24045.93  o$model2[[2]]   60 -11074.95  o$model6[[3]]   38 -26849.65
+19  o$model9[[1]] 139 -24007.57 o$model11[[2]]  108 -11049.99  o$model8[[3]]   38 -26845.97
+20  o$model5[[1]] 163 -23950.60  o$model5[[2]]   73 -11045.37  o$model5[[3]]   38 -26825.20
+21  o$model6[[1]] 163 -23862.94 o$model15[[2]]  108 -11030.68  o$model9[[3]]   38 -26695.14
+22  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
+23  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86
 
@@
 bySpecies <- bySpecies %>%
-      mutate( model1 =  map(data, mod[[1]]) ) %>%
-      mutate( model2 =  map(data, mod[[2]]) ) %>%
-      mutate( model3 =  map(data, mod[[3]]) ) %>%
-      mutate( model4 =  map(data, mod[[4]]) ) %>%
-      mutate( model5 =  map(data, mod[[5]]) ) %>%
-      mutate( model6 =  map(data, mod[[6]]) ) %>%
-      mutate( model7 =  map(data, mod[[7]]) ) %>%
-     mutate( model8 =  map(data, mod[[8]]) ) %>%
-     mutate( model9 =  map(data, mod[[9]]) ) %>%
-     mutate( model10 = map(data, mod[[10]]) ) %>%
-     mutate( model11 = map(data, mod[[11]]) ) %>%
-     mutate( model12 = map(data, mod[[12]]) ) %>%
-     mutate( model13 = map(data, mod[[13]]) ) %>%
-      mutate( model14 = map(data, mod[[14]]) ) %>%
-      mutate( model15 = map(data, mod[[15]]) ) %>%
-      mutate( model16 = map(data, mod[[16]]) ) %>%
-      mutate( model17 = map(data, mod[[17]]) ) %>%
-      mutate( model18 = map(data, mod[[18]]) ) %>%
-     mutate( model19 = map(data, mod[[19]]) ) %>%
-      mutate( model20 = map(data, mod[[20]])) #%>%
-     # mutate( model21 = map(data, mod[[21]])) %>%
-    #  mutate( model22 = map(data, mod[[22]])) %>%
+     #  mutate( model1 =  map(data, mod[[1]]) ) %>%
+     #  mutate( model2 =  map(data, mod[[2]]) ) %>%
+     #  mutate( model3 =  map(data, mod[[3]]) ) %>%
+     #  mutate( model4 =  map(data, mod[[4]]) ) %>%
+     #  mutate( model5 =  map(data, mod[[5]]) ) %>%
+     #  mutate( model6 =  map(data, mod[[6]]) ) %>%
+     #  mutate( model7 =  map(data, mod[[7]]) ) %>%
+     # mutate( model8 =  map(data, mod[[8]]) ) %>%
+     # mutate( model9 =  map(data, mod[[9]]) ) %>%
+     # mutate( model10 = map(data, mod[[10]]) ) %>%
+     # mutate( model11 = map(data, mod[[11]]) ) %>%
+     # mutate( model12 = map(data, mod[[12]]) ) %>%
+     # mutate( model13 = map(data, mod[[13]]) ) %>%
+     #  mutate( model14 = map(data, mod[[14]]) ) %>%
+     #  mutate( model15 = map(data, mod[[15]]) ) %>%
+     #  mutate( model16 = map(data, mod[[16]]) ) %>%
+     #  mutate( model17 = map(data, mod[[17]]) ) %>%
+     #  mutate( model18 = map(data, mod[[18]]) ) %>%
+     # mutate( model19 = map(data, mod[[19]]) ) %>%
+     #  mutate( model20 = map(data, mod[[20]]) )# %>%
+      mutate( model21 = map(data, mod[[21]])) %>%
+      mutate( model22 = map(data, mod[[22]])) #%>%
     #  mutate( model23 = map(data, mod[[23]]))
+```
 
+```{r}
 #2 or 5 fish have lengthByYear = NA whcih gives warining of diff # of observations when include mod with lengthByYear
@@
            o$model19[[1]],
-          o$model20[[1]]
-         # o$model21[[1]],
-         # o$model22[[1]],
-         # o$model23[[1]]
+           o$model20[[1]],
+           o$model21[[1]],
+           o$model22[[1]],
+          o$model23[[1]]
          ) %>% rownames_to_column() %>% arrange(AIC) #bkt
@@
            o$model19[[2]],
-          o$model20[[2]]
-         # o$model21[[2]],
-         # o$model22[[2]],
-         # o$model23[[2]]
+           o$model20[[2]],
+           o$model21[[2]],
+           o$model22[[2]],
+           o$model23[[2]]
          ) %>% rownames_to_column() %>% arrange(AIC)#bnt
@@
             o$model19[[3]],
-          o$model20[[3]]
-         # o$model21[[3]],
-         # o$model22[[3]],
-         # o$model23[[3]]
+           o$model20[[3]],
+           o$model21[[3]],
+           o$model22[[3]],
+          o$model23[[3]]
           ) %>% rownames_to_column() %>% arrange(AIC)#ats

### 2018-06-01 R/analyzeOutputFunctions.R

@@ -92,7 +92,7 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
     cATSData <- 0
 
   predTemplate <- data.frame(
-                              len = lenData,
+                            #  len = lenData,
                              # count = countData,
                               flow =  flowData,
                               temp =  tempData,
@@ -116,15 +116,16 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
   preds <- preds %>%
     mutate( predGr =
             ( int +
-              beta1 * len +
-              beta2 * cBKT +
-              beta3 * cBKT^2 +
-              beta4 * temp +
-              beta5 * flow +
-              beta6 * temp * flow +
 
-              beta7 * temp^2 +
-              beta8 * flow^2 +
+              beta3 * cBKT^2 +
+              beta1 * temp +
+              beta2 * flow +
+              beta3 * temp * flow +
+
+              beta4 * temp^2 +
+              beta5 * flow^2 +
+
+              beta6 * cBKT +
 
               betaBNT1 * cBNT +
               betaBNT2 * cBNT^2 +
@@ -134,7 +135,7 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
 
             ) #* interval
     ) %>%
-    select( len,flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
+    dplyr::select( flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
 
   return(preds)
 }
@@ -233,13 +234,13 @@ getPredictionSigma <- function(d, limits = 2, nPoints = 5, itersForPred, constan
     cATSData <- 0
 
   predTemplate <- data.frame(
-    len = lenData,
+  #  len = lenData,
     # count = countData,
     flow =  flowData,
-    temp =  tempData,
-    cBKT =  cBKTData,
-    cBNT =  cBNTData,
-    cATS =  cATSData
+    temp =  tempData
+  #  cBKT =  cBKTData,
+  #  cBNT =  cBNTData,
+  #  cATS =  cATSData
   )
 
 
[…]

### 2018-06-01 R/growthModelFunctions.R

@@ -8,7 +8,7 @@
 runGrowthModel_Nimble <- function(d,mcmcInfo,code){
 
   ##
-  nBetas <- 8
+  nBetas <- 6
   nBetasSigma <- 3
   nBetasBNT <- 3
   nBetasATS <- 1

### 2018-06-01 R/growthModelFunctions_Code.R

@@ -15,16 +15,15 @@ codeSpp[[1]] <- nimbleCode({
     gr[ evalRows[i] ] <-
       grInt[        isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
 
-      grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthDATA[evalRows[i]] +
+  #    grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthDATA[evalRows[i]] +
+  #    grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
+      grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] +
+      grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]] +
+      grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] * flowStd[evalRows[i]] +
 
-      grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] +
-      grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
-      grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] +
-      grBeta[ 5, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]] +
-      grBeta[ 6, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] * flowStd[evalRows[i]] +
-
[…]

### 2018-06-01 nimble/mainAnalysis_Nimble.R

@@ -19,13 +19,14 @@ library(tidyverse)
 # selection criteria
 
 reconnect()
+# run to here to start so can reconnect
 
 drainage <- "west" # ==
 
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "ats"
+speciesGr <- "bkt"
 #speciesGr = c("bkt", "bnt","ats")
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
@@ -221,7 +222,7 @@ iter=1
   #########################################
   # mcmc run data
   mcmcInfo <- list()
-  mcmcInfo$nChains <- 6
+  mcmcInfo$nChains <- 3
   mcmcInfo$nIter <- 10000
   mcmcInfo$nBurnIn <- 9000
   mcmcInfo$thinRate <- 1 #fails with thinRate of 3 and 1000/750
@@ -287,7 +288,7 @@ iter=1
   plotInt_Nimble(mcmcProcessed)
   plotBetas_Nimble(mcmcProcessed,1:2)
   plotBetas_Nimble(mcmcProcessed,3:4)
-  plotBetas_Nimble(mcmcProcessed,5:8)
+  plotBetas_Nimble(mcmcProcessed,5:6)
 
   plotBetasBNT_Nimble(mcmcProcessed,1:3)
   plotBetasATS_Nimble(mcmcProcessed,1)
@@ -309,13 +310,13 @@ iter=1
   itersForPred <- sample( 1:mcmcInfo$nSamples, nItersForPred )
 
   # predictions across the grid
-  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len", "temp", "flow","cBKT", "cBNT", "cATS") )#######################
+  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("temp", "flow","cBKT", "cBNT", "cATS") )#######################
   #p$variable <- "mean"
   # predictions of sigma across the grid
[…]

### 2018-06-20 manuscriptAnalysis/MS_Analysis.Rmd
chagned grIndRE structure

@@
             legend.key.size= unit(0.2, "cm"),
-            legend.margin = unit(0, "cm"),
+        #    legend.margin = unit(0, "cm"),
             legend.title = element_text(face="italic"),
@@
 
+riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("WB","OL","OS","IL"), ordered = T)
+
 ```
@@
 ```{r message=FALSE}
+library(linkedModels)
 library(arrayhelpers)
@@
 load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
-load("D:/projects/linkedModels/data/out/countsAndMasses.RData")
+load("D:/projects/linkedModels/data/out/rawCountsAndMasses.RData")
 
 mcmc <- list()
-load("D:/projects/linkedModels/data/out/dG_1518555667_bkt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1528425682_bkt1997_Nimble.RData")
 
@@
           grLength = (lagObservedLength - observedLength)/as.numeric((lagDetectionDate - detectionDate))
-  )  
+  )  %>%
+  ungroup()
+
 #d2 %>% filter(tag=='00088cc059') %>% select(tag,riverOrdered,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength)
@@
 
-load("D:/projects/linkedModels/data/out/dG_1518559325_bnt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1528410796_bnt1997_Nimble.RData")
 mcmc[['bnt']]  <- mcmcProcessed
 
-load("D:/projects/linkedModels/data/out/dG_1518559991_ats1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1528735018_ats1997_Nimble.RData")
 mcmc[['ats']]  <- mcmcProcessed
@@
 
+```{r check lengthExp}
+
+len2 <- array2df(mcmc[['bnt']]$sims.list$lengthExp, label.x = "est") %>%
+         rename(iter=d1,obs=d2)
+
+inds <- data.frame(ind = dG[[1]]$constants$ind[1:(length(dG[[1]]$constants$ind) - 1)],
+                   observedLen = dG[[1]]$data$lengthDATA)
+inds$obs <- 1:(length(dG[[1]]$constants$ind) - 1)
+inds <-  inds %>%
+  group_by(ind) %>%
+  mutate(first = min(obs),
+         firstObs = obs == first,
+         observed = !is.na(observedLen)) %>%
+  ungroup()
+
+len1 <- left_join(len2,inds)
+
+# means
+lenMean1 <- array2df(mcmc[['bnt']]$mean$lengthExp, label.x = "estMean") %>%
+         rename(obs=d1)
+
+len <- left_join(len1,lenMean1)
+
+len %>% filter(ind == 1, !firstObs, iter%%50==0) %>%
+  ggplot(aes(obs,est)) +
+  geom_point() +
+  geom_line(aes(group = iter)) +
+  geom_point(aes(obs,estMean), color='red', size=3) +
+  geom_point(aes(obs,observedLen), color='blue', size=3)
+
+```
+
+```{r winter growth rates}
+
+ggplot(ddG[[1]][[2]], aes(observedLength,grLength)) + 
+  geom_point() +
+  facet_grid(river + isYOY ~ season+species)
+
+```
+
 ```{r raw counts}
-allFishBySpecies$riverOrderedGG <- factor(allFishBySpecies$river,
+allFishBySpeciesYOY$riverOrderedGG <- factor(allFishBySpeciesYOY$river,
                          levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                          labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
-allFishBySpecies$seasonGG <- factor(allFishBySpecies$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
-allFishBySpecies$speciesGG <- factor(allFishBySpecies$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+allFishBySpeciesYOY$seasonGG <- factor(allFishBySpeciesYOY$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+allFishBySpeciesYOY$speciesGG <- factor(allFishBySpeciesYOY$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+
+#sum across YOY
+allFishBySpecies <- allFishBySpeciesYOY %>%
+   group_by(river,season,year,species) %>%
+   summarize( nAllFishBySpecies = sum(nAllFishBySpeciesYOY, na.rm=T),
+                massAllFishBySpecies = sum(massAllFishBySpeciesYOY, na.rm=T))
+allFishBySpeciesYOY <- left_join(allFishBySpeciesYOY,allFishBySpecies)
+
+# sum across YOY and species
+   allFish <- allFishBySpeciesYOY %>%
+     group_by(river,season,year) %>%
+     summarize( nAllFish = sum(nAllFishBySpeciesYOY, na.rm=T),
+                massAllFish = sum(massAllFishBySpeciesYOY, na.rm=T))
+   cd <- left_join(cd,allFish)
 
@@
 allFish$seasonGG <- factor(allFish$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+#########
 
-ggplot(allFishBySpecies, aes(year,nAllFishBySpecies)) +
+ggplot(allFishBySpeciesYOY, aes(year,nAllFishBySpecies)) +
   geom_point(aes(color = speciesGG)) +
@@
 
-ggsave('figures/rawCount.png')
+ggsave('figures/rawCounts.png')
 
-tmp <- d %>% distinct(season,year,sampleNumber)
-allFishBySpecies <- left_join(allFishBySpecies,tmp)
+# add in sampleNumber
+tmp <- d2 %>% distinct(season,year,sampleNumber)
+allFishBySpeciesYOY <- left_join(allFishBySpeciesYOY,tmp)
 allFish <- left_join(allFish,tmp)
 
-ggplot(allFishBySpecies, aes(sampleNumber,nAllFishBySpecies)) +
+ggplot(allFishBySpeciesYOY, aes(sampleNumber,nAllFishBySpeciesYOY)) +
   geom_point(aes(color = speciesGG)) +
@@
 
-```{r p(detection)}
-  # ggPInt <- array2df(ddD$sims.list$pBetaInt, label.x = "est")
-  # 
-  # ggPInt$chain <- rep(1:ddD$mcmc.info$n.chains, each = ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
-  # ggPInt$iter <- 1:as.numeric(ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
-  # 
-  # ggplot(filter(ggPInt), aes(iter,est)) + 
-  #   geom_point( aes(color=factor(chain)), size = 0.1 ) + 
-  #   ylim(-1.5,1.5) + 
-  #   facet_grid(d2+d4~d5+d3)
-
-  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
-    rename(est=est,species=d1,season=d2,river=d3,year=d4)
-  ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
-
-   ggsave('figures/p.png')
-
-  phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
-    rename(est=est,species=d1,season=d2,river=d3,year=d4)
-  ggplot(phi, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
-
-# # of skunked sections    
-  tmp <- dddD[[2]] %>%
-           group_by(riverOrdered,year,season,section) %>%
-           summarize( s = sum(enc) ) %>%
-           filter( s == 0 )
-  table(tmp$riverOrdered,tmp$year,tmp$season)
-
-```
-
-```{r overview graphs - Fig 1}
-d$riverOrderedGG <- factor(d$river,
-                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
-                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
-d$seasonGG <- factor(d$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
-d$speciesGG <- factor(d$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
-
-ggplot(d, aes(year,nAllFishBySpeciesP)) +
-  geom_point(aes(color=speciesGG)) +
-  geom_line(aes(color=speciesGG)) +
-  labs( x = "Year", y = "Estimated count") +
-#  ylim(0,2500) +
-  theme_publication() +
-  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
-
-ggsave('figures/count.png')
-
-ggplot(d, aes(year,nAllFishBySpeciesP)) +
-  geom_point(aes(color=species)) +
-  geom_line(aes(color=species)) +
-   geom_line(  aes(year,nAllFishP) ) +
-  labs( x = "Year", y = "Estimated count") +
-#  ylim(0,2500) +
-  theme_publication() +
-  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
-```
-```{r raw growth rates}
-
-cdMeans <- cd %>%
-  mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
-  group_by(species,riverOrdered,season) %>%
-  summarize( meanGr = mean( gr, na.rm = TRUE ),
-             sdGr = sd( gr, na.rm = TRUE )) %>%
-  mutate( meanGrUp = meanGr + sdGr,
-          meanGrDn = meanGr - sdGr
-          )
-
-pd <- position_dodge(0.05) # move them .05 to the left and right
-
-# all three species
-ggplot( cdMeans %>% filter(riverOrdered == 'west brook'), aes(season, meanGr, color = species) ) +
-  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
-  geom_point( size = 2 ) +
-  geom_line()
-
-cd$isYOY <- ifelse( cd$ageInSamples <= 3, 1, 2 )
-cdMeansByisYOY <- cd %>%
-  mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
-  group_by(species,riverOrdered,season,isYOY) %>%
-  summarize( meanGr = mean( gr, na.rm = TRUE ),
-             sdGr = sd( gr, na.rm = TRUE )) %>%
-  mutate( meanGrUp = meanGr + sdGr,
-          meanGrDn = meanGr - sdGr
-          )
-
-# all three species
-ggplot( cdMeansByisYOY %>% filter(riverOrdered == 'west brook', !(season == 2 & isYOY == 1)), aes(season, meanGr, color = species) ) +
-  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
-  geom_point( size = 2 ) +
-  geom_line()+
-  facet_wrap(~isYOY)
-
-# all three species by river
-ggplot( cdMeansByisYOY %>% filter(!(season == 2 & isYOY == 1)) , aes(season, meanGr, color = riverOrdered) ) +
-  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
-  geom_point( size = 2 ) +
-  geom_line()+
-  facet_grid(species~isYOY)
-
-# bkt only
-pdBKT <- position_dodge(0.05) # move them .05 to the left and right
-ggplot( cdMeans %>% filter(species=='bkt'), aes(season, meanGr, color = riverOrdered) ) +
-  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pdBKT) +
-  geom_point( size = 3 ) +
-  geom_line( size = 1 ) +
-  facet_wrap(~isYOY)
-
-```
-```{r growth by movement}
-d2$isYOY <- ifelse( d2$ageInSamples <= 3, 1, 2 )
-d2 <-  d2 %>%
-  group_by(tag) %>%
-  mutate( lagRiverN = lead(riverN), 
-          riverNMove = paste(riverN,lagRiverN, sep="_")
-          #gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate)
-          )
-
-#d2 %>% filter(tag=='00088cbf44') %>% select(tag,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength)
-table(d2$riverNMove)
-
-cdMeansByisYOYriverNMove <- d2 %>%
-  #mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
-  group_by(species,riverN,lagRiverN,season,isYOY) %>%
-  summarize( meanGr = mean( grLength, na.rm = TRUE ),
-             sdGr = sd( grLength, na.rm = TRUE ),
-             n = n()) %>%
-  mutate( meanGrUp = meanGr + sdGr,
-          meanGrDn = meanGr - sdGr
-          )
-
-# 
-ggplot( cdMeansByisYOYriverNMove %>% filter(!(season == 2 & isYOY == 1), species == "bkt", isYOY == 2) , aes(season, meanGr, color = factor(lagRiverN)) ) +
-  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
-  geom_point( size = 2 ) +
-  geom_line()+
-  facet_wrap(~riverN)
-
-d2 %>% filter(riverN == 1 & lagRiverN == 4) %>% select(tag,river,sampleNumber)
-d2 %>% filter(riverN == 2, is.na(lagRiverN), !is.na(grLength)) %>% select(tag,riverN,sampleNumber,lagRiverN,observedLength,lagObservedLength,gr,grLength)
-d2 %>% filter(tag=='00088cc059') %>% select(tag,riverOrdered,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength,gr,grLength)
-```
-
 ```{r figs 3,4}
-d %>% group_by(riverOrderedGG,seasonGG,year) %>%
+d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
   filter( riverOrderedGG == "West Brook" ) %>%
@@
 
-tempMods <- d %>%
+tempMods <- d2 %>%
   group_by(riverOrderedGG,seasonGG,year) %>%
@@
   mutate(tidy = map(model,broom::tidy)) %>%
-  select(-data,-model) %>%
+  dplyr::select(-data,-model) %>%
   unnest() %>%
@@
 
-d %>% group_by(riverOrderedGG,seasonGG,year) %>%
+d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
   summarize(meanT = mean(meanTemperature, na.rm=T),
@@
 
+```{r mean gr graphs}
+cd$riverOrderedGG <- factor(cd$river,
+                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
+                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
+cd$seasonGG <- factor(cd$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+cd$speciesGG <- factor(cd$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+
+pd <- position_dodge(0.65)
+
+cd %>% group_by(speciesGG,riverOrderedGG,seasonGG) %>%
+  filter(isYOY == 1) %>%
+  summarize(meanGR = mean(grLength, na.rm=T),
+            sdGR = sd(grLength, na.rm=T)) %>%
+ggplot( aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
+  geom_point( position = pd, size = 2 ) +
+  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
+  ggtitle( "isYOY = 1" ) +
+  labs( x = "Season", y = "Growth rate (mm/d)" ) +
+  #scale_x_continuous( breaks = 1997:2015 ) +
+  theme_publication() +
+  theme( panel.grid.minor = element_blank() ) +
+  facet_wrap( ~ riverOrderedGG)
+
+ggsave('figures/meanGRYOY1.png', width = 7, height = 7, units='in')
+
+cd %>% group_by(speciesGG,riverOrderedGG,seasonGG) %>%
+  filter(isYOY == 2) %>%
+  summarize(meanGR = mean(grLength, na.rm=T),
+            sdGR = sd(grLength, na.rm=T)) %>%
+ggplot( aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
+  geom_point( position = pd,size = 2 ) +
+  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
+  ggtitle( "isYOY = 2" ) +
+  labs( x = "Season", y = "Growth rate (mm/d)" ) +
+  #scale_x_continuous( breaks = 1997:2015 ) +
+  theme_publication() +
+  theme( panel.grid.minor = element_blank() ) +
+  facet_wrap( ~ riverOrderedGG)
+
+ggsave('figures/meanGRYOY2.png', width = 7, height = 7, units='in')
+
+```
+```{r - why bad convergence for bnt in winter?}
+
+cd %>% filter() %>%
+  ggplot(aes(observedLength,grLength)) +
+  geom_point() +
+  facet_grid(season~species)
+
+```
+
 ```{r questions}
@@
 
-```{r mcmc output analysis}
+```{r p(detection)}
+  # ggPInt <- array2df(ddD$sims.list$pBetaInt, label.x = "est")
+  # 
+  # ggPInt$chain <- rep(1:ddD$mcmc.info$n.chains, each = ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
+  # ggPInt$iter <- 1:as.numeric(ddD$mcmc.info$n.samples/ddD$mcmc.info$n.chains)
+  # 
+  # ggplot(filter(ggPInt), aes(iter,est)) + 
+  #   geom_point( aes(color=factor(chain)), size = 0.1 ) + 
+  #   ylim(-1.5,1.5) + 
+  #   facet_grid(d2+d4~d5+d3)
 
-riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
+  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
+    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5)
+  ggplot(p, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid(river ~ season + isYOY)
+
+  # seem to need to run the ggsave outside of markdown by pasting into console
+   ggsave('figures/p.png')
+
+  phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
+    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5)
+  ggplot(phi, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid(river ~ season + isYOY)
+
+  ggsave('figures/phi.png')
+
+# # of skunked sections    
+  tmp <- dddD[[2]] %>%
+           group_by(riverOrdered,year,season,section) %>%
+           summarize( s = sum(enc) ) %>%
+           filter( s == 0 )
+  table(tmp$riverOrdered,tmp$year,tmp$season)
+
+```
+
+```{r r-hat}
+
+rHat <- list()
+rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:5,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
+rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:5,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
+rHat[['ats']] <- array2df(mcmc[['ats']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="rHat")
+
+# rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:8,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
+# rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:8,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
+# rHat[['ats']] <- array2df(mcmc[['ats']]$Rhat$grBeta, levels = list(beta=1:8,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="rHat")
+
+ggplot(rHat[[3]], aes(beta,rHat)) +
+  geom_point() +
+  facet_grid(river+isYOY~season)
+
+```
+
+```{r mcmc output analysis-grInt}
 
@@
 
-ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(exp(int))) +
+ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
   geom_freqpoly() +
-  geom_freqpoly(aes(exp(int)),color = 'brown', data = grInt[['bnt']]) +
-  geom_freqpoly(aes(exp(int)),color = 'lightblue', data = grInt[['ats']]) +
+  geom_freqpoly(aes((int)),color = 'brown', data = grInt[['bnt']]) +
+  geom_freqpoly(aes((int)),color = 'lightblue', data = grInt[['ats']]) +
  # xlim(-0.5,1.5) +
@@
 
+##################################################
 # as range plot
+
+plotHPD <- function(sppToPlot){
+
+  nRivers <- list()
+  nRivers[['bkt']] <- 4; nRivers[['bnt']] <- 2; nRivers[['ats']] <- 1
+
   probs <- c(0.05,0.1,0.5,0.9,0.95)
-q <- grInt[['bkt']] %>%
+  q <- grInt[[sppToPlot]] %>%
     group_by(isYOY,season,river) %>%
@@
 
-p <- array2df(mcmc[['bkt']]$mean$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>%
+  p <- array2df(mcmc[[sppToPlot]]$mean$grInt, levels = list(isYOY=c(1,2),season=1:4,river=riverOrderedIn[1:nRivers[[sppToPlot]]]), label.x="int") %>%
     mutate( season = as.numeric(season) ) %>%
@@
 
-pUp <- array2df(mcmc[['bkt']]$q97.5$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="intUp") %>%
+  pUp <- array2df(mcmc[[sppToPlot]]$q97.5$grInt, levels = list(isYOY=c(1,2),season=1:4,river=riverOrderedIn[1:nRivers[[sppToPlot]]]), label.x="intUp") %>%
     mutate( season = as.numeric(season) ) 
-pDown <- array2df(mcmc[['bkt']]$q2.5$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="intDown") %>%
+  pDown <- array2df(mcmc[[sppToPlot]]$q2.5$grInt, levels = list(isYOY=c(1,2),season=1:4,river=riverOrderedIn[1:nRivers[[sppToPlot]]]), label.x="intDown") %>%
     mutate( season = as.numeric(season) )
+
+  p <- left_join(p,pUp); p <- left_join(p,pDown)
+
   p$intByDayUp <- p$intUp/p$meanSampleInterval; p$intByDayDown <- p$intDown/p$meanSampleInterval
   p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
-p <- left_join(p,pUp) %>% left_join(.,pDown)
+  p$intByDayUp <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDayUp)
+  p$intByDayDown <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDayDown)
 
-   ggplot(p, aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(season), shape = factor(season))) + 
+  #print(c(min(p$intByDayDown,na.rm=T),max(p$intByDayDown,na.rm=T)))
+
+    gg <- ggplot(p, aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(season), shape = factor(isYOY))) + 
+        theme_publication() +  
         geom_point(size = 3) +
-      facet_grid(~isYOY)
+        geom_segment(aes(x = intByDay, xend = intByDayUp, yend = reorder(parameter, intByDay)), 
+        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
+        geom_segment(aes(x = intByDay, xend = intByDayDown, yend = reorder(parameter, intByDay)), 
+        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
+        xlim(c(-0.0015,0.01)) +
+        xlab("Mean daily growth (mm/d)") + ylab("River_Season") 
+       # ggtitle(sppToPlot)
 
-      geom_segment(aes(x = Low, 
-      xend = High, yend = reorder(Parameter, median)), 
-      size = 1.5) + geom_segment(aes(x = low, xend = high, 
-      yend = reorder(Parameter, median)), size = 0.5) + 
-      xlab("HPD") + ylab("Parameter")
+    return(gg)
+}
 
+plotHPD('bkt'); ggsave('figures/HDP_bkt.png', height = 3, width = 3, scale = 2)
+plotHPD('bnt'); ggsave('figures/HDP_bnt.png', height = 3, width = 3, scale = 2)
+plotHPD('ats'); ggsave('figures/HDP_ats.png', height = 3, width = 3, scale = 2)
 ```
 
-```{r}
+```{r sigmaInt}
 
@@
   facet_grid(season ~ river + isYOY)
+
+##################################################
+# as range plot
+
+plotHPDSigma <- function(sppToPlot){
+
+  nRivers <- list()
+  nRivers[['bkt']] <- 4; nRivers[['bnt']] <- 2; nRivers[['ats']] <- 1
+
+  probs <- c(0.05,0.1,0.5,0.9,0.95)
+  q <- sigmaInt[[sppToPlot]] %>%
+    group_by(isYOY,season,river) %>%
+    summarize(
+      p = list(probs),
+      q = list(quantile(int,probs))
+    ) %>%
+    unnest() %>%
+    spread(key = p, value = q)
+
+  p <- array2df(mcmc[[sppToPlot]]$mean$sigmaInt, levels = list(isYOY=c(1,2),season=1:4,river=riverOrderedIn[1:nRivers[[sppToPlot]]]), label.x="int") %>%
+    mutate( season = as.numeric(season) ) %>%
+    left_join(.,meanSampleIntervalMean, by = 'season')
+ # p$intByDay <- p$int/p$meanSampleInterval
+#  p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
+  p$parameter <- paste(p$river,p$season,sep="_")
+
+  pUp <- array2df(mcmc[[sppToPlot]]$q97.5$sigmaInt, levels = list(isYOY=c(1,2),season=1:4,river=riverOrderedIn[1:nRivers[[sppToPlot]]]), label.x="intUp") %>%
+    mutate( season = as.numeric(season) ) 
+  pDown <- array2df(mcmc[[sppToPlot]]$q2.5$sigmaInt, levels = list(isYOY=c(1,2),season=1:4,river=riverOrderedIn[1:nRivers[[sppToPlot]]]), label.x="intDown") %>%
+    mutate( season = as.numeric(season) )
+
+  p <- left_join(p,pUp); p <- left_join(p,pDown)
+
+ # p$intByDayUp <- p$intUp/p$meanSampleInterval; p$intByDayDown <- p$intDown/p$meanSampleInterval
+  p$int <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$int)
+  p$intUp <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intUp)
+  p$intDown <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intDown)
+
+  #print(c(min(p$intDown,na.rm=T),max(p$intDown,na.rm=T)))
+
+    gg <- ggplot(p, aes(x = exp(int), y = reorder(parameter,int,na.rm=TRUE), color = factor(season), shape = factor(isYOY))) + 
+        theme_publication() +  
+        geom_point(size = 3) +
+        geom_segment(aes(x = exp(int), xend = exp(intUp), yend = reorder(parameter, int)), 
+        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
+        geom_segment(aes(x = exp(int), xend = exp(intDown), yend = reorder(parameter, int)), 
+        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
+        #xlim(c(-0.0015,0.01)) +
+        xlab("Standard deviation of daily growth (mm/d)") + ylab("River_Season") 
+       # ggtitle(sppToPlot)
+
+    return(gg)
+}
+
+plotHPDSigma('bkt'); ggsave('figures/HDPSigma_bkt.png', height = 3, width = 3, scale = 2)
+plotHPDSigma('bnt'); ggsave('figures/HDPSigma_bnt.png', height = 3, width = 3, scale = 2)
+plotHPDSigma('ats'); ggsave('figures/HDPsigma_ats.png', height = 3, width = 3, scale = 2)
+```
+
+```{r}
+riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
+
+grIntMu <- list()
+grIntMu[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grIntMu, levels = list(iter=NA,season=1:4), label.x="int")
+grIntMu[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grIntMu, levels = list(iter=NA,season=1:4), label.x="int")
+grIntMu[['ats']] <- array2df(mcmc[['ats']]$sims.list$grIntMu, levels = list(iter=NA,season=1:4), label.x="int")
+
+bw <- 0.05
+ggplot( grIntMu[['bkt']] , aes(int)) +
+  geom_freqpoly(binwidth = bw, size=1.2) +
+  geom_freqpoly(aes(int),binwidth = bw,color = 'brown', data = grIntMu[['bnt']]) +
+  geom_freqpoly(aes(int),binwidth = bw,color = 'lightblue', data = grIntMu[['ats']]) +
+  #xlim(-4.5,-1) +
+  xlim(-0.25,0.75) +
+  ylim(0,500) +
+  theme_publication() +
+  facet_wrap(~season )
 
@@
 
+```{r predictions}
+# #run if get new predictions - takes a while to run
+# load('D:/projects/linkedModels/data/out/P_ForMike_bkt.RData')
+# pBoth$species <- 'bkt'
+# pAll <- pBoth; rm(pBoth)
+# 
+# load('D:/projects/linkedModels/data/out/P_ForMike_bnt.RData')
+# pBoth$species <- 'bnt'
+# pAll <- rbind(pAll,pBoth); rm(pBoth)
+# 
+# load('D:/projects/linkedModels/data/out/P_ForMike_ats.RData')
+# pBoth$species <- 'ats'
+# pAll <- rbind(pAll,pBoth); rm(pBoth)
+# 
+# 
+# pred <- pAll %>% group_by(species,flow,temp,cBKT,cBNT,cATS,isYOY,season,river) %>%
+#   summarize(meanPredGR = mean(predGr, na.rm=T),
+#             sdpredGR = sd(predGr, na.rm=T)) %>%
+#    ungroup()
+# 
+# save(pred,file = 'D:/projects/linkedModels/data/out/P_ForMike_allMeans.RData')
+load('D:/projects/linkedModels/data/out/P_ForMike_allMeans.RData')
+
+pred <- pred %>% filter( !(isYOY == 0 & season == 2) ) 
+#pred <- pred %>% filter( !(isYOY == 0 & river == 'wb jimmy' & season == 2) )
+#graph function, in analyzeOutputFunctions.R
+
+pred$riverGG <- factor(pred$river,
+                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
+                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
+pred$seasonGG <- factor(pred$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+pred$speciesGG <- factor(pred$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+
+plotPredMeans(pred, "meanPredGR", "flow", 0)
+plotPredMeans(pred, "meanPredGR", "flow", 1)
+
+plotPredMeans(pred, "meanPredGR", "temp", 0)
+plotPredMeans(pred, "meanPredGR", "temp", 1)
+
+plotPredMeans(pred, "meanPredGR", "cBKT", 0)
+plotPredMeans(pred, "meanPredGR", "cBKT", 1)
+
+plotPredMeans(pred, "meanPredGR", "cBNT", 0)
+plotPredMeans(pred, "meanPredGR", "cBNT", 1)
+
+plotPredMeans(pred, "meanPredGR", "cATS", 0)
+plotPredMeans(pred, "meanPredGR", "cATS", 1)
+
+plotPredMeans(pred, "meanPredGR", c("temp","flow"), 0)
+plotPredMeans(pred, "meanPredGR", c("temp","flow"), 1)
+
+plotPredMeans(pred, "meanPredGR", c("flow","temp"), 0)
+plotPredMeans(pred, "meanPredGR", c("flow","temp"), 1)
+
+ggsave('figures/tmp.png', width = 9, height = 7, units='in')
+```
+
 ```{r tables}
@@
 # isYOY1
-d %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>%
+d2 %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>%
   filter(isYOYDATA == 1) %>%
@@
 ```
+
+```{r growth by movement}
+d2$isYOY <- ifelse( d2$ageInSamples <= 3, 1, 2 )
+d2 <-  d2 %>%
+  group_by(tag) %>%
+  mutate( lagRiverN = lead(riverN), 
+          riverNMove = paste(riverN,lagRiverN, sep="_")
+          #gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate)
+          )
+
+#d2 %>% filter(tag=='00088cbf44') %>% select(tag,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength)
+table(d2$riverNMove)
+
+cdMeansByisYOYriverNMove <- d2 %>%
+  #mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
+  group_by(species,riverN,lagRiverN,season,isYOY) %>%
+  summarize( meanGr = mean( grLength, na.rm = TRUE ),
+             sdGr = sd( grLength, na.rm = TRUE ),
+             n = n()) %>%
+  mutate( meanGrUp = meanGr + sdGr,
+          meanGrDn = meanGr - sdGr
+          )
+
+# 
+ggplot( cdMeansByisYOYriverNMove %>% filter(!(season == 2 & isYOY == 1), species == "bkt", isYOY == 2) , aes(season, meanGr, color = factor(lagRiverN)) ) +
+  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
+  geom_point( size = 2 ) +
+  geom_line()+
+  facet_wrap(~riverN)
+
+d2 %>% filter(riverN == 1 & lagRiverN == 4) %>% select(tag,river,sampleNumber)
+d2 %>% filter(riverN == 2, is.na(lagRiverN), !is.na(grLength)) %>% select(tag,riverN,sampleNumber,lagRiverN,observedLength,lagObservedLength,gr,grLength)
+d2 %>% filter(tag=='00088cc059') %>% select(tag,riverOrdered,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength,gr,grLength)
+```

### 2018-06-20 manuscriptAnalysis/linearGR_ModelsMap_BKT.Rmd
chagned grIndRE structure

@@
 ```{r}
+# add squared terms back in to good model for ats? NO
+
+mod[[24]] <- function(df) {
+    print(c('mod = 24' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                   isYOY * river * season * cATSStd2 +
+                   isYOY * river * season * tempStd2 +
+
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[25]] <- function(df) {
+    print(c('mod = 25' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                   isYOY * river * season * cATSStd2 +
+
+                   isYOY * river * season * flowStd2 +
+                   (1|ind) + (1|season), data = df ) }
+
+mod[[26]] <- function(df) {
+    print(c('mod = 26' ))
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                   isYOY * river * season * cATSStd2 +
+                   isYOY * river * season * tempStd2 +
+                   isYOY * river * season * flowStd2 +
+                   (1|ind) + (1|season), data = df ) }
+```
+
+          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
+1  o$model17[[1]] 272 -24796.58 o$model18[[2]]  122 -11217.98 o$model11[[3]]   80 -29379.29
+2  o$model18[[1]] 241 -24795.12 o$model16[[2]]  122 -11211.56 o$model15[[3]]   59 -28755.46
+3  o$model16[[1]] 249 -24778.30 o$model17[[2]]  136 -11207.54 o$model24[[3]]   66 -28732.88
+4  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model26[[3]]   73 -28728.16
+5  o$model19[[1]] 249 -24730.67 o$model22[[2]]  136 -11193.90 o$model25[[3]]   66 -28722.50
+6  o$model20[[1]] 218 -24727.16 o$model20[[2]]  108 -11169.43 o$model22[[3]]   73 -28459.70
+7  o$model21[[1]] 272 -24699.83 o$model13[[2]]  108 -11167.05 o$model23[[3]]   80 -28405.91
+8  o$model13[[1]] 226 -24689.16  o$model8[[2]]   66 -11166.73 o$model16[[3]]   66 -28318.31
+9  o$model10[[1]] 195 -24650.05 o$model21[[2]]  136 -11152.36 o$model17[[3]]   73 -28313.67
+10 o$model22[[1]] 272 -24608.90 o$model19[[2]]  122 -11146.57 o$model14[[3]]   59 -28310.73
+11 o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model13[[3]]   59 -28306.10
+12 o$model23[[1]] 303 -24567.09 o$model23[[2]]  149 -11139.31 o$model19[[3]]   66 -28282.69
+13 o$model25[[1]] 241 -24463.80  o$model7[[2]]   66 -11129.29 o$model18[[3]]   66 -28267.13
+14 o$model24[[1]] 241 -24462.46 o$model10[[2]]   94 -11119.43 o$model21[[3]]   73 -28244.31
+15 o$model26[[1]] 272 -24413.64  o$model9[[2]]   66 -11108.18 o$model10[[3]]   52 -28077.66
+16  o$model7[[1]] 139 -24336.63  o$model1[[2]]   59 -11091.02 o$model20[[3]]   59 -28017.53
+17 o$model12[[1]] 155 -24316.48  o$model6[[2]]   73 -11085.12 o$model12[[3]]   52 -27717.41
+18 o$model11[[1]] 187 -24259.03  o$model2[[2]]   60 -11074.95  o$model7[[3]]   38 -27339.65
+19  o$model1[[1]] 131 -24064.23 o$model11[[2]]  108 -11049.99  o$model3[[3]]   45 -27221.73
+20  o$model2[[1]] 132 -24049.02  o$model5[[2]]   73 -11045.37  o$model4[[3]]   52 -27214.79
+21  o$model8[[1]] 139 -24045.93 o$model25[[2]]  122 -11045.32  o$model6[[3]]   38 -26849.65
+22  o$model9[[1]] 139 -24007.57 o$model15[[2]]  108 -11030.68  o$model8[[3]]   38 -26845.97
+23  o$model5[[1]] 163 -23950.60  o$model3[[2]]   87 -11011.79  o$model5[[3]]   38 -26825.20
+24  o$model6[[1]] 163 -23862.94 o$model26[[2]]  136 -10980.93  o$model9[[3]]   38 -26695.14
+25  o$model4[[1]] 226 -23856.48 o$model24[[2]]  122 -10963.97  o$model1[[3]]   31 -26673.04
+26  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86
+
+```{r}
 
 bySpecies <- bySpecies %>%
-     #  mutate( model1 =  map(data, mod[[1]]) ) %>%
-     #  mutate( model2 =  map(data, mod[[2]]) ) %>%
-     #  mutate( model3 =  map(data, mod[[3]]) ) %>%
-     #  mutate( model4 =  map(data, mod[[4]]) ) %>%
-     #  mutate( model5 =  map(data, mod[[5]]) ) %>%
-     #  mutate( model6 =  map(data, mod[[6]]) ) %>%
-     #  mutate( model7 =  map(data, mod[[7]]) ) %>%
-     # mutate( model8 =  map(data, mod[[8]]) ) %>%
-     # mutate( model9 =  map(data, mod[[9]]) ) %>%
-     # mutate( model10 = map(data, mod[[10]]) ) %>%
-     # mutate( model11 = map(data, mod[[11]]) ) %>%
-     # mutate( model12 = map(data, mod[[12]]) ) %>%
-     # mutate( model13 = map(data, mod[[13]]) ) %>%
-     #  mutate( model14 = map(data, mod[[14]]) ) %>%
-     #  mutate( model15 = map(data, mod[[15]]) ) %>%
-     #  mutate( model16 = map(data, mod[[16]]) ) %>%
-     #  mutate( model17 = map(data, mod[[17]]) ) %>%
-     #  mutate( model18 = map(data, mod[[18]]) ) %>%
-     # mutate( model19 = map(data, mod[[19]]) ) %>%
-     #  mutate( model20 = map(data, mod[[20]]) )# %>%
-      mutate( model21 = map(data, mod[[21]])) %>%
-      mutate( model22 = map(data, mod[[22]])) #%>%
-    #  mutate( model23 = map(data, mod[[23]]))
+       mutate( model1 =  map(data, mod[[1]]) ) %>%
+       mutate( model2 =  map(data, mod[[2]]) ) %>%
+       mutate( model3 =  map(data, mod[[3]]) ) %>%
+       mutate( model4 =  map(data, mod[[4]]) ) %>%
+       mutate( model5 =  map(data, mod[[5]]) ) %>%
+       mutate( model6 =  map(data, mod[[6]]) ) %>%
+       mutate( model7 =  map(data, mod[[7]]) ) %>%
+       mutate( model8 =  map(data, mod[[8]]) ) %>%
+       mutate( model9 =  map(data, mod[[9]]) ) %>%
+       mutate( model10 = map(data, mod[[10]]) ) %>%
+       mutate( model11 = map(data, mod[[11]]) ) %>%
+       mutate( model12 = map(data, mod[[12]]) ) %>%
+       mutate( model13 = map(data, mod[[13]]) ) %>%
+       mutate( model14 = map(data, mod[[14]]) ) %>%
+       mutate( model15 = map(data, mod[[15]]) ) %>%
+       mutate( model16 = map(data, mod[[16]]) ) %>%
+       mutate( model17 = map(data, mod[[17]]) ) %>%
+       mutate( model18 = map(data, mod[[18]]) ) %>%
+       mutate( model19 = map(data, mod[[19]]) ) %>%
+       mutate( model20 = map(data, mod[[20]]) ) %>%
+       mutate( model21 = map(data, mod[[21]]) ) %>%
+       mutate( model22 = map(data, mod[[22]]) ) %>%
+       mutate( model23 = map(data, mod[[23]]) ) %>%
+       mutate( model24 = map(data, mod[[24]]) ) %>%
+       mutate( model25 = map(data, mod[[25]]) ) %>%
+       mutate( model26 = map(data, mod[[26]]) )
 ```
 
+> bySpecies$model18[[1]]
+Linear mixed model fit by REML ['lmerMod']
+Formula: grLength ~ isYOY * river * season * tempStd * flowStd + isYOY *  
+    river * season * cBKTStd + isYOY * river * season * cBNTStd +      isYOY * season * cATSStd + isYOY * river * season * cBNTStd2 +  
+    isYOY * river * season * cBNTStd * cBKTStd + (1 | ind) +      (1 | season)
+   Data: df
+REML criterion at convergence: -25277.12
+Random effects:
+ Groups   Name        Std.Dev.
+ ind      (Intercept) 0.02184 
+ season   (Intercept) 0.04763 
+ Residual             0.06008 
+Number of obs: 9967, groups:  ind, 5731; season, 4
+
 ```{r}
-#2 or 5 fish have lengthByYear = NA whcih gives warining of diff # of observations when include mod with lengthByYear
+#2 or 5 fish have lengthByYear = NA whcih gives warning of diff # of observations when include mod with lengthByYear
 
@@
            o$model22[[1]],
-          o$model23[[1]]
+          o$model23[[1]],
+           o$model24[[1]],
+           o$model25[[1]],
+          o$model26[[1]]
          ) %>% rownames_to_column() %>% arrange(AIC) #bkt
@@
            o$model22[[2]],
-           o$model23[[2]]
+           o$model23[[2]],
+           o$model24[[2]],
+           o$model25[[2]],
+          o$model26[[2]]
          ) %>% rownames_to_column() %>% arrange(AIC)#bnt
@@
            o$model22[[3]],
-          o$model23[[3]]
+          o$model23[[3]],
+           o$model24[[3]],
+           o$model25[[3]],
+           o$model26[[3]]
           ) %>% rownames_to_column() %>% arrange(AIC)#ats
@@
 (all <- data.frame(b,n,a))
+
+```
+
+#mod18
+  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
+                   isYOY * river * season * cBKTStd +
+                   isYOY * river * season * cBNTStd +
+                   isYOY *         season * cATSStd +
+                   isYOY * river * season * cBKTStd2 +
+                   isYOY * river * season * cBNTStd2 +
+                   isYOY * river * season * cBNTStd * cBKTStd +
+                   (1|ind) + (1|season), data = df ) }
+
+```{r predict}
+
+x <- seq(-1.5,1.5, by = 0.5)
+
+xGrid <- expand.grid( isYOY=unique(d$isYOY), river=unique(d$river), season=unique(d$season), 
+                      tempStd=x, flowStd=x, cBKTStd=x, cBNTStd=x, cATSStd=x,
+                      ind=1867) %>%
+                    mutate(cBKTStd2=cBKTStd^2, cBNTStd2=cBNTStd^2)
+
+p <- predict( bySpecies$model18[[1]], xGrid )
+xGridP <- cbind(xGrid,p)
+
+tmp <- 
+xGridP %>%
+  group_by(isYOY,river,season) %>%
+  summarize( meanP = round(mean(p),2) )
+
+d %>%
+  group_by(isYOY,river,season) %>%
+#  summarize( meanP = round(mean(grLength, na.rm=T),2) )
+  summarize( meanP = round(mean(flowStd, na.rm=T),2) ) %>%
+  data.frame()
+
+varsToPlot='flowStd'
+isYOYGG=2
+speciesGG='bkt'
+
+#plotPredGrid <- function(xGridP, depVar, varsToPlot, isYOYGG, speciesGG) {
+  all = c('tempStd','flowStd','cBKTStd','cBNTStd','cATSStd')
+
+  #print(c(depVar,(as.name(depVar))))
+
+ # if(length(varsToPlot) == 1) {
+    notPlot <- NA
+    notPlot[1] <- all[!(all %in% varsToPlot)][1]
+    notPlot[2] <- all[!(all %in% varsToPlot)][2]
+    notPlot[3] <- all[!(all %in% varsToPlot)][3]
+    notPlot[4] <- all[!(all %in% varsToPlot)][4]
+ #   notPlot[5] <- all[!(all %in% varsToPlot)][5]
+
+ #   pGG <- p %>% filter(isYOY == isYOYGG, species == speciesGG, eval(as.name(notPlot[1])) == 0, eval(as.name(notPlot[2])) == 0, eval(as.name(notPlot[3])) == 0 ) %>%
+#                 distinct(eval(as.name(varsToPlot[1])), iter, isYOY, river, species, season, .keep_all = TRUE)
+    pGG <- xGridP %>% filter(isYOY == isYOYGG, eval(as.name(notPlot[1])) == 0, eval(as.name(notPlot[2])) == 0, eval(as.name(notPlot[3])) == 0,
+                                          eval(as.name(notPlot[4])) == 0
+                                        #, eval(as.name(notPlot[5])) == 0
+                        ) %>%
+      distinct(eval(as.name(varsToPlot[1])), isYOY, river, season, .keep_all = TRUE)
+
+    ggOut <- 
+      ggplot( pGG, aes( eval(as.name(varsToPlot[1])), p ) ) +
+      geom_line( alpha=0.25 ) +
+      theme_bw() +
+      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank()) +
+      ggtitle(paste0('isYOY = ',isYOYGG,', species = ',speciesGG)) +
+      geom_hline(yintercept = 0) +
+    #  ylim(-0.25,1.33) +
+      scale_x_continuous(varsToPlot[1]) +
+      facet_grid(river~season)
+ggOut
 

### 2018-06-20 R/analyzeOutputFunctions.R

@@ -113,7 +113,31 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
     preds <- cbind( predTemplateLong,grBetaLong )
 
   # This model structure needs to match that in grModelx.jags
-  if(speciesGr == 'ats'){
+    if(speciesGr == 'bkt'){
+      preds <- preds %>%
+        mutate( predGr =
+                  ( int +
+
+                      beta1 * temp +
+                      beta2 * flow +
+                      beta3 * temp * flow +
+
+                      beta4 * cBKT +
+                      beta5 * cBKT^2 +
+
+                      betaBNT1 * cBNT +
+                      betaBNT2 * cBNT^2 +
+                      betaBNT3 * cBNT * cBKT +
+
+                      betaATS1 * cATS
+
+                  ) #* interval
+        ) %>%
+        dplyr::select( flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
+    }
+
+
+  if(speciesGr == 'bnt'){
     preds <- preds %>%
     mutate( predGr =
             ( int +
@@ -122,46 +146,44 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
               beta2 * flow +
               beta3 * temp * flow +
 
-              beta4 * temp^2 +
-              beta5 * flow^2 +
-
-              beta6 * cBKT +
+              beta4 * cBKT +
+              beta5 * cBKT^2 +
 
               betaBNT1 * cBNT +
-           #   betaBNT2 * cBNT^2 +
+              betaBNT2 * cBNT^2 +
           #    betaBNT3 * cBNT * cBKT +
 
               betaATS1 * cATS
-           #   betaATS2 * cATS^2
+          #    betaATS2 * cATS^2
 
             ) #* interval
     ) %>%
     dplyr::select( flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
 
-  } else {
-  preds <- preds %>%
-    mutate( predGr =
-              ( int +
-
-                  beta1 * temp +
-                  beta2 * flow +
-                  beta3 * temp * flow +
-
-                  beta4 * temp^2 +
-                  beta5 * flow^2 +
-
-                  beta6 * cBKT +
-
-                  betaBNT1 * cBNT +
-                  betaBNT2 * cBNT^2 +
-                  betaBNT3 * cBNT * cBKT +
-
[…]

### 2018-06-20 R/growthModelFunctions.R

@@ -57,7 +57,7 @@ runGrowthModel_Nimble <- function(d,mcmcInfo,code,speciesGr,nB){
                 sigmaBeta = array(rnorm(nBetasSigma * 2 * constants$nSeasons * constants$nRivers, 0, 0.05), c(nBetasSigma, 2, constants$nSeasons, constants$nRivers)),
                 #grATSOffset = array(rnorm( 2 * constants$nSeasons, 0, 0.1), c(2,constants$nSeasons) ),
                 grIndRE = rnorm(constants$nInd, 0, 0.1),
-                sigmaIndRE = 1,
+                sigmaIndRE = 0.1,
                 grIntMu = rep(0, constants$nSeasons),
                 grIntSigma = rep(1, constants$nSeasons),
                 grBetaMu = array(0, c(nBetas, constants$nSeasons)),
@@ -93,12 +93,22 @@ runGrowthModel_Nimble <- function(d,mcmcInfo,code,speciesGr,nB){
                 # sigmaBetaBNTSigma = array(1, c(nBetasBNT, constants$nSeasons))
   )
   ##
-  params <- c('grInt', 'grIntMu', 'grIntSigma', 'grBeta', 'grBetaMu',
-              'grBetaSigma', 'sigmaInt', 'sigmaIntMu', 'sigmaIntSigma',
-              'sigmaBeta', 'sigmaBetaMu', 'sigmaBetaSigma', 'grIndRE', 'sigmaIndRE',
+  params <- c('grInt',
+              'grIntMu',
+              'grIntSigma',
+              'grBeta', 'grBetaMu',
+              'grBetaSigma',
+              'sigmaInt',
+              'sigmaIntMu',
+             'sigmaIntSigma',
+              'sigmaBeta', 'sigmaBetaMu',
+              'sigmaBetaSigma',
+              'grIndRE',
+              'sigmaIndRE',
               'lengthExp',
               'grBetaATS','grBetaATSMu','grBetaATSSigma',
-              'grBetaBNT','grBetaBNTMu','grBetaBNTSigma')
+              'grBetaBNT','grBetaBNTMu','grBetaBNTSigma'
+             )
 
   return(list(code=code,data=data,constants=constants,inits=inits,params=params))
 }

### 2018-06-20 R/growthModelFunctions_Code.R

@@ -15,21 +15,22 @@ codeSpp[[1]] <- nimbleCode({
     gr[ evalRows[i] ] <-
       grInt[        isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] +
 
-  #    grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthDATA[evalRows[i]] +
-  #    grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
-      grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] +
-      grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]] +
-      grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] * flowStd[evalRows[i]] +
-
-    #  grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd2[evalRows[i]] +
-      grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] +
-      grBeta[ 5, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
-
-      grBetaBNT[1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]] +
-      grBetaBNT[2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]]^2 +
-      grBetaBNT[3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]] * cBKTStd[evalRows[i]] +
-
[…]

### 2018-06-20 R/plotFunctions.R

@@ -10,7 +10,7 @@ plotInt_Nimble <- function(d){
   ggGrInt$iter <- 1:as.numeric(mcmcInfo$nSamples/mcmcInfo$nChains)
 
   gg <- ggplot(filter(ggGrInt), aes(iter,est)) + geom_point( aes(color=factor(chain)), size = 0.1 ) +
-    ylim(-.5,.5) +
+#    ylim(-.5,.5) +
     #   facet_grid(d2+d4~d5+d3)
     facet_grid(yoy + river ~ season )
   print(gg)
@@ -83,7 +83,9 @@ plotSigmaInt_Nimble <- function(d){
   ggSigmaInt$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples/mcmcInfo$nChains)
   ggSigmaInt$iter <- 1:as.numeric(mcmcInfo$nSamples/mcmcInfo$nChains)
 
-  gg <- ggplot(filter(ggSigmaInt), aes(iter,est)) + geom_point( aes(color=factor(chain)), size = 0.1 ) + ylim(-5,5) + facet_grid(d2+d4~d3)
+  gg <- ggplot(filter(ggSigmaInt), aes(iter,est)) + geom_point( aes(color=factor(chain)), size = 0.1 ) +
+#    ylim(-4,-2.25) +
+    facet_grid(d2+d4~d3)
   print(gg)
 }
 

### 2018-06-20 nimble/mainAnalysis_Nimble.R

@@ -27,7 +27,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "bnt"
+speciesGr <- "bkt"
 #speciesGr = c("bkt", "bnt","ats")
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
@@ -224,26 +224,27 @@ iter=1
   # mcmc run data
   mcmcInfo <- list()
   mcmcInfo$nChains <- 3
-  mcmcInfo$nIter <- 1000#25000
-  mcmcInfo$nBurnIn <- 750#24000
+  mcmcInfo$nIter <- 2000 #25000
+  mcmcInfo$nBurnIn <- 1750 #24000
   mcmcInfo$thinRate <- 1 #fails with thinRate of 3 and 1000/750
   mcmcInfo$nSamples <- round( (mcmcInfo$nIter - mcmcInfo$nBurnIn) * mcmcInfo$nChains / mcmcInfo$thinRate )
 
+
+
+
+  #########################################
+  # Get data for model run
+  source('./R/growthModelFunctions_Code.R') #################################################
+  code <- codeSpp[[as.numeric(speciesInGr)]]
 
   #####
   start <- Sys.time()
   print(start)
   print(c("in loop",meanOrIter,ii,iter))
-
-  #########################################
-  # Get data for model run
-  source('./R/growthModelFunctions_Code.R')
-  code <- codeSpp[[as.numeric(speciesInGr)]]
-
   nB <- list()
 
   if(speciesGr == 'bkt'){
-    nB$nBetas <-5
+    nB$nBetas <- 4
     nB$nBetasBNT <- 3
     nB$nBetasATS <- 1
     nB$nBetasSigma <- 3
@@ -301,18 +302,41 @@ iter=1
   obsPred$rmse
   #obsPred$outliers%>% as.data.frame()
 
+  #hist(mcmcProcessed$mean$grIndRE,breaks=1000)
+  mcmcProcessed$mean$sigmaIndRE
+
+  mcmcProcessed$Rhat$grIntMu
+  mcmcProcessed$Rhat$grIntSigma
+  mcmcProcessed$Rhat$grInt
[…]

### 2018-06-22 manuscriptAnalysis/MS_Analysis.Rmd
updated mcmcInfo

@@
 load("D:/projects/linkedModels/data/cd_west_1997.RData")
+```
+
+```{r bnt density}
+
+ggplot(d2, aes(cBNTStd)) +
+  geom_histogram() +
+  facet_grid(season~riverOrdered)
+
+ggplot(d2, aes(cBNTStd, grLength)) +
+  geom_point(alpha=0.1) +
+  geom_smooth(method='lm') +
+  facet_grid(isYOY+season~riverOrdered)
+
+ggplot(d2, aes(cBKTStd, grLength)) +
+  geom_point(alpha=0.1) +
+  geom_smooth(method='lm') +
+  facet_grid(isYOY+season~riverOrdered)
 ```

### 2018-06-22 manuscriptAnalysis/linearGR_ModelsMap_BKT.Rmd
updated mcmcInfo

@@
 Number of obs: 9967, groups:  ind, 5731; season, 4
+
+> bySpecies$model18[[2]]
+Linear mixed model fit by REML ['lmerMod']
+Formula: grLength ~ isYOY * river * season * tempStd * flowStd + isYOY *  
+    river * season * cBKTStd + isYOY * river * season * cBNTStd +  
+    isYOY * season * cATSStd + isYOY * river * season * cBNTStd2 +  
+    isYOY * river * season * cBNTStd * cBKTStd + (1 | ind) +      (1 | season)
+   Data: df
+REML criterion at convergence: -11461.98
+Random effects:
+ Groups   Name        Std.Dev.
+ ind      (Intercept) 0.01955 
+ season   (Intercept) 0.08491 
+ Residual             0.06018 
+Number of obs: 4495, groups:  ind, 2714; season, 4
+
+> bySpecies$model11[[3]]
+Linear mixed model fit by REML ['lmerMod']
+Formula: grLength ~ isYOY * river * season * tempStd * flowStd + isYOY *  
+    season * cBKTStd * cBNTStd * cATSStd + (1 | ind) + (1 | season)
+   Data: df
+REML criterion at convergence: -29539.29
+Random effects:
+ Groups   Name        Std.Dev.
+ ind      (Intercept) 0.01831 
+ season   (Intercept) 0.03268 
+ Residual             0.03954 
+Number of obs: 8732, groups:  ind, 4183; season, 4
 

### 2018-06-22 R/analyzeOutputFunctions.R

@@ -123,7 +123,6 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
                       beta3 * temp * flow +
 
                       beta4 * cBKT +
-                      beta5 * cBKT^2 +
 
                       betaBNT1 * cBNT +
                       betaBNT2 * cBNT^2 +
@@ -147,11 +146,10 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
               beta3 * temp * flow +
 
               beta4 * cBKT +
-              beta5 * cBKT^2 +
 
               betaBNT1 * cBNT +
               betaBNT2 * cBNT^2 +
-          #    betaBNT3 * cBNT * cBKT +
+              betaBNT3 * cBNT * cBKT +
 
               betaATS1 * cATS
           #    betaATS2 * cATS^2

### 2018-06-22 R/growthModelFunctions_Code.R

@@ -29,7 +29,7 @@ codeSpp[[1]] <- nimbleCode({
         grBetaBNT[2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]]^2 +
         grBetaBNT[3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]] * cBKTStd[evalRows[i]] +
       # #
-      #  grBetaATS[1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cATSStd[evalRows[i]]
+        grBetaATS[1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cATSStd[evalRows[i]] +
       # #  grBetaATS[2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cATSStd[evalRows[i]]^2 +
 
       grIndRE[ ind[evalRows[i]] ]
@@ -167,14 +167,13 @@ codeSpp[[2]] <- nimbleCode({
       grBeta[ 1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] +
       grBeta[ 2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * flowStd[evalRows[i]] +
       grBeta[ 3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[evalRows[i]] * flowStd[evalRows[i]] +
-
-   #   grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd2[evalRows[i]] +
       grBeta[ 4, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] +
-      grBeta[ 5, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
+
[…]

### 2018-06-22 R/plotFunctions.R

@@ -6,11 +6,11 @@ plotInt_Nimble <- function(d){
     #  rename(yoy=d2,species=d3,season=d4,river=d5)
     rename(yoy=d2,season=d3,river=d4)
 
-  ggGrInt$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples/mcmcInfo$nChains)
-  ggGrInt$iter <- 1:as.numeric(mcmcInfo$nSamples/mcmcInfo$nChains)
+  ggGrInt$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples)
+  ggGrInt$iter <- 1:as.numeric(mcmcInfo$nSamples)#/mcmcInfo$nChains)
 
   gg <- ggplot(filter(ggGrInt), aes(iter,est)) + geom_point( aes(color=factor(chain)), size = 0.1 ) +
-#    ylim(-.5,.5) +
+    ylim(-.5,.5) +
     #   facet_grid(d2+d4~d5+d3)
     facet_grid(yoy + river ~ season )
   print(gg)
@@ -21,8 +21,8 @@ plotInt_Nimble <- function(d){
 plotBetas_Nimble <- function(d,b){
   ggGrBeta <- array2df(d$sims.list$grBeta, label.x = "est")
 
-  ggGrBeta$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples/mcmcInfo$nChains)
-  ggGrBeta$iter <- 1:as.numeric(mcmcInfo$nSamples/mcmcInfo$nChains)
+  ggGrBeta$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples)#/mcmcInfo$nChains)
+  ggGrBeta$iter <- 1:as.numeric(mcmcInfo$nSamples)#/mcmcInfo$nChains)
 
   gg <- list()
   numBetas <- 18
@@ -40,8 +40,8 @@ plotBetas_Nimble <- function(d,b){
 plotBetasBNT_Nimble <- function(d,b){
   ggGrBeta <- array2df(d$sims.list$grBetaBNT, label.x = "est")
 
-  ggGrBeta$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples/mcmcInfo$nChains)
[…]

### 2018-06-22 nimble/mainAnalysis_Nimble.R

@@ -27,7 +27,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "bkt"
+speciesGr <- "bnt"
 #speciesGr = c("bkt", "bnt","ats")
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
@@ -220,17 +220,28 @@ iter=1
     #save(dG,ddG,dddG, file = paste0('./data/out/dG_', modelName, '_forLmer.RData')) # for Lmer model with all spp
 
 
+  # #########################################
+  # # mcmc run data
+  # mcmcInfo <- list()
+  # mcmcInfo$nChains <- 3
+  # mcmcInfo$nIter <- 1000 #25000
+  # mcmcInfo$thinRate <- 10 # nIter gets thinned
+  # mcmcInfo$nSamples <- 25 # Number of thinned samples
+  #
+  # try( if(mcmcInfo$nSamples > mcmcInfo$nIter/mcmcInfo$thinRate) stop( 'nSamples > thinned nIter' ) )
+  #
+  # mcmcInfo$nBurnIn <- mcmcInfo$nIter/mcmcInfo$thinRate - mcmcInfo$nSamples
+  # #mcmcInfo$nSamples <- round( (mcmcInfo$nIter - mcmcInfo$nBurnIn) * mcmcInfo$nChains / mcmcInfo$thinRate )
+
   #########################################
   # mcmc run data
   mcmcInfo <- list()
   mcmcInfo$nChains <- 3
-  mcmcInfo$nIter <- 2000 #25000
-  mcmcInfo$nBurnIn <- 1750 #24000
-  mcmcInfo$thinRate <- 1 #fails with thinRate of 3 and 1000/750
-  mcmcInfo$nSamples <- round( (mcmcInfo$nIter - mcmcInfo$nBurnIn) * mcmcInfo$nChains / mcmcInfo$thinRate )
-
-
-
+  mcmcInfo$nIter <- 10000 #25000
+  mcmcInfo$nBurnIn <- 7500
+  mcmcInfo$AvailForSampling <- mcmcInfo$nIter - mcmcInfo$nBurnIn
+  mcmcInfo$thinRate <- 10
[…]

### 2018-06-25 manuscriptAnalysis/MS_Analysis.Rmd
with good long runs

@@
 mcmc <- list()
-load("D:/projects/linkedModels/data/out/dG_1528425682_bkt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1529763682_bkt1997_Nimble.RData")
 
@@
 
-load("D:/projects/linkedModels/data/out/dG_1528410796_bnt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1529720799_bnt1997_Nimble.RData")
 mcmc[['bnt']]  <- mcmcProcessed
 
-load("D:/projects/linkedModels/data/out/dG_1528735018_ats1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1529778009_ats1997_Nimble.RData")
 mcmc[['ats']]  <- mcmcProcessed
@@
 
-len %>% filter(ind == 1, !firstObs, iter%%50==0) %>%
+len %>% filter(ind == 20, !firstObs, iter%%50==0) %>%
   ggplot(aes(obs,est)) +
@@
 rHat <- list()
-rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:5,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
-rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:5,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
+rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
+rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
 rHat[['ats']] <- array2df(mcmc[['ats']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="rHat")
@@
 
-ggplot(rHat[[3]], aes(beta,rHat)) +
+ggplot(rHat[[1]], aes(beta,rHat)) +
   geom_point() +

### 2018-06-25 R/analyzeOutputFunctions.R

@@ -300,20 +300,20 @@ getPredictionSigma <- function(d, limits = 2, nPoints = 5, itersForPred, constan
   preds <- cbind( predTemplateLong,grBetaLong )
 
   # This model structure needs to match that in grModelx.jags
-  if(speciesGr == 'ats'){
-  preds <- preds %>%
-    mutate( predGrSigma =
-              exp( int
-
-                #  beta1 * temp
-                 ## beta2 * flow +
-                #  beta3 * temp * flow
-
-              ) #* interval
-    ) %>%
-    dplyr::select( flow,temp,iter,isYOY,season,river,predGrSigma )
-
-  } else {
+  # if(speciesGr == 'ats'){
+  # preds <- preds %>%
+  #   mutate( predGrSigma =
+  #             exp( int
+  #
+  #               #  beta1 * temp
+  #                ## beta2 * flow +
+  #               #  beta3 * temp * flow
+  #
+  #             ) #* interval
+  #   ) %>%
+  #   dplyr::select( flow,temp,iter,isYOY,season,river,predGrSigma )
+  #
+  # } else {
   preds <- preds %>%
     mutate( predGrSigma =
               exp( int +
@@ -325,7 +325,7 @@ getPredictionSigma <- function(d, limits = 2, nPoints = 5, itersForPred, constan
               ) #* interval
     ) %>%
     dplyr::select( flow,temp,iter,isYOY,season,river,predGrSigma )
-  }
+#  }
 
   return(preds)
 
@@ -694,15 +694,22 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
   outlierFish <- ddGIn %>% filter(tag %in% outlierFish1$tag) %>%
     dplyr::select(tag,season,sampleName,observedLength,lengthDATALnStd,observedLength,estLen,resid,rowNumber,isOutlier,species)
 
-  gg <- ggplot( ddGIn, aes( observedLength, estLen, color = factor(year) ) ) +
+  gg <- ggplot( ddGIn, aes( observedLengthOriginal, estLen, color = factor(year) ) ) +
         geom_point( alpha = 0.8 ) +
         geom_abline(intercept = 0, slope = 1) +
  #   ylim(-2,4) +
         facet_grid(isYOY+riverN~season+leftOut)
   print(gg)
 
[…]

### 2018-06-25 R/growthModelFunctions_Code.R

@@ -465,7 +465,7 @@ codeSpp[[3]] <- nimbleCode({
 
   }
   ##
-  sigmaIndRE ~ dunif(0.01,0.5)
+  sigmaIndRE ~ dunif(0.001,0.5)
 
 
 })

### 2018-06-25 nimble/mainAnalysis_Nimble.R

@@ -27,7 +27,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "ats"
+speciesGr <- "bkt"
 #speciesGr = c("bkt", "bnt","ats")
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
@@ -39,7 +39,7 @@ maxSampleInterval <- 200 # <
 recreatecdFileBeforeDetMod_TF <- FALSE
 runDetectionModel_TF <- FALSE
 recreateCD_TF <- FALSE
-runCrossValidation_TF <- FALSE
+runCrossValidation_TF <- TRUE
 percentLeftOut <- 10
 
 meanOrIter <- "mean"; iter <- 1
@@ -237,8 +237,8 @@ iter=1
   # mcmc run data
   mcmcInfo <- list()
   mcmcInfo$nChains <- 3
-  mcmcInfo$nIter <- 2000 #25000
-  mcmcInfo$nBurnIn <- 1500
+  mcmcInfo$nIter <- 5000 #25000
+  mcmcInfo$nBurnIn <- 4000
   mcmcInfo$AvailForSampling <- mcmcInfo$nIter - mcmcInfo$nBurnIn
   mcmcInfo$thinRate <- 10
   mcmcInfo$nSamples <- mcmcInfo$AvailForSampling / mcmcInfo$thinRate
@@ -337,7 +337,7 @@ iter=1
 
   #########################################
   # save data to file
-  save(mcmcInfo,mcmcProcessed,dG,ddG,nB, file = paste0('./data/out/dG_', as.integer(Sys.time()),'_', modelName, '_Nimble.RData'))
+  save(mcmcInfo,mcmcProcessed,dG,ddG,nB,speciesGr,riverOrderedIn, file = paste0('./data/out/dG_', as.integer(Sys.time()),'_crossVal',runCrossValidation_TF,"_", modelName, '_Nimble.RData'))
 
   ######################
   # Plot traces
@@ -359,6 +359,11 @@ iter=1
 
   #########################
   # Predictions
+  ### temporary variables needed if do predictions after loading output files
+  ii <- 1
[…]

### 2018-07-06 manuscriptAnalysis/MS_Analysis.Rmd
add pred graph for WB only

@@
 library(tidyverse)
+library(gridExtra)
 
@@
 mcmc <- list()
-load("D:/projects/linkedModels/data/out/dG_1529763682_bkt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1530190754_crossValFALSE_bkt1997_Nimble.RData")
 
@@
 
-load("D:/projects/linkedModels/data/out/dG_1529720799_bnt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1530220511_crossValFALSE_bnt1997_Nimble.RData")
 mcmc[['bnt']]  <- mcmcProcessed
 
-load("D:/projects/linkedModels/data/out/dG_1529778009_ats1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1530239054_crossValFALSE_ats1997_Nimble.RData")
 mcmc[['ats']]  <- mcmcProcessed
@@
 rHat <- list()
-rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
-rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
-rHat[['ats']] <- array2df(mcmc[['ats']]$Rhat$grBeta, levels = list(beta=1:4,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="rHat")
+rHat[['bkt']] <- array2df(mcmc[['bkt']]$Rhat$grBeta, levels = list(beta=1:7,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="rHat")
+rHat[['bnt']] <- array2df(mcmc[['bnt']]$Rhat$grBeta, levels = list(beta=1:7,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="rHat")
+rHat[['ats']] <- array2df(mcmc[['ats']]$Rhat$grBeta, levels = list(beta=1:7,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="rHat")
 
@@
 
-ggplot(rHat[[1]], aes(beta,rHat)) +
+ggplot(rHat[["ats"]], aes(beta,rHat)) +
   geom_point() +
@@
 ```{r}
-riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
+#riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
 
@@
   xlim(-0.25,0.75) +
-  ylim(0,500) +
+ # ylim(0,2500) +
   theme_publication() +
@@
 ```{r predictions}
-# #run if get new predictions - takes a while to run
+# 
+#####run if get new predictions - takes a while to run ####
+
  # load('D:/projects/linkedModels/data/out/P_ForMike_bkt.RData')
@@
  # 
-# pred <- pAll %>% group_by(species,flow,temp,cBKT,cBNT,cATS,isYOY,season,river) %>%
+ # pred <- pAll %>% group_by(species,len,flow,temp,cBKT,cBNT,cATS,isYOY,season,river) %>%
  #   summarize(meanPredGR = mean(predGr, na.rm=T),
@@
  # save(pred,file = 'D:/projects/linkedModels/data/out/P_ForMike_allMeans.RData')
+
 load('D:/projects/linkedModels/data/out/P_ForMike_allMeans.RData')
@@
 ggsave('figures/tmp.png', width = 9, height = 7, units='in')
+```
+
+```{r}
+
+all <- c('len','temp','flow','cBKT','cBNT','cATS')
+allLabels <- c('Length (mm)','Temperature (C)','Flow (m3/s)','Brook Trout abundance','Brown Trout abundance','Atlantic Salmon abundance')
+
+all <- c('len','cBKT','temp','cBNT','flow','cATS')
+allLabels <- c('Length (mm)','Brook Trout abundance','Stream temperature (C)','Brown Trout abundance','Stream flow (m3/s)','Atlantic Salmon abundance')
+
+remFacetLabel <- c(3,4,5,6)
+
+selectSingleVar <- function(p, all, depVar, varsToPlot, isYOYGG){
+
+  notPlot <- NA
+  notPlot[1] <- all[!(all %in% varsToPlot)][1]
+  notPlot[2] <- all[!(all %in% varsToPlot)][2]
+  notPlot[3] <- all[!(all %in% varsToPlot)][3]
+  notPlot[4] <- all[!(all %in% varsToPlot)][4]
+  notPlot[5] <- all[!(all %in% varsToPlot)][5]
+
+  pGG <- p %>% filter(isYOY == isYOYGG, 
+                        eval(as.name(notPlot[1])) == 0, 
+                        eval(as.name(notPlot[2])) == 0, 
+                        eval(as.name(notPlot[3])) == 0,                                         
+                        eval(as.name(notPlot[4])) == 0, 
+                        eval(as.name(notPlot[5])) == 0
+                      )#%>%
+              # distinct(species, isYOY, riverGG, seasonGG, speciesGG, .keep_all = TRUE)
+
+  return(pGG)  
+}
+
+isYOYGG <- 0
+
+ggSingle <- list()
+singleDat <- list()
+for(i in 1:length(all))
+  #https://stackoverflow.com/questions/31993704/storing-ggplot-objects-in-a-list-from-within-loop-in-r
+      local({ i <- i
+  singleDat[[i]] <- selectSingleVar(pred, all, "meanPredGR", all[i], isYOYGG)
+  print(c(i,all[i]))
+ # print(str(singleDat[[i]]))
+
+  tmp <- singleDat[[i]] %>% filter(riverGG == "West Brook")
+  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), meanPredGR, color=speciesGG ) ) +
+      geom_line( size = 1.225 ) +
+      theme_bw() +
+      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
+            axis.title.y = element_blank(),
+            legend.position="none") +
+      geom_hline(yintercept = 0) +
+      ylim(-0.15,0.8) +
+      scale_x_continuous(allLabels[i]) +
+      facet_grid(~seasonGG)
+
+  if( i %in% remFacetLabel ) {
+    ggSingle[[i]] <<- ggSingle[[i]] +
+    theme(
+      strip.background = element_blank(),
+      strip.text.x = element_blank()
+    )
+  }
+})
+
+grid.arrange(grobs=ggSingle, left = "Growth rate (mm/d)")
+
 ```

### 2018-07-06 R/analyzeOutputFunctions.R

@@ -146,22 +146,26 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
     mutate( predGr =
             ( int +
 
-              beta1 * temp +
-              beta2 * flow +
-              beta3 * temp * flow +
+                beta1 * temp +
+                beta2 * flow +
+                beta3 * temp * flow +
+                beta4 * temp^2 +
+                beta5 * flow^2 +
 
-              beta4 * cBKT +
+                beta6 * cBKT +
+
+                beta7 * len +
 
               betaBNT1 * cBNT +
               betaBNT2 * cBNT^2 +
               betaBNT3 * cBNT * cBKT +
 
-              betaATS1 * cATS
-          #    betaATS2 * cATS^2
+              betaATS1 * cATS +
+              betaATS2 * cATS^2
 
             ) #* interval
     ) %>%
-    dplyr::select( flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
+    dplyr::select( len,flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
 
   }
 
@@ -173,17 +177,23 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
                       beta1 * temp +
                       beta2 * flow +
                       beta3 * temp * flow +
+                      beta4 * temp^2 +
+                      beta5 * flow^2 +
 
-                      beta4 * cBKT +
+                      beta6 * cBKT +
+
+                      beta7 * len +
 
                       betaBNT1 * cBNT +
+                      betaBNT2 * cBNT^2 +
+                      betaBNT3 * cBNT * cBKT +
 
                       betaATS1 * cATS +
                       betaATS2 * cATS^2
 
                   ) #* interval
         ) %>%
-        dplyr::select( flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
+        dplyr::select( len,flow,temp,cBKT,cBNT,cATS,iter,isYOY,season,river,predGr )
 
     }
 
@@ -721,4 +731,59 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
                pValue = sum(isAbovePred,na.rm=T) / sum(!is.na(isAbovePred)) )
 
   return(list(rmse = rmse, outliers = outlierFish))
+}
+
+
+#http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/
[…]

### 2018-07-06 R/growthModelFunctions_Code.R

@@ -41,14 +41,15 @@ codeSpp[[1]] <- nimbleCode({
   #     grBeta[ 6, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * tempStd[ evalRows[i] ]^2 * flowStd[ evalRows[i] ]^2 +
       grBeta[ 6, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] +
   #     grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
-       grBeta[ 7, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]] +
+      grBeta[ 7, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]] +
+      grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]]^2 +
       # #
       grBetaBNT[1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]] +
-      grBetaBNT[2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]]^2 +
-      grBetaBNT[3, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]] * cBKTStd[evalRows[i]] +
+ #     grBetaBNT[2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]]^2 +
+      grBetaBNT[2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]] * cBKTStd[evalRows[i]] +
       # #
-      grBetaATS[1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cATSStd[evalRows[i]] +
[…]

### 2018-07-06 R/plotFunctions.R

@@ -24,15 +24,26 @@ plotBetas_Nimble <- function(d,b){
   ggGrBeta$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples)#/mcmcInfo$nChains)
   ggGrBeta$iter <- 1:as.numeric(mcmcInfo$nSamples)#/mcmcInfo$nChains)
 
+  ggOverlap0 <- array2df(d$overlap0$grBeta, label.x = "est0") %>%
+    rename( d2=d1,d3=d2,d4=d3,d5=d4 )
+
+  ggNEff <- array2df(d$n.eff$grBeta, label.x = "estNE") %>%
+    rename( d2=d1,d3=d2,d4=d3,d5=d4 )
+
   gg <- list()
-  numBetas <- 18
+  numBetas <- nB$nBetas
   for (i in 1:numBetas){
     gg[[i]] <- ggplot(filter(ggGrBeta,d2 == i), aes(iter,est)) +
       geom_hline(yintercept = 0) +
       geom_point( aes(color = factor(chain)), size = 0.1 ) +
       ylim(-.05,.05) +
+      geom_text(aes(label = est0, x=-100, y = 0, color = factor(est0+90)),
+                data = filter(ggOverlap0,d2 == i) ) +
+      geom_text(aes(label = estNE, x=250, y = 0.03),
+                data = filter(ggNEff,d2 == i) ) +
       facet_grid(d3+d5 ~ d4) +
       ggtitle(paste("beta =", i))
+
     if(i %in% b) print(gg[[i]])
   }
 }
@@ -43,6 +54,9 @@ plotBetasBNT_Nimble <- function(d,b){
   ggGrBeta$chain <- rep(1:mcmcInfo$nChains, each = mcmcInfo$nSamples)#/mcmcInfo$nChains)
   ggGrBeta$iter <- 1:as.numeric(mcmcInfo$nSamples)#/mcmcInfo$nChains)
 
+  ggOverlap0 <- array2df(d$overlap0$grBetaBNT, label.x = "est0") %>%
+    rename( d2=d1,d3=d2,d4=d3,d5=d4 )
+
   gg <- list()
   numBetas <- 8
   for (i in 1:numBetas){
@@ -50,10 +64,13 @@ plotBetasBNT_Nimble <- function(d,b){
       geom_hline(yintercept = 0) +
       geom_point( aes(color = factor(chain)), size = 0.1 ) +
          ylim(-.1,.1) +
[…]

### 2018-07-06 nimble/mainAnalysis_Nimble.R

@@ -27,7 +27,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "bkt"
+speciesGr <- "bnt"
 #speciesGr = c("bkt", "bnt","ats")
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
@@ -243,23 +243,23 @@ iter=1
   nB <- list()
 
   if(speciesGr == 'bkt'){
-    nB$nBetas <- 7
-    nB$nBetasBNT <- 3
-    nB$nBetasATS <- 2
+    nB$nBetas <- 8
+    nB$nBetasBNT <- 2
+    nB$nBetasATS <- 1
     nB$nBetasSigma <- 3
   }
 
   if(speciesGr == 'bnt'){
-    nB$nBetas <- 4
-    nB$nBetasBNT <- 3
+    nB$nBetas <- 8
+    nB$nBetasBNT <- 2
     nB$nBetasATS <- 1
     nB$nBetasSigma <- 3
   }
 
   if(speciesGr == 'ats'){
-    nB$nBetas <- 4
-    nB$nBetasBNT <- 1
-    nB$nBetasATS <- 2
+    nB$nBetas <- 8
+    nB$nBetasBNT <- 2
+    nB$nBetasATS <- 1
     nB$nBetasSigma <- 3
   }
 
@@ -326,11 +326,12 @@ iter=1
   obsPred$rmse
   #obsPred$outliers%>% as.data.frame()
 
-  getPropOverlapBetas(mcmcProcessed,nB)
+  getPropOverlap0Betas(mcmcProcessed,nB)
 
   #hist(mcmcProcessed$mean$grIndRE[mcmcProcessed$mean$grIndRE != 0] ,breaks=1000)
   mcmcProcessed$mean$sigmaIndRE
 
+  # rHats
   mcmcProcessed$Rhat$grIntMu
   mcmcProcessed$Rhat$grIntSigma
   mcmcProcessed$Rhat$grInt
@@ -361,7 +362,7 @@ iter=1
   plotInt_Nimble(mcmcProcessed)
 
   plotBetas_Nimble(mcmcProcessed,1:4)
-  plotBetas_Nimble(mcmcProcessed,6:9)
[…]

### 2018-07-10 manuscriptAnalysis/MS_Analysis.Rmd
add grBetas graph

@@
 output: html_notebook
+editor_options: 
+  chunk_output_type: console
 ---
@@
 mcmc <- list()
-load("D:/projects/linkedModels/data/out/dG_1530190754_crossValFALSE_bkt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1530971738_crossValFALSE_bkt1997_Nimble.RData")
 
@@
 
-load("D:/projects/linkedModels/data/out/dG_1530220511_crossValFALSE_bnt1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1530971744_crossValFALSE_bnt1997_Nimble.RData")
 mcmc[['bnt']]  <- mcmcProcessed
 
-load("D:/projects/linkedModels/data/out/dG_1530239054_crossValFALSE_ats1997_Nimble.RData")
+load("D:/projects/linkedModels/data/out/dG_1530993703_crossValFALSE_ats1997_Nimble.RData")
 mcmc[['ats']]  <- mcmcProcessed
@@
 
+```{r mcmc output analysis-grBeta}
+
+# get all betas in a DF
+grBeta <- list()
+grBeta[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grBeta, levels = list(iter=NA,beta=1:7,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>%
+  mutate( species = 'bkt')
+grBeta[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grBeta, levels = list(iter=NA,beta=1:7,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int") %>%
+  mutate( species = 'bnt')
+grBeta[['ats']] <- array2df(mcmc[['ats']]$sims.list$grBeta, levels = list(iter=NA,beta=1:7,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int") %>%
+  mutate( species = 'ats')
+
+grBetaDF1 <- rbind(grBeta[['bkt']],grBeta[['bnt']],grBeta[['ats']])
+
+grBetaBNT <- list()
+grBetaBNT[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grBetaBNT, levels = list(iter=NA,beta=8:9,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>%
+  mutate( species = 'bkt')
+grBetaBNT[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grBetaBNT, levels = list(iter=NA,beta=8:9,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int") %>%
+  mutate( species = 'bnt')
+grBetaBNT[['ats']] <- array2df(mcmc[['ats']]$sims.list$grBetaBNT, levels = list(iter=NA,beta=8:9,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int") %>%
+  mutate( species = 'ats')
+
+grBetaBNTDF <- rbind(grBetaBNT[['bkt']],grBetaBNT[['bnt']],grBetaBNT[['ats']])
+
+grBetaATS <- list()
+grBetaATS[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grBetaATS, levels = list(iter=NA,beta=10,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>%
+  mutate( species = 'bkt')
+grBetaATS[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grBetaATS, levels = list(iter=NA,beta=10,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int") %>%
+  mutate( species = 'bnt')
+grBetaATS[['ats']] <- array2df(mcmc[['ats']]$sims.list$grBetaATS, levels = list(iter=NA,beta=10,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int") %>%
+  mutate( species = 'ats')
+
+grBetaATSDF <- rbind(grBetaATS[['bkt']],grBetaATS[['bnt']],grBetaATS[['ats']])
+
+grBetaDF <- rbind(grBetaDF1,grBetaBNTDF,grBetaATSDF)
+##################################################
+# as range plot
+
+  nRivers <- list()
+  nRivers[['bkt']] <- 4; nRivers[['bnt']] <- 2; nRivers[['ats']] <- 1
+  speciesList <- list('bkt','bnt','ats')
+
+  probs <- c(0.05,0.1,0.5,0.9,0.95)
+  nSpecies <- 3
+
+  q <- grBetaDF %>%
+    group_by(beta,isYOY,season,river,species) %>%
+    summarize(
+      p = list(probs),
+      q = list(quantile(int,probs))
+    ) %>%
+    unnest() %>%
+    spread(key = p, value = q) %>%
+    data.frame() %>%
+    rename( median = X0.5, lo = X0.05, hi = X0.95 )
+
+  q <- q %>% filter( !(river == 'west brook' & season == 2 & isYOY == 0))
+
+q$riverGG <- factor(q$river,
+                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
+                         labels = c("WB","OL","OS","IL"), ordered = T)
+q$seasonGG <- factor(q$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+q$speciesGG <- factor(q$species, levels = c('bkt','bnt','ats'), labels = c("BKT", "BNT", "ATS"), ordered = T)
+q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"), ordered = T)
+q$parameter = paste0(q$riverGG,"_",q$speciesGG)
+q$parameterOrd <- factor(q$parameter, levels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), labels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
+
+  q <- q %>% filter( !(betaGG == 'ATS' & (riverGG == "OS" | riverGG == "IL" | riverGG == "OL")) )
+  q <- q %>% filter( !(betaGG == 'BNT' & (riverGG == "OS" | riverGG == "IL")) )
+  q <- q %>% filter( !(betaGG == 'BNT*BKT' & (riverGG == "OS" | riverGG == "IL")) )
+#reorder(parameter,median,na.rm=TRUE)
+(min(q$median))
+  (max(q$median))
+#  q[q$median < -0.13,]
+
+    ggplot(q, aes(x = median, y = parameterOrd, color = factor(speciesGG), shape = factor(isYOY))) + 
+        geom_vline(xintercept = 0,color='black') +
+        theme_publication() +  
+        geom_point(size = 3) +
+        geom_segment(aes(x = median, xend = hi, yend = parameterOrd), 
+        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
+        geom_segment(aes(x = median, xend = lo, yend = parameterOrd), 
+        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
+        xlim(c(-0.15,0.14)) +
+        xlab("Parameter estimate") + ylab("River_Species") +
+        facet_grid(seasonGG~betaGG)
+
+ggsave('figures/grBetas.png', height = 7, width = 10, scale = 2)
+
+```
+
 ```{r ind RE among spp}
@@
 
-```{r}
+```{r mean prediction graphs}
 
@@
 
+##### by species
+
 isYOYGG <- 0
+riverGGToPlot <- "Open Large"
 
@@
 
-  tmp <- singleDat[[i]] %>% filter(riverGG == "West Brook")
+  tmp <- singleDat[[i]] %>% filter(riverGG == riverGGToPlot)
   ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), meanPredGR, color=speciesGG ) ) +
@@
 
+###### by river for bkt
+
+isYOYGG <- 1
+speciesGGToPlot <- "Brook Trout"
+
+ggSingle <- list()
+singleDat <- list()
+for(i in 1:length(all))
+  #https://stackoverflow.com/questions/31993704/storing-ggplot-objects-in-a-list-from-within-loop-in-r
+      local({ i <- i
+  singleDat[[i]] <- selectSingleVar(pred, all, "meanPredGR", all[i], isYOYGG)
+  print(c(i,all[i]))
+ # print(str(singleDat[[i]]))
+
+  tmp <- singleDat[[i]] %>% filter(speciesGG == speciesGGToPlot)
+  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), meanPredGR, color=riverGG ) ) +
+      geom_line( size = 1.225 ) +
+      theme_bw() +
+      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
+            axis.title.y = element_blank(),
+            legend.position="none"
+            ) +
+      geom_hline(yintercept = 0) +
+      ylim(-0.15,0.8) +
+      scale_x_continuous(allLabels[i]) +
+      facet_grid(~seasonGG)
+
+  if( i %in% remFacetLabel ) {
+    ggSingle[[i]] <<- ggSingle[[i]] +
+    theme(
+      strip.background = element_blank(),
+      strip.text.x = element_blank()
+    )
+  }
+})
+
+grid.arrange(grobs=ggSingle, left = "Growth rate (mm/d)")
+
+```
+
+```{r 2d denstiy plots of mean predictions}
+
+selectPairVars <- function(p, all, depVar, varsToPlot, isYOYGG){
+
+  notPlot <- NA
+  notPlot[1] <- all[!(all %in% varsToPlot)][1]
+  notPlot[2] <- all[!(all %in% varsToPlot)][2]
+  notPlot[3] <- all[!(all %in% varsToPlot)][3]
+  notPlot[4] <- all[!(all %in% varsToPlot)][4]
+#  notPlot[5] <- all[!(all %in% varsToPlot)][5]
+
+  pGG <- p %>% filter( isYOY == isYOYGG, 
+                        eval(as.name(notPlot[1])) == 0, 
+                        eval(as.name(notPlot[2])) == 0, 
+                        eval(as.name(notPlot[3])) == 0,                                         
+                        eval(as.name(notPlot[4])) == 0 )
+  return(pGG)  
+}
+
+isYOYGG <- 1
+speciesToPlot <- "ats"
+
+for(i in c('bkt','bnt', 'ats')){
+  for(j in 0:1){
+  print(c(i,j))
+
+  p <- selectPairVars(pred, all, "meanPredGR", c("flow","temp"), j)  %>%
+         filter(species == i)
+
+  ggplot(p, aes(x = flow, y = temp, z = meanPredGR)) +
+    geom_tile(aes(fill = meanPredGR)) +
+    stat_contour(bins = 15, color = 'darkgrey') +
+    ggtitle(paste(j,i)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank(), panel.grid.major =        element_blank(), 
+          #axis.title.y = element_blank(),
+          legend.position="none"
+          ) +
+    facet_grid( riverGG ~ seasonGG )
+
+  ggsave(paste0('figures/predGRGrid',"_",i,"_",j,'.png'), width = 9, height = 7, units='in')
+
+  }
+}
+
+#raw data plot - not very useful
+ggplot(d2, aes(x=flowStd,y=tempStd,z=grLength)) +
+ #  stat_density_2d( color = 'darkgrey') +
+  stat_density_2d(geom = "raster", aes(fill = ..density..), contour = FALSE,interpolate=TRUE,h=2.5) +
+  facet_grid(season+isYOY~river+species)
+
+ggplot(d2, aes(x=tempStd,y=grLength)) +
+  geom_smooth() +
+  geom_smooth(method='lm',color='black',se=FALSE) +
+  ylim(c(0,0.8)) +
+  facet_grid(river+isYOY~season)
 ```

### 2018-07-10 R/analyzeOutputFunctions.R

@@ -129,11 +129,11 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
                       beta7 * len +
 
                       betaBNT1 * cBNT +
-                      betaBNT2 * cBNT^2 +
-                      betaBNT3 * cBNT * cBKT +
+                  #    betaBNT2 * cBNT^2 +
+                      betaBNT2 * cBNT * cBKT +
 
-                      betaATS1 * cATS +
-                      betaATS2 * cATS^2
+                      betaATS1 * cATS
+                 #     betaATS2 * cATS^2
 
                   ) #* interval
         ) %>%
@@ -156,12 +156,12 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
 
                 beta7 * len +
 
-              betaBNT1 * cBNT +
-              betaBNT2 * cBNT^2 +
-              betaBNT3 * cBNT * cBKT +
+                betaBNT1 * cBNT +
+                #    betaBNT2 * cBNT^2 +
+                betaBNT2 * cBNT * cBKT +
 
-              betaATS1 * cATS +
-              betaATS2 * cATS^2
+                betaATS1 * cATS
+              #     betaATS2 * cATS^2
 
             ) #* interval
     ) %>%
@@ -185,11 +185,11 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
                       beta7 * len +
 
                       betaBNT1 * cBNT +
-                      betaBNT2 * cBNT^2 +
-                      betaBNT3 * cBNT * cBKT +
+                      #    betaBNT2 * cBNT^2 +
+                      betaBNT2 * cBNT * cBKT +
 
-                      betaATS1 * cATS +
-                      betaATS2 * cATS^2
+                      betaATS1 * cATS
+                    #     betaATS2 * cATS^2
 
                   ) #* interval
         ) %>%

### 2018-07-10 R/getPropOverlap.R

@@ -1,11 +1,11 @@
 #'Estimate proportion overlap for betas
 #'
 #'@param mcmcProcessed a list generated using process.output()
-#'@param nB a data frame containing the number of beats for the run
+#'@param nB a data frame containing the number of betas for the run
 #'@return Prints the proportion of [,isYOY,season,river] beta means that overlap 0
 #'@export
 
-getPropOverlapBetas <- function(mcmcProcessed,nB){
+getPropOverlap0Betas <- function(mcmcProcessed,nB){
 
   getProp <- function(i) {
     sum(i*1)/length(i)
@@ -25,7 +25,7 @@ getPropOverlapBetas <- function(mcmcProcessed,nB){
   # for each BNT beta
   print("grBetaBNT")
   for ( i in 1:nB$nBetasBNT ){
-    prop <- lapply( mcmcProcessed$overlap0$grBetaBNT[i,,,], getProp )
+    prop <- lapply( mcmcProcessed$overlap0$grBetaBNT[i,,,1:2], getProp )
     print( sum(data.frame(prop)) / length(data.frame(prop)) )
   }
   print("")
@@ -33,7 +33,7 @@ getPropOverlapBetas <- function(mcmcProcessed,nB){
   # for each ATS beta
   print("grBetaATS")
   for ( i in 1:nB$nBetasATS ){
-    prop <- lapply( mcmcProcessed$overlap0$grBetaATS[i,,,], getProp )
+    prop <- lapply( mcmcProcessed$overlap0$grBetaATS[i,,,1], getProp )
     print( sum(data.frame(prop)) / length(data.frame(prop)) )
   }
 }

### 2018-07-10 R/growthModelFunctions_Code.R

@@ -42,7 +42,7 @@ codeSpp[[1]] <- nimbleCode({
       grBeta[ 6, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] +
   #     grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
       grBeta[ 7, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]] +
-      grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]]^2 +
+  #    grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]]^2 +
       # #
       grBetaBNT[1, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]] +
  #     grBetaBNT[2, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBNTStd[evalRows[i]]^2 +
@@ -219,7 +219,7 @@ codeSpp[[2]] <- nimbleCode({
       grBeta[ 6, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]] +
       #     grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * cBKTStd[evalRows[i]]^2 +
       grBeta[ 7, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]] +
-      grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]]^2 +
+   #   grBeta[ 8, isYOYDATA[evalRows[i]], season[evalRows[i]], riverDATA[evalRows[i]] ] * lengthStd[evalRows[i]]^2 +
       # #
[…]

### 2018-07-10 nimble/mainAnalysis_Nimble.R

@@ -27,7 +27,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "bnt"
+speciesGr <- "ats"
 #speciesGr = c("bkt", "bnt","ats")
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
@@ -243,21 +243,21 @@ iter=1
   nB <- list()
 
   if(speciesGr == 'bkt'){
-    nB$nBetas <- 8
+    nB$nBetas <- 7
     nB$nBetasBNT <- 2
     nB$nBetasATS <- 1
     nB$nBetasSigma <- 3
   }
 
   if(speciesGr == 'bnt'){
-    nB$nBetas <- 8
+    nB$nBetas <- 7
     nB$nBetasBNT <- 2
     nB$nBetasATS <- 1
     nB$nBetasSigma <- 3
   }
 
   if(speciesGr == 'ats'){
-    nB$nBetas <- 8
+    nB$nBetas <- 7
     nB$nBetasBNT <- 2
     nB$nBetasATS <- 1
     nB$nBetasSigma <- 3

### 2018-07-16 manuscriptAnalysis/MS_Analysis.Rmd
added grSigma graph

@@
 ```{r functions}
-theme_publication <- function(base_size=14, base_family="") {
-  library(grid)
-  library(ggthemes)
-  (theme_foundation(base_size=base_size, base_family=base_family)
-    + theme(plot.title = element_text(face = "bold",
-                                      size = rel(1.2), hjust = 0.5),
-            text = element_text(),
-            panel.background = element_rect(colour = NA),
-            plot.background = element_rect(colour = NA),
-            axis.title = element_text(face = "bold",size = rel(1)),
-            axis.title.y = element_text(angle=90,vjust =2),
-            axis.title.x = element_text(vjust = -0.2),
-            axis.text = element_text(),
-            axis.line = element_line(colour="black"),
-            axis.ticks = element_line(),
-            panel.grid.major = element_line(colour="#f0f0f0"),
-            panel.grid.minor = element_blank(),
-            legend.key = element_rect(colour = NA),
-            legend.position = "bottom",
-            legend.direction = "horizontal",
-            legend.key.size= unit(0.2, "cm"),
-        #    legend.margin = unit(0, "cm"),
-            legend.title = element_text(face="italic"),
-            plot.margin=unit(c(10,5,5,5),"mm"),
-            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
-            strip.text = element_text(face="bold"),
-            panel.border = element_rect(colour = "black")
-    ))
-
-}
-
-scale_fill_Publication <- function(...){
-  library(scales)
-  discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
-
-}
-
-scale_colour_Publication <- function(...){
-  library(scales)
-  discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
-
-}
 
@@
 
-```{r figs 3,4}
+```{r figs 3,4, flow and temp}
 d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
@@
 
-```
+# mean growth by species
+```
+
+```{r mean growth rate ratios}
+
+cd %>% group_by(species) %>%
+  summarize(meanGR = mean(grLength, na.rm=T),
+            sdGR = sd(grLength, na.rm=T))
+.162/.194 #bkt/bnt
+.151/.194 #ats/bnt
+
+cd %>% group_by(isYOY) %>%
+  summarize(meanGR = mean(grLength, na.rm=T),
+            sdGR = sd(grLength, na.rm=T))
+.119/.215 #juv/yoy
+.215/.119
+
+cd %>% group_by(river) %>%
+  summarize(meanGR = mean(grLength, na.rm=T),
+            sdGR = sd(grLength, na.rm=T))
+#   river       meanGR  sdGR
+#   <chr>        <dbl> <dbl>
+# 1 wb jimmy     0.132 0.131
+# 2 wb mitchell  0.179 0.160
+# 3 wb obear     0.137 0.129
+# 4 west brook   0.170 0.175
+((.132+.137)/2)/((.17+.179)/2)
+((.17+.179)/2)/((.132+.137)/2)
+
+cd %>% group_by(season) %>%
+  summarize(meanGR = mean(grLength, na.rm=T),
+            sdGR = sd(grLength, na.rm=T))
+((.0464+.0894+.0914)/3)/(.417)
+.417/((.0464+.0894+.0914)/3)
+```
+
 ```{r - why bad convergence for bnt in winter?}
@@
 
-  q <- q %>% filter( !(river == 'west brook' & season == 2 & isYOY == 0))
+  q <- q %>% filter( !(season == 2 & isYOY == 0))
 
@@
 q$speciesGG <- factor(q$species, levels = c('bkt','bnt','ats'), labels = c("BKT", "BNT", "ATS"), ordered = T)
-q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"), ordered = T)
+q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","Length","BKT","BNT","BNT*BKT","ATS"), ordered = T)
 q$parameter = paste0(q$riverGG,"_",q$speciesGG)
@@
   q <- q %>% filter( !(betaGG == 'BNT*BKT' & (riverGG == "OS" | riverGG == "IL")) )
+#  q <- q %>% filter( !((riverGG == "OS" | riverGG == "IL")) )
+
 #reorder(parameter,median,na.rm=TRUE)
@@
         size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
-        xlim(c(-0.15,0.14)) +
+        xlim(c(-0.15,0.11)) +
         xlab("Parameter estimate") + ylab("River_Species") +
@@
 ggsave('figures/grBetas.png', height = 7, width = 10, scale = 2)
+
+```
+
+```{r mcmc output analysis-grBetaSigma}
+
+# get all betas in a DF
+grBetaSigma <- list()
+grBetaSigma[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$sigmaBeta, levels = list(iter=NA,beta=1:3,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>%
+  mutate( species = 'bkt')
+grBetaSigma[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$sigmaBeta, levels = list(iter=NA,beta=1:3,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int") %>%
+  mutate( species = 'bnt')
+grBetaSigma[['ats']] <- array2df(mcmc[['ats']]$sims.list$sigmaBeta, levels = list(iter=NA,beta=1:3,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int") %>%
+  mutate( species = 'ats')
+
+grBetaSigmaDF <- rbind(grBetaSigma[['bkt']],grBetaSigma[['bnt']],grBetaSigma[['ats']])
+
+##################################################
+# as range plot
+
+  nRivers <- list()
+  nRivers[['bkt']] <- 4; nRivers[['bnt']] <- 2; nRivers[['ats']] <- 1
+  speciesList <- list('bkt','bnt','ats')
+
+  probs <- c(0.05,0.1,0.5,0.9,0.95)
+  nSpecies <- 3
+
+  q <- grBetaSigmaDF %>%
+    group_by(beta,isYOY,season,river,species) %>%
+    summarize(
+      p = list(probs),
+      q = list(quantile(int,probs))
+    ) %>%
+    unnest() %>%
+    spread(key = p, value = q) %>%
+    data.frame() %>%
+    rename( median = X0.5, lo = X0.05, hi = X0.95 )
+
+  q <- q %>% filter( !(season == 2 & isYOY == 0))
+
+q$riverGG <- factor(q$river,
+                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
+                         labels = c("WB","OL","OS","IL"), ordered = T)
+q$seasonGG <- factor(q$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+q$speciesGG <- factor(q$species, levels = c('bkt','bnt','ats'), labels = c("BKT", "BNT", "ATS"), ordered = T)
+q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","Length","BKT","BNT","BNT*BKT","ATS"), ordered = T)
+q$parameter = paste0(q$riverGG,"_",q$speciesGG)
+q$parameterOrd <- factor(q$parameter, levels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), labels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
+
+  q <- q %>% filter( !(betaGG == 'ATS' & (riverGG == "OS" | riverGG == "IL" | riverGG == "OL")) )
+  q <- q %>% filter( !(betaGG == 'BNT' & (riverGG == "OS" | riverGG == "IL")) )
+  q <- q %>% filter( !(betaGG == 'BNT*BKT' & (riverGG == "OS" | riverGG == "IL")) )
+#  q <- q %>% filter( !((riverGG == "OS" | riverGG == "IL")) )
+
+#reorder(parameter,median,na.rm=TRUE)
+(min(q$median))
+  (max(q$median))
+#  q[q$median < -0.13,]
+
+    ggplot(q, aes(x = median, y = parameterOrd, color = factor(speciesGG), shape = factor(isYOY))) + 
+        geom_vline(xintercept = 0,color='black') +
+        theme_publication() +  
+        geom_point(size = 3) +
+        geom_segment(aes(x = median, xend = hi, yend = parameterOrd), 
+        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
+        geom_segment(aes(x = median, xend = lo, yend = parameterOrd), 
+        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
+        xlim(c(-0.35,0.5)) +
+        xlab("Parameter estimate") + ylab("River_Species") +
+        facet_grid(seasonGG~betaGG)
+
+ggsave('figures/grBetaSigmas.png', height = 7, width = 10, scale = 2)
 
@@
 
+table(mcmc[['bkt']]$q50$grIndRE==0)/length(mcmc[['bkt']]$q50$grIndRE)
+table(mcmc[['bnt']]$q50$grIndRE==0)/length(mcmc[['bnt']]$q50$grIndRE)
+table(mcmc[['ats']]$q50$grIndRE==0)/length(mcmc[['ats']]$q50$grIndRE)
+
 ggplot( grIndRE[[1]], aes(value,..density..) ) +
-  geom_freqpoly(binwidth = 0.0025) +
-  geom_freqpoly(aes(value), color = "brown", binwidth = 0.0025, data = grIndRE[[2]]) +
-  geom_freqpoly(aes(value), color = "lightblue", binwidth = 0.0025, data = grIndRE[[3]])
+  geom_freqpoly(binwidth = 0.00025) +
+  geom_freqpoly(aes(value), color = "brown", binwidth = 0.00025, data = grIndRE[[2]]) +
+  geom_freqpoly(aes(value), color = "lightblue", binwidth = 0.00025, data = grIndRE[[3]]) +
+  ylim(c(0,100))
 
@@
  # 
- # 
  # pred <- pAll %>% group_by(species,len,flow,temp,cBKT,cBNT,cATS,isYOY,season,river) %>%
  #   summarize(meanPredGR = mean(predGr, na.rm=T),
- #             sdpredGR = sd(predGr, na.rm=T)) %>%
+ #             sdPredGR =     sd(predGr, na.rm=T),
+ #             meanPredGRSigma = mean(predGrSigma, na.rm=T),
+ #             sdPredGRSigma =     sd(predGrSigma, na.rm=T),
+ #             meanPredGRCV = mean(predCV, na.rm=T),
+ #             sdPredGRCV =     sd(predCV, na.rm=T)) %>%
  #    ungroup()
  # 
+ # rm(pAll)
  # save(pred,file = 'D:/projects/linkedModels/data/out/P_ForMike_allMeans.RData')
@@
 
-```{r mean prediction graphs}
+```{r mean prediction graphs for meanPredGR}
 
@@
 isYOYGG <- 0
-riverGGToPlot <- "Open Large"
+riverGGToPlot <- "West Brook" #"Open Large"
+outputToPlot <- "meanPredGR"
 
@@
       local({ i <- i
-  singleDat[[i]] <- selectSingleVar(pred, all, "meanPredGR", all[i], isYOYGG)
+  singleDat[[i]] <- selectSingleVar(pred, all, outputToPlot, all[i], isYOYGG)
   print(c(i,all[i]))
@@
   tmp <- singleDat[[i]] %>% filter(riverGG == riverGGToPlot)
-  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), meanPredGR, color=speciesGG ) ) +
+  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=speciesGG ) ) +
       geom_line( size = 1.225 ) +
@@
 speciesGGToPlot <- "Brook Trout"
+outputToPlot <- "meanPredGR"
 
@@
   tmp <- singleDat[[i]] %>% filter(speciesGG == speciesGGToPlot)
-  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), meanPredGR, color=riverGG ) ) +
+  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=riverGG ) ) +
       geom_line( size = 1.225 ) +
@@
 
-```{r 2d denstiy plots of mean predictions}
+```{r 2d density plots of mean predictions}
 
@@
 
-isYOYGG <- 1
-speciesToPlot <- "ats"
+h <- list(); h[['bkt']] <- 8.5; h[['bnt']] <- 4.5; h[['ats']] <- 2.75
 
@@
 
-  ggsave(paste0('figures/predGRGrid',"_",i,"_",j,'.png'), width = 9, height = 7, units='in')
+  ggsave(paste0('figures/predGRGrid',"_",i,"_",j,'.png'), width = 9, height = h[[i]], units='in')
 
@@
   facet_grid(river+isYOY~season)
+```
+
+```{r mean prediction graphs for meanPredGRSigma}
+
+all <- c('temp','flow')
+allLabels <- c('Stream temperature (C)','Stream flow (m3/s)')
+
+remFacetLabel <- c(2)
+
+selectSingleVarSigma <- function(p, all, depVar, varsToPlot, isYOYGG){
+
+  notPlot <- NA
+  notPlot[1] <- all[!(all %in% varsToPlot)][1]
+
+  pGG <- p %>% filter(isYOY == isYOYGG, 
+                        eval(as.name(notPlot[1])) == 0,
+                      len == 0, cBKT == 0, cBNT == 0, cATS == 0
+                      )#%>%
+              # distinct(species, isYOY, riverGG, seasonGG, speciesGG, .keep_all = TRUE)
+
+  return(pGG)  
+}
+
+##### by species
+
+isYOYGG <- 0
+riverGGToPlot <- "Open Large" #"West Brook" #
+outputToPlot <- "meanPredGRSigma"
+
+ggSingle <- list()
+singleDat <- list()
+for(i in 1:length(all))
+  #https://stackoverflow.com/questions/31993704/storing-ggplot-objects-in-a-list-from-within-loop-in-r
+      local({ i <- i
+  singleDat[[i]] <- selectSingleVarSigma(pred, all, outputToPlot, all[i], isYOYGG)
+  print(c(i,all[i]))
+ # print(str(singleDat[[i]]))
+
+  tmp <- singleDat[[i]] %>% filter(riverGG == riverGGToPlot)
+  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=speciesGG ) ) +
+      geom_line( size = 1.225 ) +
+      theme_bw() +
+      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
+            axis.title.y = element_blank(),
+            legend.position="none") +
+      geom_hline(yintercept = 0) +
+    #  ylim(-0.15,0.8) +
+      scale_x_continuous(allLabels[i]) +
+      facet_grid(~seasonGG)
+
+  if( i %in% remFacetLabel ) {
+    ggSingle[[i]] <<- ggSingle[[i]] +
+    theme(
+      strip.background = element_blank(),
+      strip.text.x = element_blank()
+    )
+  }
+})
+
+# add thrid row to graph for interaction of tem and flow?
+
+# run this and export
+grid.arrange(grobs=ggSingle, left = "Standard deviation of growth rate (mm/d)")
+#ggsave(ggCV, paste0('figures/predGRCV_YOY',isYOYGG,'_',riverGGToPlot,'.png'), width = 9, height = 7, units='in')
+
+###### by river for bkt
+
+isYOYGG <- 0
+speciesGGToPlot <- "Brook Trout"
+outputToPlot <- "meanPredGRSigma"
+
+ggSingle <- list()
+singleDat <- list()
+for(i in 1:length(all))
+  #https://stackoverflow.com/questions/31993704/storing-ggplot-objects-in-a-list-from-within-loop-in-r
+      local({ i <- i
+  singleDat[[i]] <- selectSingleVarSigma(pred, all, outputToPlot, all[i], isYOYGG)
+  print(c(i,all[i]))
+ # print(str(singleDat[[i]]))
+
+  tmp <- singleDat[[i]] %>% filter(speciesGG == speciesGGToPlot)
+  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=riverGG ) ) +
+      geom_line( size = 1.225 ) +
+      theme_bw() +
+      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
+            axis.title.y = element_blank(),
+            legend.position="none"
+            ) +
+      geom_hline(yintercept = 0) +
+      #ylim(-0.15,0.8) +
+      scale_x_continuous(allLabels[i]) +
+      facet_grid(~seasonGG)
+
+  if( i %in% remFacetLabel ) {
+    ggSingle[[i]] <<- ggSingle[[i]] +
+    theme(
+      strip.background = element_blank(),
+      strip.text.x = element_blank()
+    )
+  }
+})
+
+grid.arrange(grobs=ggSingle, left = "Standard deviation of growth rate (mm/d)")
+
+```
+
+```{r flow*temp interaction plots}
+
+###############################
+# flow*temp interaction plots
+isYOYGG <- 1
+riverGGToPlot <- "West Brook" #"Open Large" #
+outputToPlot <- "meanPredGR" #"meanPredGRSigma"
+
+interact <- pred %>% filter(isYOY == isYOYGG,
+                            riverGG == riverGGToPlot,
+                            len == 0, cBKT == 0, cBNT == 0, cATS == 0 ) %>%
+                     mutate( temp_spp = paste0(temp,speciesGG))
+
+    ggplot( interact, aes( flow, eval(as.name(outputToPlot)), group=temp_spp, color=speciesGG ) ) +
+      geom_line( aes(alpha = temp + 3), size = 1.225 ) +
+      theme_bw() +
+      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
+            axis.title.y = element_blank()
+          #  legend.position="none"
+            ) +
+      geom_hline(yintercept = 0) +
+    #  ylim(-0.15,0.8) +
+      scale_x_continuous('Flow') +
+      facet_grid(~seasonGG)
+
 ```

### 2018-07-16 R/analyzeOutputFunctions.R

@@ -719,9 +719,18 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
   ggg <- ggplot( ddGIn, aes( observedLengthOriginal, estLen, color = factor(leftOut) ) ) +
     geom_point( alpha = 0.1 ) +
     geom_abline(intercept = 0, slope = 1) +
+    scale_x_continuous("Observed length (mm)") +
+    scale_y_continuous("Estimated length (mm)") +
+    theme_publication() +
+    theme(      strip.background = element_blank(),
+                strip.text.x = element_blank(),
+                legend.position="none") +
     #   ylim(-2,4) +
+    ggtitle(speciesGr) +
     facet_grid(~leftOut)
   print(ggg)
+
+  ggsave(paste0('figures/obsPred_',speciesGr,'.png'),width = 7,height = 5)
 
   rmse <- ddGIn %>%
     mutate( resid = estLen - observedLengthOriginal,
@@ -747,7 +756,7 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
 #
 #'Plot observed/predicted and return RMSE
 #'
-#'@param various
+#'@param various plotlist, file cols=1
 #'@return plots
 #'@export
 #'

### 2018-07-16 nimble/mainAnalysis_Nimble.R

@@ -39,7 +39,7 @@ maxSampleInterval <- 200 # <
 recreatecdFileBeforeDetMod_TF <- FALSE
 runDetectionModel_TF <- FALSE
 recreateCD_TF <- FALSE
-runCrossValidation_TF <- FALSE ############################
+runCrossValidation_TF <- TRUE ############################
 percentLeftOut <- 10
 
 meanOrIter <- "mean"; iter <- 1
@@ -322,6 +322,7 @@ iter=1
   source("./R/jagsUIFunctions.R")
   mcmcProcessed <- process.output(mcmc, DIC=FALSE, params.omit=FALSE)#,params.omit=("lengthExp")) #jagsUI function, DIC = FALSE because it requires 'deviance'
 
+  # this saves /figures/obsPred_speciesGr.png
   obsPred <- getRMSE_Nimble(mcmcProcessed,20)
   obsPred$rmse
   #obsPred$outliers%>% as.data.frame()

### 2018-07-24 manuscriptAnalysis/3spp4Rivers/MS_Analysis_3spp_4Rivers_Original.Rmd
switch to 3spp_WB as 1st paper

--- 2018-07-16 manuscriptAnalysis/MS_Analysis.Rmd
@@
 mcmc <- list()
+dGIn <- list()
+ddGIn2 <- list()
+
 load("D:/projects/linkedModels/data/out/dG_1530971738_crossValFALSE_bkt1997_Nimble.RData")
@@
 
+#input data frame
+ddGIn2[['bkt']] <- ddG[[1]][[2]]
+dGIn[['bkt']] <- dG
 # output data
@@
 load("D:/projects/linkedModels/data/out/dG_1530971744_crossValFALSE_bnt1997_Nimble.RData")
+ddGIn2[['bnt']] <- ddG[[1]][[2]]
+dGIn[['bnt']] <- dG
 mcmc[['bnt']]  <- mcmcProcessed
@@
 load("D:/projects/linkedModels/data/out/dG_1530993703_crossValFALSE_ats1997_Nimble.RData")
+ddGIn2[['ats']] <- ddG[[1]][[2]]
+dGIn[['ats']] <- dG
 mcmc[['ats']]  <- mcmcProcessed
@@
 ```{r check lengthExp}
-
-len2 <- array2df(mcmc[['bnt']]$sims.list$lengthExp, label.x = "est") %>%
-         rename(iter=d1,obs=d2)
-
-inds <- data.frame(ind = dG[[1]]$constants$ind[1:(length(dG[[1]]$constants$ind) - 1)],
-                   observedLen = dG[[1]]$data$lengthDATA)
-inds$obs <- 1:(length(dG[[1]]$constants$ind) - 1)
+len <- list()
+for( spp in c("bkt","bnt","ats") ){
+
+#  len2 <- array2df(mcmc[[spp]]$sims.list$lengthExp, label.x = "est") %>%
+#           rename(iter=d1,obs=d2)
+  offset <- 1
+  if(spp == 'ats') offset <- 0 # not sure why this is needed. REs seem meesed up in the graphs below
+  inds <- data.frame(ind = dGIn[[spp]][[1]]$constants$ind[1:(length(dGIn[[spp]][[1]]$constants$ind) - offset)],
+                     observedLength = dGIn[[spp]][[1]]$data$lengthDATA,
+                     sampleNumber = ddGIn2[[spp]]$sampleNumber[1:(length(ddGIn2[[spp]]$sampleNumber) - offset)],
+                     cohort = ddGIn2[[spp]]$cohort[1:(length(ddGIn2[[spp]]$cohort) - offset)],
+                     ageInSamples = ddGIn2[[spp]]$ageInSamples[1:(length(ddGIn2[[spp]]$ageInSamples) - offset)],
+                     riverOrdered = ddGIn2[[spp]]$riverOrdered[1:(length(ddGIn2[[spp]]$riverOrdered) - offset)],
+                     lagObservedLength = ddGIn2[[spp]]$lagObservedLength[1:(length(ddGIn2[[spp]]$lagObservedLength) - offset)],
+                     detectionDate = ddGIn2[[spp]]$detectionDate[1:(length(ddGIn2[[spp]]$detectionDate) - offset)],
+                     lagDetectionDate = ddGIn2[[spp]]$lagDetectionDate[1:(length(ddGIn2[[spp]]$lagDetectionDate) - offset)])
+  inds$obs <- 1:(length(dGIn[[spp]][[1]]$constants$ind) - offset)
+
   inds <-  inds %>%
@@
            firstObs = obs == first,
-         observed = !is.na(observedLen)) %>%
+           observed = !is.na(observedLength),
+           sampleNumber = sampleNumber,
+           nObs = n(),
+           grLength = (lagObservedLength - observedLength)/as.numeric((lagDetectionDate - detectionDate))
+           ) %>%
     ungroup()
 
-len1 <- left_join(len2,inds)
+#  len1 <- left_join(len2,inds)
+#  rm(len2,inds)
 
   # means
-lenMean1 <- array2df(mcmc[['bnt']]$mean$lengthExp, label.x = "estMean") %>%
+  lenMean1 <- array2df(mcmc[[spp]]$mean$lengthExp, label.x = "estMean") %>%
                 rename(obs=d1)
-
-len <- left_join(len1,lenMean1)
-
-len %>% filter(ind == 20, !firstObs, iter%%50==0) %>%
-  ggplot(aes(obs,est)) +
+  len[[spp]] <- left_join(inds,lenMean1)  %>%
+                  mutate( estMean = ifelse( firstObs, observedLength, estMean ) )
+
+  grIndREMean1 <- array2df(mcmc[[spp]]$mean$grIndRE, label.x = "grIndRE") %>%
+                rename(ind=d1)
+
+  len[[spp]] <- left_join(len[[spp]],grIndREMean1)
+
+#  len <- left_join(len1,lenMean1)
+#  rm(len1,lenMean1)
+  rm(inds,lenMean1)
+  gc()
+}
+
+len[['bkt']] %>% filter( nObs == 7 ) %>%
+  ggplot(aes(ageInSamples,observedLength)) +
+  geom_point(aes(color = factor(ind)), size=3) +
+  geom_point(aes(ageInSamples, estMean, color=factor(ind))) +
+  geom_line(aes(ageInSamples, estMean, color = factor(ind))) +
+  geom_point(aes(ageInSamples, estMean, color=factor(ind)), size=2) +
+  geom_point(aes(ageInSamples, estMean, color=factor(ind)), shape = 1, size = 2, color = 'black') +
+  theme(legend.position="none") +
+  facet_wrap(~cohort)
+
+focalFish <- 60
+
+len[['bkt']] %>% filter( cohort == 2001 ) %>%
+  ggplot(aes(ageInSamples,observedLength)) +
+  geom_point(aes(color = riverOrdered), size = 3) +
+  geom_point(color = 'black', shape = 1, size = 3) +
+  geom_point(aes(ageInSamples, estMean, color = riverOrdered)) +
+  geom_line( aes(ageInSamples, estMean, group = factor(ind), color = riverOrdered)) +
+  geom_point(aes(ageInSamples, estMean, color = riverOrdered), size = 2) +
+  geom_point(aes(ageInSamples, estMean, color = riverOrdered), shape = 1, size = 2, color = 'black') +
+ # theme(legend.position="none") +
+  facet_wrap(~nObs)
+
+len[['bkt']] %>% filter( cohort == 2001 ) %>%
+  ggplot(aes(ageInSamples,observedLength)) +
+  geom_point(aes(color = grIndRE), size = 3) +
+#  geom_point(color = 'black', shape = 1, size = 3) +
+  geom_point(aes(ageInSamples, estMean, color = grIndRE)) +
+  geom_line( aes(ageInSamples, estMean, group = factor(ind), color = grIndRE)) +
+  geom_point(aes(ageInSamples, estMean, color = grIndRE), size = 2) +
+#  geom_point(aes(ageInSamples, estMean, color = grIndRE), shape = 1, size = 2, color = 'black') +
+ # scale_colour_distiller(palette = "Spectral") +
+   scale_colour_gradient(low = "white", high = "black") +
+ # theme(legend.position="none") +
+  facet_wrap(~nObs)
+
+len[['bkt']] %>% #filter( cohort == 2001 ) %>%
+  ggplot(aes(ageInSamples,observedLength)) +
+  geom_point(aes(color = grIndRE), size = 3) +
+#  geom_point(color = 'black', shape = 1, size = 3) +
+  geom_point(aes(ageInSamples, estMean, color = grIndRE)) +
+  geom_line( aes(ageInSamples, estMean, group = factor(ind), color = grIndRE)) +
+  geom_point(aes(ageInSamples, estMean, color = grIndRE), size = 2) +
+#  geom_point(aes(ageInSamples, estMean, color = grIndRE), shape = 1, size = 2, color = 'black') +
+ # scale_colour_distiller(palette = "Spectral") +
+   scale_colour_gradient(low = "white", high = "black") +
+ # theme(legend.position="none") +
+  facet_grid(riverOrdered~cohort)
+
+len[['ats']] %>% filter( nObs > 0 ) %>%
+  group_by(ind) %>%
+  summarize( meanGRLength = mean(grLength,na.rm=TRUE),
+             meanGRIndRE = mean(grIndRE,na.rm=TRUE),
+             meanNObs = mean(nObs,na.rm=TRUE)) %>%
+  ggplot(aes(meanGRLength,meanGRIndRE)) +
   geom_point() +
-  geom_line(aes(group = iter)) +
-  geom_point(aes(obs,estMean), color='red', size=3) +
-  geom_point(aes(obs,observedLen), color='blue', size=3)
+  geom_smooth(method='lm') +
+#  scale_colour_gradient(low = "yellow", high = "red") +
+  facet_wrap(~meanNObs)
 
@@
 q$speciesGG <- factor(q$species, levels = c('bkt','bnt','ats'), labels = c("BKT", "BNT", "ATS"), ordered = T)
-q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","Length","BKT","BNT","BNT*BKT","ATS"), ordered = T)
+q$betaGG <- factor(q$beta, levels = 1:10, 
+                   levels = c("Temp","Flow","Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"), # make sure this order matches the nimble code
+                   labels = c("Temp","Flow","Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"),ordered = T)
 q$parameter = paste0(q$riverGG,"_",q$speciesGG)
-q$parameterOrd <- factor(q$parameter, levels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), labels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
+q$parameterOrd <- factor(q$parameter, 
+                         levels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), 
+                         labels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
 
@@
 q$speciesGG <- factor(q$species, levels = c('bkt','bnt','ats'), labels = c("BKT", "BNT", "ATS"), ordered = T)
-q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","Length","BKT","BNT","BNT*BKT","ATS"), ordered = T)
+q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"), ordered = T)
 q$parameter = paste0(q$riverGG,"_",q$speciesGG)
@@
 
-ggsave('figures/grBetaSigmas.png', height = 7, width = 10, scale = 2)
+ggsave('figures/grBetaSigmas.png', height = 7, width = 7, scale = 2)
 
@@
   ylim(c(0,100))
+
+```
+
+```{r ind trajectories}
 
@@
 
+plotPredMeans(pred, "meanPredGR", "len", 0)
+plotPredMeans(pred, "meanPredGR", "len", 1)
+
 plotPredMeans(pred, "meanPredGR", "flow", 0)
@@
 
+```{r bkt*bnt interaction plots}
+
+###############################
+# flow*temp interaction plots
+isYOYGG <- 1
+riverGGToPlot <- "Open Large" #"West Brook" #
+outputToPlot <- "meanPredGR" #"meanPredGRSigma"
+
+interact <- pred %>% filter(isYOY == isYOYGG,
+                            riverGG == riverGGToPlot,
+                            len == 0, temp == 0, flow == 0, cATS == 0 ) %>%
+                     mutate( bnt_spp = paste0(cBNT,speciesGG))
+
+    ggplot( interact, aes( cBKT, eval(as.name(outputToPlot)), group=bnt_spp, color=speciesGG ) ) +
+      geom_line( aes(alpha = cBNT + 3), size = 1.225 ) +
+      theme_bw() +
+      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
+            axis.title.y = element_blank()
+          #  legend.position="none"
+            ) +
+      geom_hline(yintercept = 0) +
+    #  ylim(-0.15,0.8) +
+      scale_x_continuous('Brook Trout abundance') +
+      facet_grid(~seasonGG)
+
+```
+
 ```{r tables}

### 2018-07-24 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
switch to 3spp_WB as 1st paper

--- 2018-07-24 manuscriptAnalysis/3spp4Rivers/MS_Analysis_3spp_4Rivers_Original.Rmd
@@
 ---
-title: "Growth model analysis"
+title: "Growth model analysis 3spp WB"
 output: html_notebook
@@
 ```{r message=FALSE}
+library(arm)
 library(linkedModels)
@@
 
-ggplot(allFishBySpeciesYOY, aes(year,nAllFishBySpecies)) +
+ggplot(allFishBySpeciesYOY %>% filter(riverOrderedGG == "West Brook"), aes(year,nAllFishBySpecies)) +
   geom_point(aes(color = speciesGG)) +
   geom_line(aes(color = speciesGG)) +
-  geom_line( data = allFish, aes(year,nAllFish) ) +
+  geom_line( data = allFish %>% filter(riverOrderedGG == "West Brook"), aes(year,nAllFish) ) +
   theme_publication() +
   labs( x = "Year", y = "Count" ) +
-  facet_grid( seasonGG ~ riverOrderedGG)#, scales = "free_y" )
-
-ggsave('figures/rawCounts.png')
+  facet_wrap( ~ seasonGG )#, scales = "free_y" )
+
+ggsave('figures/3Spp_WB/rawCounts.png')
 
@@
 ```{r figs 3,4, flow and temp}
+d2$riverOrderedGG <- factor(d2$river,
+                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
+                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
+d2$seasonGG <- factor(d2$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+
 d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
@@
 
-ggsave('figures/flow.png')
+ggsave('figures/3Spp_WB/flow.png')
 
@@
             sdT = sd(meanTemperature, na.rm=T)) %>%
+  filter(riverOrderedGG == "West Brook") %>%
   ggplot( aes(year,meanT) ) +
@@
   labs( x = "Year", y = "Stream temperature (C)" ) +
-  geom_text(data=tempModsTidy,aes(x=1999,y=18, label=paste(round(estimate,2),sig))) +
-  theme_publication() +
-  facet_grid(seasonGG ~ riverOrderedGG)
-
-ggsave('figures/temp.png')
+  geom_text(data=tempModsTidy %>% filter(riverOrderedGG == "West Brook"),aes(x=2000.5,y=17.5, label=paste(round(estimate,2),sig))) +
+  theme_publication() +
+  facet_wrap(~seasonGG)
+
+ggsave('figures/3Spp_WB/temp.png')
 ```
@@
             sdGR = sd(grLength, na.rm=T)) %>%
+  filter(riverOrderedGG == "West Brook") %>%
 ggplot( aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
@@
   theme_publication() +
-  theme( panel.grid.minor = element_blank() ) +
-  facet_wrap( ~ riverOrderedGG)
-
-ggsave('figures/meanGRYOY1.png', width = 7, height = 7, units='in')
+  theme( panel.grid.minor = element_blank() ) 
+#  facet_wrap( ~ riverOrderedGG)
+
+ggsave('figures/3Spp_WB/meanGRYOY1.png', width = 7, height = 7, units='in')
 
@@
   theme_publication() +
-  theme( panel.grid.minor = element_blank() ) +
-  facet_wrap( ~ riverOrderedGG)
-
-ggsave('figures/meanGRYOY2.png', width = 7, height = 7, units='in')
+  theme( panel.grid.minor = element_blank() ) 
+#  facet_wrap( ~ riverOrderedGG)
+
+ggsave('figures/3Spp_WB/meanGRYOY2.png', width = 7, height = 7, units='in')
 
@@
 
-cd %>% group_by(species) %>%
+cd %>% group_by(species) %>% filter(riverOrderedGG == "West Brook") %>%
   summarize(meanGR = mean(grLength, na.rm=T),
             sdGR = sd(grLength, na.rm=T))
-.162/.194 #bkt/bnt
-.151/.194 #ats/bnt
-
-cd %>% group_by(isYOY) %>%
+.182/.197 #bkt/bnt
+.151/.197 #ats/bnt
+
+cd %>% group_by(isYOY) %>% filter(riverOrderedGG == "West Brook") %>%
   summarize(meanGR = mean(grLength, na.rm=T),
             sdGR = sd(grLength, na.rm=T))
-.119/.215 #juv/yoy
+.120/.226 #adult/yoy
 .215/.119
 
-cd %>% group_by(river) %>%
+cd %>% group_by(season) %>% filter(riverOrderedGG == "West Brook") %>%
   summarize(meanGR = mean(grLength, na.rm=T),
             sdGR = sd(grLength, na.rm=T))
-#   river       meanGR  sdGR
-#   <chr>        <dbl> <dbl>
-# 1 wb jimmy     0.132 0.131
-# 2 wb mitchell  0.179 0.160
-# 3 wb obear     0.137 0.129
-# 4 west brook   0.170 0.175
-((.132+.137)/2)/((.17+.179)/2)
-((.17+.179)/2)/((.132+.137)/2)
-
-cd %>% group_by(season) %>%
-  summarize(meanGR = mean(grLength, na.rm=T),
-            sdGR = sd(grLength, na.rm=T))
-((.0464+.0894+.0914)/3)/(.417)
-.417/((.0464+.0894+.0914)/3)
+.437/((.0876+.0866+.0485)/3)
 ```
@@
   p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
-    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5)
-  ggplot(p, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid(river ~ season + isYOY)
+    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1) 
+  ggplot(p, aes(year,invlogit(est),color=factor(species))) + geom_point() + facet_grid( season ~ isYOY)
 
   # seem to need to run the ggsave outside of markdown by pasting into console
-   ggsave('figures/p.png')
+   ggsave('figures/3Spp_WB/p.png')
 
   phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
-    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5)
-  ggplot(phi, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid(river ~ season + isYOY)
-
-  ggsave('figures/phi.png')
+    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1) 
+  ggplot(phi, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid( season ~ isYOY)
+
+  ggsave('figures/3Spp_WB/phi.png')
 
@@
   p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
-  p$parameter <- paste(p$river,p$season,sep="_")
+  p$seasonGG <- factor(p$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+  p$parameter <- p$seasonGG
 
@@
 
+  p$seasonGG <- factor(p$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
   #print(c(min(p$intByDayDown,na.rm=T),max(p$intByDayDown,na.rm=T)))
 
-    gg <- ggplot(p, aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(season), shape = factor(isYOY))) + 
+    gg <- ggplot(p %>% filter(river=='west brook'), aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(seasonGG), shape = factor(isYOY))) + 
         theme_publication() +  
@@
         size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
-        xlim(c(-0.0015,0.01)) +
-        xlab("Mean daily growth (mm/d)") + ylab("River_Season") 
+        xlim(c(-0.00,0.0075)) +
+        xlab("Mean daily growth (mm/d)") + ylab("Season") 
        # ggtitle(sppToPlot)
@@
 
-plotHPD('bkt'); ggsave('figures/HDP_bkt.png', height = 3, width = 3, scale = 2)
-plotHPD('bnt'); ggsave('figures/HDP_bnt.png', height = 3, width = 3, scale = 2)
-plotHPD('ats'); ggsave('figures/HDP_ats.png', height = 3, width = 3, scale = 2)
+plotHPD('bkt'); ggsave('figures/3Spp_WB/HDP_bkt.png', height = 3, width = 3, scale = 2)
+plotHPD('bnt'); ggsave('figures/3Spp_WB/HDP_bnt.png', height = 3, width = 3, scale = 2)
+plotHPD('ats'); ggsave('figures/3Spp_WB/HDP_ats.png', height = 3, width = 3, scale = 2)
 ```
@@
 #  p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
-  p$parameter <- paste(p$river,p$season,sep="_")
+  p$seasonGG <- factor(p$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+  p$parameter <- p$seasonGG
 
@@
 
-    gg <- ggplot(p, aes(x = exp(int), y = reorder(parameter,int,na.rm=TRUE), color = factor(season), shape = factor(isYOY))) + 
+    gg <- ggplot(p %>% filter(river == 'west brook'), aes(x = exp(int), y = reorder(parameter,int,na.rm=TRUE), color = factor(season), shape = factor(isYOY))) + 
         theme_publication() +  
@@
         #xlim(c(-0.0015,0.01)) +
-        xlab("Standard deviation of daily growth (mm/d)") + ylab("River_Season") 
+        xlab("Standard deviation of daily growth (mm/d)") + ylab("Season") 
        # ggtitle(sppToPlot)
@@
 
-plotHPDSigma('bkt'); ggsave('figures/HDPSigma_bkt.png', height = 3, width = 3, scale = 2)
-plotHPDSigma('bnt'); ggsave('figures/HDPSigma_bnt.png', height = 3, width = 3, scale = 2)
-plotHPDSigma('ats'); ggsave('figures/HDPsigma_ats.png', height = 3, width = 3, scale = 2)
+plotHPDSigma('bkt'); ggsave('figures/3Spp_WB/HDPSigma_bkt.png', height = 3, width = 3, scale = 2)
+plotHPDSigma('bnt'); ggsave('figures/3Spp_WB/HDPSigma_bnt.png', height = 3, width = 3, scale = 2)
+plotHPDSigma('ats'); ggsave('figures/3Spp_WB/HDPsigma_ats.png', height = 3, width = 3, scale = 2)
 ```
@@
 q$betaGG <- factor(q$beta, levels = 1:10, 
-                   levels = c("Temp","Flow","Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"), # make sure this order matches the nimble code
+                   #levels = c("Temp","Flow","Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"), # make sure this order matches the nimble code
                    labels = c("Temp","Flow","Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"),ordered = T)
-q$parameter = paste0(q$riverGG,"_",q$speciesGG)
+q$parameter = q$speciesGG
 q$parameterOrd <- factor(q$parameter, 
-                         levels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), 
-                         labels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
+                         levels = c( "ATS", "BNT", "BKT"), 
+                         labels = c( "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
 
@@
 
-    ggplot(q, aes(x = median, y = parameterOrd, color = factor(speciesGG), shape = factor(isYOY))) + 
+    ggplot(q %>% filter(river == 'west brook'), aes(x = median, y = parameterOrd, color = factor(speciesGG), shape = factor(isYOY))) + 
         geom_vline(xintercept = 0,color='black') +
@@
         size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
-        xlim(c(-0.15,0.11)) +
-        xlab("Parameter estimate") + ylab("River_Species") +
+     #   xlim(c(-0.15,0.11)) +
+        xlab("Parameter estimate") + theme(axis.text.y = element_blank(), axis.title.y = element_blank()) +
         facet_grid(seasonGG~betaGG)
 
-ggsave('figures/grBetas.png', height = 7, width = 10, scale = 2)
+ggsave('figures/3Spp_WB/grBetas.png', height = 4, width = 10, scale = 2)
 
@@
 q$betaGG <- factor(q$beta, levels = 1:10, labels = c("Temp", "Flow", "Temp*Flow","Temp^2","Flow^2","BKT","Length","BNT","BNT*BKT","ATS"), ordered = T)
-q$parameter = paste0(q$riverGG,"_",q$speciesGG)
-q$parameterOrd <- factor(q$parameter, levels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), labels = c("IL_BKT", "OS_BKT", "OL_BNT", "OL_BKT", "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
+q$parameter = q$speciesGG
+q$parameterOrd <- factor(q$parameter, 
+                         levels = c( "ATS", "BNT", "BKT"), 
+                         labels = c( "WB_ATS", "WB_BNT", "WB_BKT"), ordered = T)
 
@@
         xlim(c(-0.35,0.5)) +
-        xlab("Parameter estimate") + ylab("River_Species") +
+        xlab("Parameter estimate") + theme(axis.text.y = element_blank(), axis.title.y = element_blank()) +
         facet_grid(seasonGG~betaGG)
 
-ggsave('figures/grBetaSigmas.png', height = 7, width = 7, scale = 2)
+ggsave('figures/3Spp_WB/grBetaSigmas.png', height = 8, width = 8)
 
@@
 plotPredMeans(pred, "meanPredGR", "len", 0)
-plotPredMeans(pred, "meanPredGR", "len", 1)
+plotPredMeans(pred %>% filter(river == 'west brook'), "meanPredGR", "len", 1)
 
@@
 
-ggsave('figures/tmp.png', width = 9, height = 7, units='in')
+ggsave('figures/3Spp_WBtmp.png', width = 9, height = 7, units='in')
 ```
@@
 
-isYOYGG <- 0
+isYOYGG <- 1
 riverGGToPlot <- "West Brook" #"Open Large"
@@
 
+# export fig to save
 grid.arrange(grobs=ggSingle, left = "Growth rate (mm/d)")
@@
 
-  ggsave(paste0('figures/predGRGrid',"_",i,"_",j,'.png'), width = 9, height = h[[i]], units='in')
+  ggsave(paste0('figures/3Spp_WBpredGRGrid',"_",i,"_",j,'.png'), width = 9, height = h[[i]], units='in')
 
@@
 grid.arrange(grobs=ggSingle, left = "Standard deviation of growth rate (mm/d)")
-#ggsave(ggCV, paste0('figures/predGRCV_YOY',isYOYGG,'_',riverGGToPlot,'.png'), width = 9, height = 7, units='in')
+#ggsave(ggCV, paste0('figures/3Spp_WBpredGRCV_YOY',isYOYGG,'_',riverGGToPlot,'.png'), width = 9, height = 7, units='in')
 
@@
 
-ggsave('figures/grByYearYOY1.png')
+ggsave('figures/3Spp_WBgrByYearYOY1.png')
 
@@
 
-ggsave('figures/grByYearYOY2.png')
+ggsave('figures/3Spp_WBgrByYearYOY2.png')
 

### 2018-07-24 R/analyzeOutputFunctions.R

@@ -16,19 +16,19 @@ getPrediction <- function(d, limits = 2, nPoints = 5, itersForPred, constants, s
   grInt <- array2df(d$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="int")
 
   # get grBeta in df format and merge in grInt
-  grBeta3 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="est")
+  grBeta3 <- array2df(d$sims.list$grBeta, levels = list(iter=NA,beta=1:nB$nBetas,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:constants$nRivers]), label.x="est")
 
   grBeta2 <- spread( grBeta3, key = beta, value = est, sep = "" ) %>%
     left_join( .,grInt )
 
   # grBetaBNT, 2 rivers only
-  grBetaBNT <- array2df(d$sims.list$grBetaBNT, levels = list(iter=NA,betaBNT=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:(4-(4-constants$nRivers))]), label.x="est")
+  grBetaBNT <- array2df(d$sims.list$grBetaBNT, levels = list(iter=NA,betaBNT=1:nB$nBetasBNT,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:(4-(4-constants$nRivers))]), label.x="est")
 
   grBeta1 <- spread( grBetaBNT, key = betaBNT, value = est, sep = "" ) %>%
     left_join( .,grBeta2 )
 
   # grBetaATS, no river
-  grBetaATS <- array2df(d$sims.list$grBetaATS, levels = list(iter=NA,betaATS=NA,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:(4-(4-constants$nRivers))]), label.x="est")
+  grBetaATS <- array2df(d$sims.list$grBetaATS, levels = list(iter=NA,betaATS=1:nB$nBetasATS,isYOY=c(0,1),season=1:constants$nSeasons,river=riverOrderedIn[1:(4-(4-constants$nRivers))]), label.x="est")
 
[…]

### 2018-07-24 R/themePublication.R

@@ -1,0 +1,58 @@
+
+#'Publication theme
+#'
+#'@param base_size Default is 14
+#'@return Theme
+#'@export
+theme_publication <- function(base_size=14, base_family="") {
+  library(grid)
+  library(ggthemes)
+  (theme_foundation(base_size=base_size, base_family=base_family)
+    + theme(plot.title = element_text(face = "bold",
+                                      size = rel(1.2), hjust = 0.5),
+            text = element_text(),
+            panel.background = element_rect(colour = NA),
+            plot.background = element_rect(colour = NA),
+            axis.title = element_text(face = "bold",size = rel(1)),
+            axis.title.y = element_text(angle=90,vjust =2),
+            axis.title.x = element_text(vjust = -0.2),
+            axis.text = element_text(),
+            axis.line = element_line(colour="black"),
+            axis.ticks = element_line(),
+            panel.grid.major = element_line(colour="#f0f0f0"),
+            panel.grid.minor = element_blank(),
+            legend.key = element_rect(colour = NA),
+            legend.position = "bottom",
+            legend.direction = "horizontal",
+            legend.key.size= unit(0.2, "cm"),
+            #    legend.margin = unit(0, "cm"),
+            legend.title = element_text(face="italic"),
+            plot.margin=unit(c(10,5,5,5),"mm"),
+            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
+            strip.text = element_text(face="bold"),
+            panel.border = element_rect(colour = "black")
+    ))
+
+}
+
+#'Publication theme fill
+#'
+#'@param none ...
+#'@return Scale
+#'@export
+scale_fill_Publication <- function(...){
+  library(scales)
+  discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+
+}
+
+#'Publication theme color
+#'
+#'@param none ...
+#'@return Scale
+#'@export
+scale_colour_Publication <- function(...){
+  library(scales)
+  discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+
+}

### 2018-07-24 nimble/mainAnalysis_Nimble.R

@@ -390,12 +390,14 @@ iter=1
   itersForPred <- sample( 1:mcmcInfo$nSamples, nItersForPred )
 
   # predictions across the grid
-  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("len","temp", "flow","cBKT", "cBNT", "cATS") )#######################
+  p <- getPrediction( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean,
+                      c("len","temp", "flow","cBKT", "cBNT", "cATS") )#######################
   #p$variable <- "mean"
   # predictions of sigma across the grid
 
   #### need to comment out betas for ATS
-  pSigma <- getPredictionSigma( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean, c("temp", "flow") )
+  pSigma <- getPredictionSigma( mcmcProcessed, limits, nPoints, itersForPred, dG[[1]]$constants, ddG[[ii]][[1]]$sampleIntervalMean,
+                                c("temp", "flow") )
 
   #pSigma$variable <- "sd"
   # combine predicted growth rates and sigma in predicted growth rates to get cv in predicted growth rates
@@ -421,7 +423,7 @@ iter=1
   plotPred(pBoth, "predGr", c("flow","cBKT"), 1, speciesGr)
   plotPred(pBoth, "predGr", c("cBKT","cBNT"), 1, speciesGr)
 
-
+  plotPred(pBoth, "predGr", c("len","cBNT"), 1, speciesGr)
   #######################
   # graph function, in analyzeOutputFunctions.R
 

### 2018-07-26 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
add projection simulation

@@
 
-```{r message=FALSE}
+```{r Load data, message=FALSE}
 library(arm)
@@
 .120/.226 #adult/yoy
-.215/.119
+.226/.120
 
@@
     left_join(.,meanSampleIntervalMean, by = 'season')
-  p$intByDay <- p$int/p$meanSampleInterval
+  p$intByDay <- p$int#/p$meanSampleInterval
   p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
@@
 
-  p$intByDayUp <- p$intUp/p$meanSampleInterval; p$intByDayDown <- p$intDown/p$meanSampleInterval
+  p$intByDayUp <- p$intUp#/p$meanSampleInterval; 
+  p$intByDayDown <- p$intDown#/p$meanSampleInterval
   p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
@@
         size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
-        xlim(c(-0.00,0.0075)) +
+        xlim(c(-0.00,0.55)) +
         xlab("Mean daily growth (mm/d)") + ylab("Season") 
@@
 
-plotHPD('bkt'); ggsave('figures/3Spp_WB/HDP_bkt.png', height = 3, width = 3, scale = 2)
-plotHPD('bnt'); ggsave('figures/3Spp_WB/HDP_bnt.png', height = 3, width = 3, scale = 2)
-plotHPD('ats'); ggsave('figures/3Spp_WB/HDP_ats.png', height = 3, width = 3, scale = 2)
+plotHPD('bkt'); ggsave('figures/3Spp_WB/HDP_bkt.png', height = 5, width = 5, scale = 1)
+plotHPD('bnt'); ggsave('figures/3Spp_WB/HDP_bnt.png', height = 5, width = 5, scale = 1)
+plotHPD('ats'); ggsave('figures/3Spp_WB/HDP_ats.png', height = 5, width = 5, scale = 1)
 ```
@@
 
-plotHPDSigma('bkt'); ggsave('figures/3Spp_WB/HDPSigma_bkt.png', height = 3, width = 3, scale = 2)
-plotHPDSigma('bnt'); ggsave('figures/3Spp_WB/HDPSigma_bnt.png', height = 3, width = 3, scale = 2)
-plotHPDSigma('ats'); ggsave('figures/3Spp_WB/HDPsigma_ats.png', height = 3, width = 3, scale = 2)
+plotHPDSigma('bkt'); ggsave('figures/3Spp_WB/HDPSigma_bkt.png', height = 5, width = 5, scale = 1)
+plotHPDSigma('bnt'); ggsave('figures/3Spp_WB/HDPSigma_bnt.png', height = 5, width = 5, scale = 1)
+plotHPDSigma('ats'); ggsave('figures/3Spp_WB/HDPsigma_ats.png', height = 5, width = 5, scale = 1)
 ```
@@
 
+#  save(q, file= "data/out/allBetas.RData")  for projections
+
   #reorder(parameter,median,na.rm=TRUE)
@@
      #   xlim(c(-0.15,0.11)) +
+        scale_x_continuous( breaks=c(-0.1,0,0.1)) +
         xlab("Parameter estimate") + theme(axis.text.y = element_blank(), axis.title.y = element_blank()) +
@@
 
-ggsave('figures/3Spp_WB/grBetas.png', height = 4, width = 10, scale = 2)
+ggsave('figures/3Spp_WB/grBetas.png', height = 4, width = 10, scale = 1.5)
 
@@
 
-###### by river for bkt
-
-isYOYGG <- 1
-speciesGGToPlot <- "Brook Trout"
-outputToPlot <- "meanPredGR"
-
-ggSingle <- list()
-singleDat <- list()
-for(i in 1:length(all))
-  #https://stackoverflow.com/questions/31993704/storing-ggplot-objects-in-a-list-from-within-loop-in-r
-      local({ i <- i
-  singleDat[[i]] <- selectSingleVar(pred, all, outputToPlot, all[i], isYOYGG)
-  print(c(i,all[i]))
- # print(str(singleDat[[i]]))
-
-  tmp <- singleDat[[i]] %>% filter(speciesGG == speciesGGToPlot)
-  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=riverGG ) ) +
-      geom_line( size = 1.225 ) +
-      theme_bw() +
-      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
-            axis.title.y = element_blank(),
-            legend.position="none"
-            ) +
-      geom_hline(yintercept = 0) +
-      ylim(-0.15,0.8) +
-      scale_x_continuous(allLabels[i]) +
-      facet_grid(~seasonGG)
-
-  if( i %in% remFacetLabel ) {
-    ggSingle[[i]] <<- ggSingle[[i]] +
-    theme(
-      strip.background = element_blank(),
-      strip.text.x = element_blank()
-    )
-  }
-})
-
-# export fig to save
-grid.arrange(grobs=ggSingle, left = "Growth rate (mm/d)")
-
-```
-
-```{r 2d density plots of mean predictions}
-
-selectPairVars <- function(p, all, depVar, varsToPlot, isYOYGG){
-
-  notPlot <- NA
-  notPlot[1] <- all[!(all %in% varsToPlot)][1]
-  notPlot[2] <- all[!(all %in% varsToPlot)][2]
-  notPlot[3] <- all[!(all %in% varsToPlot)][3]
-  notPlot[4] <- all[!(all %in% varsToPlot)][4]
-#  notPlot[5] <- all[!(all %in% varsToPlot)][5]
-
-  pGG <- p %>% filter( isYOY == isYOYGG, 
-                        eval(as.name(notPlot[1])) == 0, 
-                        eval(as.name(notPlot[2])) == 0, 
-                        eval(as.name(notPlot[3])) == 0,                                         
-                        eval(as.name(notPlot[4])) == 0 )
-  return(pGG)  
-}
-
-h <- list(); h[['bkt']] <- 8.5; h[['bnt']] <- 4.5; h[['ats']] <- 2.75
-
-for(i in c('bkt','bnt', 'ats')){
-  for(j in 0:1){
-  print(c(i,j))
-
-  p <- selectPairVars(pred, all, "meanPredGR", c("flow","temp"), j)  %>%
-         filter(species == i)
-
-  ggplot(p, aes(x = flow, y = temp, z = meanPredGR)) +
-    geom_tile(aes(fill = meanPredGR)) +
-    stat_contour(bins = 15, color = 'darkgrey') +
-    ggtitle(paste(j,i)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank(), panel.grid.major =        element_blank(), 
-          #axis.title.y = element_blank(),
-          legend.position="none"
-          ) +
-    facet_grid( riverGG ~ seasonGG )
-
-  ggsave(paste0('figures/3Spp_WBpredGRGrid',"_",i,"_",j,'.png'), width = 9, height = h[[i]], units='in')
-
-  }
-}
-
-#raw data plot - not very useful
-ggplot(d2, aes(x=flowStd,y=tempStd,z=grLength)) +
- #  stat_density_2d( color = 'darkgrey') +
-  stat_density_2d(geom = "raster", aes(fill = ..density..), contour = FALSE,interpolate=TRUE,h=2.5) +
-  facet_grid(season+isYOY~river+species)
-
-ggplot(d2, aes(x=tempStd,y=grLength)) +
-  geom_smooth() +
-  geom_smooth(method='lm',color='black',se=FALSE) +
-  ylim(c(0,0.8)) +
-  facet_grid(river+isYOY~season)
 ```
@@
 
-###### by river for bkt
-
-isYOYGG <- 0
-speciesGGToPlot <- "Brook Trout"
-outputToPlot <- "meanPredGRSigma"
-
-ggSingle <- list()
-singleDat <- list()
-for(i in 1:length(all))
-  #https://stackoverflow.com/questions/31993704/storing-ggplot-objects-in-a-list-from-within-loop-in-r
-      local({ i <- i
-  singleDat[[i]] <- selectSingleVarSigma(pred, all, outputToPlot, all[i], isYOYGG)
-  print(c(i,all[i]))
- # print(str(singleDat[[i]]))
-
-  tmp <- singleDat[[i]] %>% filter(speciesGG == speciesGGToPlot)
-  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=riverGG ) ) +
-      geom_line( size = 1.225 ) +
-      theme_bw() +
-      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
-            axis.title.y = element_blank(),
-            legend.position="none"
-            ) +
-      geom_hline(yintercept = 0) +
-      #ylim(-0.15,0.8) +
-      scale_x_continuous(allLabels[i]) +
-      facet_grid(~seasonGG)
-
-  if( i %in% remFacetLabel ) {
-    ggSingle[[i]] <<- ggSingle[[i]] +
-    theme(
-      strip.background = element_blank(),
-      strip.text.x = element_blank()
-    )
-  }
-})
-
-grid.arrange(grobs=ggSingle, left = "Standard deviation of growth rate (mm/d)")
-
 ```
@@
 
+```{r projections}
+# run 'Load data' chunk at top to get the 'mcmc' object
+
+speciesForProj <- 'bkt'
+
+# get mean on mean length by cohort for the fall yoy sample
+obsLenStats <-  
+  ddGIn2[[speciesForProj]] %>%
+    group_by(cohort,ageInSamples) %>%
+    summarise(lenMean = mean(observedLength, na.rm=TRUE),
+              lenSD = sd(observedLength, na.rm=TRUE)) %>%
+    filter(ageInSamples == 1) %>%
+    ungroup() %>%
+    summarise(lenMeanMean = mean(lenMean, na.rm=TRUE),
+              lenSDMean = sd(lenMean, na.rm=TRUE))
+
+#data for running the simulation
+simData <- list(
+  nReps = 1000, #num of mcmc iterations to grab
+  numInd = 500, # number of individual to simulate
+  nOccYOY = 3,
+  nOccAdult = 7,
+  riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear
+
+  species = speciesForProj,
+  meanInit = obsLenStats$lenMeanMean,
+  sdInit = obsLenStats$lenSDMean,
+  nSamplesAvail = mcmcInfo$nChains * mcmcInfo$nSamples
+)
+
+simData <- updateSimData(simData)
+nB <- getNBetas()
+m <- createMatrices()
+indVars <- getIndVars()
+sizeMat <- projectSizes(m)
+
+matplot(t(sizeMat[2,,]))
+
+predLen <- array2df(sizeMat, levels = list(iter=1:simData$nReps,ind=1:simData$numInd,occ=1:simData$nOcc), label.x="len")
+
+ggplot(predLen, aes(occ,len, group=ind)) +
+  geom_point(aes(color=ind))+
+  geom_line(aes(color=ind)) +
+  facet_wrap(~iter)
+
+# size=100
+# gr=10
+# sd=1
+# mean(rnorm(10000,size+gr,sd))
+# mean(size+rnorm(10000,gr,sd))
+
+```
+
 ```{r tables}
@@
 pd <- position_dodge(0.65)
+d2$speciesGG <- factor(d2$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
 
@@
 d2 %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>%
-  filter(isYOYDATA == 1) %>%
+  filter(isYOYDATA == 1, riverOrderedGG == 'West Brook') %>%
   summarize(meanGR = mean(grLength, na.rm=T),
@@
          axis.text.x  = element_text(angle=90, vjust=0.5, size=8) ) +
-  facet_grid(seasonGG ~ riverOrderedGG)
-
-ggsave('figures/3Spp_WBgrByYearYOY1.png')
+  facet_wrap(~seasonGG )
+
+ggsave('figures/3Spp_WB/grByYearYOY1.png')
 
 # isYOY2
-d %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>%
-  filter(isYOYDATA == 2) %>%
+d2 %>% group_by(speciesGG,riverOrderedGG,seasonGG,year) %>%
+  filter(isYOYDATA == 2, riverOrderedGG == 'West Brook') %>%
   summarize(meanGR = mean(grLength, na.rm=T),
@@
          axis.text.x  = element_text(angle=90, vjust=0.5, size=8) ) +
-  facet_grid(seasonGG ~ riverOrderedGG)
-
-ggsave('figures/3Spp_WBgrByYearYOY2.png')
+  facet_wrap(~seasonGG )
+
+ggsave('figures/3Spp_WB/grByYearYOY2.png')
 

### 2018-07-26 R/analyzeOutputFunctions.R

@@ -720,6 +720,7 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
   print(gg)
 
   ggg <- ggplot( ddGIn, aes( observedLengthOriginal, estLen, color = factor(leftOut) ) ) +
+  #ggg <- ggplot( ddGIn %>% filter(riverOrdered == 'west brook'), aes( observedLengthOriginal, estLen, color = factor(leftOut) ) ) +
     geom_point( alpha = 0.1 ) +
     geom_abline(intercept = 0, slope = 1) +
     scale_x_continuous("Observed length (mm)") +
@@ -734,6 +735,7 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
   print(ggg)
 
   ggsave(paste0('figures/obsPred_',speciesGr,'.png'),width = 7,height = 5)
+#  ggsave(paste0('figures/obsPred_',speciesGr,'_WB.png'),width = 7,height = 5)
 
   rmse <- ddGIn %>%
     mutate( resid = estLen - observedLengthOriginal,

### 2018-07-26 R/simulateSizesForParams.R

@@ -1,0 +1,170 @@
+#'Get params based on simData
+#'
+#'@param d a model run dataFrame
+#'@return a list
+#'@export
+#'
+updateSimData <- function(simData){
+  simData$isYOY <- c(rep(0,simData$nOccYOY),rep(1,simData$nOccAdult))
+  simData$seasons <- c(3,4,1,2,3,4,1,2,3,4) # will automate depending on nOcc_
+  simData$itersForSim <- sort(sample(1:simData$nSamplesAvail, simData$nReps))
+  simData$nOcc <- simData$nOccYOY + simData$nOccAdult
+
+  simData$lengthMean <- dGIn[[simData$species]][[1]]$constants$lengthMean
+  simData$lengthSD <- dGIn[[simData$species]][[1]]$constants$lengthSD
+
+  simData$sampInt <- c(70,122,70,101,70,122,70,101,70,122)
+  # d2 %>%
+  # group_by(season) %>%
+  # summarise(sampInt = mean(sampleInterval))
+
+  return(simData)
+}
+
+#'Get params based on simData
+#'
+#'@param d a model run dataFrame
+#'@return a list
+#'@export
+#'
+getNBetas <- function(){
+
+  nBetas <- dim(mcmc[[simData$species]]$sims.list$grBeta)[2]
+  nBetasBNT <- dim(mcmc[[simData$species]]$sims.list$grBetaBNT)[2]
+  nBetasATS <- dim(mcmc[[simData$species]]$sims.list$grBetaATS)[2]
+  nSigmaBetas <- dim(mcmc[[simData$species]]$sims.list$sigmaBeta)[2]
+#sizeMat <- intMat <- betaMat <- isYOYMat <- seasonMat <- matrix(NA, nrow = simData$numInd, ncol = simData$nOccYOY + simData$nOccAdult)
+  return(list(
+    nBetas=nBetas,nBetasBNT=nBetasBNT,nBetasATS=nBetasATS,nSigmaBetas=nSigmaBetas
+  ))
+}
+
+
+#'Create grid of input variables
+#'
+#'@param d a model run dataFrame
+#'@return a list of matrices
+#'@export
+#'
+createMatrices <- function(){
+
+  sizeMat <- intMat <- sigmaIntMat <- isYOYMat <- array(NA, c(simData$nReps, simData$numInd, simData$nOcc))
[…]

### 2018-07-31 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
add in 3spp projection sim

@@
 
-speciesForProj <- 'bkt'
+#data for running the simulation
+simData <- list(
+  nReps = 100, #num of mcmc iterations to grab
+  numInd = 500 , # number of individual to simulate
+  nOccYOY = 3,
+  nOccAdult = 7,
+  riverIndex = 1 #Levels: west brook < wb jimmy < wb mitchell < wb obear
+)
+
+stats3Spp <- anov <- list()
+
+for( speciesForProj in c('bkt','bnt','ats') ){
 
@@
       summarise(lenMeanMean = mean(lenMean, na.rm=TRUE),
-              lenSDMean = sd(lenMean, na.rm=TRUE))
-
-#data for running the simulation
-simData <- list(
-  nReps = 1000, #num of mcmc iterations to grab
-  numInd = 500, # number of individual to simulate
-  nOccYOY = 3,
-  nOccAdult = 7,
-  riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear
-
-  species = speciesForProj,
-  meanInit = obsLenStats$lenMeanMean,
-  sdInit = obsLenStats$lenSDMean,
-  nSamplesAvail = mcmcInfo$nChains * mcmcInfo$nSamples
-)
+                lenSDMean = mean(lenSD, na.rm=TRUE))
+
+  simData$species = speciesForProj
+  simData$meanInit = obsLenStats$lenMeanMean
+  simData$sdInit = obsLenStats$lenSDMean
+  simData$nSamplesAvail = mcmcInfo$nChains * mcmcInfo$nSamples
 
@@
   m <- createMatrices()
+
   indVars <- getIndVars()
-sizeMat <- projectSizes(m)
+
+  startTime <- Sys.time()
+  sizeStats <- sizeStats2 <- NULL
+  #loop over conditions
+  for(testRow in indVars$rowNum){
+    sizeMat <- projectSizes(m,simData,testRow)
+
+    sizeStats1 <- summarizeLens(sizeMat,testRow)
+    sizeStats <- rbind(sizeStats,sizeStats1[[1]]) #means over individuals (grouped by iter, occ)
+    sizeStats2 <- rbind(sizeStats2,sizeStats1[[2]]) #means by occ of means over individuals (grouped by occ)
+  }
+  endTime <- Sys.time()
+  (elapsed <- endTime - startTime)
+
+  stats3Spp[[speciesForProj]] <- list( sizeStats,sizeStats2 )
+
+  anov[[speciesForProj]] <- anova( lm( lenMean ~ temp + flow + bkt + bnt + ats, data = sizeStats %>% filter(occ == (simData$nOccYOY + simData$nOccAdult))) )
+
+}
+
+ggplot(sizeStats, aes())
 
@@
 
-predLen <- array2df(sizeMat, levels = list(iter=1:simData$nReps,ind=1:simData$numInd,occ=1:simData$nOcc), label.x="len")
-
-ggplot(predLen, aes(occ,len, group=ind)) +
+ggplot(predLen %>% filter(iter %in% 1:10), aes(occ,len, group=ind)) +
   geom_point(aes(color=ind))+
   geom_line(aes(color=ind)) +
+  theme(legend.position = 'none')+
   facet_wrap(~iter)

### 2018-07-31 R/simulateSizesForParams.R

@@ -129,17 +129,17 @@ getIndVars <- function(){
 #'@param d a model run dataFrame
 #'@return a matrix
 #'@export
+#'
+projectSizes <- function(m,simData,testRow){
 
-#project sizes
-projectSizes <- function(m){
+  d <- indVars %>% filter(rowNum == testRow)
 
-  testRow <- 22
   for(i in 1:simData$nReps){
-    print(paste0(i," out of ",simdData$nReps))
+    print(paste0(i," out of ",simData$nReps))
+    print(d)
     for(rows in 1:simData$numInd){
       for(cols in 1:(simData$nOcc-1)){
 
-        d <- indVars %>% filter(rowNum == testRow)
         gr <- m$intMat[i,rows,cols] +
           m$betaMat[i,1,rows,cols] * d$temp +
           m$betaMat[i,2,rows,cols] * d$flow +
@@ -168,3 +168,38 @@ projectSizes <- function(m){
   return(m$sizeMat)
 
 }
+
+
+#'Summarize predictions of body sizes
+#'
+#'@param d a model run dataFrame
+#'@return a matrix
+#'@export
+#'
+summarizeLens <- function(sizeMat,testRow){
+  predLen <- array2df(sizeMat, levels = list(iter=1:simData$nReps,ind=1:simData$numInd,occ=1:simData$nOcc), label.x="len")
+
+  p <- predLen %>%
+    group_by(iter,occ) %>%
+    summarize( lenMean = mean(len),
+               lenSD = sd(len),
+               n=n()) %>%
+    ungroup()
+
+  d <- indVars %>% filter(rowNum == testRow)
+  p <- cbind(p,d)
+
+  p2 <- p %>%
+    group_by(occ) %>%
+    summarize( lenMeanMean = mean(lenMean),
+               lenMeanSD = sd(lenMean),
+               lenSDMean = mean(lenSD),
+               lenSDSD = sd(lenSD),
+               n=n()) %>%
+    ungroup()
+
+  p2 <- cbind(p2,d)
+
+  return(list(p,p2))
+}
+

### 2018-07-31 manuscriptAnalysis/CTMax.R

@@ -1,0 +1,35 @@
+#From Evan's Ecology paper'
+
+d <- data.frame(temp = seq(1,20.5,0.1))
+
+# bkt first, bnt second
+
+tOpt <- c(11.9,13.3)
+cTMax <- c(19.5,19.3)
+sigma <- c(3.7,4.1)
+
+# lInf <- 354
+# k <- 0.0013
+# flowBeta <- 0.098
+# bktBeta <- -0.051
+# bntBeta <- -0.039
+#
+# bktDen <- 7.01
+# bntDen <- 13.00
+# flow <- 0.14
+#
+# gOpt <- k*(lInf-len) + flowBeta*flow + bktBeta*bktDen + bntBeta*bntDen
+
+i <- 1
+d$pT_BKT <- ifelse( d$temp <= tOpt[i],
+                 exp(-((d$temp - tOpt[i])/(2*sigma[i]))^2), #there's an error in the paper
+                 1 - ((d$temp - tOpt[i])/(tOpt[i] - cTMax[i]))^2
+              )
+
+i <- 2
+d$pT_BNT <- ifelse( d$temp <= tOpt[i],
+                    exp(-((d$temp - tOpt[i])/(2*sigma[i]))^2), #there's an error in the paper
+                    1 - ((d$temp - tOpt[i])/(tOpt[i] - cTMax[i]))^2
+)
+
+ggplot(d, aes(temp,pT_BKT)) + geom_line() + geom_line(aes(temp,pT_BNT), color = "brown")

### 2018-07-31 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
add relImp graph

@@
 library(arm)
+library(relaimpo)
 library(linkedModels)
@@
 
-stats3Spp <- anov <- list()
-
-for( speciesForProj in c('bkt','bnt','ats') ){
+stats3Spp <- anov <- elapsed <- lm <- relImp <- list()
+spp <- c('bkt','bnt','ats')
+
+for( speciesForProj in spp ){
 
@@
   endTime <- Sys.time()
-  (elapsed <- endTime - startTime)
+  (elapsed[[speciesForProj]] <- endTime - startTime)
 
@@
 
-  anov[[speciesForProj]] <- anova( lm( lenMean ~ temp + flow + bkt + bnt + ats, data = sizeStats %>% filter(occ == (simData$nOccYOY + simData$nOccAdult))) )
+  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt^2, data = sizeStats %>% filter(occ == (simData$nOccYOY + simData$nOccAdult)))
+
+  relImp[[speciesForProj]] <- calc.relimp(lm[[speciesForProj]], type = c("lmg"), rela = TRUE)
+
+  anov[[speciesForProj]] <- anova( lm[[speciesForProj]] )
 
@@
 
-ggplot(sizeStats, aes())
-
-matplot(t(sizeMat[2,,]))
-
-ggplot(predLen %>% filter(iter %in% 1:10), aes(occ,len, group=ind)) +
-  geom_point(aes(color=ind))+
-  geom_line(aes(color=ind)) +
-  theme(legend.position = 'none')+
-  facet_wrap(~iter)
+# make bar chart of relative importance of each variable for each spp
+rI <- cbind(data.frame(bktRI = relImp[['bkt']]$lmg), data.frame(bntRI = relImp[['bnt']]$lmg), data.frame(atsRI = relImp[['ats']]$lmg)) %>%
+        rownames_to_column() %>% gather(key=rowname) %>% mutate(var = rep(1:length(relImp[['bkt']]$lmg),length(spp)))
+
+ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
+  geom_col(position='dodge') +
+  scale_x_discrete('Parameter name',
+                   labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow')) +
+  scale_fill_grey() +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme( legend.position = 'none')
+
+ggsave('figures/3Spp_WB/relImp.png', width = 9, height = 7, units='in')
 

### 2018-07-31 R/simulateSizesForParams.R

@@ -135,7 +135,7 @@ projectSizes <- function(m,simData,testRow){
   d <- indVars %>% filter(rowNum == testRow)
 
   for(i in 1:simData$nReps){
-    print(paste0(i," out of ",simData$nReps))
+    print(paste0(i," out of ",simData$nReps,"  ",speciesForProj))
     print(d)
     for(rows in 1:simData$numInd){
       for(cols in 1:(simData$nOcc-1)){

### 2018-08-01 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added projection graphs

@@
 
-  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt^2, data = sizeStats %>% filter(occ == (simData$nOccYOY + simData$nOccAdult)))
+  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt^2, data = sizeStats %>% filter(occ == (simData$nOcc)))
 
@@
 
+projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
+save( projOut, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
+
+# make figures of relative importance for each sampling occasion
+rIAll <- cAll <- NULL
+for( occSelected in 2:simData$nOcc){
+  print(occSelected)
+  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
+
+  for(spp1 in spp){
+
+      lmAll[[spp1]] <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected))
+
+      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
+
+      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
+  }
+
   # make bar chart of relative importance of each variable for each spp
-rI <- cbind(data.frame(bktRI = relImp[['bkt']]$lmg), data.frame(bntRI = relImp[['bnt']]$lmg), data.frame(atsRI = relImp[['ats']]$lmg)) %>%
-        rownames_to_column() %>% gather(key=rowname) %>% mutate(var = rep(1:length(relImp[['bkt']]$lmg),length(spp)))
+  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
+              data.frame(bntRI = relImpAll[['bnt']]$lmg), 
+              data.frame(atsRI = relImpAll[['ats']]$lmg)) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  rIAll <- rbind(rIAll,rI)
 
@@
     geom_col(position='dodge') +
-  scale_x_discrete('Parameter name',
-                   labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow')) +
+    scale_x_discrete('Parameter',
+                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
     scale_fill_grey() +
     scale_y_continuous('Relative proportion of variance explained') +
+    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
     theme_publication() +
@@
 
-ggsave('figures/3Spp_WB/relImp.png', width = 9, height = 7, units='in')
+  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
+
+  # coefficients
+  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
+                 data.frame(bntC = coefsAll[['bnt']]), 
+                 data.frame(atsC = coefsAll[['ats']])) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  cAll <- rbind(cAll,coefs)
+}
+
+######################################################
+# relImp over occasions for each spp and parameter
+labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
+
+# leaving out bkt*bnt, too small
+ggplot(rIAll %>% filter(var<7), aes((occ), value, color = factor(rowname))) +
+  geom_point() +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labels))
+
+ggsave(paste0('figures/3Spp_WB/relImpOccAll.png'), width = 11, height = 9, units='in')
+
+rIMeans <- rIAll %>%
+  group_by(rowname,var) %>%
+  summarize( mean = mean(value),
+             sd = sd(value),
+             stderr = sd(value)/sqrt(length(value))) %>%
+  mutate( up = mean + stderr )
+
+dodge <- position_dodge(width=0.9)
+ggplot(rIMeans, aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = mean, ymax = up), width = 0.25, position=dodge) +
+  geom_col(position=dodge) +
+  scale_x_discrete('Parameter',
+                   labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+  scale_fill_grey() +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme( legend.position = 'none')
+
+ggsave(paste0('figures/3Spp_WB/relImpOccMean.png'), width = 9, height = 7, units='in')
+
+#######################
+# coefs
+labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
+
+ggplot(cAll %>% filter(var %in% 2:7), aes((occ), value, color = factor(rowname))) +
+  geom_point() +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Coefficients') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
+
+ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
+
+# intercept only
+ggplot(cAll %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=4) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Intercept') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
+
+ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
 

### 2018-08-01 R/simulateSizesForParams.R

@@ -149,7 +149,7 @@ projectSizes <- function(m,simData,testRow){
           m$betaMat[i,6,rows,cols] * d$bkt +
           m$betaMat[i,7,rows,cols] * ((m$sizeMat[i,rows,cols] - simData$lengthMean) / simData$lengthSD) +
           m$betaMatBNT[i,1,rows,cols] * d$bnt +
-          m$betaMatBNT[i,2,rows,cols] * d$bnt^2 +
+          m$betaMatBNT[i,2,rows,cols] * d$bnt * d$bkt +
           m$betaMatATS[i,1,rows,cols] * d$ats +
           m$indREMat[i,rows,cols]
 

### 2018-10-23 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added gr trends over time

@@
 load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
+load("D:/projects/linkedModels/data/out/ddddD_bktbntats_1997.RData")
 load("D:/projects/linkedModels/data/out/rawCountsAndMasses.RData")
@@
 load("D:/projects/linkedModels/data/cd_west_1997.RData")
+```
+
+```{r count summaries for MS}
+
+ddGInAll <- rbind(ddGIn2[[1]],ddGIn2[[2]],ddGIn2[[3]]) %>%
+  filter(year %in% 2000:2015, river == 'west brook') %>%
+  mutate( consecOcc = ifelse( is.na(grLength), 0,1 ) )
+
+ddGInAll %>%
+  group_by(river,species) %>%
+  distinct(tag) %>%
+  summarize( n = n() )
+
+#   species     n
+#   <chr>   <int>
+# 1 ats      5032
+# 2 bkt      8556
+# 3 bnt      6389
+
+ddGInAll %>%
+  group_by(river,species) %>%
+  summarize( n = n() )
+
+#   species     n
+#   <chr>   <int>
+# 1 ats     15791
+# 2 bkt     18412
+# 3 bnt     16510
+
+ddGInAll %>%
+  group_by(river,species,enc) %>%
+  summarize( n = n() )
+
+#   species   enc     n
+#   <chr>   <dbl> <int>
+# 1 ats         0  3515
+# 2 ats         1 12276
+# 3 bkt         0  3464
+# 4 bkt         1 14948
+# 5 bnt         0  3855
+# 6 bnt         1 12655
+
+ddGInAll %>%
+  group_by(river,species,consecOcc) %>%
+  summarize( n = n() ) %>%
+  spread(consecOcc,n, sep="_") %>%
+  mutate( prop0 = consecOcc_0/(consecOcc_0+consecOcc_1),
+          prop1 = 1 - prop0)
+
+#   river       species consecOcc_0 consecOcc_1 prop0 prop1
+# 5 west brook  ats           10203        5588 0.646 0.354
+# 6 west brook  bkt           13631        4781 0.740 0.260
+# 7 west brook  bnt           12420        4090 0.752 0.248
+
+length(unique(ddGInAll$sampleNumber))
+
+```
+
+```{r table of estimated abundances}
+
+ddGIn2[['bkt']] %>%
+  filter(river == 'west brook') %>%
+  distinct(river,year,season,nAllFishBySpeciesPBKT,nAllFishBySpeciesPBNT,nAllFishBySpeciesPATS) %>%
+  arrange(year, season)
+
 ```
@@
 
-```{r raw counts}
+```{r adjusted counts}
 allFishBySpeciesYOY$riverOrderedGG <- factor(allFishBySpeciesYOY$river,
@@
                 massAllFishBySpecies = sum(massAllFishBySpeciesYOY, na.rm=T))
+allFishBySpecies$seasonGG <- factor(allFishBySpecies$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
 allFishBySpeciesYOY <- left_join(allFishBySpeciesYOY,allFishBySpecies)
@@
 
-ggsave('figures/3Spp_WB/rawCounts.png')
-
+ggsave('figures/3Spp_WB/counts.png')
+
+ggplot(allFishBySpeciesYOY %>% filter(riverOrderedGG == "West Brook", year >=2000), aes(year,nAllFishBySpecies)) +
+  geom_point(aes(color = speciesGG), size=3) +
+#  geom_line(aes(color = speciesGG)) +
+  geom_smooth(aes(color = speciesGG), se=FALSE,method='lm') +
+  geom_line( data = allFish %>% filter(riverOrderedGG == "West Brook", year >=2000), aes(year,nAllFish), size=1.25, color='darkgrey', linetype = 5 ) +
+  scale_y_continuous(limits = c(0,NA)) +
+  theme_publication() +
+  labs( x = "Year", y = "Estimated abundance" ) +
+  scale_color_grey(start = 0, end = 0.9) +
+  facet_wrap( ~ seasonGG , scales = "free_y" )
+
+ggsave('figures/3Spp_WB/countsWSlope.png', width = 11, height = 9, units='in')
+
+nSlopes <- allFishBySpeciesYOY %>%
+  filter(riverOrderedGG == "West Brook", year >=2000) %>%
+  group_by( species,  season ) %>%
+  nest()
+
+nModel <- function(df){
+  lm( nAllFishBySpecies ~ year, data = df )
+}
+
+nSlopes <- nSlopes %>%
+  mutate( model = map(nSlopes$data, nModel) )
+
+nSlopesTidy <- nSlopes %>%
+  mutate( glance = map(model, broom::tidy)) %>% 
+  unnest(glance, .drop = TRUE) %>%
+  filter( term == 'year')
+
+save(nSlopesTidy,file = 'D:/projects/linkedModels/data/out/nSlopesTidy.RData')
+########################
 # add in sampleNumber
@@
   facet_wrap(  ~riverOrderedGG )#, scales = "free_y" )
+
+```
+
+```{r Table 1 - sample summary}
+
+# sample summary table
+summaryTable <- allFishBySpecies %>% 
+          select(-massAllFishBySpecies) %>% 
+          filter(river == 'west brook', year %in% 2000:2015) %>% 
+          spread(species,nAllFishBySpecies) %>% 
+          arrange(year,seasonGG)
+
+write.csv(summaryTable, file = 'D:/projects/linkedModels/tables/rawCounts.csv')
 
@@
 
+```{r mean lengths}
+
+# Has mean size changed over time?
+means <- 
+  cd %>% mutate( age = year - cohort ) %>%
+    filter( riverOrdered == 'west brook', ageInSamples %in% 1:10, age < 3, year < 2016 ) %>%
+    group_by(species,ageInSamples,year,season,age) %>%
+    summarize(meanLen = mean(observedLength,na.rm = TRUE),
+              sdLen = sd(observedLength,na.rm = TRUE),
+              meanGR = mean(grLength,na.rm = TRUE),
+              sdGR = sd(grLength,na.rm = TRUE)
+              )
+
+lenSlopes <- means %>%
+  group_by( species, ageInSamples, season, age ) %>%
+  nest()
+
+lengthModel <- function(df){
+  lm( meanLen ~ year, data = df )
+}
+
+grModel <- function(df){
+  lm( meanGR ~ year, data = df )
+}
+
+lenSlopes <- lenSlopes %>%
+  mutate( model = map(lenSlopes$data, lengthModel),
+          modelGR = map(lenSlopes$data, grModel))
+
+###################################
+######### len here, gr below ######
+lenSlopesTidy <- lenSlopes %>%
+  mutate(glance = map(model, broom::tidy)) %>% 
+  unnest(glance, .drop = TRUE) %>%
+  filter(term == 'year') %>%
+  mutate( sig = ifelse(p.value < 0.05,"*","")) %>%
+  mutate( sig = ifelse(p.value < 0.001,"**",sig)) %>%
+  mutate( sig = ifelse(p.value < 0.0001,"***",sig))
+
+save(lenSlopesTidy,file = 'D:/projects/linkedModels/data/out/lenSlopesTidy.RData')
+##
+means$seasonGG <- factor(means$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+means$speciesGG <- factor(means$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+lenSlopesTidy$seasonGG <- factor(lenSlopesTidy$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+lenSlopesTidy$speciesGG <- factor(lenSlopesTidy$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+
+ggplot( means %>% filter(year >= 2000, species != 'ats'), aes(year,meanLen, group= speciesGG)) +
+  geom_point( aes(color = speciesGG), size = 4) +
+  geom_smooth( aes(color = speciesGG), se = FALSE, method = 'lm') +
+  labs( x = "Year", y = "Mean body length (mm)" ) +
+  # geom_text(data = lenSlopesTidy %>% filter(species == 'bkt'), aes(x=1999,y=220, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
+  # geom_text(data = lenSlopesTidy %>% filter(species == 'bnt'), aes(x=1999,y=200, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
+  # geom_text(data = lenSlopesTidy %>% filter(species == 'ats'), aes(x=1999,y=180, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
+  geom_text(data = lenSlopesTidy %>% filter(species == 'bkt', age<2), aes(x=2000,y=225, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+  geom_text(data = lenSlopesTidy %>% filter(species == 'bnt', age<2), aes(x=2000,y=203, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+#  geom_text(data = lenSlopesTidy %>% filter(species == 'ats', age<2), aes(x=2000,y=181, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+
+    geom_text(data = lenSlopesTidy %>% filter(species == 'bkt', age==2), aes(x=2012.5,y=104, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+  geom_text(data = lenSlopesTidy %>% filter(species == 'bnt', age==2), aes(x=2012.5,y=82, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+#  geom_text(data = lenSlopesTidy %>% filter(species == 'ats', age==2), aes(x=2012.5,y=80, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+  theme_publication() +
+  scale_color_grey(start = 0.15, end = 0.75) +
+  facet_grid(seasonGG~age)
+
+ggsave(paste0('figures/3Spp_WB/meanLengths.png'), width = 11, height = 11, units='in')
+
+# mean increases 
+lenSlopesTidy %>%
+  filter(species != 'ats') %>%
+  summarise( means = mean(estimate),
+             sd = sd(estimate))
+
+# mean increases by species
+lenSlopesTidy %>%
+  group_by(species) %>%
+  summarise( means = mean(estimate),
+             sd = sd(estimate))
+
+# do increases (slopes) increase over age? Yes
+ggplot(lenSlopesTidy %>% filter(species != 'ats'), aes((ageInSamples),estimate, color=speciesGG)) +
+  geom_point(aes( shape = factor(seasonGG)), size = 3) +
+  geom_smooth(method='lm', se=FALSE) +
+  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
+  labs( x = "Age", y = "Slope of mean body length over years" ) +
+  theme_publication() +
+  scale_color_grey(start = 0.15, end = 0.75)
+
+ggsave(paste0('figures/3Spp_WB/meanLengthsOverAge.png'), width = 6, height = 6, units='in')
+
+summary(lm(estimate~ageInSamples, data = lenSlopesTidy %>% filter(species=='bkt')))
+summary(lm(estimate~ageInSamples, data = lenSlopesTidy %>% filter(species=='bnt')))
+
+#########################
+#### gr here, len above
+
+grSlopesTidy <- lenSlopes %>%
+  mutate(glance = map(modelGR, broom::tidy)) %>% 
+  unnest(glance, .drop = TRUE) %>%
+  filter(term == 'year') %>%
+  mutate( sig = ifelse(p.value < 0.05,"*","")) %>%
+  mutate( sig = ifelse(p.value < 0.001,"**",sig)) %>%
+  mutate( sig = ifelse(p.value < 0.0001,"***",sig))
+
+save(grSlopesTidy,file = 'D:/projects/linkedModels/data/out/grSlopesTidy.RData')
+##
+means$seasonGG <- factor(means$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+means$speciesGG <- factor(means$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+grSlopesTidy$seasonGG <- factor(grSlopesTidy$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+grSlopesTidy$speciesGG <- factor(grSlopesTidy$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+
+ggplot( means %>% filter(year >= 2000, species != 'ats'), aes(year,meanGR, group= speciesGG)) +
+  geom_point( aes(color = speciesGG), size = 4) +
+  geom_smooth( aes(color = speciesGG), se = FALSE, method = 'lm') +
+  labs( x = "Year", y = "Mean growth rate (mm/d)" ) +
+  # geom_text(data = grSlopesTidy %>% filter(species == 'bkt'), aes(x=1999,y=220, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
+  # geom_text(data = grSlopesTidy %>% filter(species == 'bnt'), aes(x=1999,y=200, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
+  # geom_text(data = grSlopesTidy %>% filter(species == 'ats'), aes(x=1999,y=180, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
+  geom_text(data = grSlopesTidy %>% filter(species == 'bkt', age<2), aes(x=2000,y=0.7, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
+  geom_text(data = grSlopesTidy %>% filter(species == 'bnt', age<2), aes(x=2000,y=0.6, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
+#  geom_text(data = grSlopesTidy %>% filter(species == 'ats', age<2), aes(x=2000,y=181, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+
+    geom_text(data = grSlopesTidy %>% filter(species == 'bkt', age==2), aes(x=2011.5,y=0.66, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
+  geom_text(data = grSlopesTidy %>% filter(species == 'bnt', age==2), aes(x=2011.5,y=0.56, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
+#  geom_text(data = grSlopesTidy %>% filter(species == 'ats', age==2), aes(x=2012.5,y=80, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
+  theme_publication() +
+  scale_color_grey(start = 0.15, end = 0.75) +
+  facet_grid(seasonGG~age)
+
+ggsave(paste0('figures/3Spp_WB/meanGRs.png'), width = 11, height = 11, units='in')
+
+# mean increases 
+grSlopesTidy %>%
+  filter(species != 'ats') %>%
+  summarise( means = mean(estimate),
+             sd = sd(estimate))
+
+# mean increases by species
+grSlopesTidy %>%
+  group_by(species) %>%
+  summarise( means = mean(estimate),
+             sd = sd(estimate))
+
+# do increases (slopes) increase over age? Yes
+ggplot(grSlopesTidy %>% filter(species != 'ats'), aes((ageInSamples),estimate, color=speciesGG)) +
+  geom_point(aes( shape = factor(seasonGG)), size = 3) +
+  geom_smooth(method='lm', se=FALSE) +
+  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
+  labs( x = "Age", y = "Slope of mean growth rate over years" ) +
+  theme_publication() +
+  scale_color_grey(start = 0.15, end = 0.75)
+
+ggsave(paste0('figures/3Spp_WB/meanGRsOverAge.png'), width = 6, height = 6, units='in')
+
+summary(lm(estimate~ageInSamples, data = grSlopesTidy %>% filter(species=='bkt')))
+summary(lm(estimate~ageInSamples, data = grSlopesTidy %>% filter(species=='bnt')))
+
+```
+
 ```{r figs 3,4, flow and temp}
@@
 
+lmFunctionF <- function(df){ lm( meanF ~ year, data=df ) }
+
+flowMods <- d2 %>%
+  group_by(riverOrderedGG,seasonGG,year) %>%
+  summarize(meanF = mean(meanFlow, na.rm=T),
+            sdF = sd(meanFlow, na.rm=T)) %>%
+  group_by( riverOrderedGG, seasonGG ) %>%
+  nest() %>%
+  mutate( model = map(data,lmFunctionF) )
+
+flowSlopesTidy <- flowMods %>%
+  mutate(tidy = map(model,broom::tidy)) %>%
+  dplyr::select(-data,-model) %>%
+  unnest() %>%
+  filter( term == 'year') %>%
+  mutate( sig = ifelse(p.value < 0.05,"*",""))
+
+save(flowSlopesTidy,file = 'D:/projects/linkedModels/data/out/flowSlopesTidy.RData')
+
+#################
+
 lmFunction <- function(df){ lm( meanT ~ year, data=df ) }
@@
 
-tempModsTidy <- tempMods %>%
+tempSlopesTidy <- tempMods %>%
   mutate(tidy = map(model,broom::tidy)) %>%
@@
   geom_smooth(method = 'lm', se=F, color = 'darkgrey') +
-  geom_point(  ) +
+  geom_point( size = 3 ) +
   geom_line() +
@@
   labs( x = "Year", y = "Stream temperature (C)" ) +
-  geom_text(data=tempModsTidy %>% filter(riverOrderedGG == "West Brook"),aes(x=2000.5,y=17.5, label=paste(round(estimate,2),sig))) +
+  geom_text(data=tempSlopesTidy %>% filter(riverOrderedGG == "West Brook"),aes(x=2000.5,y=17.5, label=paste(round(estimate,2),sig))) +
   theme_publication() +
@@
 ggsave('figures/3Spp_WB/temp.png')
+
+save(tempSlopesTidy,file = 'D:/projects/linkedModels/data/out/tempSlopesTidy.RData')
+
 ```
@@
 
-cd %>% group_by(speciesGG,riverOrderedGG,seasonGG) %>%
-  filter(isYOY == 1) %>%
+growthYOY <- 
+cd %>% group_by(speciesGG,species,riverOrderedGG,seasonGG,isYOY) %>%
+  filter( riverOrdered == 'west brook', year < 2016, species != 'ats' )  %>%
   summarize(meanGR = mean(grLength, na.rm=T),
-            sdGR = sd(grLength, na.rm=T)) %>%
-  filter(riverOrderedGG == "West Brook") %>%
-ggplot( aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
-  geom_point( position = pd, size = 2 ) +
+            sdGR = sd(grLength, na.rm=T))
+
+ggplot(growthYOY%>%filter(isYOY == 1), aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
+  geom_point( position = pd, size = 3 ) +
   geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
@@
   #scale_x_continuous( breaks = 1997:2015 ) +
+  scale_color_grey(start = 0.0, end = 0.5) +
   theme_publication() +
@@
 
-ggsave('figures/3Spp_WB/meanGRYOY1.png', width = 7, height = 7, units='in')
-
-cd %>% group_by(speciesGG,riverOrderedGG,seasonGG) %>%
-  filter(isYOY == 2) %>%
-  summarize(meanGR = mean(grLength, na.rm=T),
-            sdGR = sd(grLength, na.rm=T)) %>%
-  filter(riverOrderedGG == "West Brook") %>%
-ggplot( aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
-  geom_point( position = pd,size = 2 ) +
+ggsave('figures/3Spp_WB/meanGRYOY1.png', width = 4, height = 4, units='in')
+
+ggplot(growthYOY%>%filter(isYOY == 2), aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
+  geom_point( position = pd, size = 3 ) +
   geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
@@
   #scale_x_continuous( breaks = 1997:2015 ) +
+  scale_color_grey(start = 0.0, end = 0.5) +
   theme_publication() +
   theme( panel.grid.minor = element_blank() )
-#  facet_wrap( ~ riverOrderedGG)
-
-ggsave('figures/3Spp_WB/meanGRYOY2.png', width = 7, height = 7, units='in')
-
-# mean growth by species
+
+ggsave('figures/3Spp_WB/meanGRYOY2.png', width = 4, height = 4, units='in')
+
+# get ratios of growth rates for the 2 species
+growthYOYWide <- growthYOY %>% ungroup() %>% select(-sdGR,-speciesGG) %>% spread(key=species,value=meanGR) %>%
+  mutate(ratio = bnt/bkt)
+
+mean(growthYOYWide$ratio)
+# 1.107745
+
 ```
@@
 
-cd %>% group_by(species) %>% filter(riverOrderedGG == "West Brook") %>%
+cd %>% group_by(species) %>% filter(riverOrderedGG == "West Brook",species != 'ats') %>%
   summarize(meanGR = mean(grLength, na.rm=T),
             sdGR = sd(grLength, na.rm=T))
-.182/.197 #bkt/bnt
-.151/.197 #ats/bnt
-
-cd %>% group_by(isYOY) %>% filter(riverOrderedGG == "West Brook") %>%
+.197/.182#bnt/bkt
+
+cd %>% group_by(isYOY) %>% filter(riverOrderedGG == "West Brook",species != 'ats') %>%
   summarize(meanGR = mean(grLength, na.rm=T),
             sdGR = sd(grLength, na.rm=T))
-.120/.226 #adult/yoy
-.226/.120
-
-cd %>% group_by(season) %>% filter(riverOrderedGG == "West Brook") %>%
+.145/.244 #adult/yoy
+.244/.145
+
+cd %>% group_by(season) %>% filter(riverOrderedGG == "West Brook",species != 'ats') %>%
   summarize(meanGR = mean(grLength, na.rm=T),
             sdGR = sd(grLength, na.rm=T))
-.437/((.0876+.0866+.0485)/3)
+.434/((.114+.124+.067)/3)
 ```
@@
     rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1)
-  ggplot(p, aes(year,invlogit(est),color=factor(species))) + geom_point() + facet_grid( season ~ isYOY)
+
+  p$speciesGG <- factor(p$species, levels = 1:3, labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
+  p$seasonGG <- factor(p$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+  p$isYOYGG <- factor(p$isYOY, levels = 1:2, labels = c("Juvenile","Adult"), ordered = T)
+
+  ggplot(p, aes(year,invlogit(est),color=factor(speciesGG))) + 
+    geom_point(size = 2) + 
+    labs( x = 'Year', y = 'Probability of detection') +
+    scale_color_grey(start = 0.0, end = 0.85) +
+    theme_publication() +
+    facet_grid( seasonGG ~ isYOYGG)
 
   # seem to need to run the ggsave outside of markdown by pasting into console
-   ggsave('figures/3Spp_WB/p.png')
+   ggsave('figures/3Spp_WB/p.png', height = 11, width = 9, units = 'in')
 
@@
 
+rBkt <- unlist(mcmc[['bkt']]$Rhat)
+sort(rBkt[rBkt > 1.1])
+
+rBnt <- unlist(mcmc[['bnt']]$Rhat)
+sort(rBnt[rBnt > 1.1])
+mcmc[['bnt']]$Rhat$grBeta[,,,1]
+mcmc[['bnt']]$Rhat$grInt
+mcmc[['bnt']]$Rhat$grIntMu
+
 rHat <- list()
@@
 
-ggplot(rHat[["ats"]], aes(beta,rHat)) +
+hist(rHat[["bkt"]]$rHat)
+hist(rHat[["bnt"]]$rHat)
+rHat[["bnt"]] %>% filter( rHat >1.1 )
+
+ggplot(rHat[["bkt"]], aes(beta,rHat)) +
   geom_point() +
@@
 grInt <- list()
-grInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int")
-grInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int")
-grInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int")
+grInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>% mutate(species = 'bkt')
+grInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int") %>%   mutate(species = 'bnt')
+grInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int") %>% mutate(species = 'ats')
 
@@
 
+#grIntDF <- rbind(grInt[['bkt']],grInt[['bnt']],grInt[['ats']])
+#tmp <- grIntDF %>% filter(river == 'west brook')
+#save(tmp , file= "data/out/grIntDFAllIters.RData") #for Ron
+
 ##################################################
@@
 
-  probs <- c(0.05,0.1,0.5,0.9,0.95)
+  probs <- c(0.025,0.1,0.5,0.9,0.975)
   q <- grInt[[sppToPlot]] %>%
@@
 
-    gg <- ggplot(p %>% filter(river=='west brook'), aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(seasonGG), shape = factor(isYOY))) + 
-        theme_publication() +  
-        geom_point(size = 3) +
+  #save(p, file= paste0("data/out/allInts_",sppToPlot,".RData"))  #for projections and tables
+
+    gg <- ggplot(p %>% filter(river=='west brook'), aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(isYOY), shape = factor(isYOY))) + 
+        theme_publication() +  
+        geom_point(size = 4) +
         geom_segment(aes(x = intByDay, xend = intByDayUp, yend = reorder(parameter, intByDay)), 
@@
         xlim(c(-0.00,0.55)) +
-        xlab("Mean daily growth (mm/d)") + ylab("Season") 
+        xlab("Mean daily growth (mm/d)") + ylab("Season") +
+        scale_color_grey(start = 0, end = 0.65) 
        # ggtitle(sppToPlot)
@@
 
-  probs <- c(0.05,0.1,0.5,0.9,0.95)
+  probs <- c(0.025,0.1,0.5,0.9,0.975)
   q <- sigmaInt[[sppToPlot]] %>%
@@
 
-    gg <- ggplot(p %>% filter(river == 'west brook'), aes(x = exp(int), y = reorder(parameter,int,na.rm=TRUE), color = factor(season), shape = factor(isYOY))) + 
+    gg <- ggplot(p %>% filter(river == 'west brook'), aes(x = exp(int), y = reorder(parameter,int,na.rm=TRUE), color = factor(isYOY), shape = factor(isYOY))) + 
         theme_publication() +  
@@
         #xlim(c(-0.0015,0.01)) +
-        xlab("Standard deviation of daily growth (mm/d)") + ylab("Season") 
+        xlab("Standard deviation of daily growth (mm/d)") + ylab("Season") +
+        scale_color_grey(start = 0, end = 0.65) 
        # ggtitle(sppToPlot)
@@
 
-```{r}
+```{r grInt}
 #riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
@@
 grBetaDF <- rbind(grBetaDF1,grBetaBNTDF,grBetaATSDF)
+
+#tmp <- grBetaDF %>% filter(river == 'west brook')
+#save(tmp , file= "data/out/grBetaDFAllIters.RData") #for Ron
 ##################################################
@@
 
-  probs <- c(0.05,0.1,0.5,0.9,0.95)
+  probs <- c(0.025,0.1,0.5,0.9,0.975)
   nSpecies <- 3
@@
     data.frame() %>%
-    rename( median = X0.5, lo = X0.05, hi = X0.95 )
+    rename( median = X0.5, lo = X0.025, hi = X0.975 )
 
@@
 
-#  save(q, file= "data/out/allBetas.RData")  for projections
+  save(q, file= "data/out/allBetas.RData")  #for projections and tables
 
@@
 
-    ggplot(q %>% filter(river == 'west brook'), aes(x = median, y = parameterOrd, color = factor(speciesGG), shape = factor(isYOY))) + 
-        geom_vline(xintercept = 0,color='black') +
-        theme_publication() +  
-        geom_point(size = 3) +
+    ggplot(q %>% filter(river == 'west brook', species != 'ats'), aes(x = median, y = parameterOrd, color = factor(species), shape = factor(isYOY))) + 
+        geom_vline(xintercept = 0,color='grey') +
+        theme_publication() +  
+        geom_point(size = 4) +
         geom_segment(aes(x = median, xend = hi, yend = parameterOrd), 
-        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
+        size = 0.5, arrow = arrow(angle = 90, length = unit(0.1, "inches"))) + 
         geom_segment(aes(x = median, xend = lo, yend = parameterOrd), 
-        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
+        size = 0.5,arrow = arrow(angle = 90, length = unit(0.1, "inches"))) +
      #   xlim(c(-0.15,0.11)) +
@@
         xlab("Parameter estimate") + theme(axis.text.y = element_blank(), axis.title.y = element_blank()) +
+        scale_color_grey(start = 0, end = 0.5)  +
         facet_grid(seasonGG~betaGG)
 
-ggsave('figures/3Spp_WB/grBetas.png', height = 4, width = 10, scale = 1.5)
-
+ggsave('figures/3Spp_WB/grBetas.png', height = 8, width = 10)
+
+save(betas,file = 'D:/projects/linkedModels/data/out/nSlopesTidy.RData')
+
+```
+
+```{r table of Ints}
+load(file = "data/out/allInts_bkt.RData") #loads p
+pBKT <- p %>% mutate(species = 'bkt')
+
+load(file = "data/out/allInts_bnt.RData") #loads p
+pBNT <- p %>% mutate(species = 'bnt')
+
+pp <- rbind(pBKT,pBNT)
+
+intsForTable <- pp %>% 
+  filter(river == 'west brook', species %in% c('bkt','bnt')) %>%
+  arrange(species,isYOY,seasonGG) %>%
+  select(species,isYOY,seasonGG,intDown,int,intUp) %>%
+  mutate(lo = round(intDown,3),mean = round(int,3),hi = round(intUp,3))
+
+write.csv(intsForTable,file = 'D:/projects/linkedModels/data/out/intsForTable.csv')
+```
+
+```{r table of betas}
+
+load(file= "data/out/allBetas.RData") #loads q
+
+betasForTable <- q %>% 
+  filter(river == 'west brook', species %in% c('bkt','bnt')) %>%
+  arrange(species,betaGG,isYOY,seasonGG,betaGG) %>%
+  select(species,betaGG,isYOY,seasonGG,betaGG,lo,median,hi) %>%
+  mutate(lo = round(lo,3),median = round(median,3),hi = round(hi,3))
+
+write.csv(betasForTable,file = 'D:/projects/linkedModels/data/out/betasForTable.csv')
 ```
@@
   nRivers[['bkt']] <- 4; nRivers[['bnt']] <- 2; nRivers[['ats']] <- 1
-  speciesList <- list('bkt','bnt','ats')
-
-  probs <- c(0.05,0.1,0.5,0.9,0.95)
-  nSpecies <- 3
+  speciesList <- list('bkt','bnt')
+
+  probs <- c(0.025,0.1,0.5,0.9,0.975)
+  nSpecies <- 2
 
@@
 
-    ggplot(q %>% filter(river == 'west brook'), aes(x = median, y = parameterOrd, color = factor(speciesGG), shape = factor(isYOY))) + 
+    ggplot(q %>% filter(river == 'west brook', species != 'ats'), aes(x = median, y = parameterOrd, color = factor(speciesGG), shape = factor(isYOY))) + 
         geom_vline(xintercept = 0,color='black') +
@@
         size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
-        xlim(c(-0.35,0.5)) +
+     #   xlim(c(-0.35,0.5)) +
         xlab("Parameter estimate") + theme(axis.text.y = element_blank(), axis.title.y = element_blank()) +
+        scale_color_grey(start = 0, end = 0.5)  +
         facet_grid(seasonGG~betaGG)
@@
 
-isYOYGG <- 1
+isYOYGG <- 0
 riverGGToPlot <- "West Brook" #"Open Large"
@@
   tmp <- singleDat[[i]] %>% filter(riverGG == riverGGToPlot)
-  ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=speciesGG ) ) +
+  ggSingle[[i]] <<- ggplot( tmp %>% filter(species != 'ats'), aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=speciesGG ) ) +
       geom_line( size = 1.225 ) +
@@
       scale_x_continuous(allLabels[i]) +
+      scale_color_grey(start = 0, end = 0.5)  +
       facet_grid(~seasonGG)
@@
 grid.arrange(grobs=ggSingle, left = "Growth rate (mm/d)")
+# save from rStudio as export, width=900, height=500
+# ggsave(gridPred,'figures/3Spp_WB/predGRYOY1.png', width = 9, height = 7, units='in')
 
@@
 
-isYOYGG <- 0
-riverGGToPlot <- "Open Large" #"West Brook" #
+isYOYGG <- 1
+riverGGToPlot <- "West Brook" #
 outputToPlot <- "meanPredGRSigma"
@@
 
-  tmp <- singleDat[[i]] %>% filter(riverGG == riverGGToPlot)
+  tmp <- singleDat[[i]] %>% filter(riverGG == riverGGToPlot, species != 'ats')
   ggSingle[[i]] <<- ggplot( tmp, aes( eval(as.name(all[i])), eval(as.name(outputToPlot)), color=speciesGG ) ) +
@@
 grid.arrange(grobs=ggSingle, left = "Standard deviation of growth rate (mm/d)")
+
+# 0 = 875,600
+# 1 = 875,500
+
 #ggsave(ggCV, paste0('figures/3Spp_WBpredGRCV_YOY',isYOYGG,'_',riverGGToPlot,'.png'), width = 9, height = 7, units='in')
@@
 # flow*temp interaction plots
-isYOYGG <- 1
+isYOYGG <- 0
 riverGGToPlot <- "West Brook" #"Open Large" #
-outputToPlot <- "meanPredGR" #"meanPredGRSigma"
+outputToPlot <- "meanPredGRSigma" #"meanPredGR" #
 
@@
 
-    ggplot( interact, aes( flow, eval(as.name(outputToPlot)), group=temp_spp, color=speciesGG ) ) +
+    ggplot( interact %>% filter(species != 'ats'), aes( flow, eval(as.name(outputToPlot)), group=temp_spp, linetype=speciesGG ) ) +
       geom_line( aes(alpha = temp + 3), size = 1.225 ) +
@@
       theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
-            axis.title.y = element_blank()
-          #  legend.position="none"
+          #  axis.title.y = element_blank()
+            legend.position="none"
             ) +
@@
     #  ylim(-0.15,0.8) +
-      scale_x_continuous('Flow') +
+      scale_x_continuous('Stream flow') +
+      scale_y_continuous("Standard deviation of growth rate (mm/d)") +
+      #scale_color_manual(values=c('blue','darkgreen'))  +
       facet_grid(~seasonGG)
 
+#yoy0 = 875,350
+#yoy1 = 875,280
 ```
@@
 isYOYGG <- 1
-riverGGToPlot <- "Open Large" #"West Brook" #
+riverGGToPlot <- "West Brook" #
 outputToPlot <- "meanPredGR" #"meanPredGRSigma"
@@
 
-    ggplot( interact, aes( cBKT, eval(as.name(outputToPlot)), group=bnt_spp, color=speciesGG ) ) +
+    ggplot( interact %>% filter(species != 'ats'), aes( cBKT, eval(as.name(outputToPlot)), group=bnt_spp, linetype=speciesGG ) ) +
       geom_line( aes(alpha = cBNT + 3), size = 1.225 ) +
@@
       theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(), 
-            axis.title.y = element_blank()
-          #  legend.position="none"
+           # axis.title.y = element_blank()
+            legend.position="none"
             ) +
@@
       scale_x_continuous('Brook Trout abundance') +
+      scale_y_continuous("Growth rate (mm/d)") +
       facet_grid(~seasonGG)
+
+# for saving from export
+#yoy0 = 875,350
+#yoy1 = 875,275
 
@@
 simData <- list(
-  nReps = 100, #num of mcmc iterations to grab
+  nReps = 100,#100, #num of mcmc iterations to grab
   numInd = 500 , # number of individual to simulate
@@
 
-  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt^2, data = sizeStats %>% filter(occ == (simData$nOcc)))
+  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt*bkt, data = sizeStats %>% filter(occ == (simData$nOcc)))
 
@@
 
-projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
+projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
 save( projOut, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
+
+# if not re-running the sim
+# load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
 
@@
 
-  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
+#  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
 
@@
 # leaving out bkt*bnt, too small
-ggplot(rIAll %>% filter(var<7), aes((occ), value, color = factor(rowname))) +
+ggplot(rIAll, aes((occ), value, color = factor(rowname))) +
   geom_point() +
@@
 dodge <- position_dodge(width=0.9)
-ggplot(rIMeans, aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
-  geom_errorbar(aes(ymin = mean, ymax = up), width = 0.25, position=dodge) +
+ggplot(rIMeans %>% filter(rowname %in% c('bktRI','bntRI')), aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = mean-0.01, ymax = up), width = 0.25, position=dodge) +
   geom_col(position=dodge) +
@@
 
-ggplot(cAll %>% filter(var %in% 2:7), aes((occ), value, color = factor(rowname))) +
-  geom_point() +
+ggplot(cAll %>% filter(var %in% 2:8), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=3) +
   geom_line() +
@@
 # intercept only
-ggplot(cAll %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
+cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
+ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
   geom_point(size=4) +
@@
   scale_x_continuous('Sampling occasion',
-                    breaks = 2:10,
-                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    breaks = 1:10,
+                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
                     ) +
@@
 ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
+
+#####################################
+# no need to start sims with diff sizes by species
+yoyMeans <- 
+cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
+  group_by(species) %>%
+  summarize(meanLen = mean(observedLength,na.rm = TRUE),
+           sdLen = sd(observedLength,na.rm = TRUE))
+
+#   species meanLen sdLen
+#   <chr>     <dbl> <dbl>
+# 1 ats        69.0  5.86
+# 2 bkt        72.7  9.94
+# 3 bnt        72.9  8.73
+#####################################
+
+# projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
+load('D:/projects/linkedModels/data/out/projectionOut.RData')
+stats3Spp <- projOut[[1]]
+spp <- c('bkt','bnt','ats')
+# scenarios
+# Plot subsets of the simulations
+#means for each iter
+stats1 <- rbind(data.frame(stats3Spp[['bkt']][[1]]), 
+                data.frame(stats3Spp[['bnt']][[1]]), 
+                data.frame(stats3Spp[['ats']][[1]])) %>%
+          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[1]])))
+
+#means for each occ
+stats2 <- rbind(data.frame(stats3Spp[['bkt']][[2]]), 
+                data.frame(stats3Spp[['bnt']][[2]]), 
+                data.frame(stats3Spp[['ats']][[2]])) %>%
+          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[2]])))
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0), linetype = 2 )
 

### 2018-10-23 R/analyzeOutputFunctions.R

@@ -719,7 +719,7 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
         facet_grid(isYOY+riverN~season+leftOut)
   print(gg)
 
-  ggg <- ggplot( ddGIn, aes( observedLengthOriginal, estLen, color = factor(leftOut) ) ) +
+  ggg <- ggplot( ddGIn, aes( observedLengthOriginal, estLen ) ) +
   #ggg <- ggplot( ddGIn %>% filter(riverOrdered == 'west brook'), aes( observedLengthOriginal, estLen, color = factor(leftOut) ) ) +
     geom_point( alpha = 0.1 ) +
     geom_abline(intercept = 0, slope = 1) +
@@ -734,13 +734,13 @@ getRMSE_Nimble <- function(d,residLimit = 0.6, ii = 1){
     facet_grid(~leftOut)
   print(ggg)
 
-  ggsave(paste0('figures/obsPred_',speciesGr,'.png'),width = 7,height = 5)
+  ggsave(paste0('figures/3Spp_WB/obsPred_',speciesGr,'.png'),width = 7,height = 5)
 #  ggsave(paste0('figures/obsPred_',speciesGr,'_WB.png'),width = 7,height = 5)
 
   rmse <- ddGIn %>%
     mutate( resid = estLen - observedLengthOriginal,
             isAbovePred = (estLen > observedLengthOriginal) * 1 ) %>%
-    group_by(leftOut) %>%
+    group_by(riverOrdered,leftOut) %>%
     summarise( rmse = sqrt( sum(resid^2,na.rm=T) / sum(!is.na(resid)) ),
                pValue = sum(isAbovePred,na.rm=T) / sum(!is.na(isAbovePred)) )
 

### 2018-10-23 manuscriptAnalysis/CTMax.R

@@ -1,24 +1,15 @@
 #From Evan's Ecology paper'
+library(tidyverse)
+library(ggplot2)
 
 d <- data.frame(temp = seq(1,20.5,0.1))
 
 # bkt first, bnt second
 
+# Perf curve ###############
 tOpt <- c(11.9,13.3)
 cTMax <- c(19.5,19.3)
 sigma <- c(3.7,4.1)
-
-# lInf <- 354
-# k <- 0.0013
-# flowBeta <- 0.098
-# bktBeta <- -0.051
-# bntBeta <- -0.039
-#
-# bktDen <- 7.01
-# bntDen <- 13.00
-# flow <- 0.14
-#
-# gOpt <- k*(lInf-len) + flowBeta*flow + bktBeta*bktDen + bntBeta*bntDen
 
 i <- 1
 d$pT_BKT <- ifelse( d$temp <= tOpt[i],
@@ -33,3 +24,49 @@ d$pT_BNT <- ifelse( d$temp <= tOpt[i],
 )
 
 ggplot(d, aes(temp,pT_BKT)) + geom_line() + geom_line(aes(temp,pT_BNT), color = "brown")
+#################
+
+
+getPerf <- function(tempIn,sppIn=1,ctMaxIn=1,sigmaIn=1){
+
+  perf <- ifelse( tempIn <= tOpt[sppIn],
+                      exp(-((tempIn - tOpt[sppIn])/(2*sigma[sppIn]))^2), #there's an error in the paper
+                      1 - ((tempIn - tOpt[sppIn])/(tOpt[sppIn] - cTMax[sppIn]))^2
+  )
+  return(perf)
+}
+
+## gOpt part
+lInf <- 354
+k <- 0.0013
+flowBeta <- 0.098
+bktBeta <- -0.051
+bntBeta <- -0.039
+
+bktDen <- 7.01
+bntDen <- 13.00
+flow <- 0.14
+
+len <- 100
+
+getGOpt <- function(lenIn,flowIn=flow,bktDenIn=bktDen,bntDenIn=bntDen){
+
+  gOpt <- k*(lInf-lenIn) + flowBeta*flowIn + bktBeta*bktDenIn + bntBeta*bntDenIn
+
+  return(gOpt)
+}
+
[…]

### 2018-10-23 nimble/mainAnalysis_Nimble.R

@@ -27,7 +27,7 @@ drainage <- "west" # ==
 speciesDet <- c("bkt", "bnt","ats") #keep as all three spp
 speciesInDet <- factor(speciesDet, levels = c('bkt','bnt','ats'), ordered = T)
 
-speciesGr <- "ats"
+speciesGr <- "bnt"
 #speciesGr = c("bkt", "bnt","ats")
 speciesInGr <- factor(speciesGr, levels = c('bkt','bnt','ats'), ordered = T)
 
@@ -323,7 +323,7 @@ iter=1
   mcmcProcessed <- process.output(mcmc, DIC=FALSE, params.omit=FALSE)#,params.omit=("lengthExp")) #jagsUI function, DIC = FALSE because it requires 'deviance'
 
   # this saves /figures/obsPred_speciesGr.png
-  obsPred <- getRMSE_Nimble(mcmcProcessed,20)
+  obsPred <- getRMSE_Nimble(mcmcProcessed,20,1)
   obsPred$rmse
   #obsPred$outliers%>% as.data.frame()
 

### 2018-10-24 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added projOut, p/phi summaries

@@
 
+  p %>% group_by(species) %>%
+    summarize(meanP = mean(invlogit(est)),
+              sdP = sd(invlogit(est)))
+
+  p %>% group_by(season) %>%
+    summarize(meanP = mean(invlogit(est)))
+
+  ##################### 
   phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
@@
   ggsave('figures/3Spp_WB/phi.png')
+
+  phi %>% group_by(species) %>%
+    summarize(meanPhi = mean(invlogit(est)),
+              sdPhi = sd(invlogit(est)))
+
+  phi %>% group_by(season) %>%
+    summarize(meanPhi = mean(invlogit(est)))
 
@@
 
-projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
-save( projOut, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
+#projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
+save( stats3Spp, lm, relImp, anov, elapsed, simData, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
 
@@
 # load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
+
+# temporary while projOut is a list
+#stats3Spp <- projOut[[1]]
+#simData <- projOut[[6]]
 
@@
 
-#  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
+  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
 
@@
 # leaving out bkt*bnt, too small
-ggplot(rIAll, aes((occ), value, color = factor(rowname))) +
+ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
   geom_point() +
@@
   scale_x_discrete('Parameter',
-                   labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
   scale_fill_grey() +
@@
 ggsave(paste0('figures/3Spp_WB/relImpOccMean.png'), width = 9, height = 7, units='in')
+
+# mean rel Imp for env vs spp variables
+rIMeans %>%
+  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
+  group_by(rowname,isEnvVar) %>%
+  summarize(meanMean = mean(mean),
+            sumMean = sum(mean),
+            sdMean = sd(mean))
+
+# ratio of env/(env+spp) means
+.247/(.246+.0648) # bkt
+.122/(.122+.159) # bnt
+
+# ratio of env/(env+spp) sums - donT need to do ratio, just use sum for env
+.635/.259 # den-dep bnt/bkt
+.741/.365 # env bkt/bnt
 

### 2018-12-04 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
changed seq of indVars

@@
 simData <- list(
-  nReps = 100,#100, #num of mcmc iterations to grab
+  nReps = 25,#100, #num of mcmc iterations to grab
   numInd = 500 , # number of individual to simulate
@@
   nOccAdult = 7,
-  riverIndex = 1 #Levels: west brook < wb jimmy < wb mitchell < wb obear
+  riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear
+  minSD = -2, #range and step for independent variable values in the sim
+  maxSD = 2, 
+  step = 1
 )
+simData$nOcc <- simData$nOccYOY + simData$nOccAdult
+simData$indVarSeq = c(-1.5, -0.75, 0, 1.5) #seq(simData$minSD,simData$maxSD,simData$step)
 
@@
 
-  simData <- updateSimData(simData)
-  nB <- getNBetas()
+  simData <- updateSimData(simData) # add #season, itersForSim etc data to simData
+  nB <- getNBetas() # get number of betas from mcmc[]
   m <- createMatrices()
 
-  indVars <- getIndVars()
+  indVars <- getIndVars() # get independent variables table, -1.5, 0, 1.5
 
@@
 #projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
-save( stats3Spp, lm, relImp, anov, elapsed, simData, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
+save( stats3Spp, lm, relImp, anov, elapsed, simData, file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
 
@@
 # load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
-
 # temporary while projOut is a list
-#stats3Spp <- projOut[[1]]
-#simData <- projOut[[6]]
+# stats3Spp <- projOut[[1]]
+# relImpData <- projOut[[3]]
+# anovData <- projOut[[4]]
+# simData <- projOut[[6]]
+# spp <- c('bkt','bnt','ats')
+
+# raw sim data figs
+ggplot(stats3Spp[['bkt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0), aes(as.numeric(occ),lenMean)) +
+  #geom_point(aes(color = factor(ats))) +
+  #geom_smooth(aes(color = factor(temp), linetype = factor(flow)))+#(bnt + 2)/4 )) +
+  geom_smooth()+#(bnt + 2)/4 )) +
+  geom_smooth(color = 'green', data = stats3Spp[['bnt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0)) +
+  facet_grid(temp ~ flow)
 
@@
 
-  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
+##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
 
@@
 
-ggplot(cAll %>% filter(var %in% 2:8), aes((occ), value, color = factor(rowname))) +
+ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
   geom_point(size=3) +
@@
 
+# trajectories across indep var values for different combinations. Trying to relate to relImp results
+#temp
+p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(temp))) +
+  geom_line(aes(color = factor(temp))) +
+  geom_point(aes(color = factor(temp))) +
+  facet_wrap(~spp)
+
+#flow
+p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
+  geom_line(aes(color = factor(flow))) +
+  geom_point(aes(color = factor(flow))) +
+  facet_wrap(~spp)
+
+#bkt
+p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bkt))) +
+  geom_line(aes(color = factor(bkt))) +
+  geom_point(aes(color = factor(bkt))) +
+  facet_wrap(~spp)
+
+#bnt
+p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
+  geom_line(aes(color = factor(bnt))) +
+  geom_point(aes(color = factor(bnt))) +
+  facet_wrap(~spp)
+
+#ats
+p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(ats))) +
+  geom_line(aes(color = factor(ats))) +
+  geom_point(aes(color = factor(ats))) +
+  facet_wrap(~spp)
+
+multiplot(p1, p2, p3, p4, p5, cols=2)
+
+#temp*flow
+ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
+  geom_line(aes(color = factor(flow))) +
+  geom_point(aes(color = factor(flow))) +
+  facet_grid(temp~spp)
+
+#bkt*bnt
+ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
+  geom_line(aes(color = factor(bnt))) +
+  geom_point(aes(color = factor(bnt))) +
+  facet_grid(bkt~spp)
+
+# Multiple plot function
+#
+# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
+# - cols:   Number of columns in layout
+# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
+#
+# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
+# then plot 1 will go in the upper left, 2 will go in the upper right, and
+# 3 will go all the way across the bottom.
+#
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+
+  numPlots = length(plots)
+
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                    ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+
+ if (numPlots==1) {
+    print(plots[[1]])
+
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+
 # size=100

### 2018-12-04 R/simulateSizesForParams.R

@@ -109,14 +109,12 @@ createMatrices <- function(){
 #'@export
 
 getIndVars <- function(){
-  minSD <- -1.5
-  maxSD <- 1.5
-  step <- 1.5
-  indVars <- expand.grid( temp = seq(minSD,maxSD,step),
-                          flow = seq(minSD,maxSD,step),
-                          bkt = seq(minSD,maxSD,step),
-                          bnt = seq(minSD,maxSD,step),
-                          ats = seq(minSD,maxSD,step)
+
+  indVars <- expand.grid( temp = simData$indVarSeq,
+                          flow = simData$indVarSeq,
+                          bkt =  simData$indVarSeq,
+                          bnt =  simData$indVarSeq,
+                          ats =  simData$indVarSeq
   )
   indVars$rowNum <- 1:nrow(indVars)
   return(indVars)
@@ -152,7 +150,7 @@ projectSizes <- function(m,simData,testRow){
           m$betaMatBNT[i,2,rows,cols] * d$bnt * d$bkt +
           m$betaMatATS[i,1,rows,cols] * d$ats +
           m$indREMat[i,rows,cols]
-
+        #temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt*bkt
         sigma <- exp(
           m$sigmaIntMat[i,rows,cols] +
             m$sigmaBetaMat[i,1,rows,cols] * d$temp +

### 2018-12-11 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
sens analysis on gr instead of size

@@
 simData <- list(
-  nReps = 25,#100, #num of mcmc iterations to grab
+  nReps = 100, #num of mcmc iterations to grab
   numInd = 500 , # number of individual to simulate
@@
   riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear
-  minSD = -2, #range and step for independent variable values in the sim
-  maxSD = 2, 
-  step = 1
+  minSD = -1.5, #range and step for independent variable values in the sim
+  maxSD = 1.5, 
+  step = 1.5
 )
 simData$nOcc <- simData$nOccYOY + simData$nOccAdult
-simData$indVarSeq = c(-1.5, -0.75, 0, 1.5) #seq(simData$minSD,simData$maxSD,simData$step)
-
-stats3Spp <- anov <- elapsed <- lm <- relImp <- list()
-spp <- c('bkt','bnt','ats')
+simData$indVarSeq = seq(simData$minSD,simData$maxSD,simData$step)
+
+stats3Spp <- grStats3Spp <- anov <- elapsed <- lm <- relImp <- list()
+spp <- c('bkt','bnt') #,'ats')
 
@@
   startTime <- Sys.time()
-  sizeStats <- sizeStats2 <- NULL
+  sizeStats <- sizeStats2 <- grStats <- grStats2 <- NULL
   #loop over conditions
   for(testRow in indVars$rowNum){
-    sizeMat <- projectSizes(m,simData,testRow)
+    project <- projectSizes(m,simData,testRow)
+
+    sizeMat <- project$sizeMat
+    grMat <- project$grMat
 
@@
     sizeStats2 <- rbind(sizeStats2,sizeStats1[[2]]) #means by occ of means over individuals (grouped by occ)
+
+    grStats1 <- summarizeGRs(grMat,testRow)
+    grStats <- rbind(grStats,grStats1[[1]]) #means over individuals (grouped by iter, occ)
+    grStats2 <- rbind(grStats2,grStats1[[2]]) #means by occ of means over individuals (grouped by occ)
   }
@@
   stats3Spp[[speciesForProj]] <- list( sizeStats,sizeStats2 )
-
-  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt*bkt, data = sizeStats %>% filter(occ == (simData$nOcc)))
-
-  relImp[[speciesForProj]] <- calc.relimp(lm[[speciesForProj]], type = c("lmg"), rela = TRUE)
-
-  anov[[speciesForProj]] <- anova( lm[[speciesForProj]] )
+  grStats3Spp[[speciesForProj]] <- list( grStats,grStats2 )
+
+  # lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt*bkt, data = sizeStats %>% filter(occ == (simData$nOcc)))
+  # 
+  # relImp[[speciesForProj]] <- calc.relimp(lm[[speciesForProj]], type = c("lmg"), rela = TRUE)
+  #   
+  # anov[[speciesForProj]] <- anova( lm[[speciesForProj]] )
 
@@
 #projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
-save( stats3Spp, lm, relImp, anov, elapsed, simData, file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
+save( stats3Spp, grStats3Spp, elapsed, simData, file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
 
@@
 # load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
-# temporary while projOut is a list
-# stats3Spp <- projOut[[1]]
-# relImpData <- projOut[[3]]
-# anovData <- projOut[[4]]
-# simData <- projOut[[6]]
+# load( file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
 # spp <- c('bkt','bnt','ats')
 
-# raw sim data figs
+# raw sim data figs - size
 ggplot(stats3Spp[['bkt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0), aes(as.numeric(occ),lenMean)) +
-  #geom_point(aes(color = factor(ats))) +
+  geom_jitter(aes(color = factor(ats))) +
   #geom_smooth(aes(color = factor(temp), linetype = factor(flow)))+#(bnt + 2)/4 )) +
@@
 
-# make figures of relative importance for each sampling occasion
-rIAll <- cAll <- NULL
-for( occSelected in 2:simData$nOcc){
-  print(occSelected)
-  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
-
-  for(spp1 in spp){
-
-      lmAll[[spp1]] <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected))
-
-      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
-
-      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
-  }
-
-  # make bar chart of relative importance of each variable for each spp
-  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
-              data.frame(bntRI = relImpAll[['bnt']]$lmg), 
-              data.frame(atsRI = relImpAll[['ats']]$lmg)) %>%
+########################
+# raw sim data figs - gr
+ggplot(grStats3Spp[['bkt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0), aes(as.numeric(occ),grMean)) +
+  geom_jitter(aes(color = factor(ats)), width = 0.2, size = 0.5) +
+  #geom_smooth(aes(color = factor(temp), linetype = factor(flow)))+#(bnt + 2)/4 )) +
+  #geom_smooth()+#(bnt + 2)/4 )) +
+  geom_jitter(color = 'darkblue', width = 0.1, size = 0.5, data = grStats3Spp[['bnt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0)) +
+  facet_grid(temp ~ flow)
+
+```
+
+```{r RI across occ - use this for paper GROWTH RATE}
+
+# relative proportion stats with occ in the lm 
+grStats3Spp[['bkt']][[1]]$season <- as.factor(c(3,4,1,2,3,4,1,2,3,4))
+grStats3Spp[['bkt']][[1]]$temp2 <- grStats3Spp[['bkt']][[1]]$temp^2
+grStats3Spp[['bkt']][[1]]$flow2 <- grStats3Spp[['bkt']][[1]]$flow^2
+
+ageForRI <-  'yoy' #'yoy' or 'adult'
+occs <- if (ageForRI == 'yoy') 1:2 else 3:10
+indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
+indepVars <- c('temp', 'flow', 'temp:flow', 'bkt', 'bnt', 'ats', 'bkt:bnt')
+rIBKTBNT <- NULL
+# loop over occs
+for(rep in 1:simData$nReps){
+
+  print(rep)
+
+  datOccBKT <- grStats3Spp[['bkt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBKT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKT) 
+  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)
+
+  datOccBNT <- grStats3Spp[['bnt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBNT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNT)
+  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)
+
+  lmgBKT <- relImpAllBKT$lmg[(names(relImpAllBKT$lmg) %in% indepVars)]
+  rBKT <- lmgBKT / sum(lmgBKT)
+
+  lmgBNT <- relImpAllBNT$lmg[(names(relImpAllBNT$lmg) %in% indepVars)]
+  rBNT <- lmgBNT / sum(lmgBNT)
+
+  rIBKTBNT <- rbind(rIBKTBNT, data.frame(cbind(rBKT,rBNT)) %>% 
                       rownames_to_column() %>% 
-        gather(key=rowname) %>% 
-        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
-               occ = occSelected,
-               season = simData$seasons[occSelected])
-
-  rIAll <- rbind(rIAll,rI)
-
-  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
-    geom_col(position='dodge') +
-    scale_x_discrete('Parameter',
-                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
-    scale_fill_grey() +
-    scale_y_continuous('Relative proportion of variance explained') +
-    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
-    theme_publication() +
-    theme( legend.position = 'none')
-
-##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
-
-  # coefficients
-  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
-                 data.frame(bntC = coefsAll[['bnt']]), 
-                 data.frame(atsC = coefsAll[['ats']])) %>%
-        rownames_to_column() %>% 
-        gather(key=rowname) %>% 
-        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
-               occ = occSelected,
-               season = simData$seasons[occSelected])
-
-  cAll <- rbind(cAll,coefs)
-}
-
-######################################################
-# relImp over occasions for each spp and parameter
-labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
-
-# leaving out bkt*bnt, too small
-ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 2:10,
-                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Relative proportion of variance explained') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
-  facet_wrap(~ var, labeller=labeller(var = labels))
-
-ggsave(paste0('figures/3Spp_WB/relImpOccAll.png'), width = 11, height = 9, units='in')
-
-rIMeans <- rIAll %>%
-  group_by(rowname,var) %>%
-  summarize( mean = mean(value),
-             sd = sd(value),
-             stderr = sd(value)/sqrt(length(value))) %>%
-  mutate( up = mean + stderr )
+                      gather(key = rowname) %>% 
+                      mutate(var = rep(1:length(indepVars),2),
+                             varText = rep(names(rBKT),2),
+                             iter = rep)
+                    )
+}
+
+rIBKTBNTMeans <- rIBKTBNT %>%
+  group_by(rowname, var) %>%
+  summarise(rIMean = mean(value),
+            rISd = sd(value),
+            rIUpperCI = quantile(value, 0.95))
 
 dodge <- position_dodge(width=0.9)
-ggplot(rIMeans %>% filter(rowname %in% c('bktRI','bntRI')), aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
-  geom_errorbar(aes(ymin = mean-0.01, ymax = up), width = 0.25, position=dodge) +
+ggplot(rIBKTBNTMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
   geom_col(position=dodge) +
@@
   theme_publication() +
+  geom_hline(yintercept = 0) +
   theme( legend.position = 'none')
 
-ggsave(paste0('figures/3Spp_WB/relImpOccMean.png'), width = 9, height = 7, units='in')
-
-# mean rel Imp for env vs spp variables
-rIMeans %>%
+ggsave(paste0('figures/3Spp_WB/relImpOccMeanModWOcc_GR',simData$nReps,'_',ageForRI,'.png'), width = 9, height = 7, units='in')
+
+# uses 42 G - does not run
+#lmAll <- lm( lenMean ~ (temp + flow +  temp^2 + flow^2 + bkt + bnt + ats )*occ + temp * flow + bnt * bkt, data = stats3Spp[['bkt']][[1]] %>%               filter(iter %in% 1) )
+
+rIBKTBNT %>%
   mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
   group_by(rowname,isEnvVar) %>%
-  summarize(meanMean = mean(mean),
-            sumMean = sum(mean),
-            sdMean = sd(mean))
+  summarize(meanMean = mean(value),
+            sumMean = sum(value),
+            sdMean = sd(value))
+# 25 reps
+#   rowname isEnvVar meanMean sumMean sdMean
+#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
+# 1 rBKT           0   0.0664   0.265  0.105
+# 2 rBKT           1   0.245    0.735  0.249
+# 3 rBNT           0   0.147    0.588  0.104
+# 4 rBNT           1   0.137    0.412  0.158
+
+# 100 reps
+#   rowname isEnvVar meanMean sumMean sdMean
+#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
+# 1 rBKT           0   0.0676    27.0 0.0914
+# 2 rBKT           1   0.243     73.0 0.200 
+# 3 rBNT           0   0.146     58.2 0.0922
+# 4 rBNT           1   0.139     41.8 0.131
 
 # ratio of env/(env+spp) means
-.247/(.246+.0648) # bkt
-.122/(.122+.159) # bnt
-
-# ratio of env/(env+spp) sums - donT need to do ratio, just use sum for env
-.635/.259 # den-dep bnt/bkt
-.741/.365 # env bkt/bnt
-
-#######################
-# coefs
-labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
-
-ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
-  geom_point(size=3) +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 2:10,
-                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Coefficients') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
-  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
-
-ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
-
-# intercept only
-cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
-ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
-  geom_point(size=4) +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 1:10,
-                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Intercept') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
-
-ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
-
-#####################################
-# no need to start sims with diff sizes by species
-yoyMeans <- 
-cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
-  group_by(species) %>%
-  summarize(meanLen = mean(observedLength,na.rm = TRUE),
-           sdLen = sd(observedLength,na.rm = TRUE))
-
-#   species meanLen sdLen
-#   <chr>     <dbl> <dbl>
-# 1 ats        69.0  5.86
-# 2 bkt        72.7  9.94
-# 3 bnt        72.9  8.73
-#####################################
+.243/(.243 + .0676) # bkt 0.7823567
+.139/(.139 + .146) # bnt 0.4877193
+
+.782/.488 # 1.60
+##############################################################
+############################################################
 
 # projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
-load('D:/projects/linkedModels/data/out/projectionOut.RData')
-stats3Spp <- projOut[[1]]
-spp <- c('bkt','bnt','ats')
+load(paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
+
+#spp <- c('bkt','bnt','ats')
 # scenarios
@@
 #means for each iter
-stats1 <- rbind(data.frame(stats3Spp[['bkt']][[1]]), 
-                data.frame(stats3Spp[['bnt']][[1]]), 
-                data.frame(stats3Spp[['ats']][[1]])) %>%
-          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[1]])))
+stats1 <- rbind(data.frame(grStats3Spp[['bkt']][[1]]), 
+                data.frame(grStats3Spp[['bnt']][[1]]), 
+                data.frame(grStats3Spp[['ats']][[1]])) %>%
+          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[1]])))
 
 #means for each occ
-stats2 <- rbind(data.frame(stats3Spp[['bkt']][[2]]), 
-                data.frame(stats3Spp[['bnt']][[2]]), 
-                data.frame(stats3Spp[['ats']][[2]])) %>%
-          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[2]])))
-
-ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+stats2 <- rbind(data.frame(grStats3Spp[['bkt']][[2]]), 
+                data.frame(grStats3Spp[['bnt']][[2]]), 
+                data.frame(grStats3Spp[['ats']][[2]])) %>%
+          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[2]])))
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
   geom_point(aes(color = spp) ) +
@@
 
-ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
   geom_point(aes(color = spp) ) +
@@
 #temp
-p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(temp))) +
+p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(temp))) +
   geom_line(aes(color = factor(temp))) +
@@
 #flow
-p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
+p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
   geom_line(aes(color = factor(flow))) +
@@
 #bkt
-p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bkt))) +
+p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bkt))) +
   geom_line(aes(color = factor(bkt))) +
@@
 #bnt
-p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
+p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
   geom_line(aes(color = factor(bnt))) +
@@
 #ats
-p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(ats))) +
+p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(ats))) +
   geom_line(aes(color = factor(ats))) +
@@
 
-multiplot(p1, p2, p3, p4, p5, cols=2)
+multiplot(p1, p2, p3, p4, p5, cols=2) # multiplot function is below
 
 #temp*flow
-ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
+ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
   geom_line(aes(color = factor(flow))) +
@@
 #bkt*bnt
-ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
+ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
   geom_line(aes(color = factor(bnt))) +
@@
 
+```{r RI by occ - not used for paper GROWTH}
+
+# make figures of relative importance for each sampling occasion
+rIAll <- cAll <- NULL
+for( occSelected in 1:(simData$nOcc - 1)){
+  print(occSelected)
+  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
+
+  for(spp1 in spp){
+
+      lmAll[[spp1]] <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = grStats3Spp[[spp1]][[1]] %>% filter(occ == occSelected, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals))
+  #stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected)
+
+      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
+
+      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
+  }
+
+  # make bar chart of relative importance of each variable for each spp
+  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
+              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  rIAll <- rbind(rIAll,rI)
+
+  rIAll$age <- ifelse(rIAll$occ %in% 1:2, 0, ifelse(rIAll$occ %in% 3:6, 1, 2))
+
+  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI'), ordered = TRUE))) +
+    geom_col(position='dodge') +
+    scale_x_discrete('Parameter',
+                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+    scale_fill_grey() +
+    scale_y_continuous('Relative proportion of variance explained') +
+    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
+    theme_publication() +
+    theme( legend.position = 'none')
+
+##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
+
+  # coefficients
+  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
+                 data.frame(bntC = coefsAll[['bnt']])) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  cAll <- rbind(cAll,coefs)
+}
+
+######################################################
+# relImp over occasions for each spp and parameter
+labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
+
+ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
+  geom_point() +
+  geom_line() +
+  geom_vline(xintercept = 2.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 1:9,
+                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn')
+                    ) +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labels))
+
+ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR.png'), width = 11, height = 9, units='in')
+
+rIAllMinus <- rIAll %>% mutate(value2 = ifelse(rowname == 'bktRI',value * -1, value))
+labelsSeason <- c('1'='Autumn','2'='Winter','3'='Spring','4'='Summer','5'='Autumn','6'='Winter','7'='Spring','8'='Summer','9'='Autumn')
+labelsSeason2 <- c('1'='Spring','2'='Summer','3'='Autumn','4'='Winter')
+
+ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
+  geom_col() +
+  coord_flip() +
+  scale_x_reverse('Variable', 
+                     breaks = 1:7,
+                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
+  scale_y_continuous('Relative proportion of variance explained',
+                     breaks = c(-1.0, -0.5, 0.0, 0.5),
+                     labels = c('1.0', '0.5', '0.0', '0.5')) +
+  theme_publication() +
+  scale_fill_grey(start = 0.15, end = 0.75) +
+  facet_grid(season ~ age, labeller=labeller(season = labelsSeason2))
+
+ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR_HorizBars.png'), width = 11, height = 9, units='in')
+
+#######################
+# coefs
+labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
+
+ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=3) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Coefficients') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
+
+ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
+
+# intercept only
+cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
+ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=4) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 1:10,
+                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Intercept') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
+
+ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
+
+#####################################
+# no need to start sims with diff sizes by species
+yoyMeans <- 
+cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
+  group_by(species) %>%
+  summarize(meanLen = mean(observedLength,na.rm = TRUE),
+           sdLen = sd(observedLength,na.rm = TRUE))
+
+#   species meanLen sdLen
+#   <chr>     <dbl> <dbl>
+# 1 ats        69.0  5.86
+# 2 bkt        72.7  9.94
+# 3 bnt        72.9  8.73
+#####################################
+
+```
+
+```{r RI by occ - not used for paper SIZE}
+
+# make figures of relative importance for each sampling occasion
+rIAll <- cAll <- NULL
+for( occSelected in 2:simData$nOcc){
+  print(occSelected)
+  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
+
+  for(spp1 in spp){
+
+      lmAll[[spp1]] <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected))
+
+      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
+
+      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
+  }
+
+  # make bar chart of relative importance of each variable for each spp
+  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
+              data.frame(bntRI = relImpAll[['bnt']]$lmg), 
+              data.frame(atsRI = relImpAll[['ats']]$lmg)) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  rIAll <- rbind(rIAll,rI)
+
+  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
+    geom_col(position='dodge') +
+    scale_x_discrete('Parameter',
+                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+    scale_fill_grey() +
+    scale_y_continuous('Relative proportion of variance explained') +
+    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
+    theme_publication() +
+    theme( legend.position = 'none')
+
+##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
+
+  # coefficients
+  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
+                 data.frame(bntC = coefsAll[['bnt']]), 
+                 data.frame(atsC = coefsAll[['ats']])) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  cAll <- rbind(cAll,coefs)
+}
+
+######################################################
+# relImp over occasions for each spp and parameter
+labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
+
+# leaving out bkt*bnt, too small
+ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
+  geom_point() +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labels))
+
+ggsave(paste0('figures/3Spp_WB/relImpOccAll.png'), width = 11, height = 9, units='in')
+
+rIMeans <- rIAll %>%
+  group_by(rowname,var) %>%
+  summarize( mean = mean(value),
+             sd = sd(value),
+             stderr = sd(value)/sqrt(length(value))) %>%
+  mutate( up = mean + stderr )
+
+dodge <- position_dodge(width=0.9)
+ggplot(rIMeans %>% filter(rowname %in% c('bktRI','bntRI')), aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = mean-0.01, ymax = up), width = 0.25, position=dodge) +
+  geom_col(position=dodge) +
+  scale_x_discrete('Parameter',
+                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+  scale_fill_grey() +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme( legend.position = 'none')
+
+ggsave(paste0('figures/3Spp_WB/relImpOccMean.png'), width = 9, height = 7, units='in')
+
+# mean rel Imp for env vs spp variables
+rIMeans %>%
+  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
+  group_by(rowname,isEnvVar) %>%
+  summarize(meanMean = mean(mean),
+            sumMean = sum(mean),
+            sdMean = sd(mean))
+
+# ratio of env/(env+spp) means
+.247/(.246+.0648) # bkt
+.122/(.122+.159) # bnt
+
+# ratio of env/(env+spp) sums - donT need to do ratio, just use sum for env
+.635/.259 # den-dep bnt/bkt
+.741/.365 # env bkt/bnt
+
+#######################
+# coefs
+labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
+
+ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=3) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Coefficients') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
+
+ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
+
+# intercept only
+cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
+ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=4) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 1:10,
+                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Intercept') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
+
+ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
+
+#####################################
+# no need to start sims with diff sizes by species
+yoyMeans <- 
+cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
+  group_by(species) %>%
+  summarize(meanLen = mean(observedLength,na.rm = TRUE),
+           sdLen = sd(observedLength,na.rm = TRUE))
+
+#   species meanLen sdLen
+#   <chr>     <dbl> <dbl>
+# 1 ats        69.0  5.86
+# 2 bkt        72.7  9.94
+# 3 bnt        72.9  8.73
+#####################################
+
+```
+
 ```{r tables}
@@
 round(mcmc$summary$all.chains[startsWith(attributes(mcmc$summary$all.chains)$dimnames[[1]], "grBeta["),],2)
+
+```
+
+```{r RI across occ - use this for paper SIZE}
+
+# relative proportion stats with occ in the lm 
+stats3Spp[['bkt']][[1]]$season <- as.factor(c(3,4,1,2,3,4,1,2,3,4))
+stats3Spp[['bkt']][[1]]$temp2 <- stats3Spp[['bkt']][[1]]$temp^2
+stats3Spp[['bkt']][[1]]$flow2 <- stats3Spp[['bkt']][[1]]$flow^2
+
+ageForRI <-  'adult' #'yoy' or 'adult'
+occs <- if (ageForRI == 'yoy') 1:3 else 4:10
+indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
+rIBKTBNT <- NULL
+# loop over occs
+for(rep in 1:simData$nReps){
+
+  print(rep)
+
+  datOccBKT <- stats3Spp[['bkt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBKT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKT) 
+  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)
+
+  datOccBNT <- stats3Spp[['bnt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBNT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNT)
+  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)
+
+  rBKT <- relImpAllBKT$lmg[2:8] / sum(relImpAllBKT$lmg[2:8]) 
+  rBNT <- relImpAllBNT$lmg[2:8] / sum(relImpAllBNT$lmg[2:8])
+
+  rIBKTBNT <- rbind(rIBKTBNT, data.frame(cbind(rBKT,rBNT)) %>% 
+                      rownames_to_column() %>% 
+                      gather(key = rowname) %>% 
+                      mutate(var = rep(1:7,2),
+                             varText = rep(names(rBKT),2),
+                             iter = rep)
+                    )
+
+}
+
+rIBKTBNTMeans <- rIBKTBNT %>%
+  group_by(rowname, var) %>%
+  summarise(rIMean = mean(value),
+            rISd = sd(value),
+            rIUpperCI = quantile(value, 0.95))
+
+dodge <- position_dodge(width=0.9)
+ggplot(rIBKTBNTMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
+  geom_col(position=dodge) +
+  scale_x_discrete('Parameter',
+                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+  scale_fill_grey() +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  geom_hline(yintercept = 0) +
+  theme( legend.position = 'none')
+
+ggsave(paste0('figures/3Spp_WB/relImpOccMeanModWOcc_Size',simData$nReps,'_',ageForRI,'.png'), width = 9, height = 7, units='in')
+
+# uses 42 G - does not run
+#lmAll <- lm( lenMean ~ (temp + flow +  temp^2 + flow^2 + bkt + bnt + ats )*occ + temp * flow + bnt * bkt, data = stats3Spp[['bkt']][[1]] %>%               filter(iter %in% 1) )
+
+rIBKTBNT %>%
+  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
+  group_by(rowname,isEnvVar) %>%
+  summarize(meanMean = mean(value),
+            sumMean = sum(value),
+            sdMean = sd(value))
+# 25 reps
+#   rowname isEnvVar meanMean sumMean sdMean
+#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
+# 1 rBKT           0   0.0664   0.265  0.105
+# 2 rBKT           1   0.245    0.735  0.249
+# 3 rBNT           0   0.147    0.588  0.104
+# 4 rBNT           1   0.137    0.412  0.158
+
+# 100 reps
+#   rowname isEnvVar meanMean sumMean sdMean
+#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
+# 1 rBKT           0   0.0676    27.0 0.0914
+# 2 rBKT           1   0.243     73.0 0.200 
+# 3 rBNT           0   0.146     58.2 0.0922
+# 4 rBNT           1   0.139     41.8 0.131
+
+# ratio of env/(env+spp) means
+.243/(.243 + .0676) # bkt 0.7823567
+.139/(.139 + .146) # bnt 0.4877193
+
+.782/.488 # 1.60
+##############################################################
+############################################################
+
+# projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
+load(paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
+
+spp <- c('bkt','bnt','ats')
+# scenarios
+# Plot subsets of the simulations
+#means for each iter
+stats1 <- rbind(data.frame(stats3Spp[['bkt']][[1]]), 
+                data.frame(stats3Spp[['bnt']][[1]]), 
+                data.frame(stats3Spp[['ats']][[1]])) %>%
+          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[1]])))
+
+#means for each occ
+stats2 <- rbind(data.frame(stats3Spp[['bkt']][[2]]), 
+                data.frame(stats3Spp[['bnt']][[2]]), 
+                data.frame(stats3Spp[['ats']][[2]])) %>%
+          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[2]])))
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0), linetype = 2 )
+
+# trajectories across indep var values for different combinations. Trying to relate to relImp results
+#temp
+p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(temp))) +
+  geom_line(aes(color = factor(temp))) +
+  geom_point(aes(color = factor(temp))) +
+  facet_wrap(~spp)
+
+#flow
+p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
+  geom_line(aes(color = factor(flow))) +
+  geom_point(aes(color = factor(flow))) +
+  facet_wrap(~spp)
+
+#bkt
+p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bkt))) +
+  geom_line(aes(color = factor(bkt))) +
+  geom_point(aes(color = factor(bkt))) +
+  facet_wrap(~spp)
+
+#bnt
+p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
+  geom_line(aes(color = factor(bnt))) +
+  geom_point(aes(color = factor(bnt))) +
+  facet_wrap(~spp)
+
+#ats
+p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(ats))) +
+  geom_line(aes(color = factor(ats))) +
+  geom_point(aes(color = factor(ats))) +
+  facet_wrap(~spp)
+
+multiplot(p1, p2, p3, p4, p5, cols=2) # multiplot function is below
+
+#temp*flow
+ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
+  geom_line(aes(color = factor(flow))) +
+  geom_point(aes(color = factor(flow))) +
+  facet_grid(temp~spp)
+
+#bkt*bnt
+ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
+  geom_line(aes(color = factor(bnt))) +
+  geom_point(aes(color = factor(bnt))) +
+  facet_grid(bkt~spp)
+
+# Multiple plot function
+#
+# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
+# - cols:   Number of columns in layout
+# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
+#
+# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
+# then plot 1 will go in the upper left, 2 will go in the upper right, and
+# 3 will go all the way across the bottom.
+#
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+
+  numPlots = length(plots)
+
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                    ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+
+ if (numPlots==1) {
+    print(plots[[1]])
+
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+
+# size=100
+# gr=10
+# sd=1
+# mean(rnorm(10000,size+gr,sd))
+# mean(size+rnorm(10000,gr,sd))
 

### 2018-12-11 R/simulateSizesForParams.R

@@ -48,8 +48,8 @@ getNBetas <- function(){
 #'
 createMatrices <- function(){
 
-  sizeMat <- intMat <- sigmaIntMat <- isYOYMat <- array(NA, c(simData$nReps, simData$numInd, simData$nOcc))
-  seasonMat <- sampIntMat <- indREMat <-          array(NA, c(simData$nReps, simData$numInd, simData$nOcc))
+  sizeMat <- intMat <- sigmaIntMat <- isYOYMat <-  array(NA, c(simData$nReps, simData$numInd, simData$nOcc))
+  seasonMat <- sampIntMat <- indREMat <-  grMat <- array(NA, c(simData$nReps, simData$numInd, simData$nOcc))
   betaMat <- sigmaBetaMat <- array(NA, c(simData$nReps, nB$nBetas, simData$numInd, simData$nOcc))
   betaMatBNT <- array(NA, c(simData$nReps, nB$nBetas, simData$numInd, simData$nOcc))
   betaMatATS <- array(NA, c(simData$nReps, nB$nBetas, simData$numInd, simData$nOcc))
@@ -97,7 +97,7 @@ createMatrices <- function(){
     }
   }
 
-  return(list(isYOYMat=isYOYMat,seasonMat=seasonMat,sampIntMat=sampIntMat,sizeMat=sizeMat,indREMat=indREMat,
+  return(list(isYOYMat=isYOYMat,seasonMat=seasonMat,sampIntMat=sampIntMat,sizeMat=sizeMat,grmat=grMat,indREMat=indREMat,
               intMat=intMat,sigmaIntMat=sigmaIntMat,betaMat=betaMat,
               betaMatBNT=betaMatBNT,betaMatATS=betaMatATS,sigmaBetaMat=sigmaBetaMat))
 }
@@ -159,11 +159,11 @@ projectSizes <- function(m,simData,testRow){
         )
         # print(c(sigma,exp(sigma)))
         m$sizeMat[i,rows,cols + 1] <-  rnorm(1, m$sizeMat[i,rows,cols] + gr * m$sampIntMat[i,rows,cols], sigma)
-
+        m$grMat[i,rows,cols] <- gr
       }
     }
   }
-  return(m$sizeMat)
+  return( list(sizeMat = m$sizeMat, grMat = m$grMat) )
 
 }
 

### 2018-12-12 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added graphs for sens analysis

@@
 
-```{r RI across occ - use this for paper GROWTH RATE}
+```{r RI across all - use this for paper GROWTH RATE}
 
@@
 
+indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
+indepVars <- c('temp', 'flow', 'temp:flow', 'bkt', 'bnt', 'ats', 'bkt:bnt')
+rIBKTBNTAll <- NULL
+# loop over occs
+for(rep in 1:simData$nReps){
+
+  print(rep)
+
+  datOccBKTAll <- grStats3Spp[['bkt']][[1]] %>% filter(iter == rep, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBKT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKTAll) 
+  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)
+
+  datOccBNTAll <- grStats3Spp[['bnt']][[1]] %>% filter(iter == rep, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBNT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNTAll)
+  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)
+
+  lmgBKT <- relImpAllBKT$lmg[(names(relImpAllBKT$lmg) %in% indepVars)]
+  rBKT <- lmgBKT / sum(lmgBKT)
+
+  lmgBNT <- relImpAllBNT$lmg[(names(relImpAllBNT$lmg) %in% indepVars)]
+  rBNT <- lmgBNT / sum(lmgBNT)
+
+  rIBKTBNTAll <- rbind(rIBKTBNTAll, data.frame(cbind(rBKT,rBNT)) %>% 
+                      rownames_to_column() %>% 
+                      gather(key = rowname) %>% 
+                      mutate(var = rep(1:length(indepVars),2),
+                             varText = rep(names(rBKT),2),
+                             iter = rep)
+                    )
+}
+
+rIBKTBNTAllMeans <- rIBKTBNTAll %>%
+  group_by(rowname, var) %>%
+  summarise(rIMean = mean(value),
+            rISd = sd(value),
+            rIUpperCI = quantile(value, 0.95))
+
+dodge <- position_dodge(width=0.9)
+ggplot(rIBKTBNTAllMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
+  geom_col(position=dodge) +
+  scale_x_discrete('Parameter',
+                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+  scale_fill_grey() +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  geom_hline(yintercept = 0) +
+  theme( legend.position = 'none')
+
+ggsave(paste0('figures/3Spp_WB/relImpOccMeanModAll_GR_N',simData$nReps,'.png'), width = 9, height = 7, units='in')
+
+# for MS
+rIBKTBNTAllMeans
+#    rowname   var  rIMean    rISd rIUpperCI
+#    <chr>   <int>   <dbl>   <dbl>     <dbl>
+#  1 rBKT        1 0.132   0.0251     0.170 
+#  2 rBKT        2 0.670   0.0369     0.731 
+#  3 rBKT        3 0.0116  0.0118     0.0330
+#  4 rBKT        4 0.0346  0.0256     0.0703
+#  5 rBKT        5 0.0951  0.0284     0.140 
+#  6 rBKT        6 0.0441  0.0263     0.0919
+#  7 rBKT        7 0.0121  0.0155     0.0410
+#  8 rBNT        1 0.106   0.0212     0.141 
+#  9 rBNT        2 0.568   0.0364     0.623 
+# 10 rBNT        3 0.0885  0.0223     0.124 
+# 11 rBNT        4 0.00518 0.00556    0.0163
+# 12 rBNT        5 0.122   0.0285     0.169 
+# 13 rBNT        6 0.0314  0.0176     0.0624
+# 14 rBNT        7 0.0782  0.0270     0.122
+
+rIBKTBNTAll %>%
+  mutate(isEnvVar = ifelse(varText %in% c('temp','flow','temp:flow'), 1,0)) %>%
+  group_by(rowname,isEnvVar) %>%
+  summarize(meanMean = mean(value),
+            sumMean = sum(value),
+            sdMean = sd(value))
+
+#   rowname isEnvVar meanMean sumMean sdMean
+#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
+# 1 rBKT           0   0.0383    15.3 0.0402
+# 2 rBKT           1   0.282     84.7 0.279 
+# 3 rBNT           0   0.0736    29.4 0.0484
+# 4 rBNT           1   0.235     70.6 0.239
+
+#bkt
+.282/(.282+.038) # 0.88125
+#bnt
+.235/(.235+.074) # 0.7605178
+.881/.76 # 1.159211
+```
+
+```{r RI across yoy/adults - use this for paper GROWTH RATE}
+
+# relative proportion stats with occ in the lm 
+grStats3Spp[['bkt']][[1]]$season <- as.factor(c(3,4,1,2,3,4,1,2,3,4))
+grStats3Spp[['bkt']][[1]]$temp2 <- grStats3Spp[['bkt']][[1]]$temp^2
+grStats3Spp[['bkt']][[1]]$flow2 <- grStats3Spp[['bkt']][[1]]$flow^2
+
 ageForRI <-  'yoy' #'yoy' or 'adult'
-occs <- if (ageForRI == 'yoy') 1:2 else 3:10
+occs <- if (ageForRI == 'yoy') 1:3 else 4:10
 indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
@@
 ggsave(paste0('figures/3Spp_WB/relImpOccMeanModWOcc_GR',simData$nReps,'_',ageForRI,'.png'), width = 9, height = 7, units='in')
+
+#    rowname   var  rIMean    rISd rIUpperCI
+#    <chr>   <int>   <dbl>   <dbl>     <dbl>
+#  1 rBKT        1 0.516   0.0639     0.619 
+#  2 rBKT        2 0.123   0.0332     0.175 
+#  3 rBKT        3 0.0209  0.0222     0.0568
+#  4 rBKT        4 0.0579  0.0307     0.100 
+#  5 rBKT        5 0.193   0.0487     0.273 
+#  6 rBKT        6 0.0539  0.0374     0.126 
+#  7 rBKT        7 0.0362  0.0303     0.0889
+#  8 rBNT        1 0.154   0.0566     0.253 
+#  9 rBNT        2 0.0106  0.00999    0.0281
+# 10 rBNT        3 0.140   0.0479     0.208 
+# 11 rBNT        4 0.00421 0.00467    0.0135
+# 12 rBNT        5 0.463   0.0780     0.598 
+# 13 rBNT        6 0.173   0.0676     0.294 
+# 14 rBNT        7 0.0547  0.0340     0.121
+
+# get isEnvVar sens for yoy and adults - need to rerun the above code for each age
+rIBKTBNT %>%
+  mutate(isEnvVar = ifelse(varText %in% c('temp','flow','temp:flow'), 1,0)) %>%
+  group_by(rowname,isEnvVar) %>%
+  summarize(meanMean = mean(value),
+            sumMean = sum(value),
+            sdMean = sd(value)) %>%
+  mutate(age = ageForRI)
+
+#   rowname isEnvVar meanMean sumMean sdMean age  
+#   <chr>      <dbl>    <dbl>   <dbl>  <dbl> <chr>
+# 1 rBKT           0   0.0769    30.8 0.0763 yoy  
+# 2 rBKT           1   0.231     69.2 0.209  yoy  
+# 3 rBNT           0   0.165     66.2 0.185  yoy  
+# 4 rBNT           1   0.113     33.8 0.0888 yoy
+
+#   rowname isEnvVar meanMean sumMean sdMean age  
+#   <chr>      <dbl>    <dbl>   <dbl>  <dbl> <chr>
+# 1 rBKT           0   0.0287    11.5 0.0272 adult
+# 2 rBKT           1   0.295     88.5 0.377  adult
+# 3 rBNT           0   0.0411    16.4 0.0285 adult
+# 4 rBNT           1   0.279     83.6 0.343  adult
+
+# ratio of env/(env+spp) means - yoy
+.231/(.231 + .0769) # bkt 0.7502436
+.165/(.165 + .113) # bnt 0.5935252
+
+# ratio of env/(env+spp) means - adult
+.295/(.295 + .0287) # bkt 0.9113377
+.279/(.279 + .0411) # bnt 0.8716026
+
+.75/.593 # 1.26
+.911/.872 # 1.04
+##############################################################
+############################################################
+
+# projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
+load(paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
+
+#spp <- c('bkt','bnt','ats')
+# scenarios
+# Plot subsets of the simulations
+#means for each iter
+stats1 <- rbind(data.frame(grStats3Spp[['bkt']][[1]]), 
+                data.frame(grStats3Spp[['bnt']][[1]]), 
+                data.frame(grStats3Spp[['ats']][[1]])) %>%
+          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[1]])))
+
+#means for each occ
+stats2 <- rbind(data.frame(grStats3Spp[['bkt']][[2]]), 
+                data.frame(grStats3Spp[['bnt']][[2]]), 
+                data.frame(grStats3Spp[['ats']][[2]])) %>%
+          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[2]])))
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
+  geom_point(aes(color = spp) ) +
+  geom_line( aes(color = spp) ) +
+  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0) ) +
+  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0), linetype = 2 )
+
+# trajectories across indep var values for different combinations. Trying to relate to relImp results
+#temp
+p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(temp))) +
+  geom_line(aes(color = factor(temp))) +
+  geom_point(aes(color = factor(temp))) +
+  facet_wrap(~spp)
+
+#flow
+p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
+  geom_line(aes(color = factor(flow))) +
+  geom_point(aes(color = factor(flow))) +
+  facet_wrap(~spp)
+
+#bkt
+p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bkt))) +
+  geom_line(aes(color = factor(bkt))) +
+  geom_point(aes(color = factor(bkt))) +
+  facet_wrap(~spp)
+
+#bnt
+p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
+  geom_line(aes(color = factor(bnt))) +
+  geom_point(aes(color = factor(bnt))) +
+  facet_wrap(~spp)
+
+#ats
+p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(ats))) +
+  geom_line(aes(color = factor(ats))) +
+  geom_point(aes(color = factor(ats))) +
+  facet_wrap(~spp)
+
+multiplot(p1, p2, p3, p4, p5, cols=2) # multiplot function is below
+
+#temp*flow
+ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
+  geom_line(aes(color = factor(flow))) +
+  geom_point(aes(color = factor(flow))) +
+  facet_grid(temp~spp)
+
+#bkt*bnt
+ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
+  geom_line(aes(color = factor(bnt))) +
+  geom_point(aes(color = factor(bnt))) +
+  facet_grid(bkt~spp)
+
+# Multiple plot function
+#
+# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
+# - cols:   Number of columns in layout
+# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
+#
+# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
+# then plot 1 will go in the upper left, 2 will go in the upper right, and
+# 3 will go all the way across the bottom.
+#
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+
+  numPlots = length(plots)
+
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                    ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+
+ if (numPlots==1) {
+    print(plots[[1]])
+
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+
+# size=100
+# gr=10
+# sd=1
+# mean(rnorm(10000,size+gr,sd))
+# mean(size+rnorm(10000,gr,sd))
+
+```
+
+```{r RI by occ - use for paper GROWTH}
+
+# make figures of relative importance for each sampling occasion
+rIAll <- cAll <- NULL
+
+for(ageGroupLoop in 0:1){
+  for(seasonLoop in 1:4){
+#for( occSelected in 1:(simData$nOcc - 1)){
+  if(ageGroupLoop == 0 & seasonLoop == 2) next
+
+  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
+
+  for(spp1 in spp){
+    print(c(ageGroupLoop, seasonLoop, spp1))
+
+    datAgeGroupSeason <- grStats3Spp[[spp1]][[1]] %>%
+         mutate(ageGroup = ifelse(occ %in% 1:3, 0, 1),
+         season = rep(c(3,4,1,2,3,4,1,2,3,4), nrow(grStats3Spp[[spp1]][[1]])/simData$nOcc))
+
+      lmAll[[spp1]] <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = datAgeGroupSeason %>% filter(ageGroup == ageGroupLoop, season == seasonLoop, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals))
+
+      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
+
+      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
+  }
+
+  # make bar chart of relative importance of each variable for each spp
+  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
+              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
+               ageGroup = ageGroupLoop,
+               season = seasonLoop)
+
+  rIAll <- rbind(rIAll,rI)
+
+  #rIAll$age <- ifelse(rIAll$occ %in% 1:2, 0, ifelse(rIAll$occ %in% 3:6, 1, 2))
+
+  }  
+}
+
+######################################################
+# relImp over occasions for each spp and parameter
+labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
+
+# ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
+#   geom_point() +
+#   geom_line() +
+#   geom_vline(xintercept = 2.5) +
+#   scale_x_continuous('Sampling occasion',
+#                     breaks = 1:9,
+#                     labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn')
+#                     ) +
+#   scale_y_continuous('Relative proportion of variance explained') +
+#   theme_publication() +
+#   theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+#   facet_wrap(~ var, labeller=labeller(var = labels))
+# 
+# ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR.png'), width = 11, height = 9, units='in')
+
+rIAllMinus <- rIAll %>% mutate(value2 = ifelse(rowname == 'bktRI',value * -1, value))
+
+labelsSeason <- c('1'='Autumn','2'='Winter','3'='Spring','4'='Summer','5'='Autumn','6'='Winter','7'='Spring','8'='Summer','9'='Autumn')
+labelsSeason2 <- c('1'='Spring','2'='Summer','3'='Autumn','4'='Winter')
+labelAge <- c('0' = 'Growth year 0/1', '1' = 'Growth Year 1+')
+
+ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
+  geom_col() +
+  coord_flip() +
+  scale_x_reverse('Variable', 
+                     breaks = 1:7,
+                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
+  scale_y_continuous('Relative proportion of variance explained',
+                     breaks = c(-1.0, -0.5, 0.0, 0.5),
+                     labels = c('1.0', '0.5', '0.0', '0.5')) +
+  theme_publication() +
+  scale_fill_grey(start = 0.15, end = 0.75) +
+  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))
+
+ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR_HorizBars.png'), width = 11, height = 9, units='in')
+
+#######################
+# coefs
+labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
+
+ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=3) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Coefficients') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
+
+ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
+
+# intercept only
+cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
+ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=4) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 1:10,
+                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Intercept') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
+
+ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
+
+#####################################
+# no need to start sims with diff sizes by species
+yoyMeans <- 
+cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
+  group_by(species) %>%
+  summarize(meanLen = mean(observedLength,na.rm = TRUE),
+           sdLen = sd(observedLength,na.rm = TRUE))
+
+#   species meanLen sdLen
+#   <chr>     <dbl> <dbl>
+# 1 ats        69.0  5.86
+# 2 bkt        72.7  9.94
+# 3 bnt        72.9  8.73
+#####################################
+
+```
+
+```{r RI by occ - not used for paper SIZE}
+
+# make figures of relative importance for each sampling occasion
+rIAll <- cAll <- NULL
+for( occSelected in 2:simData$nOcc){
+  print(occSelected)
+  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
+
+  for(spp1 in spp){
+
+      lmAll[[spp1]] <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected))
+
+      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
+
+      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
+  }
+
+  # make bar chart of relative importance of each variable for each spp
+  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
+              data.frame(bntRI = relImpAll[['bnt']]$lmg), 
+              data.frame(atsRI = relImpAll[['ats']]$lmg)) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  rIAll <- rbind(rIAll,rI)
+
+  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
+    geom_col(position='dodge') +
+    scale_x_discrete('Parameter',
+                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+    scale_fill_grey() +
+    scale_y_continuous('Relative proportion of variance explained') +
+    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
+    theme_publication() +
+    theme( legend.position = 'none')
+
+##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
+
+  # coefficients
+  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
+                 data.frame(bntC = coefsAll[['bnt']]), 
+                 data.frame(atsC = coefsAll[['ats']])) %>%
+        rownames_to_column() %>% 
+        gather(key=rowname) %>% 
+        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
+               occ = occSelected,
+               season = simData$seasons[occSelected])
+
+  cAll <- rbind(cAll,coefs)
+}
+
+######################################################
+# relImp over occasions for each spp and parameter
+labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
+
+# leaving out bkt*bnt, too small
+ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
+  geom_point() +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labels))
+
+ggsave(paste0('figures/3Spp_WB/relImpOccAll.png'), width = 11, height = 9, units='in')
+
+rIMeans <- rIAll %>%
+  group_by(rowname,var) %>%
+  summarize( mean = mean(value),
+             sd = sd(value),
+             stderr = sd(value)/sqrt(length(value))) %>%
+  mutate( up = mean + stderr )
+
+dodge <- position_dodge(width=0.9)
+ggplot(rIMeans %>% filter(rowname %in% c('bktRI','bntRI')), aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = mean-0.01, ymax = up), width = 0.25, position=dodge) +
+  geom_col(position=dodge) +
+  scale_x_discrete('Parameter',
+                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+  scale_fill_grey() +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  theme( legend.position = 'none')
+
+ggsave(paste0('figures/3Spp_WB/relImpOccMean.png'), width = 9, height = 7, units='in')
+
+# mean rel Imp for env vs spp variables
+rIMeans %>%
+  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
+  group_by(rowname,isEnvVar) %>%
+  summarize(meanMean = mean(mean),
+            sumMean = sum(mean),
+            sdMean = sd(mean))
+
+# ratio of env/(env+spp) means
+.247/(.246+.0648) # bkt
+.122/(.122+.159) # bnt
+
+# ratio of env/(env+spp) sums - donT need to do ratio, just use sum for env
+.635/.259 # den-dep bnt/bkt
+.741/.365 # env bkt/bnt
+
+#######################
+# coefs
+labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
+
+ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=3) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 2:10,
+                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Coefficients') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
+  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
+
+ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
+
+# intercept only
+cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
+ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
+  geom_point(size=4) +
+  geom_line() +
+  geom_vline(xintercept = 3.5) +
+  scale_x_continuous('Sampling occasion',
+                    breaks = 1:10,
+                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
+                    ) +
+  scale_y_continuous('Intercept') +
+  theme_publication() +
+  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
+
+ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
+
+#####################################
+# no need to start sims with diff sizes by species
+yoyMeans <- 
+cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
+  group_by(species) %>%
+  summarize(meanLen = mean(observedLength,na.rm = TRUE),
+           sdLen = sd(observedLength,na.rm = TRUE))
+
+#   species meanLen sdLen
+#   <chr>     <dbl> <dbl>
+# 1 ats        69.0  5.86
+# 2 bkt        72.7  9.94
+# 3 bnt        72.9  8.73
+#####################################
+
+```
+
+```{r tables}
+
+round(mcmc$summary$all.chains[startsWith(attributes(mcmc$summary$all.chains)$dimnames[[1]], "grBeta["),],2)
+
+```
+
+```{r RI across occ - use this for paper SIZE}
+
+# relative proportion stats with occ in the lm 
+stats3Spp[['bkt']][[1]]$season <- as.factor(c(3,4,1,2,3,4,1,2,3,4))
+stats3Spp[['bkt']][[1]]$temp2 <- stats3Spp[['bkt']][[1]]$temp^2
+stats3Spp[['bkt']][[1]]$flow2 <- stats3Spp[['bkt']][[1]]$flow^2
+
+ageForRI <-  'adult' #'yoy' or 'adult'
+occs <- if (ageForRI == 'yoy') 1:3 else 4:10
+indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
+rIBKTBNT <- NULL
+# loop over occs
+for(rep in 1:simData$nReps){
+
+  print(rep)
+
+  datOccBKT <- stats3Spp[['bkt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBKT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKT) 
+  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)
+
+  datOccBNT <- stats3Spp[['bnt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
+  lmAllBNT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNT)
+  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)
+
+  rBKT <- relImpAllBKT$lmg[2:8] / sum(relImpAllBKT$lmg[2:8]) 
+  rBNT <- relImpAllBNT$lmg[2:8] / sum(relImpAllBNT$lmg[2:8])
+
+  rIBKTBNT <- rbind(rIBKTBNT, data.frame(cbind(rBKT,rBNT)) %>% 
+                      rownames_to_column() %>% 
+                      gather(key = rowname) %>% 
+                      mutate(var = rep(1:7,2),
+                             varText = rep(names(rBKT),2),
+                             iter = rep)
+                    )
+
+}
+
+rIBKTBNTMeans <- rIBKTBNT %>%
+  group_by(rowname, var) %>%
+  summarise(rIMean = mean(value),
+            rISd = sd(value),
+            rIUpperCI = quantile(value, 0.95))
+
+dodge <- position_dodge(width=0.9)
+ggplot(rIBKTBNTMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
+  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
+  geom_col(position=dodge) +
+  scale_x_discrete('Parameter',
+                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
+  scale_fill_grey() +
+  scale_y_continuous('Relative proportion of variance explained') +
+  theme_publication() +
+  geom_hline(yintercept = 0) +
+  theme( legend.position = 'none')
+
+ggsave(paste0('figures/3Spp_WB/relImpOccMeanModWOcc_Size',simData$nReps,'_',ageForRI,'.png'), width = 9, height = 7, units='in')
 
@@
 
-#spp <- c('bkt','bnt','ats')
+spp <- c('bkt','bnt','ats')
 # scenarios
@@
 #means for each iter
-stats1 <- rbind(data.frame(grStats3Spp[['bkt']][[1]]), 
-                data.frame(grStats3Spp[['bnt']][[1]]), 
-                data.frame(grStats3Spp[['ats']][[1]])) %>%
-          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[1]])))
+stats1 <- rbind(data.frame(stats3Spp[['bkt']][[1]]), 
+                data.frame(stats3Spp[['bnt']][[1]]), 
+                data.frame(stats3Spp[['ats']][[1]])) %>%
+          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[1]])))
 
 #means for each occ
-stats2 <- rbind(data.frame(grStats3Spp[['bkt']][[2]]), 
-                data.frame(grStats3Spp[['bnt']][[2]]), 
-                data.frame(grStats3Spp[['ats']][[2]])) %>%
-          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[2]])))
-
-ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
+stats2 <- rbind(data.frame(stats3Spp[['bkt']][[2]]), 
+                data.frame(stats3Spp[['bnt']][[2]]), 
+                data.frame(stats3Spp[['ats']][[2]])) %>%
+          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[2]])))
+
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
   geom_point(aes(color = spp) ) +
@@
 
-ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
+ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
   geom_point(aes(color = spp) ) +
@@
 #temp
-p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(temp))) +
+p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(temp))) +
   geom_line(aes(color = factor(temp))) +
@@
 #flow
-p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
+p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
   geom_line(aes(color = factor(flow))) +
@@
 #bkt
-p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bkt))) +
+p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bkt))) +
   geom_line(aes(color = factor(bkt))) +
@@
 #bnt
-p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
+p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
   geom_line(aes(color = factor(bnt))) +
@@
 #ats
-p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(ats))) +
+p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(ats))) +
   geom_line(aes(color = factor(ats))) +
@@
 #temp*flow
-ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
+ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
   geom_line(aes(color = factor(flow))) +
@@
 #bkt*bnt
-ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
+ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
   geom_line(aes(color = factor(bnt))) +
@@
 
-```{r RI by occ - not used for paper GROWTH}
-
-# make figures of relative importance for each sampling occasion
-rIAll <- cAll <- NULL
-for( occSelected in 1:(simData$nOcc - 1)){
-  print(occSelected)
-  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
-
-  for(spp1 in spp){
-
-      lmAll[[spp1]] <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = grStats3Spp[[spp1]][[1]] %>% filter(occ == occSelected, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals))
-  #stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected)
-
-      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
-
-      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
-  }
-
-  # make bar chart of relative importance of each variable for each spp
-  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
-              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
-        rownames_to_column() %>% 
-        gather(key=rowname) %>% 
-        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
-               occ = occSelected,
-               season = simData$seasons[occSelected])
-
-  rIAll <- rbind(rIAll,rI)
-
-  rIAll$age <- ifelse(rIAll$occ %in% 1:2, 0, ifelse(rIAll$occ %in% 3:6, 1, 2))
-
-  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI'), ordered = TRUE))) +
-    geom_col(position='dodge') +
-    scale_x_discrete('Parameter',
-                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
-    scale_fill_grey() +
-    scale_y_continuous('Relative proportion of variance explained') +
-    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
-    theme_publication() +
-    theme( legend.position = 'none')
-
-##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
-
-  # coefficients
-  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
-                 data.frame(bntC = coefsAll[['bnt']])) %>%
-        rownames_to_column() %>% 
-        gather(key=rowname) %>% 
-        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
-               occ = occSelected,
-               season = simData$seasons[occSelected])
-
-  cAll <- rbind(cAll,coefs)
-}
-
-######################################################
-# relImp over occasions for each spp and parameter
-labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
-
-ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = 2.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 1:9,
-                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn')
-                    ) +
-  scale_y_continuous('Relative proportion of variance explained') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
-  facet_wrap(~ var, labeller=labeller(var = labels))
-
-ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR.png'), width = 11, height = 9, units='in')
-
-rIAllMinus <- rIAll %>% mutate(value2 = ifelse(rowname == 'bktRI',value * -1, value))
-labelsSeason <- c('1'='Autumn','2'='Winter','3'='Spring','4'='Summer','5'='Autumn','6'='Winter','7'='Spring','8'='Summer','9'='Autumn')
-labelsSeason2 <- c('1'='Spring','2'='Summer','3'='Autumn','4'='Winter')
-
-ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
-  geom_col() +
-  coord_flip() +
-  scale_x_reverse('Variable', 
-                     breaks = 1:7,
-                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
-  scale_y_continuous('Relative proportion of variance explained',
-                     breaks = c(-1.0, -0.5, 0.0, 0.5),
-                     labels = c('1.0', '0.5', '0.0', '0.5')) +
-  theme_publication() +
-  scale_fill_grey(start = 0.15, end = 0.75) +
-  facet_grid(season ~ age, labeller=labeller(season = labelsSeason2))
-
-ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR_HorizBars.png'), width = 11, height = 9, units='in')
-
-#######################
-# coefs
-labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
-
-ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
-  geom_point(size=3) +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 2:10,
-                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Coefficients') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
-  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
-
-ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
-
-# intercept only
-cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
-ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
-  geom_point(size=4) +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 1:10,
-                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Intercept') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
-
-ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
-
-#####################################
-# no need to start sims with diff sizes by species
-yoyMeans <- 
-cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
-  group_by(species) %>%
-  summarize(meanLen = mean(observedLength,na.rm = TRUE),
-           sdLen = sd(observedLength,na.rm = TRUE))
-
-#   species meanLen sdLen
-#   <chr>     <dbl> <dbl>
-# 1 ats        69.0  5.86
-# 2 bkt        72.7  9.94
-# 3 bnt        72.9  8.73
-#####################################
-
-```
-
-```{r RI by occ - not used for paper SIZE}
-
-# make figures of relative importance for each sampling occasion
-rIAll <- cAll <- NULL
-for( occSelected in 2:simData$nOcc){
-  print(occSelected)
-  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()
-
-  for(spp1 in spp){
-
-      lmAll[[spp1]] <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected))
-
-      relImpAll[[spp1]] <- calc.relimp(lmAll[[spp1]], type = c("lmg"), rela = TRUE)
-
-      coefsAll[[spp1]] <- lmAll[[spp1]]$coefficients
-  }
-
-  # make bar chart of relative importance of each variable for each spp
-  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
-              data.frame(bntRI = relImpAll[['bnt']]$lmg), 
-              data.frame(atsRI = relImpAll[['ats']]$lmg)) %>%
-        rownames_to_column() %>% 
-        gather(key=rowname) %>% 
-        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
-               occ = occSelected,
-               season = simData$seasons[occSelected])
-
-  rIAll <- rbind(rIAll,rI)
-
-  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
-    geom_col(position='dodge') +
-    scale_x_discrete('Parameter',
-                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
-    scale_fill_grey() +
-    scale_y_continuous('Relative proportion of variance explained') +
-    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
-    theme_publication() +
-    theme( legend.position = 'none')
-
-##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')
-
-  # coefficients
-  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
-                 data.frame(bntC = coefsAll[['bnt']]), 
-                 data.frame(atsC = coefsAll[['ats']])) %>%
-        rownames_to_column() %>% 
-        gather(key=rowname) %>% 
-        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
-               occ = occSelected,
-               season = simData$seasons[occSelected])
-
-  cAll <- rbind(cAll,coefs)
-}
-
-######################################################
-# relImp over occasions for each spp and parameter
-labels <- c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")
-
-# leaving out bkt*bnt, too small
-ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 2:10,
-                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Relative proportion of variance explained') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
-  facet_wrap(~ var, labeller=labeller(var = labels))
-
-ggsave(paste0('figures/3Spp_WB/relImpOccAll.png'), width = 11, height = 9, units='in')
-
-rIMeans <- rIAll %>%
-  group_by(rowname,var) %>%
-  summarize( mean = mean(value),
-             sd = sd(value),
-             stderr = sd(value)/sqrt(length(value))) %>%
-  mutate( up = mean + stderr )
-
-dodge <- position_dodge(width=0.9)
-ggplot(rIMeans %>% filter(rowname %in% c('bktRI','bntRI')), aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
-  geom_errorbar(aes(ymin = mean-0.01, ymax = up), width = 0.25, position=dodge) +
-  geom_col(position=dodge) +
-  scale_x_discrete('Parameter',
-                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
-  scale_fill_grey() +
-  scale_y_continuous('Relative proportion of variance explained') +
-  theme_publication() +
-  theme( legend.position = 'none')
-
-ggsave(paste0('figures/3Spp_WB/relImpOccMean.png'), width = 9, height = 7, units='in')
-
-# mean rel Imp for env vs spp variables
-rIMeans %>%
-  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
-  group_by(rowname,isEnvVar) %>%
-  summarize(meanMean = mean(mean),
-            sumMean = sum(mean),
-            sdMean = sd(mean))
-
-# ratio of env/(env+spp) means
-.247/(.246+.0648) # bkt
-.122/(.122+.159) # bnt
-
-# ratio of env/(env+spp) sums - donT need to do ratio, just use sum for env
-.635/.259 # den-dep bnt/bkt
-.741/.365 # env bkt/bnt
-
-#######################
-# coefs
-labelsC <- c('1' = 'intercept', '2' = 'Temp','3' = 'Flow','4' = 'Bkt','5' = 'Bnt','6' = 'Ats','7' = 'Temp*Flow', '8' = "Bkt*Bnt")
-
-ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
-  geom_point(size=3) +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 2:10,
-                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Coefficients') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
-  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')
-
-ggsave(paste0('figures/3Spp_WB/coefsOccAll.png'), width = 11, height = 9, units='in')
-
-# intercept only
-cAll2 <- rbind(cAll,data.frame(rowname=c('bktC','bntC','atsC'),value=simData$meanInit,var=1,occ=1,season=3))
-ggplot(cAll2 %>% filter(var == 1), aes((occ), value, color = factor(rowname))) +
-  geom_point(size=4) +
-  geom_line() +
-  geom_vline(xintercept = 3.5) +
-  scale_x_continuous('Sampling occasion',
-                    breaks = 1:10,
-                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
-                    ) +
-  scale_y_continuous('Intercept') +
-  theme_publication() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10))
-
-ggsave(paste0('figures/3Spp_WB/coefsInterceptOccAll.png'), width = 11, height = 9, units='in')
-
-#####################################
-# no need to start sims with diff sizes by species
-yoyMeans <- 
-cd %>% filter( riverOrdered == 'west brook', ageInSamples == 1 ) %>%
-  group_by(species) %>%
-  summarize(meanLen = mean(observedLength,na.rm = TRUE),
-           sdLen = sd(observedLength,na.rm = TRUE))
-
-#   species meanLen sdLen
-#   <chr>     <dbl> <dbl>
-# 1 ats        69.0  5.86
-# 2 bkt        72.7  9.94
-# 3 bnt        72.9  8.73
-#####################################
-
-```
-
-```{r tables}
-
-round(mcmc$summary$all.chains[startsWith(attributes(mcmc$summary$all.chains)$dimnames[[1]], "grBeta["),],2)
-
-```
-
-```{r RI across occ - use this for paper SIZE}
-
-# relative proportion stats with occ in the lm 
-stats3Spp[['bkt']][[1]]$season <- as.factor(c(3,4,1,2,3,4,1,2,3,4))
-stats3Spp[['bkt']][[1]]$temp2 <- stats3Spp[['bkt']][[1]]$temp^2
-stats3Spp[['bkt']][[1]]$flow2 <- stats3Spp[['bkt']][[1]]$flow^2
-
-ageForRI <-  'adult' #'yoy' or 'adult'
-occs <- if (ageForRI == 'yoy') 1:3 else 4:10
-indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
-rIBKTBNT <- NULL
-# loop over occs
-for(rep in 1:simData$nReps){
-
-  print(rep)
-
-  datOccBKT <- stats3Spp[['bkt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
-  lmAllBKT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKT) 
-  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)
-
-  datOccBNT <- stats3Spp[['bnt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
-  lmAllBNT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNT)
-  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)
-
-  rBKT <- relImpAllBKT$lmg[2:8] / sum(relImpAllBKT$lmg[2:8]) 
-  rBNT <- relImpAllBNT$lmg[2:8] / sum(relImpAllBNT$lmg[2:8])
-
-  rIBKTBNT <- rbind(rIBKTBNT, data.frame(cbind(rBKT,rBNT)) %>% 
-                      rownames_to_column() %>% 
-                      gather(key = rowname) %>% 
-                      mutate(var = rep(1:7,2),
-                             varText = rep(names(rBKT),2),
-                             iter = rep)
-                    )
-
-}
-
-rIBKTBNTMeans <- rIBKTBNT %>%
-  group_by(rowname, var) %>%
-  summarise(rIMean = mean(value),
-            rISd = sd(value),
-            rIUpperCI = quantile(value, 0.95))
-
-dodge <- position_dodge(width=0.9)
-ggplot(rIBKTBNTMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
-  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
-  geom_col(position=dodge) +
-  scale_x_discrete('Parameter',
-                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
-  scale_fill_grey() +
-  scale_y_continuous('Relative proportion of variance explained') +
-  theme_publication() +
-  geom_hline(yintercept = 0) +
-  theme( legend.position = 'none')
-
-ggsave(paste0('figures/3Spp_WB/relImpOccMeanModWOcc_Size',simData$nReps,'_',ageForRI,'.png'), width = 9, height = 7, units='in')
-
-# uses 42 G - does not run
-#lmAll <- lm( lenMean ~ (temp + flow +  temp^2 + flow^2 + bkt + bnt + ats )*occ + temp * flow + bnt * bkt, data = stats3Spp[['bkt']][[1]] %>%               filter(iter %in% 1) )
-
-rIBKTBNT %>%
-  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
-  group_by(rowname,isEnvVar) %>%
-  summarize(meanMean = mean(value),
-            sumMean = sum(value),
-            sdMean = sd(value))
-# 25 reps
-#   rowname isEnvVar meanMean sumMean sdMean
-#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
-# 1 rBKT           0   0.0664   0.265  0.105
-# 2 rBKT           1   0.245    0.735  0.249
-# 3 rBNT           0   0.147    0.588  0.104
-# 4 rBNT           1   0.137    0.412  0.158
-
-# 100 reps
-#   rowname isEnvVar meanMean sumMean sdMean
-#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
-# 1 rBKT           0   0.0676    27.0 0.0914
-# 2 rBKT           1   0.243     73.0 0.200 
-# 3 rBNT           0   0.146     58.2 0.0922
-# 4 rBNT           1   0.139     41.8 0.131
-
-# ratio of env/(env+spp) means
-.243/(.243 + .0676) # bkt 0.7823567
-.139/(.139 + .146) # bnt 0.4877193
-
-.782/.488 # 1.60
-##############################################################
-############################################################
-
-# projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
-load(paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
-
-spp <- c('bkt','bnt','ats')
-# scenarios
-# Plot subsets of the simulations
-#means for each iter
-stats1 <- rbind(data.frame(stats3Spp[['bkt']][[1]]), 
-                data.frame(stats3Spp[['bnt']][[1]]), 
-                data.frame(stats3Spp[['ats']][[1]])) %>%
-          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[1]])))
-
-#means for each occ
-stats2 <- rbind(data.frame(stats3Spp[['bkt']][[2]]), 
-                data.frame(stats3Spp[['bnt']][[2]]), 
-                data.frame(stats3Spp[['ats']][[2]])) %>%
-          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[2]])))
-
-ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
-  geom_point(aes(color = spp) ) +
-  geom_line( aes(color = spp) ) +
-  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0) ) +
-  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
-
-ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
-  geom_point(aes(color = spp) ) +
-  geom_line( aes(color = spp) ) +
-  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0) ) +
-  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0), linetype = 2 )
-
-ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,lenMeanMean, group = spp)) +
-  geom_point(aes(color = spp) ) +
-  geom_line( aes(color = spp) ) +
-  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0) ) +
-  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0), linetype = 2 )
-
-# trajectories across indep var values for different combinations. Trying to relate to relImp results
-#temp
-p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(temp))) +
-  geom_line(aes(color = factor(temp))) +
-  geom_point(aes(color = factor(temp))) +
-  facet_wrap(~spp)
-
-#flow
-p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
-  geom_line(aes(color = factor(flow))) +
-  geom_point(aes(color = factor(flow))) +
-  facet_wrap(~spp)
-
-#bkt
-p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bkt))) +
-  geom_line(aes(color = factor(bkt))) +
-  geom_point(aes(color = factor(bkt))) +
-  facet_wrap(~spp)
-
-#bnt
-p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
-  geom_line(aes(color = factor(bnt))) +
-  geom_point(aes(color = factor(bnt))) +
-  facet_wrap(~spp)
-
-#ats
-p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(ats))) +
-  geom_line(aes(color = factor(ats))) +
-  geom_point(aes(color = factor(ats))) +
-  facet_wrap(~spp)
-
-multiplot(p1, p2, p3, p4, p5, cols=2) # multiplot function is below
-
-#temp*flow
-ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
-  geom_line(aes(color = factor(flow))) +
-  geom_point(aes(color = factor(flow))) +
-  facet_grid(temp~spp)
-
-#bkt*bnt
-ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
-  geom_line(aes(color = factor(bnt))) +
-  geom_point(aes(color = factor(bnt))) +
-  facet_grid(bkt~spp)
-
-# Multiple plot function
-#
-# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
-# - cols:   Number of columns in layout
-# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
-#
-# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
-# then plot 1 will go in the upper left, 2 will go in the upper right, and
-# 3 will go all the way across the bottom.
-#
-multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
-  library(grid)
-
-  # Make a list from the ... arguments and plotlist
-  plots <- c(list(...), plotlist)
-
-  numPlots = length(plots)
-
-  # If layout is NULL, then use 'cols' to determine layout
-  if (is.null(layout)) {
-    # Make the panel
-    # ncol: Number of columns of plots
-    # nrow: Number of rows needed, calculated from # of cols
-    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
-                    ncol = cols, nrow = ceiling(numPlots/cols))
-  }
-
- if (numPlots==1) {
-    print(plots[[1]])
-
-  } else {
-    # Set up the page
-    grid.newpage()
-    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
-
-    # Make each plot, in the correct location
-    for (i in 1:numPlots) {
-      # Get the i,j matrix positions of the regions that contain this subplot
-      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
-
-      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
-                                      layout.pos.col = matchidx$col))
-    }
-  }
-}
-
-# size=100
-# gr=10
-# sd=1
-# mean(rnorm(10000,size+gr,sd))
-# mean(size+rnorm(10000,gr,sd))
-
-```
-
 ```{r overview graphs - Fig Appendix}

### 2018-12-14 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added relImpOccAll_GR_HorizBarsColor graph

@@
                ageGroup = ageGroupLoop,
-               season = seasonLoop)
+               season = seasonLoop
+               )
+  rI$varText <- rep(names(relImpAll[['bkt']]$lmg),2)
 
@@
 
+### get prop env
+summ1 <- rIAll %>%
+  mutate(isEnvVar = ifelse(varText %in% c('temp','flow','temp:flow'), 1,0)) %>%
+  group_by(rowname,isEnvVar,ageGroup, season) %>%
+  summarize(mean=mean(value)) %>%
+  arrange(ageGroup,season,rowname,isEnvVar)
+
+summ2 <- summ1 %>%
+  group_by(rowname,ageGroup,season) %>%
+  summarize(sum=sum(mean))
+
+summ1a <- left_join(summ1,summ2) %>%
+  mutate(prop = mean/sum,
+         xAxisLoc = ifelse(rowname == 'bktRI',-0.85, 0.85)) %>%
+  filter(isEnvVar == 1) 
+###
+
+####
+# add in betas to rIAllMinus
+load("D:/projects/linkedModels/data/out/allBetas.RData") #loads df 'q'
+qFig1 <- q %>% filter(riverGG == 'WB', species %in% c('bkt','bnt'))
+qFig1$season <- as.numeric(as.character(qFig1$season))
+qFig1$isYOY <- as.numeric(as.character(qFig1$isYOY))
+qFig <- qFig1 %>%
+  mutate( varText = tolower(betaGG)) %>%
+  mutate( varText = ifelse(varText == 'temp*flow','temp:flow', varText)) %>%
+  mutate( varText = ifelse(varText == 'bnt*bkt','bkt:bnt', varText)) %>%
+  select(isYOY,season,species,median,varText)
+
+# prepare rIAllMinus
+rIAllMinusQ <- rIAllMinus %>%
+  mutate(species = str_sub(rowname,1,3),
+         isYOY = ageGroup) %>%
+  left_join(qFig) %>%
+  mutate(median01 = ifelse(median > 0, 1, 0),
+         medianBreaks = cut(median, breaks = c(-1, -0.025, 0 , 0.025, 1)))
+
+#
+
 ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
@@
                      labels = c('1.0', '0.5', '0.0', '0.5')) +
+  geom_text(data = summ1a, aes(y=xAxisLoc, x=7, label=paste(round(prop,2)), color=rowname),size = 5) +
+  scale_color_grey(start = 0.15, end = 0.75) +
   theme_publication() +
@@
 ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR_HorizBars.png'), width = 11, height = 9, units='in')
+
+ggplot(rIAllMinusQ, aes(var, y = value2)) +
+  geom_col(aes(fill = median)) +
+  coord_flip() +
+  scale_x_reverse('Variable', 
+                     breaks = 1:7,
+                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
+  scale_y_continuous('Relative proportion of variance explained',
+                     breaks = c(-0.9, -0.25, -0.5, 0.0, 0.25, 0.5, 0.9),
+                     labels = c('0.9', '0.25', '0.5\n\nBrook Trout\n', '0.0', '0.25', '0.5\n\nBrown Trout\n', '0.9')) +
+  geom_text(data = summ1a, aes(y=xAxisLoc, x=7, label=paste(round(prop,2))),size = 5) +
+  geom_hline(yintercept = 0) +
+  #scale_color_grey(start = 0.15, end = 0.75) +
+  theme_publication() +
+ #  scale_fill_continuous() +
+  scale_fill_distiller(name="Parameter\nestimate", palette = "RdBu", direction = 1) +
+  theme(legend.position="right",             
+        #legend.key = element_rect(colour = NA),
+        legend.direction = "vertical",
+        legend.key.size= unit(0.25, "in"),
+        #    legend.margin = unit(0, "cm"),
+        legend.title = element_text(face="plain")#element_blank()
+        ) +
+  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))
+
+ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR_HorizBarsColor.png'), width = 11, height = 9, units='in')
 

### 2019-01-30 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added section to pull out data for Carys Jones

@@
 save(tempSlopesTidy,file = 'D:/projects/linkedModels/data/out/tempSlopesTidy.RData')
-
+```
+
+```{r Carys Jones analysis}
+######
+# for Carys Jones analysis
+dJonesT <- 
+  d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
+    summarize(meanT = mean(meanTemperature, na.rm=T),
+              sdT = sd(meanTemperature, na.rm=T)) %>%
+    filter(riverOrderedGG == "West Brook", seasonGG == "Summer") %>%
+    ungroup() %>%
+    select(year,meanLen,sdLen)
+
+#####
+# Lengths
+# run 'r mean lengths' chunk above
+
+dJonesL <- 
+  means %>%
+    filter(season == 3, age == 1) %>%
+    ungroup() %>%
+    select(species,year,meanLen,sdLen)
+
+######
+# abundance
+# run 'r adjusted counts' above
+
+dJonesA <- 
+  allFishBySpeciesYOY %>% 
+    filter(riverOrderedGG == "West Brook", year >=2000, season == 3, isYOY == 2) %>%
+    ungroup() %>%
+    select(species,year,nAllFishBySpecies)
+
+######
+# phi
+# run 'r p(detection)' below
+# only has summer survival, may want annual survival
+
+dJonesP <- phi %>%
+  filter(season == 2, isYOYGG == 'Adult') %>%
+  select(speciesGG,yearGG,phi) %>%
+  rename(species = speciesGG, year = yearGG) %>%
+  mutate(species = as.character(species))
+
+dJonesAL <- left_join(dJonesA,dJonesL) 
+dJonesALT <-  left_join(dJonesAL,dJonesT)
+dJonesALTP <-  left_join(dJonesALT,dJonesP)
+
+##
+write.csv(dJonesALTP, file = 'D:/projects/linkedModels/dataForCarysJones/dJonesALTP.csv')
 ```
@@
   p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
-    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1)
+    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1, year > 3)
 
@@
   p$isYOYGG <- factor(p$isYOY, levels = 1:2, labels = c("Juvenile","Adult"), ordered = T)
-
-  ggplot(p, aes(year,invlogit(est),color=factor(speciesGG))) + 
+  p$yearGG <- p$year + 1996
+
+  ggplot(p, aes(yearGG,invlogit(est),color=factor(speciesGG))) + 
     geom_point(size = 2) + 
@@
   phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
-    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1) 
-  ggplot(phi, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid( season ~ isYOY)
+    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1, year > 3)
+
+  phi$speciesGG <- factor(phi$species, levels = 1:3, labels = c("bkt", "bnt", "ats"), ordered = T)
+  phi$seasonGG <- factor(phi$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
+  phi$isYOYGG <- factor(phi$isYOY, levels = 1:2, labels = c("Juvenile","Adult"), ordered = T)
+  phi$yearGG <- phi$year + 1996
+  phi$phi <- invlogit(phi$est)
+
+  ggplot(phi, aes(yearGG,phi,color=factor(speciesGG))) +geom_point() + facet_grid(seasonGG ~ isYOYGG)
 
@@
   arrange(species,isYOY,seasonGG) %>%
-  select(species,isYOY,seasonGG,intDown,int,intUp) %>%
-  mutate(lo = round(intDown,3),mean = round(int,3),hi = round(intUp,3))
-
-write.csv(intsForTable,file = 'D:/projects/linkedModels/data/out/intsForTable.csv')
+  mutate(lo = round(intDown,3),mean = round(int,3),hi = round(intUp,3)) %>%
+  select(species,isYOY,seasonGG,intDown,int,intUp)
+
+write.csv(intsForTable,file = 'D:/projects/linkedModels/data/out/intsForTableAgeGroup.csv')
 ```
@@
   arrange(species,betaGG,isYOY,seasonGG,betaGG) %>%
-  select(species,betaGG,isYOY,seasonGG,betaGG,lo,median,hi) %>%
-  mutate(lo = round(lo,3),median = round(median,3),hi = round(hi,3))
-
-write.csv(betasForTable,file = 'D:/projects/linkedModels/data/out/betasForTable.csv')
+  mutate(lo = round(lo,3),median = round(median,3),hi = round(hi,3)) %>%
+  select(species,betaGG,isYOY,seasonGG,betaGG,lo,median,hi)
+
+write.csv(betasForTable,file = 'D:/projects/linkedModels/data/out/betasForTableAgeGroup.csv')
 ```
@@
 
+# bars colered by beta
 ggplot(rIAllMinusQ, aes(var, y = value2)) +
